### 2024-11-25 paper/main.tex
Added skeleton paper, as it currently appears on Overleaf

%% Beginning of file 'sample631.tex'
%%
%% Modified 2022 May  
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.31 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls and other external packages such as
%% latexsym, graphicx, amssymb, longtable, and epsf.  Note that as of 
%% Oct 2020, APS now uses revtex4.2e for its journals but remember that 
%% AASTeX v6+ still uses v4.1. All of these external packages should 
%% already be present in the modern TeX distributions but not always.
%% For example, revtex4.1 seems to be missing in the linux version of
%% TexLive 2020. One should be able to get all packages from www.ctan.org.
%% In particular, revtex v4.1 can be found at 
%% https://www.ctan.org/pkg/revtex4-1.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%% using aastex version 6.3
\documentclass[preprint2,linenumbers]{aastex631}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be invoked like this:
%%
%% \documentclass[arguments]{aastex631}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
%%                but now that abstracts are required this is obsolete for
%%                AAS Journals. Authors might need it for other reasons. DO NOT
%%                use \begin{abstract} and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%   tighten      : Makes baselineskip slightly smaller, only works with 
%%                  the twocolumn substyle.
%%   times        : uses times font instead of the default
%%   linenumbers  : turn on lineno package.
%%   trackchanges : required to see the revision mark up and print its output
%%   longauthor   : Do not use the more compressed footnote style (default) for 
%%                  the author/collaboration/affiliations. Instead print all
%%                  affiliation information after each name. Creates a much 
%%                  longer author list but may be desirable for short 
%%                  author papers.
%% twocolappendix : make 2 column appendix.
%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
%%                  for dual anonymous review.
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
%% to improve the accessibility of the compiled pdf file.
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\todo}[1]{{\color{red}#1}}
\newcommand{\src}{J1755$-$2527}
\newcommand{\srcfull}{ASKAP J175534.9$-$252749.1}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{March 1, 2021}
%\revised{April 1, 2021}
%\accepted{\today}

%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the argument.
%\submitjournal{PSJ}

%% For manuscript that include authors in collaborations, AASTeX v6.31
%% builds on the \collaboration command to allow greater freedom to 
%% keep the traditional author+affiliation information but only show
%% subsets. The \collaboration command now must appear AFTER the group
%% of authors in the collaboration and it takes TWO arguments. The last
%% is still the collaboration identifier. The text given in this
%% argument is what will be shown in the manuscript. The first argument
%% is the number of author above the \collaboration command to show with
%% the collaboration text. If there are authors that are not part of any
%% collaboration the \nocollaboration command is used. This command takes
%% one argument which is also the number of authors above to show. A
%% dashed line is shown to indicate no collaboration. This example manuscript
%% shows how these commands work to display specific set of authors 
%% on the front page.
%%
%% For manuscript without any need to use \collaboration the 
%% \AuthorCollaborationLimit command from v6.2 can still be used to 
%% show a subset of authors.
%
%\AuthorCollaborationLimit=2
%
%% will only show Schwarz & Muench on the front page of the manuscript
%% (assuming the \collaboration and \nocollaboration commands are
%% commented out).
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%\shorttitle{AASTeX v6.3.1 Sample article}
%\shortauthors{Schwarz et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
%% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%% \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\graphicspath{{./}{figures/}}
%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{Confirmation of \srcfull{} as a long period radio transient}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire. In v6.31 you can include a footnote in the title.

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affiliations. The change was necessary to implement 
%% auto-indexing of affiliations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% The \author command is the same as before except it now takes an optional
%% argument which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid. If the "orcid-ID.png" image file is 
%% present or in the LaTeX pathway, the OrcID icon will appear next to
%% the authors name.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.31 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.31 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

%\correspondingauthor{August Muench}
%\email{greg.schwarz@aas.org, gus.muench@aas.org}

\author[0000-0001-6114-7469]{Samuel J. McSweeney}
\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}

\author[0000-0002-5119-4808]{Natasha Hurley-Walker}
\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}

\author{Dougal Dobie}
\affiliation{Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia}
\affiliation{ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav), Hawthorn, VIC 3122, Australia}

\author{Ziteng Wang}
\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}

%\collaboration{20}{(AAS Journals Data Editors)}

% Example with "altaffiliation"
%\author{Amy Hendrickson}
%\altaffiliation{AASTeX v6+ programmer}
%\affiliation{TeXnology Inc.}

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.31 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}

[Abstract goes here\dots]

\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% The AAS Journals now uses Unified Astronomy Thesaurus concepts:
%% https://astrothesaurus.org
%% You will be asked to selected these concepts during the submission process
%% but this old "keyword" functionality is maintained in case authors want
%% to include these concepts in their preprints.
%\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of astronomy(1868) --- Interdisciplinary astronomy(804)}

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.
%%
%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

\section{Introduction} \label{sec:intro}

\srcfull{} (hereafter, \src{}) is a transient radio source discovered in the Variables and Slow Transients (VAST) survey \citep{2024MNRAS.535..909D}.
A single, highly polarized pulse was observed, lasting approximately 2 minutes, exhibiting a steep spectrum ($\alpha = -3.1$).
Extensive follow up in new and archival data at multiple wavelengths turned up no other pulses.
Despite this, the authors concluded that \src{} was most likely a long period transient (LPT), a newly emerging class of radio source with periods ranging from minutes to hours (see Table \ref{tbl:lpts} for an up-to-date list).

\begin{deluxetable*}{lcl}
\tablecaption{Known LPTs, arranged in ascending order of period\label{tbl:lpts}}
\tablehead{
\colhead{LPT} & \colhead{Period} & \colhead{References} \\ 
 & \colhead{(min)} & 
} 
\startdata
%AR Scorpii (J162147.28-225310.3) & 1.97 &  \\
%ASKAP J175154.89-255135.3 & ${\sim}$3.6 &  \\
%J1912-4410 & 5.3 &  \\
CHIME J0630+25             & 7.02 & \citet{2024arXiv240707480D} \\
GLEAM-X J162759.5-523504.3 & 18.2 & \citet{2022Natur.601..526H} \\
GPM J1839-10               & 22.0 & \citet{2023Natur.619..487H} \\
ASKAP J1832-0911           & 44.3 & \todo{Wang} \\
ASKAP J193505.1+214841.0   & 53.8 & \citet{2024NatAs...8.1159C} \\
ASKAP J175534.9-252749.1   & 69.8 & \citet{2024MNRAS.535..909D} \\
GCRT J1745-3009            & 77.0 & \citet{2005Natur.434...50H} \\
ILT J1101+5521             & 126  & \citet{2024arXiv240811536D} \\
GLEAM-X J0704-37           & 175  & \citet{2024arXiv240815757H} \\
ASKAP J1839-0756           & 387  & \todo{Lee} \\
\enddata
%\tablecomments{This is a sample table. Add more rows as needed, and include notes in this area.}
\end{deluxetable*}

\begin{acknowledgments}

[Acknowledgements go here\dots]

\end{acknowledgments}

%% To help institutions obtain information on the effectiveness of their 
%% telescopes the AAS Journals has created a group of keywords for telescope 
%% facilities.
%
%% Following the acknowledgments section, use the following syntax and the
%% \facility{} or \facilities{} macros to list the keywords of facilities used 
%% in the research for the paper.  Each keyword is check against the master 
%% list during copy editing.  Individual instruments can be provided in 
%% parentheses, after the keyword, but they are not verified.

%\vspace{5mm}
%\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
%CTIO:1.5m,CXO}

%% Similar to \facility{}, there is the optional \software command to allow 
%% authors a place to specify which programs were used during the creation of 
%% the manuscript. Authors should list each code and include either a
%% citation or url to the code inside ()s when available.

%\software{astropy \citep{2013A&A...558A..33A,2018AJ....156..123A},  
%          Cloudy \citep{2013RMxAA..49..137F}, 
%          Source Extractor \citep{1996A&AS..117..393B}
%          }

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc. The
%% Figure and Table counter will not reset.

%\appendix

\bibliography{biblio}{}
\bibliographystyle{aasjournal}

%% This command is needed to show the entire author+affiliation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\end{document}

% End of file `sample631.tex'.

### 2024-11-26 vast/fold.py
Added to documentation for VAST non-detections

@@ -5,11 +5,11 @@ import astropy.units as u
 from astropy.coordinates import SkyCoord
 import matplotlib.pyplot as plt
 import sys
+import os
 
 sys.path.append('../dynspec')
-
 from bc_corr import bc_corr
-ephemeris_file = "../dynspec/de430.bsp"
+ephemeris_file = os.getenv("PLANETARY_EPHEMERIS")
 
 ###########################
 

### 2024-11-27 dynspec/1413381294/dm_detail.py
Adding more notes to pulse analysis

@@ -1,0 +1,16 @@
+from dynspec_tools import dedisperse as dd
+import matplotlib.pyplot as plt
+from matplotlib.ticker import FormatStrFormatter
+
+with open("../1413381294-I.yaml", 'r') as yaml_file:
+    params = dd.parse_yaml(yaml_file)
+    params['input'] = "../" + params['input']
+
+dynspec = dd.Dynspec(**params)
+
+fig, ax = plt.subplots(figsize=(12,5))
+
+dynspec.plot(ax, fscrunch=64)
+ax.set_xlim([1413381450, 1413381720])
+plt.tight_layout()
+plt.savefig('dm_detail.png')

### 2024-11-27 dynspec/1413381294/dm_detail.py
Making corrections to YAML files

@@ -10,6 +10,18 @@ dynspec = dd.Dynspec(**params)
 
 fig, ax = plt.subplots(figsize=(12,5))
 
+flo = dynspec.f[0] - dynspec.df/2
+fhi = flo + dynspec.df*dynspec.Nf
+fctr = 0.5*(flo + fhi)
+bw = 0.5*(fhi - flo)
+
+tlo = dynspec.t[0] - dynspec.dt/2
+thi = tlo + dynspec.dt*dynspec.Nt
+duration = thi - tlo
+
+print(f"{fctr} ± {bw} MHz")
+print(f"{duration} s")
+
 dynspec.plot(ax, fscrunch=64)
 ax.set_xlim([1413381450, 1413381720])
 plt.tight_layout()

### 2024-12-08 paper/main.tex
Added (empty) sections in draft paper

@@
 
-\section{Introduction} \label{sec:intro}
+\section{Introduction} \label{sec:introduction}
 
@@
 \begin{deluxetable*}{lcl}
-\tablecaption{Known LPTs, arranged in ascending order of period\label{tbl:lpts}}
+\tablecaption{Known and candidate LPTs, arranged in ascending order of period\label{tbl:lpts}}
 \tablehead{
@@
 \enddata
-%\tablecomments{This is a sample table. Add more rows as needed, and include notes in this area.}
 \end{deluxetable*}
+
+\section{Observations} \label{sec:observations}
+
+\subsection{MWA} \label{sec:mwa}
+
+\subsection{ASKAP} \label{sec:askap}
+
+\subsection{MeerKAT} \label{sec:meerkat}
+
+\begin{deluxetable*}{cccccl}
+\tablecaption{Pulse detections}
+\tablehead{
+\colhead{Obs start} & \colhead{Duration} & \colhead{Telescope} & \colhead{$\nu$} & \colhead{$\Delta\nu$} & Notes \\ 
+\colhead{time (UTC)} & \colhead{(s)} & & \colhead{(MHz)} & \colhead{(MHz)} & 
+} 
+\startdata
+2024-09-19 09:25:02 & 592\tablenotemark{a} & MWA & 184.96 & 30.72 & \\ % 1410773120 and 1410773416
+2024-09-19 10:34:06 & 592\tablenotemark{a} & MWA & 184.96 & 30.72 & \\ % 1410777264 and 1410777560
+2024-09-19 12:57:10 & 296 & MWA & 184.96 & 30.72 & \\ % 1410785848
+2024-09-19 14:06:14 & 296 & MWA & 184.96 & 30.72 & \\ % 1410789992
+2024-10-09 10:55:50 & 296 & MWA & 184.96 & 30.72 & \\ % 1412506568
+2024-10-09 12:05:34 & 296 & MWA & 184.96 & 30.72 & \\ % 1412510752
+2024-10-10 11:21:10 & 296 & MWA & 184.96 & 30.72 & \\ % 1412594488
+2024-10-10 12:30:54 & 296 & MWA & 184.96 & 30.72 & (Pulse there but too much RFI) \\ % 1412598672
+2024-10-11 10:36:46 & 296 & MWA & 184.96 & 30.72 & \\ % 1412678224
+2024-10-11 11:46:30 & 296 & MWA & 184.96 & 30.72 & \\ % 1412682408
+2024-10-12 11:02:06 & 296 & MWA & 184.96 & 30.72 & \\ % 1412766144
+2024-10-12 12:11:50 & 296 & MWA & 184.96 & 30.72 & \\ % 1412770328
+2024-10-13 10:17:42 & 296 & MWA & 184.96 & 30.72 & \\ % 1412849880
+2024-10-13 11:27:26 & 296 & MWA & 184.96 & 30.72 & \\ % 1412854064
+2024-10-14 10:43:02 & 296 & MWA & 184.96 & 30.72 & \\ % 1412937800
+2024-10-14 11:52:46 & 296 & MWA & 184.96 & 30.72 & \\ % 1412941984
+2024-10-16 10:23:58 & 296 & MWA & 184.96 & 30.72 & \\ % 1413109456
+2024-10-16 11:33:42 & 296 & MWA & 184.96 & 30.72 & \\ % 1413113640
+2024-10-17 11:59:02 & 296 & MWA & 184.96 & 30.72 & \\ % 1413201560
+2024-10-19 10:30:14 & 296 & MWA & 184.96 & 30.72 & \\ % 1413369032
+2024-10-19 11:39:58 & 296 & MWA & 184.96 & 30.72 & \\ % 1413373216
+2024-10-19 13:54:36 & 601 & MeerKAT & 812.8 & 247.6 & (Two components) \\ % 1413381294
+\enddata
+\tablenotetext{a}{Two contiguous 296-second MWA observations were combined}
+\end{deluxetable*}
+
+\section{Analysis \& results} \label{sec:analysis}
+
+\subsection{Timing solution and DM determination} \label{sec:timing_and_dm}
+
+Following the positive identification of several pulses in the GPM data set, we did a grid search of periods that would result in an integer number of pulses between two widely spaced pulses.
+A candidate period of $4186.4 \pm 0.1$ was found for which all detections fell within the same phase range ${\sim}0.05$.
+% We further refined this by attempting to phase connect to Dougal's original pulse, and got $4186.33 \pm 0.02$ s, but this needn't be part of the story, since even the above was enough to motivate the MWA campaign that followed.
+This motivated the follow-up MWA observations (under project code D0042) in which two consecutive pulses ${\sim}4190$ seconds apart were detected without any detectable emission between them, confirming our earlier estimate.
+The lever arm afforded by both the GPM and D0042 detections proved sufficient to phase-connect to the original pulse published by \citet{2024MNRAS.535..909D}, yielding a refined period of $P = 4186.329 \pm 0.002$~s.
+
+\subsection{Polarization} \label{sec:polarization}
+
+\section{Discussion} \label{sec:discussion}
+
+\section{Conclusions} \label{sec:conclusions}
 

### 2025-04-24 dynspec/meerkat/fit_component_spectra.py
Added a not-entirely-successful attempt to measure the spectrum of the two components separately

@@ -1,0 +1,100 @@
+import numpy as np
+from scipy.optimize import curve_fit
+import sys
+import os
+sys.path.append(os.path.abspath(".."))
+from timing import *
+import matplotlib.pyplot as plt
+import warnings
+warnings.simplefilter('always')
+
+dat = np.load('../1413381294_meerkat.pkl', allow_pickle=True)
+
+t = dat['TIMES'] - dat['TIMES'][0]  # in seconds from start of obs
+f = dat['FREQS'] / 1e6              # in MHz
+I, _, _ = Stokes_ds(dat)
+
+# Do some f-scrunching
+factor = 11
+f = np.nanmean(np.reshape(f, (-1, factor)), axis=1)
+I = np.nanmean(np.reshape(I, (I.shape[0], -1, factor)), axis=2)
+
+F, T = np.meshgrid(f, t)
+
+Tflat = T.ravel()
+Fflat = F.ravel()
+Iflat = I.ravel()
+
+mask = ~np.isnan(Iflat)
+
+Tclean = Tflat[mask]
+Fclean = Fflat[mask]
+Iclean = Iflat[mask]
+
+pixels = np.vstack((Tclean, Fclean))
+all_pixels = np.vstack((Tflat, Fflat))
+
+def calc_dmdelay(DM, f, f_ref):
+    return 4148.808 * DM * (1/f**2 - 1/f_ref**2)
+
+def model(pixel, comp1_1GHz, comp1_mu, comp1_sigma, comp1_alpha, comp2_1GHz, comp2_mu, comp2_sigma, comp2_alpha, baseline_m, baseline_c_1GHz, baseline_alpha, DM):
+
+    t, f = pixel
+    t_dd = t - 4148.808 * DM / f**2
+
+    baseline = (baseline_m*t_dd + baseline_c_1GHz)*(f/1e3)**baseline_alpha
+    comp1    = comp1_1GHz * (f/1e3)**comp1_alpha * np.exp(-0.5*(t_dd - comp1_mu)**2 / comp1_sigma**2)
+    comp2    = comp2_1GHz * (f/1e3)**comp2_alpha * np.exp(-0.5*(t_dd - comp2_mu)**2 / comp2_sigma**2)
+
+    return baseline + comp1 + comp2
+
[…]

### 2025-04-24 dynspec/meerkat/fit_spectrum.py

@@ -27,7 +27,7 @@ def pl(nu, norm, alpha):
     spec_nu = nu / ref_nu
     return norm * spec_nu **alpha
 
-val = np.load("./J1755-25_1729341386_scan18.pkl", allow_pickle=True)
+val = np.load("../1413381294_meerkat.pkl", allow_pickle=True)
 mjds = Time((val['TIMES']*u.s).to(u.day), format='mjd')
 freqs = val['FREQS']
 It = 1000*np.real((val['DS'][:,:,0]+val['DS'][:,:,3]))

### 2025-04-24 dynspec/plot_stacked_spectra.py
Added new attempt to line things up better

@@ -1,0 +1,32 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+data = [
+    {'pkl': 'D0042_observations_185MHz_stacked.pkl', 'fscrunch_factor': 12},
+    {'pkl': 'D0042_observations_200MHz_stacked.pkl', 'fscrunch_factor': 12},
+    {'pkl': 'GPM_observations_stacked.pkl',          'fscrunch_factor': 12},
+    {'pkl': '2023_meerkat_stacked.pkl',              'fscrunch_factor': 32},
+]
+
+fmin = np.inf
+fmax = -np.inf
+
+for datum in data:
+    pkl = datum['pkl']
+    fscrunch_factor = datum['fscrunch_factor']
+    dat = np.load(pkl, allow_pickle=True)
+    I = np.nanmean(np.reshape(dat['I'], (dat['I'].shape[0], -1, fscrunch_factor)), axis=-1)
+    f = np.nanmean(np.reshape(dat['f'], (-1, fscrunch_factor)), axis=-1)/1e6
+    t = dat['t']
+    plt.pcolormesh(t, f, I.T, alpha=0.8)
+    if min(f) < fmin:
+        fmin = min(f)
+    if max(f) > fmax:
+        fmax = max(f)
+
+# Plot didespersion sweep
+ffine = np.linspace(fmin, fmax, 1000)
+DM = 710
+plt.plot(4148.808*DM/ffine**2, ffine, 'r')
+plt.yscale('log')
+plt.show()

### 2025-04-24 dynspec/pulsestack_all.py

@@ -93,6 +93,7 @@ def main():
         if args.xlim:
             axs[0][col].set_xlim(args.xlim)
         axs[0][col].set_ylim([-1, ys[col]+1])
+        axs[0][col].axvline(0, ls='--', alpha=0.5, c='r')
     axs[0][0].set_ylabel("ObsID")
 
     if args.grid:

### 2025-04-24 dynspec/timing.py

@@ -13,7 +13,7 @@ from mwa_pb_lookup.lookup_beam import beam_lookup_1d
 def get_J1755_ephemeris():
     return {
         'PEPOCH': Time(59965.0377, scale='utc', format='mjd'),
-        'period': 4186.332579477463 * u.s,
+        'period': 4186.330 * u.s,
         'DM': 710.0 * u.pc / u.cm**3,
         'tau_sc': 0.0*u.s,
         'coord': SkyCoord("17:55:34.87 -25:27:49.1", unit=(u.hourangle, u.deg), frame='icrs'),

### 2025-04-24 dynspec/plot_stacked_spectra.py
Getting closer to having a nice dynamic spectra plot

@@ -1,15 +1,26 @@
 import numpy as np
 import matplotlib.pyplot as plt
+from matplotlib.patches import Rectangle
+from timing import *
+
+ephem = get_J1755_ephemeris()
+DM = ephem['DM'].value
 
 data = [
-    {'pkl': 'D0042_observations_185MHz_stacked.pkl', 'fscrunch_factor': 12},
-    {'pkl': 'D0042_observations_200MHz_stacked.pkl', 'fscrunch_factor': 12},
-    {'pkl': 'GPM_observations_stacked.pkl',          'fscrunch_factor': 12},
-    {'pkl': '2023_meerkat_stacked.pkl',              'fscrunch_factor': 32},
+    {'pkl': 'D0042_observations_185MHz_stacked.pkl', 'fscrunch_factor': 12,
+     'color': 'red', 'label': 'D0042 (185 MHz)'},
+    {'pkl': 'D0042_observations_200MHz_stacked.pkl', 'fscrunch_factor': 12,
+     'color': 'orange', 'label': 'D0042 (200 MHz)'},
+    {'pkl': 'GPM_observations_stacked.pkl',          'fscrunch_factor': 12,
+     'color': 'yellow', 'label': 'GPM 2024'},
+    {'pkl': '2023_meerkat_stacked.pkl',              'fscrunch_factor': 8 ,
+     'color': 'green', 'label': 'MeerKAT (2023)'},
+    {'pkl': '2024_meerkat_stacked.pkl',              'fscrunch_factor': 33,
+     'color': 'blue', 'label': 'MeerKAT (2024)'},
 ]
 
-fmin = np.inf
-fmax = -np.inf
+fig, axs = plt.subplots(nrows=2, ncols=1, figsize=(8,12), sharex=True)
+rects = []
 
 for datum in data:
     pkl = datum['pkl']
@@ -18,15 +29,35 @@ for datum in data:
     I = np.nanmean(np.reshape(dat['I'], (dat['I'].shape[0], -1, fscrunch_factor)), axis=-1)
     f = np.nanmean(np.reshape(dat['f'], (-1, fscrunch_factor)), axis=-1)/1e6
     t = dat['t']
-    plt.pcolormesh(t, f, I.T, alpha=0.8)
-    if min(f) < fmin:
-        fmin = min(f)
-    if max(f) > fmax:
-        fmax = max(f)
[…]

### 2025-04-24 dynspec/timing.py

@@ -14,8 +14,8 @@ def get_J1755_ephemeris():
     return {
         'PEPOCH': Time(59965.0377, scale='utc', format='mjd'),
         'period': 4186.330 * u.s,
-        'DM': 710.0 * u.pc / u.cm**3,
-        'tau_sc': 0.0*u.s,
+        'DM': 650.0 * u.pc / u.cm**3,
+        'tau_sc': 7.0e-2*u.s,
         'coord': SkyCoord("17:55:34.87 -25:27:49.1", unit=(u.hourangle, u.deg), frame='icrs'),
     }
 

### 2025-04-24 dynspec/plot_stacked_spectra.py
Added stacked_spectra plot

@@ -5,32 +5,43 @@ from timing import *
 
 ephem = get_J1755_ephemeris()
 DM = ephem['DM'].value
+tau_sc_1GHz = ephem['tau_sc'].value
+
+def calc_dm_delay(DM, f):
+    '''
+    DM in pc/cm³
+    f in MHz
+    result is in seconds
+    '''
+    return 4148.808 * DM / f**2
 
 data = [
     {'pkl': 'D0042_observations_185MHz_stacked.pkl', 'fscrunch_factor': 12,
-     'color': 'red', 'label': 'D0042 (185 MHz)'},
+     'tscrunch_factor': 1, 'color': 'red', 'label': 'D0042 (185 MHz)'},
     {'pkl': 'D0042_observations_200MHz_stacked.pkl', 'fscrunch_factor': 12,
-     'color': 'orange', 'label': 'D0042 (200 MHz)'},
+     'tscrunch_factor': 1, 'color': 'orange', 'label': 'D0042 (200 MHz)'},
     {'pkl': 'GPM_observations_stacked.pkl',          'fscrunch_factor': 12,
-     'color': 'yellow', 'label': 'GPM 2024'},
-    {'pkl': '2023_meerkat_stacked.pkl',              'fscrunch_factor': 8 ,
-     'color': 'green', 'label': 'MeerKAT (2023)'},
+     'tscrunch_factor': 1, 'color': 'yellow', 'label': 'GPM 2024'},
+    {'pkl': '2023_meerkat_stacked.pkl',              'fscrunch_factor': 16,
+     'tscrunch_factor': 2, 'color': 'green', 'label': 'MeerKAT (2023)'},
     {'pkl': '2024_meerkat_stacked.pkl',              'fscrunch_factor': 33,
-     'color': 'blue', 'label': 'MeerKAT (2024)'},
+     'tscrunch_factor': 1, 'color': 'blue', 'label': 'MeerKAT (2024)'},
 ]
 
-fig, axs = plt.subplots(nrows=2, ncols=1, figsize=(8,12), sharex=True)
+fig, axs = plt.subplots(nrows=2, ncols=1, figsize=(5,8))
 rects = []
 
 for datum in data:
     pkl = datum['pkl']
     fscrunch_factor = datum['fscrunch_factor']
+    tscrunch_factor = datum['tscrunch_factor']
     dat = np.load(pkl, allow_pickle=True)
[…]

### 2025-04-24 dynspec/timing.py

@@ -14,7 +14,7 @@ def get_J1755_ephemeris():
     return {
         'PEPOCH': Time(59965.0377, scale='utc', format='mjd'),
         'period': 4186.330 * u.s,
-        'DM': 650.0 * u.pc / u.cm**3,
+        'DM': 710.0 * u.pc / u.cm**3,
         'tau_sc': 7.0e-2*u.s,
         'coord': SkyCoord("17:55:34.87 -25:27:49.1", unit=(u.hourangle, u.deg), frame='icrs'),
     }

### 2025-04-24 dynspec/plot_stacked_spectra.py
Changed ordering of elements in stacked_spectra.py

@@ -16,16 +16,16 @@ def calc_dm_delay(DM, f):
     return 4148.808 * DM / f**2
 
 data = [
-    {'pkl': 'D0042_observations_185MHz_stacked.pkl', 'fscrunch_factor': 12,
-     'tscrunch_factor': 1, 'color': 'red', 'label': 'D0042 (185 MHz)'},
-    {'pkl': 'D0042_observations_200MHz_stacked.pkl', 'fscrunch_factor': 12,
-     'tscrunch_factor': 1, 'color': 'orange', 'label': 'D0042 (200 MHz)'},
+    {'pkl': '2023_meerkat_stacked.pkl',              'fscrunch_factor': 16,
+     'tscrunch_factor': 2, 'color': 'blue', 'label': 'MeerKAT (2023)'},
+    {'pkl': '2024_meerkat_stacked.pkl',              'fscrunch_factor': 33,
+     'tscrunch_factor': 1, 'color': 'green', 'label': 'MeerKAT (2024)'},
     {'pkl': 'GPM_observations_stacked.pkl',          'fscrunch_factor': 12,
      'tscrunch_factor': 1, 'color': 'yellow', 'label': 'GPM 2024'},
-    {'pkl': '2023_meerkat_stacked.pkl',              'fscrunch_factor': 16,
-     'tscrunch_factor': 2, 'color': 'green', 'label': 'MeerKAT (2023)'},
-    {'pkl': '2024_meerkat_stacked.pkl',              'fscrunch_factor': 33,
-     'tscrunch_factor': 1, 'color': 'blue', 'label': 'MeerKAT (2024)'},
+    {'pkl': 'D0042_observations_200MHz_stacked.pkl', 'fscrunch_factor': 12,
+     'tscrunch_factor': 1, 'color': 'orange', 'label': 'D0042 (200 MHz)'},
+    {'pkl': 'D0042_observations_185MHz_stacked.pkl', 'fscrunch_factor': 12,
+     'tscrunch_factor': 1, 'color': 'red', 'label': 'D0042 (185 MHz)'},
 ]
 
 fig, axs = plt.subplots(nrows=2, ncols=1, figsize=(5,8))

### 2025-04-24 dynspec/pulsestack_all.py
Improved pulsestack by flattening baselines

@@ -1,4 +1,5 @@
 import numpy as np
+from scipy.optimize import curve_fit
 import matplotlib.pyplot as plt
 from matplotlib import colormaps, colors, cm
 import astropy.units as u
@@ -26,7 +27,7 @@ def main():
 
     ephemeris = get_J1755_ephemeris()
 
-    fig, axs = plt.subplots(ncols=args.ncols, figsize=(5*args.ncols+2,12), squeeze=False)
+    fig, axs = plt.subplots(ncols=args.ncols, figsize=(4*args.ncols+1.5,10), squeeze=False)
     yticks = [[] for i in range(args.ncols)]
     ylabels = [[] for i in range(args.ncols)]
     #cmap = colormaps[args.colormap]
@@ -74,6 +75,14 @@ def main():
         # Form lightcurve
         lightcurve = np.nanmean(Idd, axis=1)
 
+        # A quick fit of a gaussian in order to smooth out the baseline
+        def model(ph, m, c, A, mu, sigma):
+            return m*ph + c + A*np.exp(-0.5*(ph-mu)**2/sigma**2)
+        p0 = [0, 0, np.max(lightcurve), 0, 10/ephemeris['period'].to('s').value]
+        popt, _ = curve_fit(model, phases, lightcurve, p0=p0)
+        m, c, _, _, _ = popt
+        lightcurve -= m*phases + c
+
         if len(set(pulses)) != 1:
             phase_0_idx = np.argmin(np.abs(phases))
             pulse_at_phase_0 = pulses[phase_0_idx]
@@ -83,7 +92,7 @@ def main():
 
         axs[0][col].plot(phases*ephemeris['period'], lightcurve/np.nanmax(lightcurve) + ys[col], 'k')
         yticks[col].append(ys[col])
-        ylabels[col].append(f"{dat['OBSID']}")#\n(Pulse #{int(np.round(np.median(pulses)))})")
+        ylabels[col].append(f"{times[0].iso[:16]}")#\n(Pulse #{int(np.round(np.median(pulses)))})")
         ys[col] += 1
 
     for col in range(args.ncols):
@@ -93,7 +102,7 @@ def main():
         if args.xlim:
             axs[0][col].set_xlim(args.xlim)
         axs[0][col].set_ylim([-1, ys[col]+1])
-        axs[0][col].axvline(0, ls='--', alpha=0.5, c='r')
[…]

### 2025-04-24 dynspec/pulsestack_all.py
Did some extra time scrunching for the pulsestack

@@ -47,15 +47,22 @@ def main():
 
         I, fmask, _ = Stokes_ds(dat, pol='I')
 
-        # Dedispersion requires no nans
-        I[np.isnan(I)] = 0.0
-
         f = dat['FREQS'] * u.Hz
         #color = cmap(cmap_norm(np.mean(f)))
 
         location = EarthLocation.of_site(dat['TELESCOPE'])
         times = Time(dat['TIMES']/86400.0, scale='utc', format='mjd', location=location)
         dt = (times[1] - times[0]).to('s')
+        if dt < 3*u.s:
+            times = times[1::2] - dt/2
+            dt *= 2
+            t_len = len(times)
+            print(I.shape)
+            print(t_len)
+            I = np.nanmean(np.reshape(I[:t_len*2,:], (-1, 2, I.shape[1])), axis=1)
+
+        # Dedispersion requires no nans
+        I[np.isnan(I)] = 0.0
 
         # Dedisperse
         f_ref = np.mean(f)

### 2025-04-24 dynspec/pulsestack_all.py
Added mwa ips lightcurve as pickle file

@@ -57,8 +57,6 @@ def main():
             times = times[1::2] - dt/2
             dt *= 2
             t_len = len(times)
-            print(I.shape)
-            print(t_len)
             I = np.nanmean(np.reshape(I[:t_len*2,:], (-1, 2, I.shape[1])), axis=1)
 
         # Dedispersion requires no nans

### 2025-04-24 dynspec/timing.py

@@ -146,7 +146,8 @@ def get_flags(dat):
     else:
         fmask = set()
 
-    fmask |= set(np.where(np.all(np.isnan(dat['DS']), axis=0))[0])
+    if len(dat['FREQS']) > 1: # A hack to save my single-frequency dynspecs
+        fmask |= set(np.where(np.all(np.isnan(dat['DS']), axis=0))[0])
     fmask = list(fmask)
 
     # Get time flags

### 2025-04-24 mwa_ips/bin_it_up.py

@@ -1,6 +1,7 @@
 import numpy as np
 import matplotlib.pyplot as plt
 from astropy.time import Time
+import pickle
 
 on = np.loadtxt('ts_on_source.txt')
 off = np.loadtxt('ts_off_source.txt')
@@ -56,3 +57,20 @@ plt.legend()
 plt.tight_layout()
 
 plt.savefig(f'binned_to_{b*sample_time:.0f}s.png')
+
+# Save to pickle file
+ds = np.empty((len(binned_on), 1, 4))
+ds[:,0,0] = binned_on # Stokes I
+ds[:,:,1:] = np.nan # Stokes Q, U, V
+dat = {
+    'DS': ds,
+    'DS_MED': ds,
+    'DS_STD': ds,
+    'POLS': ['I', 'Q', 'U', 'V'],
+    'TIMES': t.mjd*86400,
+    'FREQS': np.array([161920000]),
+    'TELESCOPE': 'MWA',
+}
+pkl = f'../dynspec/{t[0].gps:.0f}_ips.pkl'
+with open(pkl, 'wb') as f:
+    pickle.dump(dat, f)

### 2025-04-24 dynspec/pulsestack_all.py
Added askap lightcurves as pickles

@@ -97,7 +97,7 @@ def main():
 
         axs[0][col].plot(phases*ephemeris['period'], lightcurve/np.nanmax(lightcurve) + ys[col], 'k')
         yticks[col].append(ys[col])
-        ylabels[col].append(f"{times[0].iso[:16]}")#\n(Pulse #{int(np.round(np.median(pulses)))})")
+        ylabels[col].append(f"{times[0].iso[:16]}\n{dat['TELESCOPE']}")#\n(Pulse #{int(np.round(np.median(pulses)))})")
         ys[col] += 1
 
     for col in range(args.ncols):

### 2025-04-24 vast/make_pickles.py
Added a short script to turn ASKAP lightcurves into pickles. This will become redundant when better data are provided

@@ -1,0 +1,63 @@
+import numpy as np
+import pickle
+from astropy.time import Time
+
+##########
+# First light curve (from 2023)
+
+I = np.loadtxt('askap1-I.txt')
+
+# Save to pickle file
+ds = np.empty((len(I), 1, 4))
+ds[:,0,0] = I # Stokes I
+ds[:,:,1:] = np.nan # Stokes Q, U, V
+dat = {
+    'DS': ds,
+    'DS_MED': ds,
+    'DS_STD': ds,
+    'POLS': ['I', 'Q', 'U', 'V'],
+    'TIMES': np.arange(len(I))*10 + 59965.03588541667*86400,
+    'FREQS': np.array([887500000]),
+    'TELESCOPE': 'ASKAP',
+}
+pkl = f"../dynspec/{Time(59965.03588541667, scale='utc', format='mjd').gps:.0f}_askap.pkl"
+with open(pkl, 'wb') as f:
+    pickle.dump(dat, f)
+
+##########
+# Second light curve (from 2024)
+
+ts = []
+Is = []
+Qs = []
+Us = []
+Vs = []
+with open('j1755_burst2_unsub_lc.csv', 'r') as f:
+    lines = f.readlines()
+    for line in lines[1:]:
+        t, I, L, Q, U, V, pa = line.split(',')
+        ts.append(float(t))
+        Is.append(float(I))
+        Qs.append(float(Q))
+        Us.append(float(U))
+        Vs.append(float(V))
+
+# Save to pickle file
+ds = np.empty((len(ts), 1, 4))
+ds[:,0,0] = Is
+ds[:,0,1] = Qs
+ds[:,0,2] = Us
+ds[:,0,3] = Vs
+dat = {
+    'DS': ds,
+    'DS_MED': ds,
+    'DS_STD': ds,
+    'POLS': ['I', 'Q', 'U', 'V'],
+    'TIMES': np.array(ts),
+    'FREQS': np.array([887500000]),
+    'TELESCOPE': 'ASKAP',
+}
+pkl = f"../dynspec/{Time(ts[0]/86400, scale='utc', format='mjd').gps:.0f}_askap.pkl"
+with open(pkl, 'wb') as f:
+    pickle.dump(dat, f)
+

### 2025-04-24 dynspec/fit_toas.py
A few more little patchups to get the fit_toas working on pathological dynspec

@@ -24,7 +24,10 @@ def fit_toa(dat, fit_scattering=False, output_plot=None, obsid=None):
     t = Time(dat['TIMES']/86400.0, scale='utc', format='mjd', location=EarthLocation.of_site(dat['TELESCOPE']))
     dt = t[1] - t[0]
     f = dat['FREQS'] * u.Hz
-    df = f[1] - f[0]
+    try:
+        df = f[1] - f[0]
+    except:
+        df = dat['BW'] * u.Hz
     nchans = len(f)
 
     f += 0.5*df # A hack because frequencies are labelled as lower edge of channels instead of middle of channels where they should be
@@ -79,7 +82,7 @@ def fit_toa(dat, fit_scattering=False, output_plot=None, obsid=None):
     #print(f"{peak_idx = }")
     #print(f"{p0 = }")
     #print(f"{bounds = }")
-    popt, pcov = curve_fit(model, t_base.to('s').value, lightcurve, p0=p0, sigma=noise, bounds=bounds)
+    popt, pcov = curve_fit(model, t_base.to('s').value, lightcurve, p0=p0, sigma=noise if noise != 0.0 else None, bounds=bounds)
 
     # Pull out the ToA
     toa = t[0] + popt[1]*u.s

### 2025-04-24 dynspec/fit_toas.py
Got all the ToA fits working

@@ -18,6 +18,7 @@ src_period = ephemeris['period']
 #src_Porb = ephemeris['Porb']
 src_pepoch = ephemeris['PEPOCH']
 src_dm = ephemeris['DM']
+src_tau_sc_1GHz = ephemeris['tau_sc']
 
 def fit_toa(dat, fit_scattering=False, output_plot=None, obsid=None):
 
@@ -70,27 +71,32 @@ def fit_toa(dat, fit_scattering=False, output_plot=None, obsid=None):
     A0 = matched_filter_results[peak_idx] / np.sum(model_pulse)
 
     # Fit a pulse to it
+    p0 = (100*A0, t_base[peak_idx].value, 0.0, 0.0, 30) # Not 100% sure why we need 100*A0, but it helps!
+    bounds = [(0,      -np.inf, -np.inf, -np.inf, 0.1*dt.to('s').value),
+              (np.inf,  np.inf,  np.inf,  np.inf, np.inf              )]
+
     if fit_scattering:
-        p0 = (A0, t_base[peak_idx].value, 50.0, 0.0, 0.0, 30)
-        bounds = [(0, -np.inf, 1e-6*dt.to('s').value, -np.inf, -np.inf, 0.1*dt.to('s').value), (np.inf, np.inf, np.inf, np.inf, np.inf, np.inf)]
-        model = scattered_pulse_model
+        def scattered_pulse_model_at_freq(t_s, A, μ_s, m, c, σ_s):
+            τ_s = src_tau_sc_1GHz.to('s').value * (f_ref/u.GHz).decompose()**(-4)
+            return scattered_pulse_model(t_s, A, μ_s, m, c, σ_s, τ_s)
+        model = scattered_pulse_model_at_freq
     else:
-        p0 = (A0, t_base[peak_idx].value, 0.0, 0.0)
-        bounds = [(0, -np.inf, -np.inf, -np.inf), (np.inf, np.inf, np.inf, np.inf)]
         model = pulse_model
     #print(f"{obsid = }")
     #print(f"{peak_idx = }")
     #print(f"{p0 = }")
     #print(f"{bounds = }")
     popt, pcov = curve_fit(model, t_base.to('s').value, lightcurve, p0=p0, sigma=noise if noise != 0.0 else None, bounds=bounds)
+    A, μ, m, c, σ = popt
[…]

### 2025-04-24 dynspec/timing.py

@@ -59,7 +59,7 @@ def pulse_model(t_s, A, μ_s, m=0, c=0, σ_s=30):
     baseline = m*t_s + c
     return discrete_gaussian(t_s, A, μ_s, σ_s) + baseline
 
-def scattered_pulse_model(t_s, A, μ_s, τ_s, m=0, c=0, σ_s=30):
+def scattered_pulse_model(t_s, A, μ_s, m, c, σ_s, τ_s):
     baseline = m*t_s + c
     return discrete_emg(t_s, A, μ_s, σ_s, τ_s) + baseline
 

### 2025-04-24 dynspec/fit_toas.py
Added fitted pulses to pulsestack too

@@ -150,7 +150,7 @@ def fit_toa(dat, fit_scattering=False, output_plot=None, obsid=None):
         plt.savefig(output_plot)
         plt.close(fig)
 
-    return f_ref, toa, toa_err, fluence, fluence_err, peak_signal, peak_snr
+    return f_ref, toa, toa_err, fluence, fluence_err, peak_signal, peak_snr, σ*u.s, σ_err*u.s
 
 
 def main():
@@ -163,9 +163,9 @@ def main():
     args = parser.parse_args()
 
     # Summarise everything into a table
-    table = QTable(names=['ObsID', 'freq', 'ToA', 'ToA_err', 'telescope', 'fluence', 'fluence_err', 'fitted_peak_flux_density', 'peak_snr'],
-                   dtype=[str, float, float, float, str, float, float, float, float],
-                   units=[None, u.MHz, None, u.d, None, u.Jy*u.s, u.Jy*u.s, u.Jy, None])
+    table = QTable(names=['ObsID', 'freq', 'ToA', 'ToA_err', 'telescope', 'fluence', 'fluence_err', 'fitted_peak_flux_density', 'peak_snr', 'width', 'width_err'],
+                   dtype=[str, float, float, float, str, float, float, float, float, float, float],
+                   units=[None, u.MHz, None, u.d, None, u.Jy*u.s, u.Jy*u.s, u.Jy, None, u.s, u.s])
 
     for pkl in args.ds_files:
         print(f"{pkl}...")
@@ -176,9 +176,21 @@ def main():
 
         output_plot = f"{pkl[:-4]}_toa.png"
 
-        f_ref, toa, toa_err, fluence, fluence_err, peak_signal, peak_snr = fit_toa(dat, fit_scattering=args.fit_scattering, output_plot=output_plot, obsid=obsid)
+        f_ref, toa, toa_err, fluence, fluence_err, peak_signal, peak_snr, σ, σ_err = fit_toa(dat, fit_scattering=args.fit_scattering, output_plot=output_plot, obsid=obsid)
 
-        table.add_row([obsid, f_ref, toa.mjd, toa_err, dat['TELESCOPE'], fluence, fluence_err, peak_signal, peak_snr])
+        table.add_row([
+            obsid,
+            f_ref,
+            toa.mjd,
+            toa_err,
+            dat['TELESCOPE'],
+            fluence,
+            fluence_err,
+            peak_signal,
+            peak_snr,
+            σ,
[…]

### 2025-04-24 dynspec/pulsestack_all.py

@@ -80,12 +80,16 @@ def main():
         # Form lightcurve
         lightcurve = np.nanmean(Idd, axis=1)
 
-        # A quick fit of a gaussian in order to smooth out the baseline
-        def model(ph, m, c, A, mu, sigma):
-            return m*ph + c + A*np.exp(-0.5*(ph-mu)**2/sigma**2)
-        p0 = [0, 0, np.max(lightcurve), 0, 10/ephemeris['period'].to('s').value]
+        # Fit a scattered pulse
+        def model(ph, A, μ, m, c, σ):
+            τ = (ephemeris['tau_sc']/ephemeris['period'] * (f_ref/u.GHz)**(-4)).decompose()
+            return scattered_pulse_model(ph, A, μ, m, c, σ, τ)
+        p0 = [np.max(lightcurve), 0, 0, 0, 10/ephemeris['period'].to('s').value]
+        #def model(ph, m, c, A, mu, sigma):
+        #    return m*ph + c + A*np.exp(-0.5*(ph-mu)**2/sigma**2)
+        #p0 = [0, 0, np.max(lightcurve), 0, 10/ephemeris['period'].to('s').value]
         popt, _ = curve_fit(model, phases, lightcurve, p0=p0)
-        m, c, _, _, _ = popt
+        A, μ, m, c, σ = popt
         lightcurve -= m*phases + c
 
         if len(set(pulses)) != 1:
@@ -96,6 +100,10 @@ def main():
             lightcurve = lightcurve[mask]
 
         axs[0][col].plot(phases*ephemeris['period'], lightcurve/np.nanmax(lightcurve) + ys[col], 'k')
+        ph_fine = np.linspace(phases[0], phases[-1], 1000)
+        y = pulse_model(ph_fine, A, μ, 0, 0, σ)
+        ynorm = y / np.nanmax(y)
+        axs[0][col].plot(ph_fine*ephemeris['period'], ynorm + ys[col], 'b--')
         yticks[col].append(ys[col])
         ylabels[col].append(f"{times[0].iso[:16]}\n{dat['TELESCOPE']}")#\n(Pulse #{int(np.round(np.median(pulses)))})")
         ys[col] += 1

### 2025-04-24 paper/main.tex
Udated main.tex to match Overleaf

--- 2024-11-25 paper/main.tex
@@
 \documentclass[preprint2,linenumbers]{aastex631}
+
+\usepackage{amsmath}
 
@@
 \newcommand{\srcfull}{ASKAP J175534.9$-$252749.1}
+
+\defcitealias{2024MNRAS.535..909D}{Paper~I}
 
@@
 
+\author[0009-0003-0996-9176]{Csanad Horv\'{a}th}
+\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}
+
+\author{Angie Waszewski}
+\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}
+
+\author{John Morgan}
+\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}
+
 \author{Ziteng Wang}
@@
 
-\section{Introduction} \label{sec:intro}
+\section{Introduction} \label{sec:introduction}
 
-\srcfull{} (hereafter, \src{}) is a transient radio source discovered in the Variables and Slow Transients (VAST) survey \citep{2024MNRAS.535..909D}.
+\srcfull{} (hereafter, \src{}) is a transient radio source discovered in the Variables and Slow Transients (VAST) survey \citep[][hereafter \citetalias{2024MNRAS.535..909D}]{2024MNRAS.535..909D}.
 A single, highly polarized pulse was observed, lasting approximately 2 minutes, exhibiting a steep spectrum ($\alpha = -3.1$).
@@
 
+Although optical follow-up has confirmed that at least some LPTs are white dwarfs with main sequence companions \citep{2024arXiv240811536D,2025arXiv250103315R}, it remains unclear if this model can account for all known LPTs \citep[e.g.][]{2022ApJ...940...72R,Lee2025}.
+Unfortunately, optical follow-up is not possible for LPTs and LPT candidates which are obscured by Galactic foregrounds.
+This is almost certainly the case for \src{}, which is situated very close to the Galactic plane ($b = -0\overset{\circ}{.}12$), and has a dispersion measure (DM) derived distance of ${\sim}4.7\,$kpc \citepalias{2024MNRAS.535..909D}; unsurprisingly, optical follow-up at \src{}'s location did not turn up any source down to ${\sim}23$ AB mag.
+Without more detections in the radio or at other wavelengths, it seemed unlikely that the nature of \src{} could ever be resolved.
+
+In this short paper, we present new radio observations (spanning frequencies from $154\,$MHz to $1.7\,$GHz) in which \src{} was re-detected, confirming that it is indeed an LPT with a period of ${\sim}1.16\,$hours.
+In \S\ref{sec:observations}, we describe the observations themselves, some of which were taken as part of independent surveys, and some of which were taken as dedicated follow-up of \src{} once it became apparent that it was still active.
+In \S\ref{sec:analysis} we present a timing analysis of the new detections, as well as revised estimates of the DM and the scattering timescale.
+We also include new polarization detections in which the polarisation angle (PA) behavior differs significantly from the originally detected pulse.
+In \S\ref{sec:discussion} we revisit the question of the nature of \src{}, arguing in favor of a white dwarf interpretation.
+The main conclusions are summarized in \S\ref{sec:conclusions}.
+
 \begin{deluxetable*}{lcl}
-\tablecaption{Known LPTs, arranged in ascending order of period\label{tbl:lpts}}
+\tablecaption{Known and candidate LPTs, arranged in ascending order of period\label{tbl:lpts}}
 \tablehead{
@@
 GLEAM-X J0704-37           & 175  & \citet{2024arXiv240815757H} \\
-ASKAP J1839-0756           & 387  & \todo{Lee} \\
+ASKAP J1839-0756           & 387  & \citet{Lee2025} \\
 \enddata
-%\tablecomments{This is a sample table. Add more rows as needed, and include notes in this area.}
 \end{deluxetable*}
+
+\section{Observations} \label{sec:observations}
+
+The observations included in this paper were made at the Murchison Widefield Array \citep[MWA;][]{Tingay2013},
+
+\subsection{MWA} \label{sec:mwa}
+
+\subsection{ASKAP} \label{sec:askap}
+
+\subsection{MeerKAT} \label{sec:meerkat}
+
+%\begin{deluxetable*}{cccccc}
+%\tablecaption{Pulse detections and non-detections}
+%\tablehead{
+%\colhead{Obs start} & \colhead{Duration} & \colhead{Telescope} & \colhead{$\nu$} & %\colhead{$\Delta\nu$} & \colhead{Detected?} \\
+%\colhead{time (UTC)} & \colhead{(s)} & & \colhead{(MHz)} & \colhead{(MHz)} &
+%}
+%\startdata
+%2024-09-19 09:25:02 & 592\tablenotemark{a} & MWA & 184.96 & 30.72 & Y \\ % 1410773120 and 1410773416
+%2024-09-19 10:34:06 & 592\tablenotemark{a} & MWA & 184.96 & 30.72 & Y \\ % 1410777264 and 1410777560
+%2024-09-19 12:57:10 & 296 & MWA & 184.96 & 30.72 & Y \\ % 1410785848
+%2024-09-19 14:06:14 & 296 & MWA & 184.96 & 30.72 & Y \\ % 1410789992
+%2024-10-09 10:55:50 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412506568
+%2024-10-09 12:05:34 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412510752
+%2024-10-10 11:21:10 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412594488
+%2024-10-10 12:30:54 & 296 & MWA\tablenotemark{b} & 200.32 & 30.72 & Y \\ % 1412598672
+%2024-10-11 10:36:46 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412678224
+%2024-10-11 11:46:30 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412682408
+%2024-10-12 11:02:06 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412766144
+%2024-10-12 12:11:50 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412770328
+%2024-10-13 10:17:42 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412849880
+%2024-10-13 11:27:26 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412854064
+%2024-10-14 10:43:02 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412937800
+%2024-10-14 11:52:46 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412941984
+%2024-10-16 10:23:58 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413109456
+%2024-10-16 11:33:42 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413113640
+%2024-10-17 11:59:02 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413201560
+%2024-10-19 10:30:14 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413369032
+%2024-10-19 11:39:58 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413373216
+%2024-10-19 13:54:36 & 601 & MeerKAT\tablenotemark{c} & 812.8 & 247.6 & Y \\ % 1413381294
+%\enddata
+%\tablenotetext{a}{Two contiguous 296-second MWA observations were combined}
+%\tablenotetext{b}{Too much RFI to use in downstream analysis}
+%\tablenotetext{c}{Two components in pulse}
+%\end{deluxetable*}
+
+\begin{deluxetable*}{cccccc}
+\tablecaption{Observations}
+\tablehead{
+\colhead{Date range} & \colhead{Telescope} & Project & \colhead{$\nu$} & \colhead{$\Delta\nu$} & \colhead{Number of} \\
+\colhead{(MJD)} & & & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{pulses}
+}
+\startdata
+59965 & ASKAP\tablenotemark{a} & SB47253 & 887.5 & 288 & 1 \\
+59966 & MWA & G0060 & 161.92 & 15.36 & 1 \\
+60084 & MWA & G0057 & 154.24 & 30.72 & $\le$ 1 \\
+60092 - 60093 & MeerKAT & & & & 4 \\
+60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & 18 \\
+60503 & ASKAP &  & 887.5 & 288 & 1 \\
+60572 & MWA & D0042 & 184.96 & 30.72 & 4 \\
+60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & 16 \\
+60602 & MeerKAT & & 812.8 & 495.3 & 1 \\
+\enddata
+\tablenotetext{a}{Original discovery \citep{2024MNRAS.535..909D}}
+\end{deluxetable*}
+
+\section{Analysis \& results} \label{sec:analysis}
+
+[Reference for scattering kernels:] \citep{10.1093/mnras/stw1724}.
+
+\subsection{Pulse morphology}
+
+All observed pulses consist of a single burst, approximately Gaussian in shape, with the sole exception of the MeerKAT pulse observed on 2024-10-19, for which two bursts were observed separated by ${\sim}125\,$s.
+Generally, the MWA pulses tend
+\begin{itemize}
+    \item to be wider than their higher frequency counterparts,
+    \item to exhibit an asymmetry similar to scattering, and
+    \item to be very similar in morphology to each other.
+\end{itemize}
+
+The asymmetry is consistent with a scattering time scale of a few tens of seconds at MWA frequencies, which scales to a few tens of milliseconds at 1\,GHz.
+This is in broad agreement with the model predictions of NE2001 ($\tau_{\rm sc,1 GHz} = 0.066\,$s) and YMW16 ($\tau_{\rm sc,1 GHz} = 0.075\,$s) at the source's location assuming a DM of 710\,pc\,cm$^{-3}$.
+The effect of scattering on the timing is discussed in \S\ref{sec:timing} below.
+
+\subsection{Timing solution} \label{sec:timing}
+
+%Following the positive identification of several pulses in the GPM data set, we performed a grid search of periods that would result in an integer number of pulses between two widely spaced pulses.
+%A candidate period of $P = 4186.4 \pm 0.1$ was found for which all detections fell within a narrow window of ${\sim}0.05$ of phase.
+% We further refined this by attempting to phase connect to Dougal's original pulse, and got $4186.33 \pm 0.02$ s, but this needn't be part of the story, since even the above was enough to motivate the MWA campaign that followed.
+%This motivated the follow-up MWA observations (under project code D0042) in which two consecutive pulses ${\sim}4190$ seconds apart were detected without any discernible emission between them, ruling out periods $P/n$, for $n \ge 2$.
+%The lever arm afforded by both the GPM and D0042 detections proved sufficient to phase-connect to the original pulse published by \citet{2024MNRAS.535..909D}, yielding a refined period of $P = 4186.33 \pm 0.02$~s.
+
+%We then measured times of arrival (ToAs) of individual pulses.
+%The ASKAP and MWA pulses were morphologically similar and well fit by a simple Gaussian.
+
+\subsection{Scattering}
+
+\begin{figure}[th]
+    \centering
+    \includegraphics[width=0.95\linewidth]{stacked_spectra.pdf}
+    \caption{Stacked (semi-transparent) dynamic spectra, where each rectangle indicates the observing campaign whose spectra were barycentred and folded according to the ephemeris.
+The spectra have not been dedispersed, but the cyan dashed lines indicate where the two components seen in the MeerKAT (2024) observation would appear due to dispersion.
+The white curve in the top panel is the dedispersed profile of the MeerKAT (2024) observation, and the white curves in the bottom panel are the same profile subjected to scattering with $\tau_{\rm sc} = \tau_{\rm sc,1\,GHz} (\nu/{\rm 1\,GHz})^{-4}$ at frequencies 175, 195, and 210 MHz, where $\tau_{\rm sc,1\,GHz} = 0.07\,$s.}
+    \label{fig:stacked_spectra}
+\end{figure}
+
+\begin{figure*}[pt]
+    \centering
+    \includegraphics[width=0.9\linewidth]{pulsestack.pdf}
+    \caption{Pulsestack of barycentred, dedispersed profiles from the ephemeris. The dashed red vertical line marks zero phase. Baselines have been fitted and subtracted from each lightcurve.}
+    \label{fig:pulsestack}
+\end{figure*}
+
+\subsection{Polarization} \label{sec:polarization}
+
+\section{Discussion} \label{sec:discussion}
+
+\begin{enumerate}
+    \item Why does the source appear to not be active all the time at higher frequencies?
+    \item As per convo with John (see MWA Users Slack, 2025-01-24), point out that (lack of detection of source in) MWA IPS is not very constraining in terms of scattering disk / timescale / screen.
+\end{enumerate}
+
+\section{Conclusions} \label{sec:conclusions}
 
@@
 
-[Acknowledgements go here\dots]
+% PTUSE (https://skaafrica.atlassian.net/wiki/spaces/ESDKB/pages/1591672833/User+Supplied+Equipment+USE#PTUSE)
+Observations made use of the Pulsar Timing User Supplied Equipment (PTUSE) servers at MeerKAT which were funded by the MeerTime Collaboration members ASTRON, AUT, CSIRO, ICRAR-Curtin, MPIfR, INAF, NRAO, Swinburne University of Technology, the University of Oxford, UBC and the University of Manchester.
+The system design and integration was led by Swinburne University of Technology and Auckland University of Technology in collaboration with SARAO and supported by the ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav) under grant CE170100004.
 

### 2025-04-25 dynspec/ephemeris_fits.py
Added a small script for fitting to ephemeris

@@ -1,0 +1,45 @@
+from astropy.table import QTable
+import numpy as np
+from scipy.optimize import curve_fit
+from timing import *
+
+table = QTable.read('toas.ecsv', format='ascii.ecsv')
+
+def period_model(toas_mjd, period_d, pepoch_mjd):
+    pulses, phases = np.divmod((toas_mjd - pepoch_mjd)/period_d, 1)
+    rounded_pulses = np.round(pulses)
+    predicted_toas = rounded_pulses * period_d + pepoch_mjd
+    return predicted_toas
+
+toas_mjd = table['ToA']
+toas_mjd_err = table['ToA_err']
+
+ephemeris = get_J1755_ephemeris()
+
+p0 = [ephemeris['period'].to('d').value,
+      ephemeris['PEPOCH'].mjd]
+
+popt, pcov = curve_fit(period_model, toas_mjd, toas_mjd, p0=p0)
+errs = np.sqrt(np.diag(pcov))
+print("Period-only model:")
+print(f'P            = {popt[0]*86400} ± {errs[0]*86400} s')
+print(f'PEPOCH (MJD) = {popt[1]} ± {errs[1]}')
+print()
+
+def period_and_pdot_model(toas_mjd, period_d, pepoch_mjd, fdot):
+    t = toas_mjd - pepoch_mjd
+    pulses, phases = np.divmod(fdot*t**2 + t/period_d, 1)
+    rounded_pulses = np.round(pulses)
+    predicted_toas = rounded_pulses * period_d + pepoch_mjd
+    return predicted_toas
+
+p0.append(0.0)
+popt, pcov = curve_fit(period_and_pdot_model, toas_mjd, toas_mjd, p0=p0)
+errs = np.sqrt(np.diag(pcov))
+
+print("Period and Pdot model:")
+print(f'P            = {popt[0]*86400} ± {errs[0]*86400} s')
+print(f'Fdot         = {popt[2]} ± {errs[2]} / day²')
+print(f'PEPOCH (MJD) = {popt[1]} ± {errs[1]}')
+print()
+

### 2025-04-25 paper/main.tex
Updated paper from Overleaf

@@
 \newcommand{\srcfull}{ASKAP J175534.9$-$252749.1}
+
+\DeclareMathOperator{\erfcx}{erfcx}
 
@@
   59966 & MWA & G0060 & 161.92 & 15.36 & 1 \\
-60084 & MWA & G0057 & 154.24 & 30.72 & $\le$ 1 \\
+  %60084 & MWA & G0057 & 154.24 & 30.72 & $\le$ 1 \\
   60092 - 60093 & MeerKAT & & & & 4 \\
@@
 All observed pulses consist of a single burst, approximately Gaussian in shape, with the sole exception of the MeerKAT pulse observed on 2024-10-19, for which two bursts were observed separated by ${\sim}125\,$s.
-Generally, the MWA pulses tend
+Generally, the low-frequency (MWA) pulses tend
 \begin{itemize}
@@
               \item to exhibit an asymmetry similar to scattering, and
-    \item to be very similar in morphology to each other.
+                    \item to have minimal pulse-to-pulse variation.
 \end{itemize}
 
-The asymmetry is consistent with a scattering time scale of a few tens of seconds at MWA frequencies, which scales to a few tens of milliseconds at 1\,GHz.
-This is in broad agreement with the model predictions of NE2001 ($\tau_{\rm sc,1 GHz} = 0.066\,$s) and YMW16 ($\tau_{\rm sc,1 GHz} = 0.075\,$s) at the source's location assuming a DM of 710\,pc\,cm$^{-3}$.
-The effect of scattering on the timing is discussed in \S\ref{sec:timing} below.
+The low-frequency asymmetry is consistent with a scattering time scale of a few tens of seconds at MWA frequencies, which scales to a few tens of milliseconds at 1\,GHz.
+This is in broad agreement with the model predictions of NE2001 ($\tau_{\rm sc,1GHz} = 0.066\,$s) and YMW16 ($\tau_{\rm sc,1 GHz} = 0.075\,$s) at the source's location assuming a DM of 710\,pc\,cm$^{-3}$.
+
+To account for the asymmetry, we fit exponentially modified Gaussians to each pulse with the form,
+\begin{equation}
+  \begin{aligned}
+        y(t) &= A \frac{\sigma}{\tau}\sqrt{\frac{\pi}{2}}
+                   \exp\left(-\frac12 \left( \frac{t - \mu}{\tau} \right)^2 \right) \\
+                            &\qquad \erfcx \left(\frac{1}{\sqrt{2}} \left(\frac{\sigma}{\tau} 
+                             - \frac{t - \mu}{\tau} \right) \right),
+  \end{aligned}
+  \label{eqn:emg}
+\end{equation}
+where $A$, $\mu$, and $\sigma$ are the height, location, and scale of an unscattered Gaussian pulse, and the scattering time scale was fixed at
+\begin{equation}
+      \tau = 0.07\, \left(\frac{\nu}{\rm GHz}\right)^{-4} \, {\rm s},
+\end{equation}
+according to each observation's centre frequency.
+A pulse stack containing all observed pulses and their fits is shown in Fig. \ref{fig:pulsestack}.
+
+\begin{figure*}[tp]
+      \centering
+          \includegraphics[width=0.9\linewidth]{pulsestack.pdf}
+              \caption{Pulsestack of barycentred, dedispersed profiles from the ephemeris.
+The dashed red vertical line marks zero phase.
+Baselines have been fitted and subtracted from each lightcurve.
+The blue dashed lines show (normalised) fitted Gaussians without scattering (see main text for details).}
+                  \label{fig:pulsestack}
+\end{figure*}
+
+For the MeerKAT pulse with two components, we fit only the brighter component.
 
 \subsection{Timing solution} \label{sec:timing}
+
+Because the large scattering time scale at low frequencies significantly distorts the pulse shapes, we identified the times of arrival (ToAs) with the fitted $\mu$ parameter in the fits given in Eq.
+\eqref{eqn:emg}, which represents the location of the Gaussian pulse before scattering.
+
+The distortion of the pulse shapes at MWA frequencies creates a degeneracy between DM and scattering time scales that is not easily disambiguated.
+This is demonstrated in Fig. \ref{fig:stacked_spectra}, which shows stacked MWA and MeerKAT spectra.
+Without accounting for scattering, the measured DM would significantly exceed the 710\,pc\,cm$^{-3}$ (cyan lines).
+The scattering predicted by Galactic electron density models, however, is sufficient to account for the apparent extra delay.
+
+\begin{figure}[th]
+      \centering
+          \includegraphics[width=0.95\linewidth]{stacked_spectra.pdf}
+              \caption{Stacked (semi-transparent) dynamic spectra, where each rectangle indicates the observing campaign whose spectra were barycentred and folded according to the ephemeris.
+The spectra have not been dedispersed, but the cyan dashed lines indicate where the two components seen in the MeerKAT (2024) observation would appear due to dispersion.
+The white curve in the top panel is the dedispersed profile of the MeerKAT (2024) observation, and the white curves in the bottom panel are the same profile subjected to scattering with $\tau_{\rm sc} = \tau_{\rm sc,1\,GHz} (\nu/{\rm 1\,GHz})^{-4}$ at frequencies 175, 195, and 210 MHz, where $\tau_{\rm sc,1\,GHz} = 0.07\,$s.}
+                  \label{fig:stacked_spectra}
+\end{figure}
+
+The degeneracy between DM and scattering (as well as variations in pulse width and ToA) render the lower frequency pulses less useful for measuring either DM or scattering alone.
+Breaking the degeneracy is possible in principle with a much higher S/N average profile than what is possible with the current data set.
+
+For this work, we therefore did not attempt to fit the DM or the scattering time scale individually.
+Instead, we adopted the original ASKAP measurement of ${\rm DM} = 710\,$pc\,cm$^{-3}$ and a scattering timescale of $\tau_{\rm sc,1 GHz} = 0.07\,$s for the timing analysis.
+We did, however, confirm that fits to individual pulses using Eq.
+\eqref{eqn:emg}, but also allowing the $\tau$ parameter to freely vary, produced fitted values that were broadly consistent with our chosen value.
+
+The ToAs were then fit
 
@@
 
-\subsection{Scattering}
-
-\begin{figure}[th]
-    \centering
-    \includegraphics[width=0.95\linewidth]{stacked_spectra.pdf}
-    \caption{Stacked (semi-transparent) dynamic spectra, where each rectangle indicates the observing campaign whose spectra were barycentred and folded according to the ephemeris.
-The spectra have not been dedispersed, but the cyan dashed lines indicate where the two components seen in the MeerKAT (2024) observation would appear due to dispersion.
-The white curve in the top panel is the dedispersed profile of the MeerKAT (2024) observation, and the white curves in the bottom panel are the same profile subjected to scattering with $\tau_{\rm sc} = \tau_{\rm sc,1\,GHz} (\nu/{\rm 1\,GHz})^{-4}$ at frequencies 175, 195, and 210 MHz, where $\tau_{\rm sc,1\,GHz} = 0.07\,$s.}
-    \label{fig:stacked_spectra}
-\end{figure}
-
-\begin{figure*}[pt]
-    \centering
-    \includegraphics[width=0.9\linewidth]{pulsestack.pdf}
-    \caption{Pulsestack of barycentred, dedispersed profiles from the ephemeris. The dashed red vertical line marks zero phase. Baselines have been fitted and subtracted from each lightcurve.}
-    \label{fig:pulsestack}
-\end{figure*}
-
 \subsection{Polarization} \label{sec:polarization}
@@
 \section{Discussion} \label{sec:discussion}
+
+The precursor burst seen with MeerKAT is apparently unique, and is not visible at other telescopes and frequencies, even after averaging them together to make a single profile.
+The only burst of comparable S/N, and at a similar frequency, in which the dimmer precursor component might be expected to be visible is the original 2023-01-21 ASKAP burst \citep{2024MNRAS.535..909D}, where again it is absent.
+
+The two pulses observed in January 2023 (the original ASKAP pulse and the MWA (IPS) pulse observed the following day) are significantly wider than all other pulses, suggesting that a morphological change occurred between
 

### 2025-04-26 dynspec/ephemeris_fits.py
Fixed ephemeris-fitting bugs. Now the script produces actual numbers and uncertainties

@@ -1,40 +1,46 @@
 from astropy.table import QTable
+from astropy.coordinates import SkyCoord, EarthLocation
+from astropy.time import Time
 import numpy as np
 from scipy.optimize import curve_fit
 from timing import *
 
 table = QTable.read('toas.ecsv', format='ascii.ecsv')
+ephemeris = get_J1755_ephemeris()
 
 def period_model(toas_mjd, period_d, pepoch_mjd):
-    pulses, phases = np.divmod((toas_mjd - pepoch_mjd)/period_d, 1)
-    rounded_pulses = np.round(pulses)
-    predicted_toas = rounded_pulses * period_d + pepoch_mjd
-    return predicted_toas
+    _, phases = np.divmod((toas_mjd - pepoch_mjd)/period_d + 0.5, 1)
+    return phases - 0.5
 
-toas_mjd = table['ToA']
+toas_mjd = []
+for row in table:
+
+    location = EarthLocation.of_site(row['telescope'])
+    freq = row['freq']
+    toa = Time(row['ToA'], scale='utc', format='mjd', location=location)
+    toa_bary_dd = barycentre(toa, ephemeris['coord']) - calc_dmdelay(ephemeris['DM'], freq, np.inf*u.MHz)
+    toas_mjd.append(toa_bary_dd.mjd)
+
+toas_mjd = np.array(toas_mjd)
 toas_mjd_err = table['ToA_err']
-
-ephemeris = get_J1755_ephemeris()
 
 p0 = [ephemeris['period'].to('d').value,
       ephemeris['PEPOCH'].mjd]
 
-popt, pcov = curve_fit(period_model, toas_mjd, toas_mjd, p0=p0)
+popt, pcov = curve_fit(period_model, toas_mjd, np.zeros(toas_mjd.shape), p0=p0)
 errs = np.sqrt(np.diag(pcov))
 print("Period-only model:")
-print(f'P            = {popt[0]*86400} ± {errs[0]*86400} s')
-print(f'PEPOCH (MJD) = {popt[1]} ± {errs[1]}')
+print(f'P            = {popt[0]*86400:.5f} ± {errs[0]*86400:.5f} s')
+print(f'PEPOCH (MJD) = {popt[1]:.6f} ± {errs[1]:.6f}')
 print()
 
 def period_and_pdot_model(toas_mjd, period_d, pepoch_mjd, fdot):
     t = toas_mjd - pepoch_mjd
[…]

### 2025-04-26 dynspec/ephemeris_fits.py
Included DM fitting into ephemeris fitting script as well

@@ -7,6 +7,7 @@ from timing import *
 
 table = QTable.read('toas.ecsv', format='ascii.ecsv')
 ephemeris = get_J1755_ephemeris()
+freqs = table['freq']
 
 def period_model(toas_mjd, period_d, pepoch_mjd):
     _, phases = np.divmod((toas_mjd - pepoch_mjd)/period_d + 0.5, 1)
@@ -30,8 +31,8 @@ p0 = [ephemeris['period'].to('d').value,
 popt, pcov = curve_fit(period_model, toas_mjd, np.zeros(toas_mjd.shape), p0=p0)
 errs = np.sqrt(np.diag(pcov))
 print("Period-only model:")
-print(f'P            = {popt[0]*86400:.5f} ± {errs[0]*86400:.5f} s')
-print(f'PEPOCH (MJD) = {popt[1]:.6f} ± {errs[1]:.6f}')
+print(f'  P            = {popt[0]*86400:.5f} ± {errs[0]*86400:.5f} s')
+print(f'  PEPOCH (MJD) = {popt[1]:.6f} ± {errs[1]:.6f}')
 print()
 
 def period_and_pdot_model(toas_mjd, period_d, pepoch_mjd, fdot):
@@ -44,8 +45,25 @@ popt, pcov = curve_fit(period_and_pdot_model, toas_mjd, np.zeros(toas_mjd.shape)
 errs = np.sqrt(np.diag(pcov))
 
 print("Period and Pdot model:")
-print(f'P            = {popt[0]*86400} ± {errs[0]*86400} s')
-print(f'Fdot         = {popt[2]} ± {errs[2]} / day²')
-print(f'PEPOCH (MJD) = {popt[1]} ± {errs[1]}')
+print(f'  P            = {popt[0]*86400:.5f} ± {errs[0]*86400:.5f} s')
+print(f'  Fdot         = {popt[2]} ± {errs[2]} / day²')
+print(f'  PEPOCH (MJD) = {popt[1]:.6f} ± {errs[1]:.6f}')
+print()
+
+def period_and_dm_model(toas_mjd_and_freqs, period_d, pepoch_mjd, dm):
+    toas_mjd, freqs = toas_mjd_and_freqs.T
+    t = toas_mjd - pepoch_mjd - calc_dmdelay(dm*u.pc/u.cm**3 - ephemeris['DM'], freqs*u.MHz, np.inf*u.MHz).to('d').value
[…]

### 2025-04-26 dynspec/timing.py

@@ -12,9 +12,9 @@ from mwa_pb_lookup.lookup_beam import beam_lookup_1d
 
 def get_J1755_ephemeris():
     return {
-        'PEPOCH': Time(59965.0377, scale='utc', format='mjd'),
-        'period': 4186.330 * u.s,
-        'DM': 710.0 * u.pc / u.cm**3,
+        'PEPOCH': Time(59965.037830, scale='utc', format='mjd'),
+        'period': 4186.32879 * u.s,
+        'DM': 771.0 * u.pc / u.cm**3,
         'tau_sc': 7.0e-2*u.s,
         'coord': SkyCoord("17:55:34.87 -25:27:49.1", unit=(u.hourangle, u.deg), frame='icrs'),
     }

### 2025-04-26 paper/main.tex
Updated paper with timing ephemeris table

@@
 Because the large scattering time scale at low frequencies significantly distorts the pulse shapes, we identified the times of arrival (ToAs) with the fitted $\mu$ parameter in the fits given in Eq.
-\eqref{eqn:emg}, which represents the location of the Gaussian pulse before scattering.
+\eqref{eqn:emg}, which represents the location of the assumed Gaussian pulse before scattering.
 
@@
 This is demonstrated in Fig. \ref{fig:stacked_spectra}, which shows stacked MWA and MeerKAT spectra.
-Without accounting for scattering, the measured DM would significantly exceed the 710\,pc\,cm$^{-3}$ (cyan lines).
+Without accounting for scattering, the measured DM would significantly exceed the 771\,pc\,cm$^{-3}$ (cyan lines).
 The scattering predicted by Galactic electron density models, however, is sufficient to account for the apparent extra delay.
@@
 
-The degeneracy between DM and scattering (as well as variations in pulse width and ToA) render the lower frequency pulses less useful for measuring either DM or scattering alone.
+The degeneracy between DM and scattering (as well as variations in pulse width and ToA) render the lower frequency pulses less useful for measuring either DM or scattering alone (\todo{see Appendix \dots}).
 Breaking the degeneracy is possible in principle with a much higher S/N average profile than what is possible with the current data set.
+Having said that, we note that fits of Eq.
+\eqref{eqn:emg} to the brightest MWA pulses where the scattering time scale was left as a free parameter were broadly consistent with the predictions of the NE2001 and YMW16 models.
 
-For this work, we therefore did not attempt to fit the DM or the scattering time scale individually.
-Instead, we adopted the original ASKAP measurement of ${\rm DM} = 710\,$pc\,cm$^{-3}$ and a scattering timescale of $\tau_{\rm sc,1 GHz} = 0.07\,$s for the timing analysis.
-We did, however, confirm that fits to individual pulses using Eq.
-\eqref{eqn:emg}, but also allowing the $\tau$ parameter to freely vary, produced fitted values that were broadly consistent with our chosen value.
+Because the scattering time scale could not be reliably measured for all individual pulses, we obtained ToAs by assuming a fixed scattering time of $\tau_{\rm sc,1 GHz} = 0.07\,$s.
+These ToAs were then barycentred and fit for both period and DM, resulting in the values given in Table \ref{tbl:ephemeris}.
+We also tried fitting a timing model that included a spin-down parameter, and found that it was consistent with zero spin-down to within $1\sigma$.
 
-The ToAs were then fit
+\begin{table}
+  \caption{Timing ephemeris for \src{}}
+  \label{tbl:ephemeris}
+  \begin{tabular}[lc]
+    \hline
+    Parameter & Value \\
+    \hline
+    Period (s) & $4186.3288 \pm 0.0003$ \\
+    PEPOCH (MJD) & $59965.03783 \pm 0.00003$ \\
+    DM (pc/cm$^{-3}$) & $771 \pm 27$ \\
+    \hline
+  \end{tabular}
+\end{table}
 

### 2025-04-26 dynspec/timing.py

@@ -12,9 +12,9 @@ from mwa_pb_lookup.lookup_beam import beam_lookup_1d
 
 def get_J1755_ephemeris():
     return {
-        'PEPOCH': Time(59965.037830, scale='utc', format='mjd'),
-        'period': 4186.32879 * u.s,
-        'DM': 771.0 * u.pc / u.cm**3,
+        'PEPOCH': Time(59965.037829, scale='utc', format='mjd'),
+        'period': 4186.328785 * u.s,
+        'DM': 771.5 * u.pc / u.cm**3,
         'tau_sc': 7.0e-2*u.s,
         'coord': SkyCoord("17:55:34.87 -25:27:49.1", unit=(u.hourangle, u.deg), frame='icrs'),
     }

### 2025-05-05 paper/appendix/scattered_toas.py
Finished fixing plot of excess DM

@@ -51,12 +51,25 @@ def matched_filter(ts, lag, h, μ, σ, τ):
     # we're just using this to find a root, so none of this should matter.
     return np.sum(integrand)
 
+def slope_for_logspace_data(x, y):
+    '''
+    Should only use this if x is logarithmically spaced.
+    '''
+    x0 = x[:-1]
+    x1 = x[1:]
+    x_gm = np.sqrt(x0*x1) # Geometric mean ("mid"-points of logspaced data)
+
+    y0 = y[:-1]
+    y1 = y[1:]
+    y_gm = np.sqrt(y0*y1)
+    return x_gm, y_gm/x_gm * np.log(y1/y0) / np.log(x1/x0)
+
 def main():
     parser = argparse.ArgumentParser(description='Make plots for paper appendix')
     parser.add_argument('--output_image', help='File name of output image. Supports same image formats as "plt.savefig()". If not provided, will plt.show().')
     args = parser.parse_args()
 
-    τs = np.logspace(-1, 5, 500)
+    τs = np.logspace(-3, 3, 500)
     σ = 1
     h = 1
     μ = 0
@@ -72,7 +85,7 @@ def main():
 
     LEHM_roots = np.array([root(lambda t: emg(t, h, μ, σ, τ) - 0.5*emg_mode(h, μ, σ, τ)[1], -0.1).x for τ in τs]).squeeze()
     #LEHM_roots_approx = np.array([root(lambda t: h*σ/τ*np.sqrt(π/2)*np.exp(-0.5*((t-μ)/σ)**2)*erfcx(1/np.sqrt(2)*(σ/τ - (t[0]-μ)/σ)) - 0.5*h*np.exp(-0.5*(np.sqrt(2)*erfcxinv(τ/σ*np.sqrt(2/π)) - σ/τ)**2), -0.1).x for τ in τs]).squeeze()
-    LEHM_roots_approx = np.array([root(lambda t: h*σ/τ*np.sqrt(π/2)*np.exp(-0.5*((t-μ)/σ)**2)*erfcx(1/np.sqrt(2)*(σ/τ - (t[0]-μ)/σ)) - 0.5*h*np.exp(-0.5*(np.sqrt(2)*erfcxinv(τ/σ*np.sqrt(2/π)))**2), -0.1).x for τ in τs]).squeeze()
[…]

### 2025-05-05 paper/appendix/scattered_toas.py
Touching up the plot

@@ -3,6 +3,7 @@ from scipy.optimize import root
 from scipy.special import erf, erfc
 from numpy import pi as π
 import matplotlib.pyplot as plt
+from matplotlib.gridspec import GridSpec
 from ctypes import *
 import os
 import argparse
@@ -69,7 +70,7 @@ def main():
     parser.add_argument('--output_image', help='File name of output image. Supports same image formats as "plt.savefig()". If not provided, will plt.show().')
     args = parser.parse_args()
 
-    τs = np.logspace(-3, 3, 500)
+    τs = np.logspace(-4, 4, 500)
     σ = 1
     h = 1
     μ = 0
@@ -89,7 +90,7 @@ def main():
     #LEHM_roots_approx = np.array([root(lambda t: h*σ/τ*np.sqrt(π/2)*np.exp(-0.5*((t-μ)/σ)**2)*erfcx(1/np.sqrt(2)*(σ/τ - (t[0]-μ)/σ)) - 0.5*h*np.exp(-0.5*(np.sqrt(2)*np.sqrt(np.log(τ/σ*np.sqrt(1/(2*π)))) - σ/τ)**2), -0.1).x for τ in τs]).squeeze()
     #LEHM_roots_approx = np.array([root(lambda t: h*σ/τ*np.sqrt(π/2)*np.exp(-0.5*((t-μ)/σ)**2)*erfcx(1/np.sqrt(2)*(σ/τ - (t[0]-μ)/σ)) - 0.5*h*np.exp(-0.5*(np.sqrt(2)*np.sqrt(np.log(τ/σ*np.sqrt(1/(2*π)))))**2), -0.1).x for τ in τs]).squeeze()
     IPLE_roots = np.array([root(lambda t: σ/τ + (t - μ)/σ - (σ/τ)**2*np.sqrt(π/2) * erfcx(1/np.sqrt(2)*(σ/τ - (t[0] - μ)/σ)), -0.1).x for τ in τs]).squeeze()
-    MODE_roots = np.array([emg_mode(h, μ, σ, τ)[0] for τ in τs]).squeeze()
+    PEAK_roots = np.array([emg_mode(h, μ, σ, τ)[0] for τ in τs]).squeeze()
     ts = np.linspace(-10, 10, 1000)
     MCHF_roots = np.array([root(lambda lag: matched_filter(ts, lag, h, μ, σ, τ), 1.0).x for τ in τs]).squeeze()
 
@@ -98,7 +99,7 @@ def main():
 
[…]

### 2025-05-05 dynspec/timing.py
Added another panel to appendix plot

@@ -6,7 +6,7 @@ from astropy.io import fits
 from astropy.time import Time
 from astropy.coordinates import SkyCoord, EarthLocation
 import sys
-from mwa_pb_lookup.lookup_beam import beam_lookup_1d
+#from mwa_pb_lookup.lookup_beam import beam_lookup_1d
 
 π = np.pi
 

### 2025-05-05 paper/appendix/scattered_toas.py

@@ -92,7 +92,7 @@ def main():
     IPLE_roots = np.array([root(lambda t: σ/τ + (t - μ)/σ - (σ/τ)**2*np.sqrt(π/2) * erfcx(1/np.sqrt(2)*(σ/τ - (t[0] - μ)/σ)), -0.1).x for τ in τs]).squeeze()
     PEAK_roots = np.array([emg_mode(h, μ, σ, τ)[0] for τ in τs]).squeeze()
     ts = np.linspace(-10, 10, 1000)
-    MCHF_roots = np.array([root(lambda lag: matched_filter(ts, lag, h, μ, σ, τ), 1.0).x for τ in τs]).squeeze()
+    TMPL_roots = np.array([root(lambda lag: matched_filter(ts, lag, h, μ, σ, τ), 1.0).x for τ in τs]).squeeze()
 
     # Get the rate of change per frequency (relative to the frequency at which τ=σ)
     νs = τs**-0.25
@@ -100,41 +100,48 @@ def main():
     _, LEHM_roots_slope = slope_for_logspace_data(νs, LEHM_roots)
     _, IPLE_roots_slope = slope_for_logspace_data(νs, IPLE_roots)
     _, PEAK_roots_slope = slope_for_logspace_data(νs, PEAK_roots)
-    νs_gm, MCHF_roots_slope = slope_for_logspace_data(νs, MCHF_roots)
+    νs_gm, TMPL_roots_slope = slope_for_logspace_data(νs, TMPL_roots)
 
     # Equivalent DM from above slopes. Choose ν_s = 200 MHz and σ = 1 min. Will change later as needed
     import astropy.units as u
-    σ_ref = 1 * u.min
-    ν_s = 200 * u.MHz
+    σ_ref = 25 * u.s
+    ν_s = (((70*u.ms)/σ_ref)**(0.25)*1*u.GHz).to('MHz')
+    print(f'{ν_s = }')
     D = 4148.808 * u.MHz**2 / u.pc * u.cm**3 * u.s
 
-    LEHM_DM = (0.5 * νs_gm**3 * LEHM_roots_slope * σ_ref * ν_s**2 / D).to('pc cm-3')
-    IPLE_DM = (0.5 * νs_gm**3 * IPLE_roots_slope * σ_ref * ν_s**2 / D).to('pc cm-3')
[…]

### 2025-05-05 paper/appendix/scattered_toas.py
Added final version of the appendix plot to the paper folder

@@ -202,8 +202,8 @@ def main():
     #ax3.set_ylim([-500, 500])
 
     ax0.text(0.97, 0.95, "(a)", transform=ax0.transAxes, va='top', ha='right')
-    ax1.text(0.97, 0.95, "(b)", transform=ax1.transAxes, va='top', ha='right')
-    ax2.text(0.97, 0.95, "(c)", transform=ax2.transAxes, va='top', ha='right')
+    ax1.text(0.97, 0.95, "(c)", transform=ax1.transAxes, va='top', ha='right')
+    ax2.text(0.97, 0.95, "(b)", transform=ax2.transAxes, va='top', ha='right')
     ax3.text(0.97, 0.95, "(d)", transform=ax3.transAxes, va='top', ha='right')
 
     plt.setp(ax0.get_xticklabels(), visible=False)

### 2025-05-05 paper/main.tex
Added another sentence or two to paper
Sync'ed paper with Overleaf version

@@
 \DeclareMathOperator{\erfcx}{erfcx}
+\DeclareMathOperator{\erf}{erf}
+\DeclareMathOperator{\emg}{emg}
+
+\newcommand{\deriv}[2]{\frac{{\rm d}{#1}}{{\rm d}{#2}}}
+\newcommand{\dd}[2]{\frac{{\rm d^2}{#1}}{{\rm d}{#2}^2}}
+\newcommand{\ToA}[1]{{\rm ToA}_{\rm {#1}}}
 
@@
     \item to be wider than their higher frequency counterparts,
-              \item to exhibit an asymmetry similar to scattering, and
-                    \item to have minimal pulse-to-pulse variation.
+    \item to exhibit an asymmetry resembling a scatter-broadened tail, and
+    \item to have minimal pulse-to-pulse morphological variation.
 \end{itemize}
@@
   \begin{aligned}
-        y(t) &= A \frac{\sigma}{\tau}\sqrt{\frac{\pi}{2}}
+        \emg(t) &= A \frac{\sigma}{\tau}\sqrt{\frac{\pi}{2}}
                    \exp\left(-\frac12 \left( \frac{t - \mu}{\tau} \right)^2 \right) \\
@@
 These ToAs were then barycentred and fit for both period and DM, resulting in the values given in Table \ref{tbl:ephemeris}.
+The measured DM of $771 \pm 27\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of \citetalias{2024MNRAS.535..909D}.
+
 We also tried fitting a timing model that included a spin-down parameter, and found that it was consistent with zero spin-down to within $1\sigma$.
@@
   \label{tbl:ephemeris}
-  \begin{tabular}[lc]
+  \begin{tabular}{lc}
     \hline
@@
 
-%\appendix
+\appendix
+
+It can be shown that pulses scatter-broadened by a thin screen will appear to the observer as the original pulse convolved with a one-sided exponential kernel with an associated timescale $\tau$ [CITATION].
+For intrinsically Gaussian pulses of scale $\sigma$, the result of this convolution is well described by the \textit{exponentially modified Gaussian} (EMG), as given in Eq. \eqref{eqn:emg}.
+
+In the regime $\tau \ll \sigma$, the effect of scattering is negligible and the scattered pulse resembles the original pulse.
+ToAs can be obtained in the usual way, i.e., using a matched filter ``template'' constructed from the average pulse profile.
+
+On the other hand, in the regime $\tau \gg \sigma$, the leading edge of the EMG rises sharply (resembling the error function, $\erf$) and the trailing edge resembles the exponential kernel itself.
+For this reason, pulse ToAs are typically mapped to the rising edge of highly scattered pulses, which closely approximates the centre of the original unscattered pulse.
+
+In this appendix, we discuss the effect of scattering on measuring a DM from pulse observations if scattering is not taken into account.
+As will be shown, the effect is most dramatic when $\tau \approx \sigma$, and in the case of wide, highly scattered pulses from LPTs like \src{}, can lead to a discrepant DM measurement of several hundreds of pm\,cm$^{-3}$.
+
+We consider four methods for defining ToAs:
+\begin{subequations}
+(1) the position where the leading edge reaches half-maximum (LEHM),
+\begin{equation}
+    \emg(\ToA{LEHM}) = \frac{1}{2} A\exp\left(-\frac{1}{2}\left(\frac{\mu - t_m}{\sigma}\right)^2\right),
+\end{equation}
+where
+\begin{equation*}
+    t_m = \mu - \sqrt{2}\sigma\erfcx^{-1}\left(\frac{\tau}{\sigma}\sqrt{\frac{2}{\pi}}\right) + \frac{\sigma^2}{\tau^2}
+\end{equation*}
+is the mode of the EMG,
+(2) the inflection point on the leading edge (IPLE),
+\begin{equation}
+    \left.\dd{\emg(t)}{t}\right|_{t = \ToA{IPLE}} = 0,
+\end{equation}
+(3) the position of the peak of the pulse (PEAK),
+\begin{equation}
+    \ToA{PEAK} = t_m,
+\end{equation}
+and (4) the maximum of the convolution of the pulse with a Gaussian profile with scale $\sigma$ (TMPL)
+\begin{equation}
+    \left.\deriv{}{t}\left(\emg(t) \ast \exp\left[ -\frac{1}{2} \left(\frac{t - \mu}{\sigma}\right)^2 \right]\right)\right|_{t = \ToA{TMPL}} = 0.
+\end{equation}
+The last definition is akin to template matching with a high-frequency (negligibly scattered) pulse profile.
+\end{subequations}
+
+None of the methods is entirely accurate in the presence of scattering.
+We define the errors of the ToAs to be the difference between the measured ToA and the mean of the unscattered pulse,
+\begin{equation}
+    \Delta \ToA{} \equiv \ToA{} - \mu.
+\end{equation}
+For LEHM and IPLE, the ToA is measured to be earlier than $\mu$ ($\Delta{\rm ToA} < 0$); for PEAK and TMPL, later ($\Delta{\rm ToA} > 0$).
+$\ToA{LEHM}$ and $\ToA{IPLE}$ will perform much better than $\ToA{PEAK}$ and $\ToA{TMPL}$ highly scattered pulses ($\tau \gg \sigma$), whereas the converse is true when scattering is minimal ($\tau \ll \sigma$).
+All methods, however, perform relatively poorly in the intermediate regime when $\tau \approx \sigma$.
+
+\begin{figure}[th]
+    \centering
+    \includegraphics[width=0.98\linewidth]{scattering_DM.png}
+    \caption{Analysis of DM measurement errors if scattering is not properly taken into account.
+Panel (a) shows the errors measured for each defined type of ToA, normalised to the scale of the original pulse, $\sigma$.
+In panel (b), the predicted error in DM is shown if the ToA error (compared to a high-frequency ToA measurement) is erroneously attributed to dispersion.
+Panel (c) shows the rate of change of the ToA error with frequency, and panel (d) shows the error in DM measured if this rate of change (the ``slope'' of the pulse across the observed dynamic spectrum) is erroneously attributed to dispersion.
+In panels (c) and (d), the derived DM errors assume a pulse scale of $\sigma = 25\,$s and $\nu_s = 230\,$MHz, as estimated for \src{}.
+In all panels, the blue curves indicate \emph{negative} ToA errors (i.e.
+the measured ToAs are earlier than the pulse's unscattered mean, $\mu$), and the red curves indicate positive quantities.}
+    \label{fig:scattering_DM}
+\end{figure}
+
+We computed numerically \citep[using SciPy's \texttt{root} function;][]{2020NatMe..17..261V} the errors for the four ToA types defined above, in the regime around $\tau \approx \sigma$.
+These are shown in the panel (a) of Fig. \ref{fig:scattering_DM}, normalised to the scale of the pulse, $\sigma$.
+The axis along the top shows the normalised timescale (inverted, with largest timescales on the left), while the axis along the bottom shows the equivalent frequencies normalised to $\nu_s$, defined as the frequency at which $\tau = \sigma$.
+We have assumed a scattering index of $-4$, such that
+\begin{equation}
+    \frac{\tau}{\sigma} = \left(\frac{\nu}{\nu_s}\right)^{-4}.
+\end{equation}
+
+A set of ToAs may be converted to DM measurements in two ways: (1) by comparing the ToAs to those measured at much higher frequencies (e.g.
+with TMPL) where the scattering is known to be negligible, and (2) by measuring the slope of the pulse in the dynamic spectrum (for example, by measuring the ToAs in subbands across the observed frequency range).
+Panel (c) of Fig. \ref{fig:scattering_DM} shows the expected slope measurements for the ToA errors given in the panel (a).
+
+In the first case, the ToA error of a pulse measured at frequency $\nu$, if attributed erroneously to the effect of dispersion, will yield a discrepant DM of
+\begin{equation}
+    \Delta{\rm DM}_{\rm hi-freq} \approx \frac{\Delta\ToA{}\,\nu^2}{\mathcal{D}}.
+\end{equation}
+For the specific case of \src{}, for which we estimate $\sigma = 25\,$s and $\nu_s = 230\,$MHz, consistent with $\tau_{\rm sc,1 GHz} = 70\,$ms, the DM error can be as high as a few hundreds of pc\,cm$^{-3}$.
+When using this DM method, it is better to use LEHM or IPLE at frequencies $\nu \lesssim \nu_s$, and PEAK or TMPL for $\nu \gtrsim \nu_s$; however, it should be remembered that LRHM and IPLE will \emph{underestimate} the DM, while PEAK and TMPL will \emph{overestimate} it.
+All ToA definitions produce sizeable DM errors in the approximate range $\nu_s \lesssim \nu \lesssim 3\nu_s$.
+
+The situation is not much improved for DMs determined via the slope of the pulse across the observed band, for which the scattering-induced slope is mapped to an (erroneous) equivalent DM measurement of
+\begin{equation}
+    \Delta{\rm DM}_{\rm in-band} \approx \deriv{{\rm ToA}}{\nu} \frac{\nu^3}{2\mathcal{D}}
+\end{equation}
+The calculated numbers for \src{} are illustrated in panel (d).
+For this case, LEHM and IPLE are always preferred to PEAK and TMPL, but the magnitude of the derived DM error is still in the hundreds of pc\,cm$^{-3}$ at frequencies in the range $\nu_s \lesssim \nu \lesssim 3\nu_s$.
+
+We confirm the order of magnitude of the above results by reporting a measured in-band DM for one of the MWA pulses at 185\,MHz, using the TMPL method to measure ToAs in 1.28\,MHz subbands from ${\sim}170$ to ${\sim}200\,$MHz, of ${\rm DM}_{\rm in-band} = 1221\pm257\,$pc\,cm$^{-3}$.
+This exceeds the DM reported in this work by ${\sim}450\,$pc\,cm$^{-3}$, in excess of the prediction shown in panel (d), but consistent within measurement errors.
 

### 2025-05-06 dynspec/pulsestack_all.py
Updated pulsestack plot with cosmetic changes

@@ -27,7 +27,7 @@ def main():
 
     ephemeris = get_J1755_ephemeris()
 
-    fig, axs = plt.subplots(ncols=args.ncols, figsize=(4*args.ncols+1.5,10), squeeze=False)
+    fig, axs = plt.subplots(ncols=args.ncols, figsize=(4*args.ncols+1.5,12), squeeze=False)
     yticks = [[] for i in range(args.ncols)]
     ylabels = [[] for i in range(args.ncols)]
     #cmap = colormaps[args.colormap]
@@ -99,11 +99,11 @@ def main():
             phases = phases[mask]
             lightcurve = lightcurve[mask]
 
-        axs[0][col].plot(phases*ephemeris['period'], lightcurve/np.nanmax(lightcurve) + ys[col], 'k')
+        axs[0][col].plot(phases*ephemeris['period'], 0.9*lightcurve/np.nanmax(lightcurve) + ys[col], 'k', lw=0.5, alpha=0.5)
         ph_fine = np.linspace(phases[0], phases[-1], 1000)
         y = pulse_model(ph_fine, A, μ, 0, 0, σ)
         ynorm = y / np.nanmax(y)
-        axs[0][col].plot(ph_fine*ephemeris['period'], ynorm + ys[col], 'b--')
+        axs[0][col].plot(ph_fine*ephemeris['period'], 0.9*ynorm + ys[col], 'b--')
         yticks[col].append(ys[col])
         ylabels[col].append(f"{times[0].iso[:16]}\n{dat['TELESCOPE']}")#\n(Pulse #{int(np.round(np.median(pulses)))})")
         ys[col] += 1
@@ -114,9 +114,9 @@ def main():
         axs[0][col].set_xlabel("Time (s)")
         if args.xlim:
             axs[0][col].set_xlim(args.xlim)
-        axs[0][col].set_ylim([-1, ys[col]+1])
+        axs[0][col].set_ylim([-0.5, ys[col]+0.5])
         axs[0][col].axvline(0, ls='--', alpha=0.5, c='r', zorder=-100)
-    axs[0][0].set_ylabel("ObsID")
+    axs[0][0].set_ylabel("Observation start time (UTC)")
 
     if args.grid:
         plt.grid(axis='x')

### 2025-05-07 paper/appendix/scattered_toas.py
Trying to do a taylor expansion in the tau = sigma regime

@@ -142,6 +142,11 @@ def main():
     ax0.plot(νs, np.abs(IPLE_roots), **plot_styles['IPLE'])
     ax0.plot(νs, np.abs(PEAK_roots), **plot_styles['PEAK'])
     ax0.plot(νs, np.abs(TMPL_roots), **plot_styles['TMPL'])
+    #ax0.plot(νs, τs, 'k')
+    #ax0.plot(νs, np.sqrt(np.log(τs**2/2/π)) + 1/τs, 'g')
+    ax0.plot(νs, np.exp(0.253314137315500*np.log(τs) + 0.110222420968151*np.log(τs)**2), 'g')
+    #print(f'{erfcxinv(1) = }')
+    #print(f'{erfcx(0) = }')
     #ax0.plot(τs, np.full(τs.shape, np.sqrt(2*np.log(2))), 'k--', alpha=0.2, label="expected max deviation")
     #ax0.plot(τs, -(np.arctan(np.log(τs)) - π/2)*np.sqrt(2*np.log(2))/π, label="sandbox function (arctan)")
     #ax0.plot(τs, 1/(τs + 1)*np.sqrt(2*np.log(2)), label="sandbox function (logistic)")
@@ -162,6 +167,7 @@ def main():
 
     ax0.set_xscale('log')
     ax0.set_yscale('log')
+    ax0.set_ylim([1e-5, 1e2])
     #ax0.set_xlim([1e-4, 1e4])
     #ax0.set_xlabel("$\\tau/\\sigma$")
     ax0.set_ylabel("$\\dfrac{|\\Delta{\\rm ToA}|}{\\sigma}$")

### 2025-05-07 paper/appendix/scattered_toas.py
Working on yet another taylor expansion

@@ -144,8 +144,9 @@ def main():
     ax0.plot(νs, np.abs(TMPL_roots), **plot_styles['TMPL'])
     #ax0.plot(νs, τs, 'k')
     #ax0.plot(νs, np.sqrt(np.log(τs**2/2/π)) + 1/τs, 'g')
-    ax0.plot(νs, np.exp(0.253314137315500*np.log(τs) + 0.110222420968151*np.log(τs)**2), 'g')
-    #print(f'{erfcxinv(1) = }')
+    ax0.plot(νs, np.exp(-0.360440368132497 + 0.206684133125372*np.log(τs) + 0.185148765236309*np.log(τs)**2), 'g')
+    print(f'{erfcxinv(np.sqrt(2/π)) = }')
+    print(f'{emg_mode(h, μ, σ, 1)[0] = }')
     #print(f'{erfcx(0) = }')
     #ax0.plot(τs, np.full(τs.shape, np.sqrt(2*np.log(2))), 'k--', alpha=0.2, label="expected max deviation")
     #ax0.plot(τs, -(np.arctan(np.log(τs)) - π/2)*np.sqrt(2*np.log(2))/π, label="sandbox function (arctan)")

### 2025-05-07 paper/appendix/scattered_toas.py
For now, giving up on trying to get a good taylor expansion

@@ -70,7 +70,7 @@ def main():
     parser.add_argument('--output_image', help='File name of output image. Supports same image formats as "plt.savefig()". If not provided, will plt.show().')
     args = parser.parse_args()
 
-    τs = np.logspace(-4, 4, 500)
+    τs = np.logspace(-4, 4, 501)
     σ = 1
     h = 1
     μ = 0
@@ -96,11 +96,17 @@ def main():
 
     # Get the rate of change per frequency (relative to the frequency at which τ=σ)
     νs = τs**-0.25
+    τs_gm = np.sqrt(τs[1:]*τs[:-1])
+    one_idx = len(τs)//2
 
     _, LEHM_roots_slope = slope_for_logspace_data(νs, LEHM_roots)
     _, IPLE_roots_slope = slope_for_logspace_data(νs, IPLE_roots)
     _, PEAK_roots_slope = slope_for_logspace_data(νs, PEAK_roots)
     νs_gm, TMPL_roots_slope = slope_for_logspace_data(νs, TMPL_roots)
+
+    print(f'{τs_gm[one_idx] = }')
+    print(f'{np.log(PEAK_roots[one_idx]/PEAK_roots[one_idx-1])/np.log(τs[one_idx]/τs[one_idx-1]) = }')
+    print(f'{np.log(PEAK_roots_slope[one_idx]/PEAK_roots_slope[one_idx-1])/np.log(τs[one_idx]/τs[one_idx-1]) = }')
 
     # Equivalent DM from above slopes. Choose ν_s = 200 MHz and σ = 1 min. Will change later as needed
     import astropy.units as u
@@ -144,9 +150,12 @@ def main():
     ax0.plot(νs, np.abs(TMPL_roots), **plot_styles['TMPL'])
     #ax0.plot(νs, τs, 'k')
     #ax0.plot(νs, np.sqrt(np.log(τs**2/2/π)) + 1/τs, 'g')
-    ax0.plot(νs, np.exp(-0.360440368132497 + 0.206684133125372*np.log(τs) + 0.185148765236309*np.log(τs)**2), 'g')
-    print(f'{erfcxinv(np.sqrt(2/π)) = }')
-    print(f'{emg_mode(h, μ, σ, 1)[0] = }')
+    #A = 0.983609933711519
+    #B = -0.624608147601429
+    #C = -1.13780849255619
[…]

### 2025-05-07 dynspec/timing.py
Did pb correction for 1402931808

@@ -6,7 +6,7 @@ from astropy.io import fits
 from astropy.time import Time
 from astropy.coordinates import SkyCoord, EarthLocation
 import sys
-#from mwa_pb_lookup.lookup_beam import beam_lookup_1d
+from mwa_pb_lookup.lookup_beam import beam_lookup_1d
 
 π = np.pi
 

### 2025-05-07 dynspec/make_toa_table.py
Added a short script for generating the ToA table from the toas.ecsv file

@@ -1,0 +1,32 @@
+import argparse
+import numpy as np
+from astropy.table import QTable
+
+def main():
+    parser = argparse.ArgumentParser(description="Construct a LaTeX table from ToA data (default=toas.ecsv) and print to stdout")
+    parser.add_argument('--toas_file', default="toas.ecsv", help="Choose a different input file from the default 'toas.ecsv")
+
+    args = parser.parse_args()
+
+    table = QTable.read(args.toas_file)
+
+    print("Telescope & Freq & ToA & Fluence & $\\sigma$ \\\\")
+    print(" & (MHz) & (MJD) & ($\\times 10^3\\,$Jy\\,s) & (s) \\\\")
+    for row in table:
+        toa_err = row['ToA_err']
+        toa_precision = int(np.floor(-np.log10(toa_err.to('d').value))) + 1
+        toa_str = f"{row['ToA']:.{toa_precision+1}f}({int(np.round(row['ToA_err'].to('d').value*10**(toa_precision+1))):02.0f})"
+
+        fluence_err = row['fluence_err']
+        fluence_precision = int(np.floor(-np.log10(fluence_err.to('Jy s').value/1e3))) + 1
+        fluence_str = f"{row['fluence'].to('Jy s').value/1e3:.{fluence_precision}f}({int(np.round(fluence_err.to('Jy s').value*10**(fluence_precision-3))):.0f})"
+        
+        width = row['width']
+        width_err = row['width_err']
+        width_precision = int(np.floor(-np.log10(width_err.to('s').value))) + 1
+        width_str = f"{width.to('s').value:.{width_precision}f}({int(np.round(width_err.to('s').value*10**(width_precision))):.0f})"
+
+        print(f"{row['telescope']} & {row['freq'].to('MHz').value:.0f} & {toa_str} & {fluence_str} & {width_str}")
+
+if __name__ == '__main__':
+    main()

### 2025-05-07 paper/main.tex
Synched paper with Overleaf version

@@
    ASKAP J193505.1+214841.0   & 53.8 & \citet{2024NatAs...8.1159C} \\
-   ASKAP J175534.9-252749.1   & 69.8 & \citet{2024MNRAS.535..909D} \\
+   ASKAP J175534.9-252749.1   & 69.8 & \citetalias{2024MNRAS.535..909D} \\
    GCRT J1745-3009            & 77.0 & \citet{2005Natur.434...50H} \\
@@
   \enddata
-  \tablenotetext{a}{Original discovery \citep{2024MNRAS.535..909D}}
+  \tablenotetext{a}{Original discovery \citepalias{2024MNRAS.535..909D}}
 \end{deluxetable*}
@@
 The low-frequency asymmetry is consistent with a scattering time scale of a few tens of seconds at MWA frequencies, which scales to a few tens of milliseconds at 1\,GHz.
-This is in broad agreement with the model predictions of NE2001 ($\tau_{\rm sc,1GHz} = 0.066\,$s) and YMW16 ($\tau_{\rm sc,1 GHz} = 0.075\,$s) at the source's location assuming a DM of 710\,pc\,cm$^{-3}$.
+This is in broad agreement with the model predictions of NE2001 ($\tau_{\rm sc,1GHz} = 0.066\,$s) and YMW16 ($\tau_{\rm sc,1 GHz} = 0.075\,$s) at the source's location assuming the DM value of 710\,pc\,cm$^{-3}$ reported in \citepalias{2024MNRAS.535..909D}.
 
@@
 \begin{equation}
-      \tau = 0.07\, \left(\frac{\nu}{\rm GHz}\right)^{-4} \, {\rm s},
+      \tau(\nu) = 0.07\, \left(\frac{\nu}{\rm GHz}\right)^{-4} \, {\rm s},
 \end{equation}
@@
       \centering
-          \includegraphics[width=0.9\linewidth]{pulsestack.pdf}
+          \includegraphics[width=0.95\linewidth]{pulsestack.pdf}
               \caption{Pulsestack of barycentred, dedispersed profiles from the ephemeris.
@@
 
-Because the large scattering time scale at low frequencies significantly distorts the pulse shapes, we identified the times of arrival (ToAs) with the fitted $\mu$ parameter in the fits given in Eq.
-\eqref{eqn:emg}, which represents the location of the assumed Gaussian pulse before scattering.
+Because the large scattering time scale at low frequencies significantly distorts the pulse shapes, common methods for defining ToAs can potentially result in systematic errors of up to tens of seconds, as discussed in detail in Appendix \ref{app:scattering_dm}.
+These systematic errors set up a degeneracy between DM and scattering time scales that is not easily disambiguated.
 
-The distortion of the pulse shapes at MWA frequencies creates a degeneracy between DM and scattering time scales that is not easily disambiguated.
 This is demonstrated in Fig. \ref{fig:stacked_spectra}, which shows stacked MWA and MeerKAT spectra.
-Without accounting for scattering, the measured DM would significantly exceed the 771\,pc\,cm$^{-3}$ (cyan lines).
-The scattering predicted by Galactic electron density models, however, is sufficient to account for the apparent extra delay.
+The cyan lines show the expected ToAs across the whole observed frequency range if one assumes only a DM measured at higher frequencies, where scattering is negligible.
+The scattering predicted by Galactic electron density models, however, is sufficient to account for the apparent extra delay, as is evidenced by the relatively good agreement with the modelled unscattered pulses with the expected ToAs derived from the ephemeris, illustrated in the pulsestack shown in Fig.
+\ref{fig:pulsestack}.
 
@@
 
-The degeneracy between DM and scattering (as well as variations in pulse width and ToA) render the lower frequency pulses less useful for measuring either DM or scattering alone (\todo{see Appendix \dots}).
-Breaking the degeneracy is possible in principle with a much higher S/N average profile than what is possible with the current data set.
-Having said that, we note that fits of Eq.
-\eqref{eqn:emg} to the brightest MWA pulses where the scattering time scale was left as a free parameter were broadly consistent with the predictions of the NE2001 and YMW16 models.
+We therefore identified the times of arrival (ToAs) with the $\mu$ parameter in the fits given in Eq. \eqref{eqn:emg}, which represents the location of the assumed Gaussian pulse before scattering.
+Because the scattering time scale could not be reliably measured for all individual pulses, we obtained ToAs by assuming a fixed scattering time of $\tau_{\rm sc,1 GHz} = 0.07\,$s.
+The pulse parameters from these fits, including their ToAs are given in Table \ref{tbl:toas}.
 
-Because the scattering time scale could not be reliably measured for all individual pulses, we obtained ToAs by assuming a fixed scattering time of $\tau_{\rm sc,1 GHz} = 0.07\,$s.
+\begin{deluxetable*}{ccccc}
+  \tablecaption{Times of arrival and pulse properties\label{tbl:toas}}
+  \tablehead{
+    \colhead{Telescope} & \colhead{$\nu$} & \colhead{ToA} & \colhead{Fluence} & \colhead{$\sigma$} \\
+    & \colhead{(MHz)} & \colhead{(MJD)} & \colhead{($10^3$\,Jy\,s)} & \colhead{(s)}
+  }
+  \startdata
+ASKAP & 1032 & 59965.0425644(45) & 1.03(4) & 29.4(5) \\
+MWA & 170 & 59966.061584(40) & 31.7(7) & 40(7) \\
+MeerKAT & 1284 & 60092.899547(10) & - & 13(1) \\
+MeerKAT & 1284 & 60092.947978(10) & - & 11(1) \\
+MeerKAT & 1284 & 60092.996463(10) & - & 15(1) \\
+MeerKAT & 1284 & 60093.044917(12) & - & 17(1) \\
+MWA & 200 & 60481.637466(65) & 3.0(2) & 24(8) \\
+MWA & 200 & 60485.658977(33) & 1.18(7) & 16(4) \\
+MWA & 200 & 60489.632266(20) & 1.65(6) & 14(2) \\
+MWA & 200 & 60492.588020(24) & 3.12(9) & 14(3) \\
+MWA & 200 & 60496.609639(18) & 2.87(8) & 17(2) \\
+MWA & 200 & 60503.587085(14) & 3.40(8) & 17(2) \\
+ASKAP & 1032 & 60503.634781(17) & 0.13(2) & 15(2) \\
+MWA & 200 & 60506.542809(33) & 1.35(6) & 9(4) \\
+MWA & 200 & 60510.564531(11) & 3.08(7) & 16(1) \\
+MWA & 200 & 60519.528812(29) & 3.1(1) & 14(4) \\
+MWA & 200 & 60522.533028(16) & 3.50(8) & 18(2) \\
+MWA & 200 & 60527.524033(14) & 2.89(7) & 16(2) \\
+MWA & 200 & 60530.528339(16) & 2.90(8) & 17(2) \\
+MWA & 200 & 60537.506042(13) & 3.91(9) & 17(2) \\
+MWA & 200 & 60541.479448(47) & 1.48(9) & 14(5) \\
+MWA & 200 & 60544.483761(15) & 3.91(9) & 20(2) \\
+MWA & 200 & 60551.461625(16) & 3.35(8) & 16(2) \\
+MWA & 185 & 60572.395455(15) & 2.86(7) & 15(2) \\
+MWA & 185 & 60572.443943(21) & 3.01(8) & 16(2) \\
+MWA & 185 & 60572.540824(18) & 2.57(8) & 16(2) \\
+MWA & 185 & 60572.589281(31) & 4.3(2) & 21(4) \\
+MWA & 200 & 60592.456765(27) & 1.63(8) & 19(3) \\
+MWA & 200 & 60592.505159(33) & 1.67(9) & 19(4) \\
+MWA & 200 & 60593.474369(26) & 1.08(6) & 15(3) \\
+MWA & 200 & 60593.522901(46) & 1.3(1) & 19(5) \\
+MWA & 200 & 60594.443484(20) & 1.94(8) & 18(2) \\
+MWA & 200 & 60594.491990(33) & 0.55(5) & 12(4) \\
+MWA & 200 & 60595.461118(29) & 1.53(8) & 19(3) \\
+MWA & 200 & 60595.509617(25) & 0.89(5) & 13(3) \\
+MWA & 200 & 60596.430282(20) & 1.55(7) & 16(2) \\
+MWA & 200 & 60596.478721(23) & 1.65(7) & 17(3) \\
+MWA & 200 & 60597.447846(41) & 0.86(7) & 16(5) \\
+MWA & 200 & 60597.496319(30) & 1.82(9) & 19(3) \\
+MWA & 200 & 60599.434635(17) & 1.28(5) & 13(2) \\
+MWA & 200 & 60599.483121(24) & 1.00(5) & 13(3) \\
+MWA & 200 & 60600.500655(31) & 1.24(7) & 16(4) \\
+MWA & 200 & 60602.438964(32) & 1.9(1) & 21(4) \\
+MWA & 200 & 60602.487394(27) & 1.98(9) & 20(3) \\
+MeerKAT & 813 & 60602.5835731(40) & 0.061(7) & 14.9(4)
+  \enddata
+\end{deluxetable*}
+
 These ToAs were then barycentred and fit for both period and DM, resulting in the values given in Table \ref{tbl:ephemeris}.
-The measured DM of $771 \pm 27\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of \citetalias{2024MNRAS.535..909D}.
-
-We also tried fitting a timing model that included a spin-down parameter, and found that it was consistent with zero spin-down to within $1\sigma$.
+We also tried fitting a timing model that included a spin-down parameter, and found that it was consistent with zero spin-down to within $1\sigma$, and so is not included in the ephemeris.
 
@@
   \begin{tabular}{lc}
-    \hline
+    \tableline
     Parameter & Value \\
-    \hline
+    \tableline
     Period (s) & $4186.3288 \pm 0.0003$ \\
@@
     DM (pc/cm$^{-3}$) & $771 \pm 27$ \\
-    \hline
+    $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$\tablenotemark{a} \\
+    \tableline
   \end{tabular}
+ \tablenotetext{a}{Assumed value, degenerate with DM (see main text).}
 \end{table}
+
+The measured DM of $771 \pm 27\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of $710^{+200}_{-180}\,{\rm pc}\,{\rm cm}^{-3}$ given in \citetalias{2024MNRAS.535..909D}.
+Because we have not attempted to simultaneously fit for both DM and scattering timescale, there will remain some small systematic error on this reported DM measurement.
+Breaking the degeneracy is possible in principle with a much higher S/N average profile than what is possible with the current data set.
+
+For planning observations of \src{} at low ($\lesssim 300 MHz$), care should be taken to incorporate scattering into the predicted ToAs.
+The $N$th pulse since PEPOCH is predicted to arrive at the Solar System barycentre at
+\begin{equation}
+    {\rm MJD} = {\rm PEPOCH} + NP + \Delta t_{\rm DM}(\nu) + \Delta t_{\rm sc}(\nu),
+\end{equation}
+where PEPOCH and the period, $P$, are given in Table \ref{tbl:ephemeris},
+\begin{equation}
+    \Delta t_{\rm DM}(\nu) = 4148\,{\rm s} \, \left(\frac{\rm DM}{{\rm pc\,cm}^{-3}}\right) \left(\frac{\nu}{\rm MHz}\right)^{-2}
+\end{equation}
+is the usual dispersion attributed to the interstellar medium, and
+\begin{equation}
+    \Delta t_{\rm sc}(\nu) = -\sqrt{2}\sigma\erfcx^{-1}\left(\frac{\tau(\nu)}{\sigma}\sqrt{\frac{2}{\pi}}\right) + \frac{\sigma^2}{\tau(\nu)}
+    \label{eqn:scattering_delay}
+\end{equation}
+is the amount that the \emph{peak} of the observed pulse is delayed by scattering.
+When calculating this quantity, we recommend using $\sigma = 15\,$s, a typical value for low-frequency pulses (see Table \ref{tbl:ephemeris}).
+At frequencies above $300\,$MHz, $\tau(\nu) \ll \sigma$, and the delay due to scattering, which asymptotically behaves like $\Delta t_{\rm sc}(\nu) \sim \tau$, can be safely neglected.
+At frequencies below $150\,$MHz, the asymptotic behaviour
+\begin{equation}
+    \Delta t_{\rm sc}(\nu) \sim \sigma \sqrt{\ln \left(\frac{\tau^2}{2\pi \sigma^2}\right)} + \frac{\sigma^2}{\tau}
+\end{equation}
+is accurate to within a few seconds.
+At intermediate frequencies, Eq. \eqref{eqn:scattering_delay} should be used directly.
 
@@
 %This motivated the follow-up MWA observations (under project code D0042) in which two consecutive pulses ${\sim}4190$ seconds apart were detected without any discernible emission between them, ruling out periods $P/n$, for $n \ge 2$.
-%The lever arm afforded by both the GPM and D0042 detections proved sufficient to phase-connect to the original pulse published by \citet{2024MNRAS.535..909D}, yielding a refined period of $P = 4186.33 \pm 0.02$~s.
+%The lever arm afforded by both the GPM and D0042 detections proved sufficient to phase-connect to the original pulse published by \citetalias{2024MNRAS.535..909D}, yielding a refined period of $P = 4186.33 \pm 0.02$~s.
 
@@
 The precursor burst seen with MeerKAT is apparently unique, and is not visible at other telescopes and frequencies, even after averaging them together to make a single profile.
-The only burst of comparable S/N, and at a similar frequency, in which the dimmer precursor component might be expected to be visible is the original 2023-01-21 ASKAP burst \citep{2024MNRAS.535..909D}, where again it is absent.
+The only burst of comparable S/N, and at a similar frequency, in which the dimmer precursor component might be expected to be visible is the original 2023-01-21 ASKAP burst \citepalias{2024MNRAS.535..909D}, where again it is absent.
 
@@
 \appendix
+
+\section{The effect of scattering on timing}
+\label{app:scattering_dm}
 

### 2025-05-07 dynspec/make_toa_table.py

@@ -26,7 +26,7 @@ def main():
         width_precision = int(np.floor(-np.log10(width_err.to('s').value))) + 1
         width_str = f"{width.to('s').value:.{width_precision}f}({int(np.round(width_err.to('s').value*10**(width_precision))):.0f})"
 
-        print(f"{row['telescope']} & {row['freq'].to('MHz').value:.0f} & {toa_str} & {fluence_str} & {width_str}")
+        print(f"{row['telescope']} & {row['freq'].to('MHz').value:.0f} & {toa_str} & {fluence_str} & {width_str} \\\\")
 
 if __name__ == '__main__':
     main()

### 2025-05-08 dynspec/calc_pb_corr.py
Tidied up pip requirements and imports a bit

@@ -1,6 +1,7 @@
 import numpy as np
 import pickle
 import argparse
+from mwa_pb_lookup.lookup_beam import beam_lookup_1d
 from astropy.io import fits
 from timing import *
 

### 2025-05-08 dynspec/timing.py

@@ -6,7 +6,6 @@ from astropy.io import fits
 from astropy.time import Time
 from astropy.coordinates import SkyCoord, EarthLocation
 import sys
-from mwa_pb_lookup.lookup_beam import beam_lookup_1d
 
 π = np.pi
 

### 2025-05-08 dynspec/make_toa_plots.py
Working on a plot for pulse properties

@@ -1,0 +1,91 @@
+import argparse
+import numpy as np
+import matplotlib.pyplot as plt
+from astropy.table import QTable
+from astropy.time import Time
+from astropy.coordinates import EarthLocation
+from timing import *
+from brokenaxes import brokenaxes
+
+def main():
+    parser = argparse.ArgumentParser(description="Construct a LaTeX table from ToA data (default=toas.ecsv) and print to stdout")
+    parser.add_argument('--toas_file', default="toas.ecsv", help="Choose a different input file from the default 'toas.ecsv")
+    parser.add_argument('--output_plot', default="toa_details.pdf", help="Set output plot filename (default='toa_details.pdf')")
+
+    args = parser.parse_args()
+
+    # Load the table
+    table = QTable.read(args.toas_file)
+
+    # Calculate timing residuals
+    ephem = get_J1755_ephemeris()
+    freq = table['freq']
+    locations = [EarthLocation.of_site(table['telescope'][i]) for i in range(len(table['ToA']))]
+    toas = Time([Time(table['ToA'][i], scale='utc', format='mjd', location=locations[i]) for i in range(len(table['ToA']))])
+    bary_toas = barycentre(toas, ephem['coord'])
+    bary_toas_dd = bary_toas - calc_dmdelay(ephem['DM'], freq, np.inf)
+    pulses, phases = fold(bary_toas_dd, ephem['period'], ephem['PEPOCH'])
+
+    # Set the 2023 MeerKAT fluences to None --- we don't trust them!
+    mask = (table['telescope'] == 'MeerKAT') & (np.array([d.isocalendar().year for d in toas.to_datetime()]) == 2023)
+    for row_number in np.where(mask)[0]:
+        table[row_number]['fluence'] = np.nan
+
+    # Make plots
+    nrows = 3
+    ncols = 3
+    width_ratios = [1, 3, 5]
+    fig, axs = plt.subplots(nrows=nrows, ncols=ncols, sharex='col', sharey='row',
+                            gridspec_kw={'width_ratios': [0.1, 0.1, 0.8], 'wspace': 0.05, 'hspace': 0},
+                            figsize=(10,10))
+    toa_row, fluence_row, width_row = 0, 1, 2
+
+    point_fmt = {'fmt': 'o', 'ls': 'none', 'capsize': 4, 'markersize': 2}
+    for col in range(ncols):
[…]

### 2025-05-08 dynspec/make_toa_plots.py
Still working on my pulse properties plot. WIP

@@ -34,17 +34,26 @@ def main():
     # Make plots
     nrows = 3
     ncols = 3
-    width_ratios = [1, 3, 5]
+    width_ratios = [1, 1, 8]
     fig, axs = plt.subplots(nrows=nrows, ncols=ncols, sharex='col', sharey='row',
-                            gridspec_kw={'width_ratios': [0.1, 0.1, 0.8], 'wspace': 0.05, 'hspace': 0},
+                            gridspec_kw={'width_ratios': width_ratios, 'wspace': 0.03, 'hspace': 0},
                             figsize=(10,10))
     toa_row, fluence_row, width_row = 0, 1, 2
 
-    point_fmt = {'fmt': 'o', 'ls': 'none', 'capsize': 4, 'markersize': 2}
+    # Colormap setup
+    cmap = plt.cm.viridis
+    norm = plt.Normalize(freq.min().value, freq.max().value)
+    print(norm)
+
     for col in range(ncols):
-        axs[fluence_row, col].errorbar(table['ToA'], table['fluence'], yerr=table['fluence_err'], **point_fmt)
-        axs[width_row, col].errorbar(table['ToA'], table['width'], yerr=table['width_err'], **point_fmt)
-        axs[toa_row, col].errorbar(table['ToA'], phases*ephem['period'].to('s'), yerr=table['ToA_err'].to('s'), **point_fmt)
+        for i in range(len(table['ToA'])):
+            color = cmap(norm(i))
+            point_fmt = {'fmt': 'o', 'ls': 'none', 'capsize': 4, 'markersize': 2, 'color': color, 'ecolor': color}
+            axs[fluence_row, col].errorbar(table['ToA'][i], table['fluence'][i], yerr=table['fluence_err'][i], **point_fmt)
+            axs[width_row, col].errorbar(table['ToA'][i], table['width'][i], yerr=table['width_err'][i], **point_fmt)
+            axs[toa_row, col].errorbar(table['ToA'][i], phases[i]*ephem['period'].to('s'), yerr=table['ToA_err'][i].to('s'), **point_fmt)
+        axs[toa_row, col].axhline(0, ls='--', color='k', alpha=0.2)
+
     axs[fluence_row, 0].set_ylabel(f"Fluence ({table['fluence'].unit})")
     axs[width_row, 0].set_ylabel(f"$\\sigma$ ({table['width'].unit})")
     axs[toa_row, 0].set_ylabel(f"Timing residual (s)")
[…]

### 2025-05-08 dynspec/make_toa_plots.py
Still just fiddling with the pulse properties plot look/feel. WIP

@@ -1,6 +1,7 @@
 import argparse
 import numpy as np
 import matplotlib.pyplot as plt
+from matplotlib.colors import PowerNorm
 from astropy.table import QTable
 from astropy.time import Time
 from astropy.coordinates import EarthLocation
@@ -41,13 +42,12 @@ def main():
     toa_row, fluence_row, width_row = 0, 1, 2
 
     # Colormap setup
-    cmap = plt.cm.viridis
-    norm = plt.Normalize(freq.min().value, freq.max().value)
-    print(norm)
+    cmap = plt.cm.rainbow_r
+    norm = PowerNorm(0.3, freq.min().value, 1400)
 
     for col in range(ncols):
         for i in range(len(table['ToA'])):
-            color = cmap(norm(i))
+            color = cmap(norm(freq[i].value))
             point_fmt = {'fmt': 'o', 'ls': 'none', 'capsize': 4, 'markersize': 2, 'color': color, 'ecolor': color}
             axs[fluence_row, col].errorbar(table['ToA'][i], table['fluence'][i], yerr=table['fluence_err'][i], **point_fmt)
             axs[width_row, col].errorbar(table['ToA'][i], table['width'][i], yerr=table['width_err'][i], **point_fmt)
@@ -99,6 +99,13 @@ def main():
     axs[0, 0].set_xlim([59964, 59967])
     axs[0, 1].set_xlim([60092.85, 60093.1])
     axs[0, 2].set_xlim([60475, 60610])
+
+    # Add colorbar manually
+    from matplotlib.cm import ScalarMappable
+    sm = ScalarMappable(cmap=cmap, norm=norm)
+    sm.set_array([])
+    cbar = fig.colorbar(sm, ax=axs[:, -1])
+    cbar.set_label(f'Frequency ({freq.unit})')
 
     plt.tight_layout()
     plt.savefig(args.output_plot)

### 2025-05-08 dynspec/make_toa_plots.py
Getting plots more or less in shape

@@ -37,13 +37,13 @@ def main():
     ncols = 3
     width_ratios = [1, 1, 8]
     fig, axs = plt.subplots(nrows=nrows, ncols=ncols, sharex='col', sharey='row',
-                            gridspec_kw={'width_ratios': width_ratios, 'wspace': 0.03, 'hspace': 0},
-                            figsize=(10,10))
+                            gridspec_kw={'width_ratios': width_ratios,},# 'wspace': 0.03, 'hspace': 0},
+                            figsize=(10,10), constrained_layout=True)
     toa_row, fluence_row, width_row = 0, 1, 2
 
     # Colormap setup
     cmap = plt.cm.rainbow_r
-    norm = PowerNorm(0.3, freq.min().value, 1400)
+    norm = PowerNorm(0.6, 150, 1400)
 
     for col in range(ncols):
         for i in range(len(table['ToA'])):
@@ -86,7 +86,9 @@ def main():
                 axs[i, j].yaxis.tick_right()
 
     # Add shared x label
-    fig.text(0.5, 0.04, 'Time (MJD)', ha='center')
+    #fig.text(0.5, 0.04, 'Time (MJD)', ha='center')
+    #fig.subplots_adjust(bottom=0.15)
+    fig.supxlabel('Time (MJD)                       ', y=0.0, ha='center', fontsize=10)
 
     # Add secondary y-axis for residuals
     def forward(y): return y/ephem['period'].to('s').value
@@ -107,7 +109,7 @@ def main():
     cbar = fig.colorbar(sm, ax=axs[:, -1])
     cbar.set_label(f'Frequency ({freq.unit})')
 
-    plt.tight_layout()
+    #plt.tight_layout()
     plt.savefig(args.output_plot)
     #plt.show()
 

### 2025-05-08 dynspec/timing.py

@@ -11,9 +11,9 @@ import sys
 
 def get_J1755_ephemeris():
     return {
-        'PEPOCH': Time(59965.037829, scale='utc', format='mjd'),
-        'period': 4186.328785 * u.s,
-        'DM': 771.5 * u.pc / u.cm**3,
+        'PEPOCH': Time(59965.037908, scale='utc', format='mjd'),
+        'period': 4186.32827 * u.s,
+        'DM': 765 * u.pc / u.cm**3,
         'tau_sc': 7.0e-2*u.s,
         'coord': SkyCoord("17:55:34.87 -25:27:49.1", unit=(u.hourangle, u.deg), frame='icrs'),
     }

### 2025-05-08 meerkat/pb_correct.py
Simple pb-correction code

@@ -1,0 +1,35 @@
+#/usr/bin/env python
+
+import numpy as np
+from astropy.coordinates import SkyCoord
+from astropy import units as u
+import sys
+
+def gaussian_1d(x, mu, sigma):
+  """
+  Calculates the Gaussian function for each element in x.
+
+  Parameters:
+    x (array_like): The input array.
+    mu (float): The mean of the Gaussian distribution.
+    sigma (float): The standard deviation of the Gaussian distribution.
+
+  Returns:
+    ndarray: An array of the same shape as x, containing the Gaussian values.
+  """
+  return (1 / (sigma * np.sqrt(2 * np.pi))) * np.exp(-0.5 * ((x - mu) / sigma)**2)
+
+c = 3.e8*u.m/u.s
+D = 13.5*u.m
+
+coords_1 = SkyCoord(sys.argv[1], unit=(u.hour, u.deg), frame='fk5') # hmsdms
+coords_2 = SkyCoord(sys.argv[2], unit=(u.hour, u.deg), frame='fk5') # hmsdms
+nu = sys.argv[3]*u.MHz #MHz
+
+# Calibrated to the plots of Villiers 2023
+fwhm = 1.13*np.degrees(((c/nu) / D)*u.rad)
+theta = fwhm/2.355
+
+sep = coords_1.separation(coords_2)
+
+print(gaussian_1d(sep.deg, 0, theta.value))

### 2025-05-08 meerkat/pb_correct.py
Fixed normalisation, made pretty plot

@@ -17,7 +17,8 @@ def gaussian_1d(x, mu, sigma):
   Returns:
     ndarray: An array of the same shape as x, containing the Gaussian values.
   """
-  return (1 / (sigma * np.sqrt(2 * np.pi))) * np.exp(-0.5 * ((x - mu) / sigma)**2)
+  #return (1 / (sigma * np.sqrt(2 * np.pi))) * np.exp(-0.5 * ((x - mu) / sigma)**2)
+  return np.exp(-0.5 * ((x - mu) / sigma)**2)
 
 c = 3.e8*u.m/u.s
 D = 13.5*u.m
@@ -28,8 +29,24 @@ nu = sys.argv[3]*u.MHz #MHz
 
 # Calibrated to the plots of Villiers 2023
 fwhm = 1.13*np.degrees(((c/nu) / D)*u.rad)
-theta = fwhm/2.355
+print(f"Beam FWHM = {fwhm}")
+sigma = fwhm/2.355
+print(f"Beam sigma = {sigma}")
 
 sep = coords_1.separation(coords_2)
+print(f"Distance from pointing centre = {sep.deg} deg")
 
-print(gaussian_1d(sep.deg, 0, theta.value))
+print(gaussian_1d(sep.deg, 0, sigma.value))
+
+from matplotlib import pyplot as plt
+
+x = np.linspace(0, 1.5*fwhm.value)
+fig = plt.figure(figsize=(5,5))
+ax = fig.add_subplot(111)
+ax.plot(x, gaussian_1d(x, 0, sigma.value), label='primary beam', color='black')
+ax.scatter(sep.deg, gaussian_1d(sep.deg, 0, sigma.value), label='source position', color='red')
+ax.set_xlabel("Distance from boresight / deg")
+ax.set_ylabel("Primary beam value (normalised to 1.0)")
+ax.set_title(f"Primary beam at {nu}")
+ax.legend()
+fig.savefig("Primary beam correction.png", bbox_inches="tight")

### 2025-05-08 meerkat/pb_correct.py
Label printed correction value

@@ -36,7 +36,7 @@ print(f"Beam sigma = {sigma}")
 sep = coords_1.separation(coords_2)
 print(f"Distance from pointing centre = {sep.deg} deg")
 
-print(gaussian_1d(sep.deg, 0, sigma.value))
+print(f"Primary beam correction (divide by this): {gaussian_1d(sep.deg, 0, sigma.value)}")
 
 from matplotlib import pyplot as plt
 

### 2025-05-14 dynspec/measure_rm.py
Started working on the polarisation plots to compare ASKAP and MeerKAT pulses. WIP

@@ -1,0 +1,182 @@
+import numpy as np
+from scipy.optimize import curve_fit
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import astropy.units as u
+from astropy.time import Time
+from astropy.coordinates import SkyCoord, EarthLocation
+from astropy.constants import c
+import sys
+import argparse
+
+from timing import *
+
+import warnings
+
+def safe_nanmean(arr, **kwargs):
+    with warnings.catch_warnings():
+        warnings.simplefilter("ignore", category=RuntimeWarning)
+        np.seterr(all="ignore")
+        result = np.nanmean(arr, **kwargs)
+        np.seterr(all="warn")
+    return result
+
+# Model
+def L_model(f_MHz, RM, L_1GHz, α, PA_rad):
+    # RM in rad/m^2
+    # L_1GHz is linearly polarised flux density at 1 GHz
+    # α is spectral index of linearly polarised component
+    # PA_rad is the intrinsic polarisation angle, in radians
+    L_f = L_1GHz*(f_MHz/1000)**α # Abs value of linear polarisation at given frequencies
+    λ = 299792458/(f_MHz*1e6) # Wavelengths in m
+    ψ = RM * λ**2 + PA_rad
+    return L_f*np.exp(2j*ψ)
+
+# But curve_fit doesn't deal with models with complex outputs, so here's a wrapper
+def real_L_model(f_MHz, RM, L_1GHz, α, PA_rad):
+    L = L_model(f_MHz, RM, L_1GHz, α, PA_rad)
+    return np.concatenate([L.real, L.imag])
+
+def parse_args():
+    parser = argparse.ArgumentParser(description="Measure RM")
+
+    parser.add_argument('--ds_files', nargs='*', help="The name of the input .pkl file")
+    parser.add_argument('--output_image', help="The filename to use for the average DS image. If not given, will plt.show().")
+    parser.add_argument('--fscrunch_factor', type=int, help="Average this many channels together for the output plot")
[…]

### 2025-05-14 dynspec/make_askap_and_meerkat_polarisation_plot.py
Adjusted polarisation plot script in a possible meaningless way...

@@ -11,34 +11,38 @@ def main():
     args = parser.parse_args()
 
     # Hardcode which dynamic spectra we're opening for plotting
-    askap1_dat = np.load('1358297519_askap.pkl', allow_pickle=True)
-    askap2_dat = np.load('1404832334_askap.pkl', allow_pickle=True)
-    meerkat_dat = np.load('1413381294_meerkat.pkl', allow_pickle=True)
+    pkls = ['1358297519_askap.pkl', '1404832334_askap.pkl', '1413381294_meerkat.pkl']
 
-    # Get Stokes I and dedisperse
-    t = Time(dat['TIMES']/86400.0, scale='utc', format='mjd', location=EarthLocation.of_site(dat['TELESCOPE']))
-    dt = t[1] - t[0]
-    f = dat['FREQS'] * u.Hz
-    try:
-        df = f[1] - f[0]
-    except:
-        df = dat['BW'] * u.Hz
-    nchans = len(f)
+    for pkl in pkls:
+        dat = np.load(dat, allow_pickle=True)
 
-    f += 0.5*df # A hack because frequencies are labelled as lower edge of channels instead of middle of channels where they should be
-    for pol in "IQUV":
-        S, fmask, tmask = Stokes_ds(dat, pol=pol)
+        # Get Stokes I and dedisperse
+        t = Time(dat['TIMES']/86400.0, scale='utc', format='mjd', location=EarthLocation.of_site(dat['TELESCOPE']))
+        dt = t[1] - t[0]
+        f = dat['FREQS'] * u.Hz
+        try:
+            df = f[1] - f[0]
+        except:
+            df = dat['BW'] * u.Hz
+        nchans = len(f)
 
-        # Dedispersing requires no nans
-        S[np.isnan(I)] = 0.0
+        f += 0.5*df # A hack because frequencies are labelled as lower edge of channels instead of middle of channels where they should be
+        Ss = {}
+        for pol in "IQUV":
+            S, fmask, tmask = Stokes_ds(dat, pol=pol)
 
-        # Dedisperse
-        f_ref = np.nanmean(f)
-        Sdd = dedisperse_ds(S, src_dm, f, f_ref, dt)
+            # Dedispersing requires no nans
+            S[np.isnan(I)] = 0.0
 
-        # Reapply channel flags 
-        if len(fmask) > 0:
-            Idd[:,fmask] = np.nan
+            # Dedisperse
[…]

### 2025-05-15 paper/main.tex
Synched paper with Overleaf version

@@
 \newcommand{\ToA}[1]{{\rm ToA}_{\rm {#1}}}
+
+%MNRAS style
+\newcommand{\figs}{Figs.}
+\newcommand{\Fig}{Fig.}
+\newcommand{\EFig}{Extended Data Fig.}
+\newcommand{\Figs}{Figs.}
+\newcommand{\sect}{Section}
+\newcommand{\sects}{Sections}
+\newcommand{\Sect}{Section}
+\newcommand{\Sects}{Sections}
+\newcommand{\tab}{Table}
+\newcommand{\tabs}{Tables}
+\newcommand{\Tab}{Table}
+\newcommand{\Tabs}{Tables}
+\newcommand{\eqn}{equation}
+\newcommand{\eqns}{equations}
+\newcommand{\Eqn}{Equation}
+\newcommand{\Eqns}{Equations}
+\newcommand{\etal}{et~al.}
 
@@
 
-The observations included in this paper were made at the Murchison Widefield Array \citep[MWA;][]{Tingay2013},
+\subsection{MWA} \label{sec:mwa}
 
-\subsection{MWA} \label{sec:mwa}
+\src{} was detected blindly with the Murchison Widefield Array \citep[MWA;][]{Tingay2013} in observations taken between June--September 2024 under the ``Galactic Plane Monitor'', project code G0080.
+The prime objective of the campaign was to search for long-period transients by scanning the Galactic plane over $285^\circ < l < 65^\circ$, $|b|<\pm15^\circ$ on a bi-weekly cadence at 185--215\,MHz (see Methods of \citet{2023Natur.619..487H}); a full description will be released by Hurley-Walker et al., in prep.
+We also observed over June--September 2022 but made no detections in these data.
+
+We re-imaged the 2024 data at the location of \src{} using \textsc{WSClean}, masking \src{} itself, forming a deep model of the sky.
+After subtracting this from the visibilities, we phase-rotated to \src{}, and averaged the baseline data to produce a dynamic spectrum.
+% SM to write a 'joining sentence' to explain that the timing analysis was a bit more complicated because of the low frequencies and refer the reader to the relevant section -- SM (memo to self): Not that complicated because DM + tau_sc can be ignored if making ToA predictions solely based on pulses at the target frequency.
+
+% SM: commenting the following out because it's a repeat of above...?
+%The GPM also conducted observations of this region in June--September 2022, but \src{} was not detected, either by a blind search, nor by a re-examination of the data following the methods above.
+
+% NWH to add what went into the followup observations: D0042 (both 185 and 200 MHz). SM
+
+% ** ANGIE **
+% Plz add a short paragraph here with the essential details of the IPS observation included in this paper: G0060, upper half-band only, how the images were made.
+I'll (SM) add a few sentences about how I selected that observation in the first place.
+An additional MWA observation made as part of the MWA Interplanetary Scintillation (IPS) Survey, project code G0060, has also been included in this present study.
+A full description of how MWA IPS observations are scheduled and processed can be found in Section~2 of \citet{Morgan2022}, whereas here we only provide a brief overview.
+The two adjacent 200-second observations included in this work are a sub-section of a full 10-minute near-Sun observation (30$^{\circ}$ elongation).
+These observations are taken over two equal bands of frequency, centered on approximately 80\,MHz and 160\,MHz. For this study, only the upper band has been processed.
+IPS observations require a short time integration of 0.5\,s, but can allow for a larger frequency resolution of 40\,kHz, which is then averaged to an even higher 160\,kHz during imaging.
+% SM: TODO: describe various scrunching I did to produce light curve in pulsestack
+The observation was self-calibrated against a sky model based on the GLEAM survey \citep{Hurley-Walker2017} using \textsc{mwa\_hyperdrive}\footnote{\url{https://github.com/MWATelescope/mwa_hyperdrive}}, and then imaged using \textsc{WSClean}.
 
@@
 
+Paper~1 presented an exhaustive search of the ASKAP data available at the time of writing, comprising 60\,h of data, and yielding only a single detection of \src{} (in Scheduling Block ID 47253).
+Subsequent to the writing of Paper~1, a further epoch of the VAST survey was performed (SBID 63600) in which \src{} produced a detectable pulsation.
+We followed a similar procedure as the above to generate dynamic spectra for each of the observations.
+
 \subsection{MeerKAT} \label{sec:meerkat}
+
+MeerKAT observations were undertaken on 2024-10-19, under proposal code
+DDT-20241015-NH-01 and capture block 1729341386, using the UHF band spanning 544 -- 1088\,MHz.
+As well as correlator observations undertaken at 2-s/132.812-kHz resolution, we also employed the Pulsar Timing User Supplied Equipment \citep[PTUSE;][]{2020PASA...37...28B} in search mode, using 37.45-$\mu$s sampling.
+The observation included typical bandpass, polarisation, and phase calibrators, as well as phase-up and test pulsar observations.
+\src{} was tracked from 13:54:36 to 14:04:35 UTC.
+
+The correlator data were calibrated using the standard SARAO SDP calibration pipeline, and imaged using \textsc{WSClean}.
+We formed a deep model of the sources within the primary beam, excepting \src{}, and subtracted this from the visibilities.
+We then averaged the visibilities, excluding all baselines shorter than 150\,m, to produce a dynamic spectrum of the source, shown in \Fig~\ref{fig:scattering_DM}.
+
+We also re-imaged the original 2023-05-28 L-band MeerKAT observation described in Paper~1, which was taken under project code DDT-20230525-DD-01 under capture block 1685306788.
+We performed a similar processing of the data, and identified four pulses with TOAs consistent with an ephemeris derived from the other data.
+The dynamic spectrum of one of the brightest pulses is shown in \Fig~\ref{fig:scattering_DM}.
+
+A summary of all the observations used in this paper is given in \Tab~\ref{tbl:obs}.
+
+\begin{deluxetable*}{lllccc}
+  \tablecaption{Observations summary\label{tbl:obs}}
+  \tablehead{
+    \colhead{Date range} & \colhead{Telescope} & Project & \colhead{$\nu$} & \colhead{$\Delta\nu$} & \colhead{Number of} \\
+    \colhead{(MJD)} & & & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{pulses}
+  }
+  \startdata
+  59965 & ASKAP\tablenotemark{a} & SB47253 & 887.5 & 288 & 1 \\
+  59966 & MWA & G0060 & 161.92 & 15.36 & 1 \\
+  %60084 & MWA & G0057 & 154.24 & 30.72 & $\le$ 1 \\
+  60092 - 60093 & MeerKAT & DDT-20230525-DD-01 & 1284 & 856 & 4 \\
+  60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & 16 \\
+  60503 & ASKAP & SB63600 & 887.5 & 288 & 1 \\
+  60572 & MWA & D0042 & 184.96 & 30.72 & 4 \\
+  60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & 17 \\
+  60602 & MeerKAT & DDT-20241015-NH-01 & 812.8 & 495.3 & 1 \\
+  \enddata
+  \tablenotetext{a}{Original discovery \citepalias{2024MNRAS.535..909D}}
+\end{deluxetable*}
 
@@
 
-\begin{deluxetable*}{cccccc}
-  \tablecaption{Observations}
-  \tablehead{
-    \colhead{Date range} & \colhead{Telescope} & Project & \colhead{$\nu$} & \colhead{$\Delta\nu$} & \colhead{Number of} \\
-    \colhead{(MJD)} & & & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{pulses}
-  }
-  \startdata
-  59965 & ASKAP\tablenotemark{a} & SB47253 & 887.5 & 288 & 1 \\
-  59966 & MWA & G0060 & 161.92 & 15.36 & 1 \\
-  %60084 & MWA & G0057 & 154.24 & 30.72 & $\le$ 1 \\
-  60092 - 60093 & MeerKAT & & & & 4 \\
-  60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & 18 \\
-  60503 & ASKAP &  & 887.5 & 288 & 1 \\
-  60572 & MWA & D0042 & 184.96 & 30.72 & 4 \\
-  60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & 16 \\
-  60602 & MeerKAT & & 812.8 & 495.3 & 1 \\
-  \enddata
-  \tablenotetext{a}{Original discovery \citepalias{2024MNRAS.535..909D}}
-\end{deluxetable*}
-
 \section{Analysis \& results} \label{sec:analysis}
@@
         \emg(t) &= A \frac{\sigma}{\tau}\sqrt{\frac{\pi}{2}}
-                   \exp\left(-\frac12 \left( \frac{t - \mu}{\tau} \right)^2 \right) \\
+                   \exp\left(-\frac12 \left( \frac{t - \mu}{\tau} \right)^2 \right) \cdot {} \\
                             &\qquad \erfcx \left(\frac{1}{\sqrt{2}} \left(\frac{\sigma}{\tau}
@@
 according to each observation's centre frequency.
-A pulse stack containing all observed pulses and their fits is shown in Fig. \ref{fig:pulsestack}.
+A pulse stack containing all observed pulses and the corresponding unscattered pulses derived from the fits is shown in Fig. \ref{fig:pulsestack}.
 
@@
 Because the scattering time scale could not be reliably measured for all individual pulses, we obtained ToAs by assuming a fixed scattering time of $\tau_{\rm sc,1 GHz} = 0.07\,$s.
-The pulse parameters from these fits, including their ToAs are given in Table \ref{tbl:toas}.
 
-\begin{deluxetable*}{ccccc}
-  \tablecaption{Times of arrival and pulse properties\label{tbl:toas}}
-  \tablehead{
-    \colhead{Telescope} & \colhead{$\nu$} & \colhead{ToA} & \colhead{Fluence} & \colhead{$\sigma$} \\
-    & \colhead{(MHz)} & \colhead{(MJD)} & \colhead{($10^3$\,Jy\,s)} & \colhead{(s)}
-  }
-  \startdata
-ASKAP & 1032 & 59965.0425644(45) & 1.03(4) & 29.4(5) \\
-MWA & 170 & 59966.061584(40) & 31.7(7) & 40(7) \\
-MeerKAT & 1284 & 60092.899547(10) & - & 13(1) \\
-MeerKAT & 1284 & 60092.947978(10) & - & 11(1) \\
-MeerKAT & 1284 & 60092.996463(10) & - & 15(1) \\
-MeerKAT & 1284 & 60093.044917(12) & - & 17(1) \\
-MWA & 200 & 60481.637466(65) & 3.0(2) & 24(8) \\
-MWA & 200 & 60485.658977(33) & 1.18(7) & 16(4) \\
-MWA & 200 & 60489.632266(20) & 1.65(6) & 14(2) \\
-MWA & 200 & 60492.588020(24) & 3.12(9) & 14(3) \\
-MWA & 200 & 60496.609639(18) & 2.87(8) & 17(2) \\
-MWA & 200 & 60503.587085(14) & 3.40(8) & 17(2) \\
-ASKAP & 1032 & 60503.634781(17) & 0.13(2) & 15(2) \\
-MWA & 200 & 60506.542809(33) & 1.35(6) & 9(4) \\
-MWA & 200 & 60510.564531(11) & 3.08(7) & 16(1) \\
-MWA & 200 & 60519.528812(29) & 3.1(1) & 14(4) \\
-MWA & 200 & 60522.533028(16) & 3.50(8) & 18(2) \\
-MWA & 200 & 60527.524033(14) & 2.89(7) & 16(2) \\
-MWA & 200 & 60530.528339(16) & 2.90(8) & 17(2) \\
-MWA & 200 & 60537.506042(13) & 3.91(9) & 17(2) \\
-MWA & 200 & 60541.479448(47) & 1.48(9) & 14(5) \\
-MWA & 200 & 60544.483761(15) & 3.91(9) & 20(2) \\
-MWA & 200 & 60551.461625(16) & 3.35(8) & 16(2) \\
-MWA & 185 & 60572.395455(15) & 2.86(7) & 15(2) \\
-MWA & 185 & 60572.443943(21) & 3.01(8) & 16(2) \\
-MWA & 185 & 60572.540824(18) & 2.57(8) & 16(2) \\
-MWA & 185 & 60572.589281(31) & 4.3(2) & 21(4) \\
-MWA & 200 & 60592.456765(27) & 1.63(8) & 19(3) \\
-MWA & 200 & 60592.505159(33) & 1.67(9) & 19(4) \\
-MWA & 200 & 60593.474369(26) & 1.08(6) & 15(3) \\
-MWA & 200 & 60593.522901(46) & 1.3(1) & 19(5) \\
-MWA & 200 & 60594.443484(20) & 1.94(8) & 18(2) \\
-MWA & 200 & 60594.491990(33) & 0.55(5) & 12(4) \\
-MWA & 200 & 60595.461118(29) & 1.53(8) & 19(3) \\
-MWA & 200 & 60595.509617(25) & 0.89(5) & 13(3) \\
-MWA & 200 & 60596.430282(20) & 1.55(7) & 16(2) \\
-MWA & 200 & 60596.478721(23) & 1.65(7) & 17(3) \\
-MWA & 200 & 60597.447846(41) & 0.86(7) & 16(5) \\
-MWA & 200 & 60597.496319(30) & 1.82(9) & 19(3) \\
-MWA & 200 & 60599.434635(17) & 1.28(5) & 13(2) \\
-MWA & 200 & 60599.483121(24) & 1.00(5) & 13(3) \\
-MWA & 200 & 60600.500655(31) & 1.24(7) & 16(4) \\
-MWA & 200 & 60602.438964(32) & 1.9(1) & 21(4) \\
-MWA & 200 & 60602.487394(27) & 1.98(9) & 20(3) \\
-MeerKAT & 813 & 60602.5835731(40) & 0.061(7) & 14.9(4)
-  \enddata
-\end{deluxetable*}
+%\begin{deluxetable*}{ccccc}
+%  \tablecaption{Times of arrival and pulse properties\label{tbl:toas}}
+%  \tablehead{
+%    \colhead{Telescope} & \colhead{$\nu$} & \colhead{ToA} & \colhead{Fluence} & \colhead{$\sigma$} \\
+%    & \colhead{(MHz)} & \colhead{(MJD)} & \colhead{($10^3$\,Jy\,s)} & \colhead{(s)}
+%  }
+%  \startdata
+%ASKAP & 1032 & 59965.0429358(45) & 0.48(2) & 29.1(4) \\
+%MWA & 170 & 59966.061584(40) & 31.7(7) & 40(7) \\
+%MeerKAT & 1284 & 60092.899548(10) & 0.003(3) & 13(1) \\
+%MeerKAT & 1284 & 60092.947966(10) & 0.003(3) & 12(1) \\
+%MeerKAT & 1284 & 60092.996466(11) & 0.005(3) & 16(1) \\
+%MeerKAT & 1284 & 60093.044919(12) & 0.005(4) & 16(1) \\
+%MWA & 200 & 60481.637466(65) & 3.0(2) & 24(8) \\
+%MWA & 200 & 60485.658977(33) & 1.18(7) & 16(4) \\
+%MWA & 200 & 60489.632266(20) & 1.65(6) & 14(2) \\
+%MWA & 200 & 60492.588020(24) & 3.12(9) & 14(3) \\
+%MWA & 200 & 60496.609639(18) & 2.87(8) & 17(2) \\
+%MWA & 200 & 60503.587085(14) & 3.40(8) & 17(2) \\
+%ASKAP & 1032 & 60503.634781(17) & 0.09(1) & 16.6(5) \\
+%MWA & 200 & 60506.542809(33) & 1.35(6) & 9(4) \\
+%MWA & 200 & 60510.564531(11) & 3.08(7) & 16(1) \\
+%MWA & 200 & 60519.528812(29) & 3.1(1) & 14(4) \\
+%MWA & 200 & 60522.533028(16) & 3.50(8) & 18(2) \\
+%MWA & 200 & 60527.524033(14) & 2.89(7) & 16(2) \\
+%MWA & 200 & 60530.528339(16) & 2.90(8) & 17(2) \\
+%MWA & 200 & 60537.506042(13) & 3.91(9) & 17(2) \\
+%MWA & 200 & 60541.479448(47) & 1.48(9) & 14(5) \\
+%MWA & 200 & 60544.483761(15) & 3.91(9) & 20(2) \\
+%MWA & 200 & 60551.461625(16) & 3.35(8) & 16(2) \\
+%MWA & 185 & 60572.395455(15) & 2.86(7) & 15(2) \\
+%MWA & 185 & 60572.443943(21) & 3.01(8) & 16(2) \\
+%MWA & 185 & 60572.540824(18) & 2.57(8) & 16(2) \\
+%MWA & 185 & 60572.589281(31) & 4.3(2) & 21(4) \\
+%MWA & 200 & 60592.456765(27) & 1.63(8) & 19(3) \\
+%MWA & 200 & 60592.505159(33) & 1.67(9) & 19(4) \\
+%MWA & 200 & 60593.474369(26) & 1.08(6) & 15(3) \\
+%MWA & 200 & 60593.522901(46) & 1.3(1) & 19(5) \\
+%MWA & 200 & 60594.443484(20) & 1.94(8) & 18(2) \\
+%MWA & 200 & 60594.491990(33) & 0.55(5) & 12(4) \\
+%MWA & 200 & 60595.461118(29) & 1.53(8) & 19(3) \\
+%MWA & 200 & 60595.509617(25) & 0.89(5) & 13(3) \\
+%MWA & 200 & 60596.430282(20) & 1.55(7) & 16(2) \\
+%MWA & 200 & 60596.478721(23) & 1.65(7) & 17(3) \\
+%MWA & 200 & 60597.447846(41) & 0.86(7) & 16(5) \\
+%MWA & 200 & 60597.496319(30) & 1.82(9) & 19(3) \\
+%MWA & 200 & 60599.434635(17) & 1.28(5) & 13(2) \\
+%MWA & 200 & 60599.483121(24) & 1.00(5) & 13(3) \\
+%MWA & 200 & 60600.500655(31) & 1.24(7) & 16(4) \\
+%MWA & 200 & 60602.438964(32) & 1.9(1) & 21(4) \\
+%MWA & 200 & 60602.487394(27) & 1.98(9) & 20(3) \\
+%MeerKAT & 813 & 60602.5835731(40) & 0.061(7) & 14.9(4)
+  %\enddata
+%\end{deluxetable*}
 
 These ToAs were then barycentred and fit for both period and DM, resulting in the values given in Table \ref{tbl:ephemeris}.
+The residuals are plotted in \ref{fig:pulse_details}, along with the fitted pulse widths and fluences.
 We also tried fitting a timing model that included a spin-down parameter, and found that it was consistent with zero spin-down to within $1\sigma$, and so is not included in the ephemeris.
@@
     \tableline
-    Period (s) & $4186.3288 \pm 0.0003$ \\
-    PEPOCH (MJD) & $59965.03783 \pm 0.00003$ \\
-    DM (pc/cm$^{-3}$) & $771 \pm 27$ \\
+    Period (s) & $4186.3283 \pm 0.0003$ \\
+    PEPOCH (MJD) & $59965.03790 \pm 0.00003$ \\
+    DM (pc/cm$^{-3}$) & $764 \pm 25$ \\
     $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$\tablenotemark{a} \\
@@
 
-The measured DM of $771 \pm 27\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of $710^{+200}_{-180}\,{\rm pc}\,{\rm cm}^{-3}$ given in \citetalias{2024MNRAS.535..909D}.
+\begin{figure*}[th]
+  \centering
+  \includegraphics[width=0.98\linewidth]{pulse_details.pdf}
+  \caption{Timing residuals (top panel) and other pulse properties derived from the fits of Eq. \eqref{eqn:emg} to the individual light curves (lower two panels). \dots}
+  \label{fig:pulse_details}
+\end{figure*}
+
+The measured DM of $764 \pm 25\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of $710^{+200}_{-180}\,{\rm pc}\,{\rm cm}^{-3}$ given in \citetalias{2024MNRAS.535..909D}.
 Because we have not attempted to simultaneously fit for both DM and scattering timescale, there will remain some small systematic error on this reported DM measurement.
@@
 is the amount that the \emph{peak} of the observed pulse is delayed by scattering.
-When calculating this quantity, we recommend using $\sigma = 15\,$s, a typical value for low-frequency pulses (see Table \ref{tbl:ephemeris}).
+When calculating this quantity, we recommend using $\sigma = 15\,$s, a typical value for low-frequency pulses (see Fig. \ref{fig:pulse_details}).
 At frequencies above $300\,$MHz, $\tau(\nu) \ll \sigma$, and the delay due to scattering, which asymptotically behaves like $\Delta t_{\rm sc}(\nu) \sim \tau$, can be safely neglected.
@@
 is accurate to within a few seconds.
-At intermediate frequencies, Eq. \eqref{eqn:scattering_delay} should be used directly.
+At intermediate frequencies ($150\,{\rm MHz} \lesssim \nu \lesssim 300\,{\rm MHz}$), Eq. \eqref{eqn:scattering_delay} should be used directly.
 

### 2025-05-15 dynspec/measure_rm.py
More written in measure_rm.py script. And also updated incomplete PB_CORR in ASKAP and MeerKAT pickles, necessary for correct polarisation interpretation

@@ -13,6 +13,30 @@ from timing import *
 
 import warnings
 
+data = [
+    {
+        'ds_file': '1358297519_askap.pkl',
+        'flip_RM': False,
+        'ToA': Time(59965.042934515615, scale='utc', format='mjd'),
+        'xlim': [-200, 200],
+    },
+    {
+        'ds_file': '1404832334_askap.pkl',
+        'flip_RM': False,
+        'ToA': Time(60503.63475701395, scale='utc', format='mjd'),
+        'xlim': [-200, 200],
+    },
+    {
+        'ds_file': '1413381294_meerkat.pkl',
+        'flip_RM': True,
+        'baseline': [-0.05087631833089632, -0.010672092754814125],
+        'ToA': Time(60602.58357327181, scale='utc', format='mjd'),
+        'xlim': [-265, 135],
+    },
+]
+
+# Hardcoded "baseline", derived from pulsestack_all.py
+
 def safe_nanmean(arr, **kwargs):
     with warnings.catch_warnings():
         warnings.simplefilter("ignore", category=RuntimeWarning)
@@ -40,7 +64,6 @@ def real_L_model(f_MHz, RM, L_1GHz, α, PA_rad):
 def parse_args():
     parser = argparse.ArgumentParser(description="Measure RM")
 
-    parser.add_argument('--ds_files', nargs='*', help="The name of the input .pkl file")
     parser.add_argument('--output_image', help="The filename to use for the average DS image. If not given, will plt.show().")
     parser.add_argument('--fscrunch_factor', type=int, help="Average this many channels together for the output plot")
     parser.add_argument('--bins', type=int, nargs='*', help="Use the specified bins for the RM fit")
@@ -96,16 +119,30 @@ def plot_RM(ax, f, Q, U, popt=None, pcov=None, fscrunch_factor=None):
 
 def main():
     args = parse_args()
-    fig = plt.figure(figsize=(4*len(args.ds_files),5))
-    gs = gridspec.GridSpec(4, len(args.ds_files), figure=fig, hspace=0.0)
+    fig = plt.figure(figsize=(4*len(data),7))
+    gs = gridspec.GridSpec(5, len(data), figure=fig, hspace=0.0, wspace=0.0)
 
[…]

### 2025-05-15 dynspec/pulsestack_all.py

@@ -90,6 +90,7 @@ def main():
         #p0 = [0, 0, np.max(lightcurve), 0, 10/ephemeris['period'].to('s').value]
         popt, _ = curve_fit(model, phases, lightcurve, p0=p0)
         A, μ, m, c, σ = popt
+        #print(f'{pkl}: {m = }, {c = }')
         lightcurve -= m*phases + c
 
         if len(set(pulses)) != 1:

### 2025-05-15 dynspec/measure_rm.py
WIP on measure_rm.py

@@ -18,20 +18,20 @@ data = [
         'ds_file': '1358297519_askap.pkl',
         'flip_RM': False,
         'ToA': Time(59965.042934515615, scale='utc', format='mjd'),
-        'xlim': [-200, 200],
+        'xlim': [-150, 150],
     },
     {
         'ds_file': '1404832334_askap.pkl',
         'flip_RM': False,
         'ToA': Time(60503.63475701395, scale='utc', format='mjd'),
-        'xlim': [-200, 200],
+        'xlim': [-150, 150],
     },
     {
         'ds_file': '1413381294_meerkat.pkl',
         'flip_RM': True,
         'baseline': [-0.05087631833089632, -0.010672092754814125],
         'ToA': Time(60602.58357327181, scale='utc', format='mjd'),
-        'xlim': [-265, 135],
+        'xlim': [-200, 100],
     },
 ]
 
@@ -191,6 +191,9 @@ def main():
             try:
                 popt, pcov = fit_RM_to_QU(Qcol, Ucol, f, p0=p0, bounds=bounds)
             except:
+                RMs.append(np.nan)
+                alphas.append(np.nan)
+                alpha_errs.append(np.nan)
                 continue
             errs = np.sqrt(np.diag(pcov))
 
@@ -199,15 +202,15 @@ def main():
             alpha, alpha_err = popt[2], errs[2]
             PA, PA_err = np.divmod(popt[3] + np.pi/2, np.pi)[1] - np.pi/2, errs[3]
 
+            RMs.append(RM)
+            alphas.append(alpha)
+            alpha_errs.append(alpha_err)
             if alpha_err < threshold:
-                RMs.append(RM)
-                alphas.append(alpha)
-                alpha_errs.append(alpha_err)
                 ax_RM.errorbar([t_base[phase_bin].value], [RM], yerr=[RM_err], capsize=2, color='k', fmt='.')
                 ax_al.errorbar([t_base[phase_bin].value], [alpha], yerr=[alpha_err], capsize=2, color='k', fmt='.')
 
         # Choose an RM
-        RM = np.mean(RMs) * u.rad/u.m**2
+        RM = safe_nanmean(RMs) * u.rad/u.m**2
         λ = c/f
         ψ = RM*λ**2
         L = Q + U*1j
@@ -216,12 +219,13 @@ def main():
[…]

### 2025-05-15 dynspec/measure_rm.py
Fixed indentation bug in timing.py so that U and V plots can be made correctly

@@ -18,20 +18,23 @@ data = [
         'ds_file': '1358297519_askap.pkl',
         'flip_RM': False,
         'ToA': Time(59965.042934515615, scale='utc', format='mjd'),
-        'xlim': [-150, 150],
+        'xlim': [-149, 149],
+        'title': "ASKAP, MJD 59965, 888 MHz",
     },
     {
         'ds_file': '1404832334_askap.pkl',
         'flip_RM': False,
         'ToA': Time(60503.63475701395, scale='utc', format='mjd'),
-        'xlim': [-150, 150],
+        'xlim': [-149, 149],
+        'title': "ASKAP, MJD 60503, 888 MHz",
     },
     {
         'ds_file': '1413381294_meerkat.pkl',
         'flip_RM': True,
         'baseline': [-0.05087631833089632, -0.010672092754814125],
         'ToA': Time(60602.58357327181, scale='utc', format='mjd'),
-        'xlim': [-200, 100],
+        'xlim': [-199, 99],
+        'title': "MeerKAT, MJD 60602, 813 MHz",
     },
 ]
 
@@ -134,10 +137,10 @@ def main():
         print(f'Opening {ds_file}...')
         dat = np.load(ds_file, allow_pickle=True)
 
-        axs_RM.append(fig.add_subplot(gs[0, i],                    sharey=axs_RM[0] if i != 0 else None))
-        axs_al.append(fig.add_subplot(gs[1, i], sharex=axs_RM[-1], sharey=axs_al[0] if i != 0 else None))
-        axs_PA.append(fig.add_subplot(gs[2, i], sharex=axs_RM[-1], sharey=axs_PA[0] if i != 0 else None))
-        axs_lc.append(fig.add_subplot(gs[3:,i], sharex=axs_RM[-1], sharey=axs_lc[0] if i != 0 else None))
+        axs_RM.append(fig.add_subplot(gs[0, i]))
+        axs_al.append(fig.add_subplot(gs[1, i]))
+        axs_PA.append(fig.add_subplot(gs[2, i]))
+        axs_lc.append(fig.add_subplot(gs[3:,i]))
 
         ax_RM = axs_RM[-1]
         ax_PA = axs_PA[-1]
@@ -209,8 +212,12 @@ def main():
[…]

### 2025-05-15 dynspec/timing.py

@@ -98,9 +98,9 @@ def Stokes_ds(dat, pol='I', pb_corr=True):
             for i in range(len(dat['POLS'])):
                 this_pol = dat['POLS'][i]
 
-            if np.all(np.isnan(dat['PB_CORR'][:,i])):
-                print(f"WARNING: PB corrections for {this_pol} are all nans. No correction applied to this pol.")
-                dat['PB_CORR'][:,i] = np.ones(dat['FREQS'].shape)
+                if np.all(np.isnan(dat['PB_CORR'][:,i])):
+                    print(f"WARNING: PB corrections for {this_pol} are all nans. No correction applied to this pol.")
+                    dat['PB_CORR'][:,i] = np.ones(dat['FREQS'].shape)
 
     else:
         # This creates a PB correction field (full of ones) in memory, but doesn't save to disk

### 2025-05-15 dynspec/measure_rm.py
Updated polarisation plot with a legend

@@ -213,10 +213,14 @@ def main():
                 ax_al.errorbar([t_base[phase_bin].value], [alpha], yerr=[alpha_err], capsize=2, color='k', fmt='.')
 
         # Plot only decent PA points
-        mask = np.array(alpha_errs) < threshold
+        mask = (np.array(alpha_errs) < threshold) & (np.array(alphas) > -10)
+        alphas = np.array(alphas)[mask]
+        print(f'avg(α_L) = {np.nanmean(alphas)} ± {np.nanstd(alphas)}')
 
-        # Choose an RM
-        RM = safe_nanmean(np.array(RMs)[mask]) * u.rad/u.m**2
+        # Choose an RM. Weight the individual RMs by profile
+        weights = safe_nanmean(I, axis=-1)[mask]
+        RM = safe_nanmean(np.array(RMs)[mask] * weights)/np.mean(weights) * u.rad/u.m**2
+        print(f'avg(RM) = {RM} ± {np.nanstd(np.array(RMs)[mask])}')
         RM_err = np.nanstd(np.array(RMs)[mask]) * u.rad/u.m**2
         λ = c/f
         ψ = RM*λ**2
@@ -228,7 +232,6 @@ def main():
         ax_RM.axhline(RM.value, c='r', zorder=-100)
         #ax_RM.axhspan((RM - RM_err).value, (RM + RM_err).value, color='r', zorder=-1000, alpha=0.2)
 
-        # Remove baseline from Stokes I, if needed
         I_lc = safe_nanmean(I, axis=-1)
         Q_lc = safe_nanmean(Qrot, axis=-1)
         U_lc = safe_nanmean(Urot, axis=-1)
@@ -236,6 +239,7 @@ def main():
         ψ_lc = 0.5*np.arctan2(U_lc, Q_lc)
         V_lc = safe_nanmean(V, axis=-1)
 
+        # Remove baseline from Stokes I, if needed
         if 'baseline' in data[i].keys():
             phase = (t_base / ephem['period']).decompose()
             M, C = data[i]['baseline']
@@ -243,9 +247,9 @@ def main():
 
         ax_PA.scatter(t_base[mask], np.rad2deg(ψ_lc[mask]), c='k', s=2)
         ax_PA.scatter(t_base[mask], np.rad2deg(ψ_lc[mask]) + 180*u.deg, c='k', s=2)
[…]

### 2025-05-15 paper/main.tex
Synch paper with Overleaf version

@@
 Extensive follow up in new and archival data at multiple wavelengths turned up no other pulses.
-Despite this, the authors concluded that \src{} was most likely a long period transient (LPT), a newly emerging class of radio source with periods ranging from minutes to hours (see Table \ref{tbl:lpts} for an up-to-date list).
+Despite this, the authors concluded that \src{} was most likely a long period transient (LPT), a newly emerging class of radio source with periods ranging from minutes to hours.
 
@@
 The main conclusions are summarized in \S\ref{sec:conclusions}.
-
-\begin{deluxetable*}{lcl}
-  \tablecaption{Known and candidate LPTs, arranged in ascending order of period\label{tbl:lpts}}
-  \tablehead{
-    \colhead{LPT} & \colhead{Period} & \colhead{References} \\
-     & \colhead{(min)} &
-   }
-   \startdata
-   %AR Scorpii (J162147.28-225310.3) & 1.97 &  \\
-   %ASKAP J175154.89-255135.3 & ${\sim}$3.6 &  \\
-   %J1912-4410 & 5.3 &  \\
-   CHIME J0630+25             & 7.02 & \citet{2024arXiv240707480D} \\
-   GLEAM-X J162759.5-523504.3 & 18.2 & \citet{2022Natur.601..526H} \\
-   GPM J1839-10               & 22.0 & \citet{2023Natur.619..487H} \\
-   ASKAP J1832-0911           & 44.3 & \todo{Wang} \\
-   ASKAP J193505.1+214841.0   & 53.8 & \citet{2024NatAs...8.1159C} \\
-   ASKAP J175534.9-252749.1   & 69.8 & \citetalias{2024MNRAS.535..909D} \\
-   GCRT J1745-3009            & 77.0 & \citet{2005Natur.434...50H} \\
-   ILT J1101+5521             & 126  & \citet{2024arXiv240811536D} \\
-   GLEAM-X J0704-37           & 175  & \citet{2024arXiv240815757H} \\
-   ASKAP J1839-0756           & 387  & \citet{Lee2025} \\
-   \enddata
-\end{deluxetable*}
 
@@
 
-[Reference for scattering kernels:] \citep{10.1093/mnras/stw1724}.
+%[Reference for scattering kernels:] \citep{10.1093/mnras/stw1724}.
 
@@
 
+No significant polarised emission was detected in the MWA pulses, as well as the 2023 MeerKAT pulses.
+The apparent lack of polarisation in the MeerKAT data set is likely due to low S/N coupled with the source not being not being centred in the beam.
+Much more careful analysis would be needed to obtain reliable limits on the polarised components of those pulses.
+
+The apparent lack of linear polarisation in the MWA pulses, however, is expected due to the high RM of ${\sim}961\,{\rm rad}/{\rm m}^2$ \citepalias[as reported in][]{2024MNRAS.535..909D}, causing the pulses to be depolarised within individual channels.
+We also report that no significantly circularly polarised emission was seen at MWA frequencies.
+
+The three pulses for which we report significant polarisation are (1) the 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, (2) the 2024 ASKAP pulse, and (3) the 2024 MeerKAT pulse.
+The high S/N of each time bin allowed us to test whether the rotation measure (RM) was consistent across each pulse.
+We therefore performed a joint fit of the Stokes Q and U spectra of each time bin to
+\begin{equation}
+    Q(\nu) = {\rm Re}(\mathcal{L}(\nu)),
+    \quad
+    U(\nu) = {\rm Im}(\mathcal{L}(\nu)),
+    \label{eqn:RM}
+\end{equation}
+where
+\begin{equation}
+    \mathcal{L}(\nu)
+        = L_{\rm 1\,GHz}\left(\frac{\nu}{\rm 1\,GHz}\right)^{\alpha_L} e^{2i({\rm RM}\,\lambda^2 + \psi_0)},
+\end{equation}
+$L_{\rm 1\,GHz}$ is the flux density of the linear polarisation component at 1\,GHz, $\alpha_L$ is the spectral index of the linear component, RM is the rotation measure, $\lambda = c/\nu$ is the wavelength, and $\psi_0$ is the intrinsic polarisation angle.
+The RMs and spectral indices of these fits are shown in the top two rows of panels of Fig. \ref{fig:RM}.
+
+\begin{figure*}[th]
+    \centering
+    \includegraphics[width=0.98\linewidth]{RM.pdf}
+    \caption{Polarisation of the 2023 and 2024 ASKAP pulses (left and middle) and the 2024 MeerKAT pulse (right).
+The top two rows show the RM and $\alpha_{\rm lin}$ parameters fitted to Eq.
+\eqref{eqn:RM} for each time bin independently.
+Only bins for which the uncertainty on $\alpha_{\rm lin}$ is less than $1.4$ are shown, a threshold which was found to cleanly eliminate off-pulse bins.
+The weighted average RMs for each pulse are indicated by the horizontal red lines.
+The PAs and lightcurves shown in the bottom two rows of panels were produced using only the average RM for the respective pulse.}
+    \label{fig:RM}
+\end{figure*}
+
+In all cases, the fitted RM was within a few rad/m$^2$ of the value originally derived for the 2023 ASKAP pulse in \citetalias{2024MNRAS.535..909D}.
+The RM appears to decrease slightly over the course of the 2023 ASKAP pulse, and \emph{increase} slightly over the course of the two 2024 MeerKAT components; however, all values are consistent with a constant RM across all three pulses.
+The per-pulse weighted averaged values (with weighting proportional to the Stokes I profile) are $962 \pm 1$ (2023 ASKAP), $965 \pm 2$ (2024 ASKAP) and $962 \pm 2$ (2024 MeerKAT).
+The spectral index of the linear component, $\alpha_L$, is similarly consistent, with averages value of $-2.1 \pm 0.4$ (2023 ASKAP), $-3.0 \pm 0.6$ (2024 ASKAP) and $-1.9 \pm 0.5$ (2024 MeerKAT).
+
+Each pulse was de-Faraday rotated with the weighted average RM given above, to derive the linear polarisation profile and the PA evolution across the pulses.
+For the 2023 ASKAP pulse, we recover the `S'-shaped PA curve discussed at length in \citetalias{2024MNRAS.535..909D} in the context of the RVM.
+Contrastingly, the PA curve of the 2024 ASKAP pulse is flat (across five 10-second bins), and that of the 2024 MeerKAT pulse is curved, but not in an RVM-like way.
+
 \section{Discussion} \label{sec:discussion}
@@
 \end{enumerate}
+
+\begin{deluxetable*}{lcl}
+  \tablecaption{Known and candidate LPTs, arranged in ascending order of period\label{tbl:lpts}}
+  \tablehead{
+    \colhead{LPT} & \colhead{Period} & \colhead{References} \\ 
+     & \colhead{(min)} & 
+   } 
+   \startdata
+   %AR Scorpii (J162147.28-225310.3) & 1.97 &  \\
+   %ASKAP J175154.89-255135.3 & ${\sim}$3.6 &  \\
+   %J1912-4410 & 5.3 &  \\
+   CHIME J0630+25             & 7.02 & \citet{2024arXiv240707480D} \\
+   GLEAM-X J162759.5-523504.3 & 18.2 & \citet{2022Natur.601..526H} \\
+   GPM J1839-10               & 22.0 & \citet{2023Natur.619..487H} \\
+   ASKAP J1832-0911           & 44.3 & \todo{Wang} \\
+   ASKAP J193505.1+214841.0   & 53.8 & \citet{2024NatAs...8.1159C} \\
+   ASKAP J175534.9-252749.1   & 69.8 & \citetalias{2024MNRAS.535..909D} \\
+   GCRT J1745-3009            & 77.0 & \citet{2005Natur.434...50H} \\
+   ILT J1101+5521             & 126  & \citet{2024arXiv240811536D} \\
+   GLEAM-X J0704-37           & 175  & \citet{2024arXiv240815757H} \\
+   ASKAP J1839-0756           & 387  & \citet{Lee2025} \\
+   \enddata
+\end{deluxetable*}
 

### 2025-05-16 dynspec/make_toa_plots.py
Updated new ASKAP detection with more correct weighting scheme, and also updated paper plots with this 'new' detection

@@ -131,7 +131,7 @@ def main():
     # Set xlims for each time chunk
     for i in range(nrows):
         axs[i, 0].set_xlim([59964, 59967])
-        axs[i, 1].set_xlim([60092.85, 60093.1])
+        axs[i, 1].set_xlim([60035, 60105])
         axs[i, 2].set_xlim([60475, 60610])
 
     # Set custom xticks for clarity
@@ -139,7 +139,7 @@ def main():
         for j in range(ncols):
             axs[i, j].set_xticks([])
     axs[-1, 0].set_xticks([59964, 59966])
-    axs[-1, 1].set_xticks([60092.9, 60093])
+    axs[-1, 1].set_xticks([60040, 60070, 60100])
     axs[-1, 0].ticklabel_format(useOffset=False, style='plain')
     axs[-1, 1].ticklabel_format(useOffset=False, style='plain')
 

### 2025-05-16 dynspec/make_toa_plots.py
Fixed tiny typo in make_toa_plots.py

@@ -15,7 +15,7 @@ from brokenaxes import brokenaxes
 
 def main():
     parser = argparse.ArgumentParser(description="Construct a LaTeX table from ToA data (default=toas.ecsv) and print to stdout")
-    parser.add_argument('--toas_file', default="toas.ecsv", help="Choose a different input file from the default 'toas.ecsv")
+    parser.add_argument('--toas_file', default="toas.ecsv", help="Choose a different input file from the default 'toas.ecsv'")
     parser.add_argument('--output_plot', help="Set output plot filename (default: display using plt.show())")
 
     args = parser.parse_args()

### 2025-05-16 dynspec/plot_lpt_comparison.py
Started a small script to plot duty cycles against periods

@@ -1,0 +1,67 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import astropy.units as u
+
+lpts = [
+    {
+        'name': 'ASKAP J1832-0911',
+        'min_width': 0 * u.s,  # TODO
+        'max_width': 0 * u.s,  # TODO
+        'period': 2656.24 * u.s,
+    },
+    {
+        'name': 'ASKAP J1839-0756',
+        'min_width': 320 * u.s,
+        'max_width': 710 * u.s,
+        'period': 23221.29 * u.s,
+    },
+    {
+        'name': 'ASKAP J1935+2148',
+        'min_width': 10 * u.s,
+        'max_width': 50 * u.s,
+        'period': 3225.313 * u.s,
+    },
+    {
+        'name': 'CHIME J0630+25',
+        'min_width': 0.2 * u.s,
+        'max_width': 0.91 * u.s,
+        'period': 421.35542 * u.s,
+    },
+    {
+        'name': 'GCRT J1745-3009',
+        'min_width': 600 * u.s,
+        'max_width': 600 * u.s,
+        'period': 4620.720 * u.s,  # Remember to cite Spreeuw et al. (2009) for this number.
+    },
+    {
+        'name': 'GLEAM-X J1627-5235',
+        'min_width': 30 * u.s,
+        'max_width': 60 * u.s,
+        'period': 1091.169 * u.s,
+    },
+    {
+        'name': 'GPM J1839-10',
+        'min_width': 30 * u.s,
+        'max_width': 300 * u.s,
+        'period': 1318.1957 * u.s,
+    },
+    {
+        'name': 'ILT J1101+5521',
+        'min_width': 30 * u.s,
+        'max_width': 90 * u.s,
+        'period': 7531.17 * u.s,
+    },
+]
+
+periods = [lpt['period'].to('s').value for lpt in lpts] * u.s
+min_duty_cycles = np.array([(lpt['min_width']/lpt['period']).decompose() for lpt in lpts])
+max_duty_cycles = np.array([(lpt['max_width']/lpt['period']).decompose() for lpt in lpts])
+duty_cycles = 0.5*(max_duty_cycles + min_duty_cycles)
+duty_cycles_err = 0.5*(max_duty_cycles - min_duty_cycles)
+
+plt.errorbar(periods.to('min').value, duty_cycles, yerr=duty_cycles_err, capsize=2, fmt='none', ls='none')
[…]

### 2025-05-16 paper/main.tex
Synched repo paper with Overleaf paper

@@
 An additional MWA observation made as part of the MWA Interplanetary Scintillation (IPS) Survey, project code G0060, has also been included in this present study. 
-A full description of how MWA IPS observations are scheduled and processed can be found in Section~2 of \citet{Morgan2022}, whereas here we only provide a brief overview.
+A full description of how MWA IPS observations are scheduled and processed can be found in Section~2 of \citet{Morgan2022}; here, we provide a brief overview.
 The two adjacent 200-second observations included in this work are a sub-section of a full 10-minute near-Sun observation (30$^{\circ}$ elongation).
@@
 The observation was self-calibrated against a sky model based on the GLEAM survey \citep{Hurley-Walker2017} using \textsc{mwa\_hyperdrive}\footnote{\url{https://github.com/MWATelescope/mwa_hyperdrive}}, and then imaged using \textsc{WSClean}.
+% NHW: then phase-rotated and averaged to produce a dynamic spectrum?
 
@@
 
+% NHW to update this in light of new historical discovery of a dim pulse in SB49153.
+
 Paper~1 presented an exhaustive search of the ASKAP data available at the time of writing, comprising 60\,h of data, and yielding only a single detection of \src{} (in Scheduling Block ID 47253).
 Subsequent to the writing of Paper~1, a further epoch of the VAST survey was performed (SBID 63600) in which \src{} produced a detectable pulsation.
-We followed a similar procedure as the above to generate dynamic spectra for each of the observations.
+
+With the re-detection of the source in the MWA data, and the calculation of an ephemeris (\Sect~\ref{sec:analysis}), we re-reduced the data in which we would predict that \src{} would appear.
+We made one further detection, in SBID~49153, at a relatively low significance ($\sim5\sigma$) compared to the blind detections.
+We followed a similar procedure as the above to generate dynamic spectra for each of the observations, using a minimum baseline length of 500\,m to suppress uncleaned Galactic diffuse emission.
 
@@
   %60084 & MWA & G0057 & 154.24 & 30.72 & $\le$ 1 \\
+  60040  & ASKAP & SB49153 & 887.5 & 288 & 1 \\
   60092 - 60093 & MeerKAT & DDT-20230525-DD-01 & 1284 & 856 & 4 \\
@@
 %  \startdata
-%ASKAP & 1032 & 59965.0429358(45) & 0.48(2) & 29.1(4) \\
+%ASKAP & 888 & 59965.0429358(45) & 0.48(2) & 29.1(4) \\
 %MWA & 170 & 59966.061584(40) & 31.7(7) & 40(7) \\
+%ASKAP & 888 & 60040.913447(32) & 0.03(1) & 25(3) \\
 %MeerKAT & 1284 & 60092.899548(10) & 0.003(3) & 13(1) \\
@@
 
-The three pulses for which we report significant polarisation are (1) the 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, (2) the 2024 ASKAP pulse, and (3) the 2024 MeerKAT pulse.
+The three sufficiently bright pulses for which we report significant polarisation are (1) the original 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, (2) the 2024 ASKAP pulse, and (3) the 2024 MeerKAT pulse.
 The high S/N of each time bin allowed us to test whether the rotation measure (RM) was consistent across each pulse.
@@
 \end{equation}
-$L_{\rm 1\,GHz}$ is the flux density of the linear polarisation component at 1\,GHz, $\alpha_L$ is the spectral index of the linear component, RM is the rotation measure, $\lambda = c/\nu$ is the wavelength, and $\psi_0$ is the intrinsic polarisation angle.
+$L_{\rm 1\,GHz}$ is the flux density of the linearly polarised component at 1\,GHz, $\alpha_L$ is its spectral index, RM is the rotation measure, $\lambda = c/\nu$ is the wavelength, and $\psi_0$ is the intrinsic polarisation angle.
 The RMs and spectral indices of these fits are shown in the top two rows of panels of Fig. \ref{fig:RM}.
@@
 
-In all cases, the fitted RM was within a few rad/m$^2$ of the value originally derived for the 2023 ASKAP pulse in \citetalias{2024MNRAS.535..909D}.
+We found that the RM derived for the MeerKAT pulse had the opposite sign, but similar magnitude, to the ASKAP pulses, which is most likely due to a different sign convention being used within the two telescopes' pre-processing software.
+The agreement presented in Fig. \ref{fig:RM} was achieved by first negating Stokes Q in the MeerKAT data.
+Any reflection in the Q-U plane (e.g.
+${\rm Q} \leftrightarrow -{\rm Q}$, ${\rm U} \leftrightarrow -{\rm U}$, or ${\rm Q} \leftrightarrow {\rm U}$) will achieve a similar correction to the sign of the RM, but different choices will introduce different offsets to the PA.
+Because of this, the MeerKAT PA values should not be directly compared with the ASKAP values.
+The most likely scenario, however, is that the MeerKAT values include an arbitrary offset of $n \times 45^\circ$, for some integer $n$.
+
+In all cases, the magnitude of the fitted RM was within a few rad/m$^2$ of the value originally derived for the 2023 ASKAP pulse in \citetalias{2024MNRAS.535..909D}.
 The RM appears to decrease slightly over the course of the 2023 ASKAP pulse, and \emph{increase} slightly over the course of the two 2024 MeerKAT components; however, all values are consistent with a constant RM across all three pulses.
-The per-pulse weighted averaged values (with weighting proportional to the Stokes I profile) are $962 \pm 1$ (2023 ASKAP), $965 \pm 2$ (2024 ASKAP) and $962 \pm 2$ (2024 MeerKAT).
+The per-pulse weighted averaged values (with weighting proportional to the Stokes I profile) are $962 \pm 1$\,${\rm rad}/{\rm m}^2$ (2023 ASKAP), $965 \pm 2$ (2024 ASKAP) and $962 \pm 2$\,${\rm rad}/{\rm m}^2$ (2024 MeerKAT).
 The spectral index of the linear component, $\alpha_L$, is similarly consistent, with averages value of $-2.1 \pm 0.4$ (2023 ASKAP), $-3.0 \pm 0.6$ (2024 ASKAP) and $-1.9 \pm 0.5$ (2024 MeerKAT).
@@
 
-The precursor burst seen with MeerKAT is apparently unique, and is not visible at other telescopes and frequencies, even after averaging them together to make a single profile.
-The only burst of comparable S/N, and at a similar frequency, in which the dimmer precursor component might be expected to be visible is the original 2023-01-21 ASKAP burst \citepalias{2024MNRAS.535..909D}, where again it is absent.
+After accounting for dispersion and scattering effects, the timing analysis of \src{} confirms its status as an LPT, as originally conjectured in \citetalias{2024MNRAS.535..909D}.
+It has the fifth largest period (${\sim}1.16\,$hours) of known published LPTs, after ASKAP J1839$-$0756 \citep[$6.45\,$hours;][]{Lee2025}, GLEAM-X J0704$-$37 \citep[$2.92\,$hours;][]{2024arXiv240815757H, 2025arXiv250103315R}, ILT J1101+5521 \citep[$2.09\,$hours;][]{deRuiter2025}, and GCRT J1745$-$3009 \citep[$1.28\,$hours;][]{2005Natur.434...50H}.
 
-The two pulses observed in January 2023 (the original ASKAP pulse and the MWA (IPS) pulse observed the following day) are significantly wider than all other pulses, suggesting that a morphological change occurred between
+With the timing solution in hand, we can explore the efficacy of the original follow-up campaign described in \citetalias{2024MNRAS.535..909D}.
+Assuming \src{} remained at a similar brightness (see Fig.
+\ref{fig:pulse_details}), it should have been detected in two ASKAP observations (2023-04-06 and 2023-10-18) and a few dozen times throughout the MWA's 2022 GPM run (2022-06-02 to 2022-09-08).
+There are also three observations in the earliest part of the 2024 GPM run (one on 2024-06-02 and two on 2024-06-10) in which no pulse was observed.
+However, pulses were detected just ten days later on 2024-06-20 (the first of the MWA 200\,MHz points in Fig.
+\ref{fig:pulse_details}), and at each epoch thereafter whenever the MWA was observing when a pulse was due to arrive.
+
+We conclude, therefore, that \src{} is intermittent and that the active periods have durations on the order of months.
+Even when the source is ``on'', it can apparently change in brightness by an order of magnitude or more (at a given frequency) in different months.
+This is reminiscent of the behaviour of GLEAM-X J162759.5$-$523504.3, which was observed over a three-month period, but has not been seen again \citep{2022Natur.601..526H}.
+The reappearance of \src{} after so many months suggests the possibility that other known intermittent LPTs (like GLEAM-X J162759.5$-$523504.3 and GCRT J1745$-$3009) may eventually do likewise.
+
+As noted in \citetalias{2024MNRAS.535..909D}, optical follow-up of \src{} is challenging due to its proximity to the Galactic plane ($b = -0.12^\circ$).
+Inferring this nature of the system (white dwarf vs neutron star, isolated vs binary) from the radio pulses alone is challenging, unless either the population of LPTs is better understood as a whole, or if some other property of the radio signal (e.g.
+intermittency, polarisation) can be linked to the system properties.
+
+\src{} shares several properties similar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are confirmed polars.
+\src{}'s period of ${\sim}1.16\,$hours is marginally shorter than the minimum known orbital period of $1.3\,$hours \citep{schwope2025polarcatcatalogpolarslowaccretion}, making it a good candidate for testing the suggestion put forward by \citet{2025arXiv250103315R} that ``short LPTs'' ($P \lesssim 78\,$mins) and ``long LPTs'' ($P \gtrsim 78\,$mins) represent AM CVns and CVs respectively.
+
+\dots
+
+%%%%% Discussion of MeerKAT precursor %%%%%
+%The precursor burst seen with MeerKAT is apparently unique, and is not visible at other telescopes and frequencies, even after averaging them together to make a single profile.
+%The only burst of comparable S/N, and at a similar frequency, in which the dimmer precursor component might be expected to be visible is the original 2023-01-21 ASKAP burst \citepalias{2024MNRAS.535..909D}, where again it is absent.
+%...
+
+%%%%% Discussion of brighter pulses in 2023 %%%%%
+%The two pulses observed in January 2023 (the original ASKAP pulse and the MWA (IPS) pulse observed the following day) are significantly wider than all other pulses, suggesting that a morphological change occurred between ...
 
@@
 
+We have shown that \src{} is in fact an LPT, as conjectured in \citetalias{2024MNRAS.535..909D}).
+Its period of ${\sim}1.16\,$hours places it 
+\begin{itemize}
+  \item Predict another spurt of inactivity in 2025
+\end{itemize}
+
 \begin{acknowledgments}
+ N.H.-W. is the recipient of an Australian Research Council Future Fellowship (project number FT190100231).
 
+ This scientific work uses data obtained from Inyarrimanha Ilgari Bundara, the CSIRO Murchison Radio-astronomy Observatory.
+Support for the operation of the MWA is provided by the Australian Government (NCRIS), under a contract to Curtin University administered by Astronomy Australia Limited.
+ASVO has received funding from the Australian Commonwealth Government through the National eResearch Collaboration Tools and Resources (NeCTAR) Project, the Australian National Data Service (ANDS), and the National Collaborative Research Infrastructure Strategy.
+% Skipped because it is acknowledged below.
+% We acknowledge the Pawsey Supercomputing Centre which is supported by the Western Australian and Australian Governments.
+% ASKAP -- I have fixed this to use the correct name for the observatory
+The Australian SKA Pathfinder is part of the Australia Telescope National Facility which is managed by CSIRO.
+Operation of ASKAP is funded by the Australian Government with support from the National Collaborative Research Infrastructure Strategy.
+ASKAP and the MWA use the resources of the Pawsey Supercomputing Centre.
+Establishment of ASKAP, Inyarrimanha Ilgari Bundara, and the Pawsey Supercomputing Centre are initiatives of the Australian Government, with support from the Government of Western Australia and the Science and Industry Endowment Fund.
+We acknowledge the Wajarri Yamaji People as the Traditional Owners and Native Title Holders of the observatory site.
+
+% MeerKAT
+The MeerKAT telescope is operated by the South African Radio Astronomy Observatory, which is a facility of the National Research Foundation, an agency of the Department of Science and Innovation.
   % PTUSE (https://skaafrica.atlassian.net/wiki/spaces/ESDKB/pages/1591672833/User+Supplied+Equipment+USE#PTUSE)

### 2025-05-17 dynspec/plot_lpt_comparison.py
Working in LPT comparison plot for discussion

@@ -1,67 +1,230 @@
 import numpy as np
 import matplotlib.pyplot as plt
+import matplotlib.lines as mlines
+from matplotlib.legend_handler import HandlerTuple
 import astropy.units as u
+
+point_types = {
+    'Polars': {
+        'color': 'r',
+        'ecolor': 'r',
+        'capsize': 2,
+    },
+    'Unknown': {
+        'color': 'k',
+        'ecolor': 'k',
+        'capsize': 2,
+    },
+    'AR Sco-like': {
+        'color': 'b',
+        'ecolor': 'b',
+        'capsize': 2,
+    },
+}
 
 lpts = [
     {
+        'name': 'ASKAP J1755-2527',
+        'type': 'Unknown',
+        'min_width': 40 * u.s, # Be sure to note: these are W10, unscattered
+        'max_width': 172 * u.s,
+        'period': 4186.32827 * u.s,
+        'text_kwargs': {
+            'ha': 'left',
+            'va': 'center',
+        },
+        'errorbar_kwargs': {
+            'fmt': 'none',
+            'ls': 'none',
+        },
+    },
+    {
         'name': 'ASKAP J1832-0911',
-        'min_width': 0 * u.s,  # TODO
-        'max_width': 0 * u.s,  # TODO
+        'type': 'Unknown',
+        'min_width': 2 * u.min,
+        'max_width': 4 * u.min,
         'period': 2656.24 * u.s,
+        'text_kwargs': {
+            'ha': 'left',
+            'va': 'center',
+        },
+        'errorbar_kwargs': {
+            'fmt': 'none',
+            'ls': 'none',
+        }
     },
     {
         'name': 'ASKAP J1839-0756',
+        'type': 'Unknown',
         'min_width': 320 * u.s,
         'max_width': 710 * u.s,
         'period': 23221.29 * u.s,
+        'text_kwargs': {
+            'ha': 'right',
+            'va': 'center',
+        },
+        'errorbar_kwargs': {
+            'fmt': 'none',
+            'ls': 'none',
+        },
+        'voffset': 1,
     },
     {
         'name': 'ASKAP J1935+2148',
+        'type': 'Unknown',
         'min_width': 10 * u.s,
         'max_width': 50 * u.s,
         'period': 3225.313 * u.s,
+        'text_kwargs': {
+            'ha': 'right',
+            'va': 'center',
+        },
[…]

### 2025-05-17 paper/main.tex
Synched paper with overleaf. Also updated lpt comparison plot script slightly. WIP

@@
 
-We conclude, therefore, that \src{} is intermittent and that the active periods have durations on the order of months.
-Even when the source is ``on'', it can apparently change in brightness by an order of magnitude or more (at a given frequency) in different months.
-This is reminiscent of the behaviour of GLEAM-X J162759.5$-$523504.3, which was observed over a three-month period, but has not been seen again \citep{2022Natur.601..526H}.
+We conclude, therefore, that \src{} is intermittent with active periods lasting on the order of months.
+The given set of observations, spanning from 2023 to 2024, may represent two or three different activity windows.
+This is reminiscent of the behaviour of GLEAM-X J162759.5$-$523504.3, which was ``on'' in January 2020, ``off'' in Feburary, and ``on'' again in March \citep{2022Natur.601..526H}.
 The reappearance of \src{} after so many months suggests the possibility that other known intermittent LPTs (like GLEAM-X J162759.5$-$523504.3 and GCRT J1745$-$3009) may eventually do likewise.
+% TODO: Note activity-window similarities to other GCRTs
 
@@
 
-\src{} shares several properties similar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are confirmed polars.
-\src{}'s period of ${\sim}1.16\,$hours is marginally shorter than the minimum known orbital period of $1.3\,$hours \citep{schwope2025polarcatcatalogpolarslowaccretion}, making it a good candidate for testing the suggestion put forward by \citet{2025arXiv250103315R} that ``short LPTs'' ($P \lesssim 78\,$mins) and ``long LPTs'' ($P \gtrsim 78\,$mins) represent AM CVns and CVs respectively.
+\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are confirmed polars (Fig.
+\ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is a WD-MD polar system.
+However, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for confirmed polars \citep{schwope2025polarcatcatalogpolarslowaccretion}.
+This makes it a good candidate for testing the suggestion advanced by \citet{2025arXiv250103315R} that ``short LPTs'' ($P \lesssim 78\,$mins) and ``long LPTs'' ($P \gtrsim 78\,$mins) represent different classes of systems (AM CVns and CVs, respectively).
+\begin{figure*}[th]
+    \centering
+    \includegraphics[width=0.98\linewidth]{lpt_comparison.pdf}
+    \caption{Duty cycle vs radio pulse period for various classes of radio emitters.
+(TODO: add AR Sco and J1912.) The duty cycles are derived from the reported pulse widths for LPTs, which are compared to the range of the fitted, unscattered pulse widths of \src{} at 10\% of the peak.}
+    \label{fig:enter-label}
+\end{figure*}
 
@@
 %The two pulses observed in January 2023 (the original ASKAP pulse and the MWA (IPS) pulse observed the following day) are significantly wider than all other pulses, suggesting that a morphological change occurred between ...
+
+%%%%% Other things to possibly discuss:
+% - Qu & Zhang #2: https://ui.adsabs.harvard.edu/abs/2025ApJ...981...34Q/abstract
+% - Gaia22ayj: https://ui.adsabs.harvard.edu/abs/2025PASP..137b4202R/abstract
+% - Trying to find a number for the radio duty cycle of AR Sco
+%   - This one's about the pair-wise alternation of (optical?) pulse brightnesses, and an interpretation involving precession: https://ui.adsabs.harvard.edu/abs/2023ApJ...958L..22G/abstract
+%   - Fancy AR Sco modelling. Magnetic mirror models are mentioned in the abstract? https://ui.adsabs.harvard.edu/abs/2025arXiv250508567D/abstract
+% - https://ui.adsabs.harvard.edu/abs/2022Ap%26SS.367..108K/abstract
+% - Suggestion that J1627 is a WD pulsar: https://ui.adsabs.harvard.edu/abs/2022Ap%26SS.367..108K/abstract
 

### 2025-05-17 dynspec/plot_lpt_comparison.py

@@ -190,6 +190,21 @@ lpts = [
             'ls': 'none',
         }
     },
+    {
+        'name': 'AR Sco',
+        'type': 'AR Sco-like',
+        'min_width': 0 * u.s, # TODO: Get numbers for this!!
+        'max_width': 0 * u.s,
+        'period': 1.97 * u.min,
+        'text_kwargs': {
+            'ha': 'left',
+            'va': 'center',
+        },
+        'errorbar_kwargs': {
+            'fmt': 'none',
+            'ls': 'none',
+        }
+    },
 ]
 
 period_units = 'min'

### 2025-05-17 dynspec/plot_lpt_comparison.py
Added J1912, but commented out AR Sco from lpt comparison plot

@@ -190,21 +190,21 @@ lpts = [
             'ls': 'none',
         }
     },
-    {
-        'name': 'AR Sco',
-        'type': 'AR Sco-like',
-        'min_width': 0 * u.s, # TODO: Get numbers for this!!
-        'max_width': 0 * u.s,
-        'period': 1.97 * u.min,
-        'text_kwargs': {
-            'ha': 'left',
-            'va': 'center',
-        },
-        'errorbar_kwargs': {
-            'fmt': 'none',
-            'ls': 'none',
-        }
-    },
+    #{
+    #    'name': 'AR Sco',
+    #    'type': 'AR Sco-like',
+    #    'min_width': 0 * u.s, # TODO: Get numbers for this!!
+    #    'max_width': 1.97/2 * u.min,
+    #    'period': 1.97 * u.min,
+    #    'text_kwargs': {
+    #        'ha': 'left',
+    #        'va': 'center',
+    #    },
+    #    'errorbar_kwargs': {
+    #        'fmt': 'none',
+    #        'ls': 'none',
+    #    }
+    #},
 ]
 
 period_units = 'min'

### 2025-05-17 dynspec/plot_lpt_comparison.py
Added current version of lpt comparison plot to paper folder

@@ -8,17 +8,14 @@ point_types = {
     'Polars': {
         'color': 'r',
         'ecolor': 'r',
-        'capsize': 2,
     },
     'Unknown': {
         'color': 'k',
         'ecolor': 'k',
-        'capsize': 2,
     },
     'AR Sco-like': {
         'color': 'b',
         'ecolor': 'b',
-        'capsize': 2,
     },
 }
 
@@ -36,6 +33,7 @@ lpts = [
         'errorbar_kwargs': {
             'fmt': 'none',
             'ls': 'none',
+            'capsize': 2,
         },
     },
     {
@@ -51,6 +49,7 @@ lpts = [
         'errorbar_kwargs': {
             'fmt': 'none',
             'ls': 'none',
+            'capsize': 2,
         }
     },
     {
@@ -66,6 +65,7 @@ lpts = [
         'errorbar_kwargs': {
             'fmt': 'none',
             'ls': 'none',
+            'capsize': 2,
         },
         'voffset': 1,
     },
@@ -82,6 +82,7 @@ lpts = [
         'errorbar_kwargs': {
             'fmt': 'none',
             'ls': 'none',
+            'capsize': 2,
         }
     },
     {
@@ -97,6 +98,7 @@ lpts = [
         'errorbar_kwargs': {
             'fmt': 'none',
             'ls': 'none',
+            'capsize': 2,
         }
     },
     {
@@ -112,6 +114,7 @@ lpts = [
         'errorbar_kwargs': {
             'fmt': 'x',
             'ls': 'none',
+            'capsize': 0,
         }
     },
     {
@@ -127,6 +130,7 @@ lpts = [
         'errorbar_kwargs': {
             'fmt': 'none',
             'ls': 'none',
+            'capsize': 2,
         }
     },
     {
@@ -142,6 +146,7 @@ lpts = [
         'errorbar_kwargs': {
             'fmt': 'none',
             'ls': 'none',
+            'capsize': 2,
         },
         'voffset': 1,
     },
@@ -158,6 +163,7 @@ lpts = [
         'errorbar_kwargs': {
             'fmt': 'none',
             'ls': 'none',
+            'capsize': 2,
         }
     },
     {
@@ -173,6 +179,7 @@ lpts = [
         'errorbar_kwargs': {
             'fmt': 'none',
             'ls': 'none',
+            'capsize': 2,
         }
     },
     {
@@ -188,6 +195,7 @@ lpts = [
[…]

### 2025-05-17 paper/main.tex
Synching with (updated) Overleaf version of paper

@@
 In \S\ref{sec:discussion} we revisit the question of the nature of \src{}, arguing in favor of a white dwarf interpretation.
-The main conclusions are summarized in \S\ref{sec:conclusions}.
+The main conclusions are summarized in \S\ref{sec:summary}.
 
@@
 Because we have not attempted to simultaneously fit for both DM and scattering timescale, there will remain some small systematic error on this reported DM measurement.
-Breaking the degeneracy is possible in principle with a much higher S/N average profile than what is possible with the current data set.
+Breaking the degeneracy is possible in principle with a much higher S/N average profile than what is achievable with the current data set.
 
@@
 However, pulses were detected just ten days later on 2024-06-20 (the first of the MWA 200\,MHz points in Fig.
-\ref{fig:pulse_details}), and at each epoch thereafter whenever the MWA was observing when a pulse was due to arrive.
+\ref{fig:pulse_details}), and at each epoch thereafter whenever the MWA was observing in \src{}'s direction when a pulse was due to arrive.
 
-We conclude, therefore, that \src{} is intermittent with active periods lasting on the order of months.
-The given set of observations, spanning from 2023 to 2024, may represent two or three different activity windows.
+We conclude, therefore, that \src{} is intermittent with active periods lasting on the order of months, and that the most recent activity period fortuitously started shortly after the start of the 2024 GPM observation run.
+The entire set of observations presented in this work, spanning from 2023 to 2024, may represent two or three different activity windows.
 This is reminiscent of the behaviour of GLEAM-X J162759.5$-$523504.3, which was ``on'' in January 2020, ``off'' in Feburary, and ``on'' again in March \citep{2022Natur.601..526H}.
-The reappearance of \src{} after so many months suggests the possibility that other known intermittent LPTs (like GLEAM-X J162759.5$-$523504.3 and GCRT J1745$-$3009) may eventually do likewise.
-% TODO: Note activity-window similarities to other GCRTs
+The periodic (or quasi-periodic) reappearance of \src{} suggests the possibility that other known intermittent LPTs (like GLEAM-X J162759.5$-$523504.3 and GCRT J1745$-$3009) may eventually do likewise.
 
@@
 However, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for confirmed polars \citep{schwope2025polarcatcatalogpolarslowaccretion}.
-This makes it a good candidate for testing the suggestion advanced by \citet{2025arXiv250103315R} that ``short LPTs'' ($P \lesssim 78\,$mins) and ``long LPTs'' ($P \gtrsim 78\,$mins) represent different classes of systems (AM CVns and CVs, respectively).
+This makes it an interesting testbed for the suggestion advanced by \citet{2025arXiv250103315R} that ``short LPTs'' ($P \lesssim 78\,$mins) and ``long LPTs'' ($P \gtrsim 78\,$mins) represent different classes of systems (AM CVns and CVs, respectively).
 \begin{figure*}[th]
@@
     \caption{Duty cycle vs radio pulse period for various classes of radio emitters.
-(TODO: add AR Sco and J1912.) The duty cycles are derived from the reported pulse widths for LPTs, which are compared to the range of the fitted, unscattered pulse widths of \src{} at 10\% of the peak.}
-    \label{fig:enter-label}
+The duty cycles are derived from the reported pulse widths for LPTs, which are compared to the range of the fitted, unscattered pulse widths of \src{} at 10\% of the peak.
+AR\,Sco \citep{2016Natur.537..374M,2018A&A...611A..66S} and other sources without well-defined periods or duty cycles \citep[e.g.][and references therein]{2021ApJ...920...45W} are not included on this plot.
+    \nocite{2024arXiv240707480D,2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C,2005Natur.434...50H,2024arXiv240811536D,Lee2025}}
+    \label{fig:lpt_comparison}
 \end{figure*}
 
-\dots
+%\begin{deluxetable*}{lcl}
+%  \tablecaption{Known and candidate LPTs, arranged in ascending order of period\label{tbl:lpts}}
+%  \tablehead{
+%    \colhead{LPT} & \colhead{Period} & \colhead{References} \\ 
+%     & \colhead{(min)} & 
+%   } 
+%   \startdata
+%   %AR Scorpii (J162147.28-225310.3) & 1.97 &  \\
+%   %ASKAP J175154.89-255135.3 & ${\sim}$3.6 &  \\
+%   %J1912-4410 & 5.3 &  \\
+%   CHIME J0630+25             & 7.02 & \citet{2024arXiv240707480D} \\
+%   GLEAM-X J162759.5-523504.3 & 18.2 & \citet{2022Natur.601..526H} \\
+%   GPM J1839-10               & 22.0 & \citet{2023Natur.619..487H} \\
+%   ASKAP J1832-0911           & 44.3 & \todo{Wang} \\
+%   ASKAP J193505.1+214841.0   & 53.8 & \citet{2024NatAs...8.1159C} \\
+%   ASKAP J175534.9-252749.1   & 69.8 & \citetalias{2024MNRAS.535..909D} \\
+%   GCRT J1745-3009            & 77.0 & \citet{2005Natur.434...50H} \\
+%   ILT J1101+5521             & 126  & \citet{2024arXiv240811536D} \\
+%   GLEAM-X J0704-37           & 175  & \citet{2024arXiv240815757H} \\
+%   ASKAP J1839-0756           & 387  & \citet{Lee2025} \\
+%   \enddata
+%\end{deluxetable*}
+
+Although there is as yet no clear consensus on whether LPTs represent one class or multiple classes of system \citep[e.g.][]{2024ApJ...961..214R}, the recent confirmation of J1912$-$4410 as a pre-evolved white dwarf pulsar \citep{2023NatAs...7..931P} and ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 as polars \citep{2024arXiv240811536D,2025arXiv250103315R} raise the intriguing possibility that other LPTs may also be radio-emitting white dwarf pulsars at various stages of evolution \citep{2021NatAs...5..648S}.
+
+In this view, the intermittency of these systems have several possible explanations.
+The limited orbital phase range in which J1912$-$4410's radio pulses were observed suggests that the geometric configuration is important in the observability of radio pulsations; ``missing'' pulses may simply occur at unfavourable orbital phases.
+This is readily testable with long-term monitoring---this kind of intermittency will have the same periodicity as the orbit itself.
+
+Interestingly, systems with spin-orbital (or beat-orbital) resonances of, e.g., 2:1 or 3:1, coupled with the idea of a limited observable orbital phase window for the radio pulses, would be indistinguishable from systems in 1:1 resonances.
+We therefore advance the possibility that the coincidence of the observed radio periodicities of ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 with their spectroscopically confirmed orbital periods does not necessarily imply that they are 1:1 polars.
+
+Similarly, systems in which the spin-orbit (or beat-orbit) ratios are \emph{close to} small-integer ratios, or, equivalently, systems in which precession of the WD is significant, will exhibit an extra beating effect in which an orbitally-induced intermittency is aliased to a much lower frequency.
+The month-long time scale of the intermittency of \src{}, and possibly even GLEAM-X\,J1627$-$5235, may be of this kind; much longer-term monitoring is needed to confirm or refute this.
+
+Another possibility is that radio emission is only observed when the MD produces dense enough particle outflows, in the form of winds, to activate the emission mechanism in the vicinity of the WD.
+Such outflows can last for months [CITATION??], and would not be strictly periodic.
+If intermittency is of this sort, then the observed activity windows will be similarly aperiodic, or quasiperiodic.
+Again, long-term monitoring can help distinguish between these scenarios.
+
+% SM: MEMO TO SELF: Add mention of early 2023 pulses being wider (and brighter) than all others.
+Note also the spectral index roughly staying the same, and state a number of roughly what that is by comparing low- and high- frequency flux densities ratios.
+All this can probably go in Analysis/Results above rather than discussion.
 
@@
 %   - Fancy AR Sco modelling. Magnetic mirror models are mentioned in the abstract? https://ui.adsabs.harvard.edu/abs/2025arXiv250508567D/abstract
+%   - Ok, I think this is as good as it gets: Stanway 2018 (reference already imported into biblio.bib.
 % - https://ui.adsabs.harvard.edu/abs/2022Ap%26SS.367..108K/abstract
@@
 
-\begin{enumerate}
-        \item Why does the source appear to not be active all the time at higher frequencies?
-              \item As per convo with John (see MWA Users Slack, 2025-01-24), point out that (lack of detection of source in) MWA IPS is not very constraining in terms of scattering disk / timescale / screen.
-\end{enumerate}
+%\begin{enumerate}
+%        \item Why does the source appear to not be active all the time at higher frequencies?
+%              \item As per convo with John (see MWA Users Slack, 2025-01-24), point out that (lack of detection of source in) MWA IPS is not very constraining in terms of scattering disk / timescale / screen.
+%\end{enumerate}
 
-\begin{deluxetable*}{lcl}
-  \tablecaption{Known and candidate LPTs, arranged in ascending order of period\label{tbl:lpts}}
-  \tablehead{
-    \colhead{LPT} & \colhead{Period} & \colhead{References} \\ 
-     & \colhead{(min)} & 
-   } 
-   \startdata
-   %AR Scorpii (J162147.28-225310.3) & 1.97 &  \\
-   %ASKAP J175154.89-255135.3 & ${\sim}$3.6 &  \\
-   %J1912-4410 & 5.3 &  \\
-   CHIME J0630+25             & 7.02 & \citet{2024arXiv240707480D} \\
-   GLEAM-X J162759.5-523504.3 & 18.2 & \citet{2022Natur.601..526H} \\
-   GPM J1839-10               & 22.0 & \citet{2023Natur.619..487H} \\
-   ASKAP J1832-0911           & 44.3 & \todo{Wang} \\
-   ASKAP J193505.1+214841.0   & 53.8 & \citet{2024NatAs...8.1159C} \\
-   ASKAP J175534.9-252749.1   & 69.8 & \citetalias{2024MNRAS.535..909D} \\
-   GCRT J1745-3009            & 77.0 & \citet{2005Natur.434...50H} \\
-   ILT J1101+5521             & 126  & \citet{2024arXiv240811536D} \\
-   GLEAM-X J0704-37           & 175  & \citet{2024arXiv240815757H} \\
-   ASKAP J1839-0756           & 387  & \citet{Lee2025} \\
-   \enddata
-\end{deluxetable*}
-
-\section{Conclusions} \label{sec:conclusions}
+\section{Summary} \label{sec:summary}
 
 We have shown that \src{} is in fact an LPT, as conjectured in \citetalias{2024MNRAS.535..909D}).
-Its period of ${\sim}1.16\,$hours places it 
-\begin{itemize}
-  \item Predict another spurt of inactivity in 2025
-\end{itemize}
+Its period of ${\sim}1.16\,$hours is slightly shorter than the minimum known orbital\dots
 

### 2025-05-17 dynspec/plot_lpt_comparison.py

@@ -248,7 +248,7 @@ plt.legend(handles=custom_lines, loc='lower right')
 plt.xscale('log')
 plt.yscale('log')
 plt.xlabel(f"Period ({period_units})")
-plt.ylabel("Duty cycle")
+plt.ylabel("Pulse duty cycle")
 
 plt.tight_layout()
 plt.savefig('lpt_comparison.pdf')

### 2025-05-18 paper/main.tex
Switched from AASTeX to MNRAS templates

@@
-%% Beginning of file 'sample631.tex'
-%%
-%% Modified 2022 May  
-%%
-%% This is a sample manuscript marked up using the
-%% AASTeX v6.31 LaTeX 2e macros.
-%%
-%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
-%% (Copyright 2000-2015).  See the classfile for details.
+% mnras_template.tex 
+%
+% LaTeX template for creating an MNRAS paper
+%
+% v3.3 released April 2024
+% (version numbers match those of mnras.cls)
+%
+% Copyright (C) Royal Astronomical Society 2015
+% Authors:
+% Keith T. Smith (Royal Astronomical Society)
 
-%% AASTeX requires revtex4-1.cls and other external packages such as
-%% latexsym, graphicx, amssymb, longtable, and epsf.  Note that as of 
-%% Oct 2020, APS now uses revtex4.2e for its journals but remember that 
-%% AASTeX v6+ still uses v4.1. All of these external packages should 
-%% already be present in the modern TeX distributions but not always.
-%% For example, revtex4.1 seems to be missing in the linux version of
-%% TexLive 2020. One should be able to get all packages from www.ctan.org.
-%% In particular, revtex v4.1 can be found at 
-%% https://www.ctan.org/pkg/revtex4-1.
+% Change log
+%
+% v3.3 April 2024
+%   Updated \pubyear to print the current year automatically
+% v3.2 July 2023
+%	Updated guidance on use of amssymb package
+% v3.0 May 2015
+%    Renamed to match the new package name
+%    Version number matches mnras.cls
+%    A few minor tweaks to wording
+% v1.0 September 2013
+%    Beta testing only - never publicly released
+%    First version: a simple (ish) template for creating an MNRAS paper
 
-%% The first piece of markup in an AASTeX v6.x document is the \documentclass
-%% command. LaTeX will ignore any data that comes before this command. The 
-%% documentclass can take an optional argument to modify the output style.
-%% The command below calls the preprint style which will produce a tightly 
-%% typeset, one-column, single-spaced document.  It is the default and thus
-%% does not need to be explicitly stated.
-%%
-%% using aastex version 6.3
-\documentclass[preprint2,linenumbers]{aastex631}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Basic setup. Most papers should leave these options alone.
+\documentclass[fleqn,usenatbib]{mnras}
 
-\usepackage{amsmath}
+% MNRAS is set in Times font. If you don't have this installed (most LaTeX
+% installations will be fine) or prefer the old Computer Modern fonts, comment
+% out the following line
+\usepackage{newtxtext,newtxmath}
+% Depending on your LaTeX fonts installation, you might get better results with one of these:
+%\usepackage{mathptmx}
+%\usepackage{txfonts}
 
-%% The default is a single spaced, 10 point font, single spaced article.
-%% There are 5 other style options available via an optional argument. They
-%% can be invoked like this:
-%%
-%% \documentclass[arguments]{aastex631}
-%% 
-%% where the layout options are:
-%%
-%%  twocolumn   : two text columns, 10 point font, single spaced article.
-%%                This is the most compact and represent the final published
-%%                derived PDF copy of the accepted manuscript from the publisher
-%%  manuscript  : one text column, 12 point font, double spaced article.
-%%  preprint    : one text column, 12 point font, single spaced article.  
-%%  preprint2   : two text columns, 12 point font, single spaced article.
-%%  modern      : a stylish, single text column, 12 point font, article with
-%%      wider left and right margins. This uses the Daniel
-%%      Foreman-Mackey and David Hogg design.
-%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
-%%                but now that abstracts are required this is obsolete for
-%%                AAS Journals. Authors might need it for other reasons. DO NOT
-%%                use \begin{abstract} and \end{abstract} with this style.
-%%
-%% Note that you can submit to the AAS Journals in any of these 6 styles.
-%%
-%% There are other optional arguments one can invoke to allow other stylistic
-%% actions. The available options are:
-%%
-%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
-%%   tighten      : Makes baselineskip slightly smaller, only works with 
-%%                  the twocolumn substyle.
-%%   times        : uses times font instead of the default
-%%   linenumbers  : turn on lineno package.
-%%   trackchanges : required to see the revision mark up and print its output
-%%   longauthor   : Do not use the more compressed footnote style (default) for 
-%%                  the author/collaboration/affiliations. Instead print all
-%%                  affiliation information after each name. Creates a much 
-%%                  longer author list but may be desirable for short 
-%%                  author papers.
-%% twocolappendix : make 2 column appendix.
-%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
-%%                  for dual anonymous review.
-%%
-%% these can be used in any combination, e.g.
-%%
-%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
-%%
-%% AASTeX v6.* now includes \hyperref support. While we have built in specific
-%% defaults into the classfile you can manually override them with the
-%% \hypersetup command. For example,
-%%
-%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
-%%
-%% will change the color of the internal links to red, the links to the
-%% bibliography to green, the file links to cyan, and the external links to
-%% magenta. Additional information on \hyperref options can be found here:
-%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
-%%
-%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
-%% to improve the accessibility of the compiled pdf file.
-%%
-%% If you want to create your own macros, you can do so
-%% using \newcommand. Your macros should appear before
-%% the \begin{document} command.
-%%
-\newcommand{\vdag}{(v)^\dagger}
-\newcommand\aastex{AAS\TeX}
-\newcommand\latex{La\TeX}
+% Use vector fonts, so it zooms properly in on-screen viewing software
+% Don't change these lines unless you know what you are doing
+\usepackage[T1]{fontenc}
+
+% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
+% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
+\DeclareRobustCommand{\VAN}[3]{#2}
+\let\VANthebibliography\thebibliography
+\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
+
+%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
+
+% Only include extra packages if you really need them.
+Avoid using amssymb if newtxmath is enabled, as these packages can cause conflicts.
+newtxmatch covers the same math symbols while producing a consistent Times New Roman font.
+Common packages are:
+\usepackage{graphicx}	% Including figure files
+\usepackage{amsmath}	% Advanced maths commands
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
+
+% Please keep new commands to a minimum, and use \newcommand not \def to avoid
+% overwriting existing commands. Example:
+%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
 
@@
 
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2
-%\received{March 1, 2021}
-%\revised{April 1, 2021}
-%\accepted{\today}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%% Command to document which AAS Journal the manuscript was submitted to.
-%% Adds "Submitted to " the argument.
-%\submitjournal{PSJ}
+%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
 
-%% For manuscript that include authors in collaborations, AASTeX v6.31
-%% builds on the \collaboration command to allow greater freedom to 
-%% keep the traditional author+affiliation information but only show
-%% subsets. The \collaboration command now must appear AFTER the group
-%% of authors in the collaboration and it takes TWO arguments. The last
-%% is still the collaboration identifier. The text given in this
-%% argument is what will be shown in the manuscript. The first argument
-%% is the number of author above the \collaboration command to show with
-%% the collaboration text. If there are authors that are not part of any
-%% collaboration the \nocollaboration command is used. This command takes
-%% one argument which is also the number of authors above to show. A
-%% dashed line is shown to indicate no collaboration. This example manuscript
-%% shows how these commands work to display specific set of authors 
-%% on the front page.
-%%
-%% For manuscript without any need to use \collaboration the 
-%% \AuthorCollaborationLimit command from v6.2 can still be used to 
-%% show a subset of authors.
-%
-%\AuthorCollaborationLimit=2
-%
-%% will only show Schwarz & Muench on the front page of the manuscript
-%% (assuming the \collaboration and \nocollaboration commands are
-%% commented out).
-%%
-%% Note that all of the author will be shown in the published article.
-%% This feature is meant to be used prior to acceptance to make the
-%% front end of a long author article more manageable. Please do not use
-%% this functionality for manuscripts with less than 20 authors. Conversely,
-%% please do use this when the number of authors exceeds 40.
-%%
-%% Use \allauthors at the manuscript end to show the full author list.
-%% This command should only be used with \AuthorCollaborationLimit is used.
+% Title of the paper, and the short title which is used in the headers.
+% Keep the title short and informative.
+\title[Confirmation of \src{} as LPT]{Confirmation of \srcfull{} as a long period radio transient}
 
-%% The following command can be used to set the latex table counters.  It
-%% is needed in this document because it uses a mix of latex tabular and
-%% AASTeX deluxetables.  In general it should not be needed.
-%\setcounter{table}{1}
+% The list of authors, and the short list which is used in the headers.
+% If you need two or more lines of authors, add an extra line using \newauthor
+\author[S. J. McSweeney et al.]{
+Samuel J. McSweeney,$^{1}$
+Natasha Hurley-Walker,$^{1}$
+Dougal Dobie$^{2,3}$
+Csanad Horv\'{a}th$^{1}$
+Angie Waszewski$^{1}$
+John Morgan$^{1}$
+and Ziteng Wang$^{1}$
+\\
+% List of institutions
+$^{1}$International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia\\
+$^{2}$Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia\\
+$^{3}$ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav), Hawthorn, VIC 3122, Australia
+}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%% The following section outlines numerous optional output that
-%% can be displayed in the front matter or as running meta-data.
-%%
-%% If you wish, you may supply running head information, although
-%% this information may be modified by the editorial offices.
-%\shorttitle{AASTeX v6.3.1 Sample article}
-%\shortauthors{Schwarz et al.}
-%%
-%% You can add a light gray and diagonal water-mark to the first page 
-%% with this command:
-%% \watermark{text}
-%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
-%% long you can control the water-mark size with:
-%% \setwatermarkfontsize{dimension}
-%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\graphicspath{{./}{figures/}}
-%% This is the end of the preamble.  Indicate the beginning of the
-%% manuscript itself with \begin{document}.
+% These dates will be filled out by the publisher
+\date{Accepted XXX. Received YYY; in original form ZZZ}
 
+% Prints the current year, for the copyright statements etc. To achieve a fixed year, replace the expression with a number. 
+\pubyear{\the\year{}}
+
+% Don't change these lines
 \begin{document}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
 
-\title{Confirmation of \srcfull{} as a long period radio transient}
-
-%% LaTeX will automatically break titles if they run longer than
-%% one line. However, you may use \\ to force a line break if
-%% you desire. In v6.31 you can include a footnote in the title.
-
-%% A significant change from earlier AASTEX versions is in the structure for 
-%% calling author and affiliations. The change was necessary to implement 
-%% auto-indexing of affiliations which prior was a manual process that could 
-%% easily be tedious in large author manuscripts.
-%%
-%% The \author command is the same as before except it now takes an optional
-%% argument which is the 16 digit ORCID. The syntax is:
-%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
-%%
-%% This will hyperlink the author name to the author's ORCID page. Note that
-%% during compilation, LaTeX will do some limited checking of the format of
-%% the ID to make sure it is valid. If the "orcid-ID.png" image file is 
-%% present or in the LaTeX pathway, the OrcID icon will appear next to
-%% the authors name.
-%%
-%% Use \affiliation for affiliation information. The old \affil is now aliased
-%% to \affiliation. AASTeX v6.31 will automatically index these in the header.
-%% When a duplicate is found its index will be the same as its previous entry.
-%%
-%% Note that \altaffilmark and \altaffiltext have been removed and thus 
-%% can not be used to document secondary affiliations. If they are used latex
-%% will issue a specific error message and quit. Please use multiple 
-%% \affiliation calls for to document more than one affiliation.
-%%
-%% The new \altaffiliation can be used to indicate some secondary information
-%% such as fellowships. This command produces a non-numeric footnote that is
-%% set away from the numeric \affiliation footnotes.  NOTE that if an
-%% \altaffiliation command is used it must come BEFORE the \affiliation call,
-%% right after the \author command, in order to place the footnotes in
-%% the proper location.
-%%
-%% Use \email to set provide email addresses. Each \email will appear on its
-%% own line so you can put multiple email address in one \email call. A new
-%% \correspondingauthor command is available in V6.31 to identify the
-%% corresponding author of the manuscript. It is the author's responsibility
-%% to make sure this name is also in the author list.
-%%
-%% While authors can be grouped inside the same \author and \affiliation
-%% commands it is better to have a single author for each. This allows for
-%% one to exploit all the new benefits and should make book-keeping easier.
-%%
-%% If done correctly the peer review system will be able to
-%% automatically put the author and affiliation information from the manuscript
-%% and save the corresponding author the trouble of entering it by hand.
-
-%\correspondingauthor{August Muench}
-%\email{greg.schwarz@aas.org, gus.muench@aas.org}
-
-\author[0000-0001-6114-7469]{Samuel J. McSweeney}
-\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}
-
-\author[0000-0002-5119-4808]{Natasha Hurley-Walker}
-\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}
-
-\author{Dougal Dobie}
-\affiliation{Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia}
-\affiliation{ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav), Hawthorn, VIC 3122, Australia}
-
-\author[0009-0003-0996-9176]{Csanad Horv\'{a}th}
-\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}
-
-\author{Angie Waszewski}
-\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}
-
-\author{John Morgan}
-\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}
-
-\author{Ziteng Wang}
-\affiliation{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}
-
-%\collaboration{20}{(AAS Journals Data Editors)}
-
-% Example with "altaffiliation"
-%\author{Amy Hendrickson}
-%\altaffiliation{AASTeX v6+ programmer}
-%\affiliation{TeXnology Inc.}
-
-%% Note that the \and command from previous versions of AASTeX is now
-%% depreciated in this version as it is no longer necessary. AASTeX 
-%% automatically takes care of all commas and "and"s between authors names.
-
-%% AASTeX 6.31 has the new \collaboration and \nocollaboration commands to
-%% provide the collaboration status of a group of authors. These commands 
-%% can be used either before or after the list of corresponding authors. The
-%% argument for \collaboration is the collaboration identifier. Authors are
-%% encouraged to surround collaboration identifiers with ()s. The 
-%% \nocollaboration command takes no argument and exists to indicate that
-%% the nearby authors are not part of surrounding collaborations.
-
-%% Mark off the abstract in the ``abstract'' environment. 
+% Abstract of the paper
 \begin{abstract}
-
-  [Abstract goes here\dots]
-
+\dots
 \end{abstract}
 
-%% Keywords should appear after the \end{abstract} command. 
-%% The AAS Journals now uses Unified Astronomy Thesaurus concepts:
-%% https://astrothesaurus.org
-%% You will be asked to selected these concepts during the submission process
-%% but this old "keyword" functionality is maintained in case authors want
-%% to include these concepts in their preprints.
-%\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of astronomy(1868) --- Interdisciplinary astronomy(804)}
+% Select between one and six entries from the list of approved keywords.
+% Don't make up new ones.
+\begin{keywords}
+radio continuum: transients -- white dwarfs
+\end{keywords}
 
-%% From the front matter, we move on to the body of the paper.
-%% Sections are demarcated by \section and \subsection, respectively.
-%% Observe the use of the LaTeX \label
-%% command after the \subsection to give a symbolic KEY to the
-%% subsection for cross-referencing in a \ref command.
-%% You can use LaTeX's \ref and \label commands to keep track of
-%% cross-references to sections, equations, tables, and figures.
-%% That way, if you change the order of any elements, LaTeX will
-%% automatically renumber them.
-%%
-%% We recommend that authors also use the natbib \citep
-%% and \citet commands to identify citations.  The citations are
-%% tied to the reference list via symbolic KEYs. The KEY corresponds
-%% to the KEY in the \bibitem in the reference list below.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{deluxetable*}{lllccc}
-  \tablecaption{Observations summary\label{tbl:obs}}
-  \tablehead{
-    \colhead{Date range} & \colhead{Telescope} & Project & \colhead{$\nu$} & \colhead{$\Delta\nu$} & \colhead{Number of} \\ 
-    \colhead{(MJD)} & & & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{pulses}
-  } 
-  \startdata
-  59965 & ASKAP\tablenotemark{a} & SB47253 & 887.5 & 288 & 1 \\
+\begin{table*}
+  \centering
+  \caption{Observations summary}
+  \label{tbl:obs}
+  \begin{tabular}{lllccc}
+    \hline
+    Date range & Telescope & Project & $\nu$ & $\Delta\nu$ & Number of \\ 
+    (MJD) & & & (MHz) & (MHz) & pulses \\
+    \hline 
+    59965 & ASKAP & SB47253 (original discovery) & 887.5 & 288 & 1 \\
     59966 & MWA & G0060 & 161.92 & 15.36 & 1 \\
@@
     60602 & MeerKAT & DDT-20241015-NH-01 & 812.8 & 495.3 & 1 \\
-  \enddata
-  \tablenotetext{a}{Original discovery \citepalias{2024MNRAS.535..909D}}
-\end{deluxetable*}
+    \hline
+  \end{tabular}
+\end{table*}
 
@@
 \begin{table}
+  \centering
   \caption{Timing ephemeris for \src{}}
@@
   \begin{tabular}{lc}
-    \tableline
+    \hline
     Parameter & Value \\
-    \tableline
+    \hline
     Period (s) & $4186.3283 \pm 0.0003$ \\
@@
     DM (pc/cm$^{-3}$) & $764 \pm 25$ \\
-    $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$\tablenotemark{a} \\
-    \tableline
+    $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$ \\
+    \hline
   \end{tabular}
- \tablenotetext{a}{Assumed value, degenerate with DM (see main text).}
 \end{table}
@@
     \includegraphics[width=0.98\linewidth]{lpt_comparison.pdf}
-    \caption{Duty cycle vs radio pulse period for various classes of radio emitters.
+    \caption{Duty cycle vs radio pulse period for various classes of radio emitters \citep{2024arXiv240707480D,2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C,2005Natur.434...50H,2024arXiv240811536D,Lee2025}.
 The duty cycles are derived from the reported pulse widths for LPTs, which are compared to the range of the fitted, unscattered pulse widths of \src{} at 10\% of the peak.
-AR\,Sco \citep{2016Natur.537..374M,2018A&A...611A..66S} and other sources without well-defined periods or duty cycles \citep[e.g.][and references therein]{2021ApJ...920...45W} are not included on this plot.
-    \nocite{2024arXiv240707480D,2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C,2005Natur.434...50H,2024arXiv240811536D,Lee2025}}
+AR\,Sco \citep{2016Natur.537..374M,2018A&A...611A..66S} and other sources without well-defined periods or duty cycles \citep[e.g.][and references therein]{2021ApJ...920...45W} are not included on this plot.}
     \label{fig:lpt_comparison}
@@
 
-\begin{acknowledgments}
+\section*{Acknowledgements}
+
 N.H.-W. is the recipient of an Australian Research Council Future Fellowship (project number FT190100231).
@@
 
-\end{acknowledgments}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Data Availability}
 
-%% To help institutions obtain information on the effectiveness of their 
-%% telescopes the AAS Journals has created a group of keywords for telescope 
-%% facilities.
-%
-%% Following the acknowledgments section, use the following syntax and the
-%% \facility{} or \facilities{} macros to list the keywords of facilities used 
-%% in the research for the paper.  Each keyword is check against the master 
-%% list during copy editing.  Individual instruments can be provided in 
-%% parentheses, after the keyword, but they are not verified.
+\dots
 
-%\vspace{5mm}
-%\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
-%CTIO:1.5m,CXO}
+%The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS.
+Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article.
+The statement may refer to original data generated in the course of the study or to third-party data analysed in the article.
+The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.
 
-%% Similar to \facility{}, there is the optional \software command to allow 
-%% authors a place to specify which programs were used during the creation of 
-%% the manuscript. Authors should list each code and include either a
-%% citation or url to the code inside ()s when available.
+%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
 
-%\software{astropy \citep{2013A&A...558A..33A,2018AJ....156..123A},  
-%          Cloudy \citep{2013RMxAA..49..137F}, 
-%          Source Extractor \citep{1996A&AS..117..393B}
-%          }
+% The best way to enter references is to use BibTeX:
 
-%% Appendix material should be preceded with a single \appendix command.
-%% There should be a \section command for each appendix. Mark appendix
-%% subsections with the same markup you use in the main body of the paper.
+\bibliographystyle{mnras}
+\bibliography{biblio} % if your bibtex file is called example.bib
 
-%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
-%% The equation counter will reset when it encounters the \appendix
-%% command and will number appendix equations (A1), (A2), etc. The
-%% Figure and Table counter will not reset.
+% Alternatively you could enter them by hand, like this:
+% This method is tedious and prone to error if you have lots of references
+%\begin{thebibliography}{99}
+%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
+%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
+%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
+%Others S., 2012, Journal of Interesting Stuff, 17, 198
+%\end{thebibliography}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
 
@@
 This exceeds the DM reported in this work by ${\sim}450\,$pc\,cm$^{-3}$, in excess of the prediction shown in panel (d), but consistent within measurement errors.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\bibliography{biblio}{}
-\bibliographystyle{aasjournal}
-
-%% This command is needed to show the entire author+affiliation list when
-%% the collaboration and author truncation commands are used.  It has to
-%% go at the end of the manuscript.
-%\allauthors
-
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
-
+% Don't change these lines
+\bsp	% typesetting comment
+\label{lastpage}
 \end{document}
 
-% End of file `sample631.tex'.
+% End of mnras_template.tex

### 2025-05-18 paper/main.tex
Fixed various small typesetting errors in main.tex

@@
 according to each observation's centre frequency.
-A pulse stack containing all observed pulses and the corresponding unscattered pulses derived from the fits is shown in Fig. \ref{fig:pulsestack}.
+A pulse stack containing all observed pulses and the corresponding unscattered pulses derived from the fits is shown in \Fig~\ref{fig:pulsestack}.
 
@@
 
-This is demonstrated in Fig. \ref{fig:stacked_spectra}, which shows stacked MWA and MeerKAT spectra.
+This is demonstrated in \Fig~\ref{fig:stacked_spectra}, which shows stacked MWA and MeerKAT spectra.
 The cyan lines show the expected ToAs across the whole observed frequency range if one assumes only a DM measured at higher frequencies, where scattering is negligible.
-The scattering predicted by Galactic electron density models, however, is sufficient to account for the apparent extra delay, as is evidenced by the relatively good agreement with the modelled unscattered pulses with the expected ToAs derived from the ephemeris, illustrated in the pulsestack shown in Fig.
-\ref{fig:pulsestack}.
+The scattering predicted by Galactic electron density models, however, is sufficient to account for the apparent extra delay, as is evidenced by the relatively good agreement with the modelled unscattered pulses with the expected ToAs derived from the ephemeris, illustrated in the pulsestack shown in \Fig~\ref{fig:pulsestack}.
 
-\begin{figure}[th]
+\begin{figure}{th}
       \centering
@@
 
-These ToAs were then barycentred and fit for both period and DM, resulting in the values given in Table \ref{tbl:ephemeris}.
+These ToAs were then barycentred and fit for both period and DM, resulting in the values given in \Tab~\ref{tbl:ephemeris}.
 The residuals are plotted in \ref{fig:pulse_details}, along with the fitted pulse widths and fluences.
@@
 
-\begin{figure*}[th]
+\begin{figure*}{th}
   \centering
@@
 \end{equation}
-where PEPOCH and the period, $P$, are given in Table \ref{tbl:ephemeris},
+where PEPOCH and the period, $P$, are given in \Tab~\ref{tbl:ephemeris},
 \begin{equation}
@@
 is the amount that the \emph{peak} of the observed pulse is delayed by scattering.
-When calculating this quantity, we recommend using $\sigma = 15\,$s, a typical value for low-frequency pulses (see Fig. \ref{fig:pulse_details}).
+When calculating this quantity, we recommend using $\sigma = 15\,$s, a typical value for low-frequency pulses (see \Fig~\ref{fig:pulse_details}).
 At frequencies above $300\,$MHz, $\tau(\nu) \ll \sigma$, and the delay due to scattering, which asymptotically behaves like $\Delta t_{\rm sc}(\nu) \sim \tau$, can be safely neglected.
@@
 $L_{\rm 1\,GHz}$ is the flux density of the linearly polarised component at 1\,GHz, $\alpha_L$ is its spectral index, RM is the rotation measure, $\lambda = c/\nu$ is the wavelength, and $\psi_0$ is the intrinsic polarisation angle.
-The RMs and spectral indices of these fits are shown in the top two rows of panels of Fig. \ref{fig:RM}.
+The RMs and spectral indices of these fits are shown in the top two rows of panels of \Fig~\ref{fig:RM}.
 
-\begin{figure*}[th]
+\begin{figure*}{th}
     \centering
@@
 We found that the RM derived for the MeerKAT pulse had the opposite sign, but similar magnitude, to the ASKAP pulses, which is most likely due to a different sign convention being used within the two telescopes' pre-processing software.
-The agreement presented in Fig. \ref{fig:RM} was achieved by first negating Stokes Q in the MeerKAT data.
+The agreement presented in \Fig~\ref{fig:RM} was achieved by first negating Stokes Q in the MeerKAT data.
 Any reflection in the Q-U plane (e.g.
@@
 With the timing solution in hand, we can explore the efficacy of the original follow-up campaign described in \citetalias{2024MNRAS.535..909D}.
-Assuming \src{} remained at a similar brightness (see Fig.
-\ref{fig:pulse_details}), it should have been detected in two ASKAP observations (2023-04-06 and 2023-10-18) and a few dozen times throughout the MWA's 2022 GPM run (2022-06-02 to 2022-09-08).
+Assuming \src{} remained at a similar brightness (see \Fig~\ref{fig:pulse_details}), it should have been detected in two ASKAP observations (2023-04-06 and 2023-10-18) and a few dozen times throughout the MWA's 2022 GPM run (2022-06-02 to 2022-09-08).
 There are also three observations in the earliest part of the 2024 GPM run (one on 2024-06-02 and two on 2024-06-10) in which no pulse was observed.
-However, pulses were detected just ten days later on 2024-06-20 (the first of the MWA 200\,MHz points in Fig.
-\ref{fig:pulse_details}), and at each epoch thereafter whenever the MWA was observing in \src{}'s direction when a pulse was due to arrive.
+However, pulses were detected just ten days later on 2024-06-20 (the first of the MWA 200\,MHz points in \Fig~\ref{fig:pulse_details}), and at each epoch thereafter whenever the MWA was observing in \src{}'s direction when a pulse was due to arrive.
 
@@
 
-\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are confirmed polars (Fig.
-\ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is a WD-MD polar system.
+\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are confirmed polars (\Fig~\ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is a WD-MD polar system.
 However, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for confirmed polars \citep{schwope2025polarcatcatalogpolarslowaccretion}.
 This makes it an interesting testbed for the suggestion advanced by \citet{2025arXiv250103315R} that ``short LPTs'' ($P \lesssim 78\,$mins) and ``long LPTs'' ($P \gtrsim 78\,$mins) represent different classes of systems (AM CVns and CVs, respectively).
-\begin{figure*}[th]
+\begin{figure*}{th}
     \centering
@@
 
-\begin{figure}[th]
+\begin{figure*}{th}
     \centering
@@
     \label{fig:scattering_DM}
-\end{figure}
+\end{figure*}
 
 We computed numerically \citep[using SciPy's \texttt{root} function;][]{2020NatMe..17..261V} the errors for the four ToA types defined above, in the regime around $\tau \approx \sigma$.
-These are shown in the panel (a) of Fig. \ref{fig:scattering_DM}, normalised to the scale of the pulse, $\sigma$.
+These are shown in the panel (a) of \Fig~\ref{fig:scattering_DM}, normalised to the scale of the pulse, $\sigma$.
 The axis along the top shows the normalised timescale (inverted, with largest timescales on the left), while the axis along the bottom shows the equivalent frequencies normalised to $\nu_s$, defined as the frequency at which $\tau = \sigma$.
@@
 with TMPL) where the scattering is known to be negligible, and (2) by measuring the slope of the pulse in the dynamic spectrum (for example, by measuring the ToAs in subbands across the observed frequency range).
-Panel (c) of Fig. \ref{fig:scattering_DM} shows the expected slope measurements for the ToA errors given in the panel (a).
+Panel (c) of \Fig~\ref{fig:scattering_DM} shows the expected slope measurements for the ToA errors given in the panel (a).
 

### 2025-05-18 paper/main.tex
Added parallactic angle correction to MeerKAT data, and other tiny textual changes

@@
 \author[S. J. McSweeney et al.]{
-Samuel J. McSweeney,$^{1}$
-Natasha Hurley-Walker,$^{1}$
-Dougal Dobie$^{2,3}$
-Csanad Horv\'{a}th$^{1}$
-Angie Waszewski$^{1}$
-John Morgan$^{1}$
+Samuel J. McSweeney$^{1}$,
+Natasha Hurley-Walker$^{1}$,
+Dougal Dobie$^{2,3}$,
+Cs\'{a}nad Horv\'{a}th$^{1}$,
+\newauthor
+Angie Waszewski$^{1}$,
+John Morgan$^{1}$,
 and Ziteng Wang$^{1}$
@@
 \begin{equation}
-  \begin{aligned}
-        \emg(t) &= A \frac{\sigma}{\tau}\sqrt{\frac{\pi}{2}}
-                   \exp\left(-\frac12 \left( \frac{t - \mu}{\tau} \right)^2 \right) \cdot {} \\
-                            &\qquad \erfcx \left(\frac{1}{\sqrt{2}} \left(\frac{\sigma}{\tau} 
-                             - \frac{t - \mu}{\tau} \right) \right),
-  \end{aligned}
+  \emg(t) = A \frac{\sigma}{\tau}\sqrt{\frac{\pi}{2}}
+    \exp\left(-\frac12 \left( \frac{t - \mu}{\tau} \right)^2 \right)  \erfcx \left(\frac{1}{\sqrt{2}} \left(\frac{\sigma}{\tau} - \frac{t - \mu}{\tau} \right) \right),
   \label{eqn:emg}
@@
 The three sufficiently bright pulses for which we report significant polarisation are (1) the original 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, (2) the 2024 ASKAP pulse, and (3) the 2024 MeerKAT pulse.
+We applied the parallactic angle correction to the MeerKAT data, as this had not already been applied during upstream processing.
+
 The high S/N of each time bin allowed us to test whether the rotation measure (RM) was consistent across each pulse.
@@
 
-As noted in \citetalias{2024MNRAS.535..909D}, optical follow-up of \src{} is challenging due to its proximity to the Galactic plane ($b = -0.12^\circ$).
+As noted in \citetalias{2024MNRAS.535..909D}, optical follow-up of \src{} is hampered by its proximity to the Galactic plane ($b = -0.12^\circ$).
 Inferring this nature of the system (white dwarf vs neutron star, isolated vs binary) from the radio pulses alone is challenging, unless either the population of LPTs is better understood as a whole, or if some other property of the radio signal (e.g.

### 2025-05-18 dynspec/measure_rm.py

@@ -4,7 +4,7 @@ import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
 import astropy.units as u
 from astropy.time import Time
-from astropy.coordinates import SkyCoord, EarthLocation
+from astropy.coordinates import SkyCoord, EarthLocation, AltAz
 from astropy.constants import c
 import sys
 import argparse
@@ -20,6 +20,7 @@ data = [
         'ToA': Time(59965.042934515615, scale='utc', format='mjd'),
         'xlim': [-149, 149],
         'title': "ASKAP, MJD 59965, 888 MHz",
+        'do_parallactic_angle_correction': False,
     },
     {
         'ds_file': '1404832334_askap.pkl',
@@ -27,6 +28,7 @@ data = [
         'ToA': Time(60503.63475701395, scale='utc', format='mjd'),
         'xlim': [-149, 149],
         'title': "ASKAP, MJD 60503, 888 MHz",
+        'do_parallactic_angle_correction': False,
     },
     {
         'ds_file': '1413381294_meerkat.pkl',
@@ -35,6 +37,7 @@ data = [
         'ToA': Time(60602.58357327181, scale='utc', format='mjd'),
         'xlim': [-199, 99],
         'title': "MeerKAT, MJD 60602, 813 MHz",
+        'do_parallactic_angle_correction': True,
     },
 ]
 
@@ -178,6 +181,17 @@ def main():
         if data[i]['flip_RM'] == True:
             Q *= -1
 
+        # MeerKAT also needs to have parallactic angle correction applied to it
+        parallactic_angle = 0*u.deg # Default behaviour = assume correction has already been applied
+        if data[i]['do_parallactic_angle_correction'] == True:
+            location = EarthLocation.of_site(dat['TELESCOPE'])
+            lst = t[0].sidereal_time('apparent', longitude=location.lon)
+            H = lst - ephem['coord'].ra
+            φ = location.lat
+            δ = ephem['coord'].dec
+            parallactic_angle = np.arctan2(np.sin(H), np.tan(φ)*np.cos(δ) - np.sin(δ)*np.cos(H))
+            print(f"Applying parallactic angle of {parallactic_angle.to('deg')}")
+
         RMs = []
         alphas = []
         alpha_errs = []
@@ -223,7 +237,7 @@ def main():
[…]

### 2025-05-18 paper/main.tex
Updated references (arXiv -> published)

@@
 
-Although optical follow-up has confirmed that at least some LPTs are white dwarfs with main sequence companions \citep{2024arXiv240811536D,2025arXiv250103315R}, it remains unclear if this model can account for all known LPTs \citep[e.g.][]{2022ApJ...940...72R,Lee2025}.
+Although optical follow-up has confirmed that at least some LPTs are white dwarfs with main sequence companions \citep{deRuiter2025,2025A&A...695L...8R}, it remains unclear if this model can account for all known LPTs \citep[e.g.][]{2022ApJ...940...72R,Lee2025}.
 Unfortunately, optical follow-up is not possible for LPTs and LPT candidates which are obscured by Galactic foregrounds.
@@
 After accounting for dispersion and scattering effects, the timing analysis of \src{} confirms its status as an LPT, as originally conjectured in \citetalias{2024MNRAS.535..909D}.
-It has the fifth largest period (${\sim}1.16\,$hours) of known published LPTs, after ASKAP J1839$-$0756 \citep[$6.45\,$hours;][]{Lee2025}, GLEAM-X J0704$-$37 \citep[$2.92\,$hours;][]{2024arXiv240815757H, 2025arXiv250103315R}, ILT J1101+5521 \citep[$2.09\,$hours;][]{deRuiter2025}, and GCRT J1745$-$3009 \citep[$1.28\,$hours;][]{2005Natur.434...50H}.
+It has the fifth largest period (${\sim}1.16\,$hours) of known published LPTs, after ASKAP J1839$-$0756 \citep[$6.45\,$hours;][]{Lee2025}, GLEAM-X J0704$-$37 \citep[$2.92\,$hours;][]{2024ApJ...976L..21H,2025A&A...695L...8R}, ILT J1101+5521 \citep[$2.09\,$hours;][]{deRuiter2025}, and GCRT J1745$-$3009 \citep[$1.28\,$hours;][]{2005Natur.434...50H}.
 
@@
 However, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for confirmed polars \citep{schwope2025polarcatcatalogpolarslowaccretion}.
-This makes it an interesting testbed for the suggestion advanced by \citet{2025arXiv250103315R} that ``short LPTs'' ($P \lesssim 78\,$mins) and ``long LPTs'' ($P \gtrsim 78\,$mins) represent different classes of systems (AM CVns and CVs, respectively).
+This makes it an interesting testbed for the suggestion advanced by \citet{2025A&A...695L...8R} that ``short LPTs'' ($P \lesssim 78\,$mins) and ``long LPTs'' ($P \gtrsim 78\,$mins) represent different classes of systems (AM CVns and CVs, respectively).
 \begin{figure*}{th}
@@
     \includegraphics[width=0.98\linewidth]{lpt_comparison.pdf}
-    \caption{Duty cycle vs radio pulse period for various classes of radio emitters \citep{2024arXiv240707480D,2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C,2005Natur.434...50H,2024arXiv240811536D,Lee2025}.
+    \caption{Duty cycle vs radio pulse period for various classes of radio emitters \citep{deRuiter2025,2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C,2005Natur.434...50H,deRuiter2025,Lee2025}.
 The duty cycles are derived from the reported pulse widths for LPTs, which are compared to the range of the fitted, unscattered pulse widths of \src{} at 10\% of the peak.
@@
 
-Although there is as yet no clear consensus on whether LPTs represent one class or multiple classes of system \citep[e.g.][]{2024ApJ...961..214R}, the recent confirmation of J1912$-$4410 as a pre-evolved white dwarf pulsar \citep{2023NatAs...7..931P} and ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 as polars \citep{2024arXiv240811536D,2025arXiv250103315R} raise the intriguing possibility that other LPTs may also be radio-emitting white dwarf pulsars at various stages of evolution \citep{2021NatAs...5..648S}.
+Although there is as yet no clear consensus on whether LPTs represent one class or multiple classes of system \citep[e.g.][]{2024ApJ...961..214R}, the recent confirmation of J1912$-$4410 as a pre-evolved white dwarf pulsar \citep{2023NatAs...7..931P} and ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 as polars \citep{deRuiter2025,2025A&A...695L...8R} raise the intriguing possibility that other LPTs may also be radio-emitting white dwarf pulsars at various stages of evolution \citep{2021NatAs...5..648S}.
 

### 2025-05-18 paper/main.tex
Wrote summary in paper. Synched with Overleaf

@@
 
-In this short paper, we present new radio observations (spanning frequencies from $154\,$MHz to $1.7\,$GHz) in which \src{} was re-detected, confirming that it is indeed an LPT with a period of ${\sim}1.16\,$hours.
+In this paper, we present new radio observations (spanning frequencies from $154\,$MHz to $1.7\,$GHz) in which \src{} was re-detected, confirming that it is indeed an LPT with a period of ${\sim}1.16\,$hours.
 In \S\ref{sec:observations}, we describe the observations themselves, some of which were taken as part of independent surveys, and some of which were taken as dedicated follow-up of \src{} once it became apparent that it was still active.
@@
 Because we have not attempted to simultaneously fit for both DM and scattering timescale, there will remain some small systematic error on this reported DM measurement.
-Breaking the degeneracy is possible in principle with a much higher S/N average profile than what is achievable with the current data set.
+Note, in particular, that the YMW16 and NE2001 models predict a slightly longer scattering time scale than the $70\,$ms that we have assumed throughout this work.
+Breaking the degeneracy is possible in principle with a higher S/N average profile than what is achievable with the current data set.
 
@@
     {\rm MJD} = {\rm PEPOCH} + NP + \Delta t_{\rm DM}(\nu) + \Delta t_{\rm sc}(\nu),
+    \label{eqn:timing}
 \end{equation}
@@
 After accounting for dispersion and scattering effects, the timing analysis of \src{} confirms its status as an LPT, as originally conjectured in \citetalias{2024MNRAS.535..909D}.
-It has the fifth largest period (${\sim}1.16\,$hours) of known published LPTs, after ASKAP J1839$-$0756 \citep[$6.45\,$hours;][]{Lee2025}, GLEAM-X J0704$-$37 \citep[$2.92\,$hours;][]{2024ApJ...976L..21H,2025A&A...695L...8R}, ILT J1101+5521 \citep[$2.09\,$hours;][]{deRuiter2025}, and GCRT J1745$-$3009 \citep[$1.28\,$hours;][]{2005Natur.434...50H}.
+It has the fifth largest period (${\sim}1.16\,$hours) of published LPTs to date, after ASKAP J1839$-$0756 \citep[$6.45\,$hours;][]{Lee2025}, GLEAM-X J0704$-$37 \citep[$2.92\,$hours;][]{2024ApJ...976L..21H,2025A&A...695L...8R}, ILT J1101+5521 \citep[$2.09\,$hours;][]{deRuiter2025}, and GCRT J1745$-$3009 \citep[$1.28\,$hours;][]{2005Natur.434...50H}.
 
@@
 
-As noted in \citetalias{2024MNRAS.535..909D}, optical follow-up of \src{} is hampered by its proximity to the Galactic plane ($b = -0.12^\circ$).
-Inferring this nature of the system (white dwarf vs neutron star, isolated vs binary) from the radio pulses alone is challenging, unless either the population of LPTs is better understood as a whole, or if some other property of the radio signal (e.g.
+As noted in \citetalias{2024MNRAS.535..909D}, optical follow-up of \src{} is hampered by its proximity to the Galactic plane ($b = -0.12^\circ$) and the associated extinction.
+Inferring this nature of the system (white dwarf vs neutron star, isolated vs binary) from the radio pulses alone is challenging, until either the population of LPTs is better understood as a whole, or some other property of the radio signal (e.g.
 intermittency, polarisation) can be linked to the system properties.
@@
     \includegraphics[width=0.98\linewidth]{lpt_comparison.pdf}
-    \caption{Duty cycle vs radio pulse period for various classes of radio emitters \citep{deRuiter2025,2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C,2005Natur.434...50H,deRuiter2025,Lee2025}.
+    \caption{Duty cycle vs radio pulse period for various long period radio emitters \citep{deRuiter2025,2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C,2005Natur.434...50H,deRuiter2025,Lee2025}.
 The duty cycles are derived from the reported pulse widths for LPTs, which are compared to the range of the fitted, unscattered pulse widths of \src{} at 10\% of the peak.
-AR\,Sco \citep{2016Natur.537..374M,2018A&A...611A..66S} and other sources without well-defined periods or duty cycles \citep[e.g.][and references therein]{2021ApJ...920...45W} are not included on this plot.}
+AR\,Sco \citep{2016Natur.537..374M,2018A&A...611A..66S} and other sources without well-defined duty cycles or periods \citep[e.g.][and references therein]{2021ApJ...920...45W} are not included on this plot.}
     \label{fig:lpt_comparison}
@@
 Such outflows can last for months [CITATION??], and would not be strictly periodic.
-If intermittency is of this sort, then the observed activity windows will be similarly aperiodic, or quasiperiodic.
+If intermittency is of this kind, then the observed activity windows will be similarly aperiodic, or quasiperiodic.
 Again, long-term monitoring can help distinguish between these scenarios.
@@
 We have shown that \src{} is in fact an LPT, as conjectured in \citetalias{2024MNRAS.535..909D}).
-Its period of ${\sim}1.16\,$hours is slightly shorter than the minimum known orbital\dots
+Its period of ${\sim}1.16\,$hours is slightly shorter than the minimum known orbital period of optically confirmed polars, marking it as an interesting case study in the context of \citet{2025A&A...695L...8R}'s suggestion that `short'-LPTs and `long'-LPTs may correspond to different classes of cataclysmic variables.
+
+A timing solution has been presented (\Eqn~\ref{eqn:timing}) which includes a term to account for scattering at low frequencies ($\lesssim 300\,$MHz).
+Without it, ToA predictions may be early by up to several tens of seconds, which is a sizeable fraction of the intrinsic pulse width.
+
+The three higher-frequency pulses for which polarimetry was observable exhibited unique single-pulse polarisation behaviours.
+Only the original ASKAP detection exhibited a PA curve that was amenable to being modelled with the rotating vector model; the others show either flat, or slightly concave up PA curves (\Fig~\ref{fig:RM}).
+
+We conjecture that if \src{} is a WD pulsar, its intermittency may be a result of the spin-orbital resonance being near, but not exactly, a small-integer ratio, creating a aliased beating pattern on a time scale of months.
+The same explanation may be applied to other LPTs with activity cycles that last on the order of months.
+An alternative explanation is that the radio emission is drived by particle wind outflows from the main sequence companion.
+Long-term monitoring of LPTs will reveal whether the intermittency is periodic, and thus help discriminate between these two scenarios.
 

### 2025-05-18 paper/main.tex
Small typographical and wording changes

@@
 
-We therefore identified the times of arrival (ToAs) with the $\mu$ parameter in the fits given in Eq. \eqref{eqn:emg}, which represents the location of the assumed Gaussian pulse before scattering.
+We therefore identified the times of arrival (ToAs) with the $\mu$ parameter in the fits given in \Eqn~\ref{eqn:emg}, which represents the location of the assumed Gaussian pulse before scattering.
 Because the scattering time scale could not be reliably measured for all individual pulses, we obtained ToAs by assuming a fixed scattering time of $\tau_{\rm sc,1 GHz} = 0.07\,$s.
@@
   \includegraphics[width=0.98\linewidth]{pulse_details.pdf}
-  \caption{Timing residuals (top panel) and other pulse properties derived from the fits of Eq. \eqref{eqn:emg} to the individual light curves (lower two panels). \dots}
+  \caption{Timing residuals (top panel) and other pulse properties derived from the fits of \Eqn~\ref{eqn:emg} to the individual light curves (lower two panels). \dots}
   \label{fig:pulse_details}
@@
 is accurate to within a few seconds.
-At intermediate frequencies ($150\,{\rm MHz} \lesssim \nu \lesssim 300\,{\rm MHz}$), Eq. \eqref{eqn:scattering_delay} should be used directly.
+At intermediate frequencies ($150\,{\rm MHz} \lesssim \nu \lesssim 300\,{\rm MHz}$), \Eqn~\ref{eqn:scattering_delay} should be used directly.
 
@@
     \caption{Polarisation of the 2023 and 2024 ASKAP pulses (left and middle) and the 2024 MeerKAT pulse (right).
-The top two rows show the RM and $\alpha_{\rm lin}$ parameters fitted to Eq.
-\eqref{eqn:RM} for each time bin independently.
+The top two rows show the RM and $\alpha_{\rm lin}$ parameters fitted to \Eqn~\ref{eqn:RM} for each time bin independently.
 Only bins for which the uncertainty on $\alpha_{\rm lin}$ is less than $1.4$ are shown, a threshold which was found to cleanly eliminate off-pulse bins.
@@
 
-Interestingly, systems with spin-orbital (or beat-orbital) resonances of, e.g., 2:1 or 3:1, coupled with the idea of a limited observable orbital phase window for the radio pulses, would be indistinguishable from systems in 1:1 resonances.
-We therefore advance the possibility that the coincidence of the observed radio periodicities of ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 with their spectroscopically confirmed orbital periods does not necessarily imply that they are 1:1 polars.
+Interestingly, systems with spin-orbital (or beat-orbital) resonances of, e.g., 2:1 or 3:1, would be indistinguishable from systems in 1:1 resonances if the only pulses that can be observed occur within a limited orbital phase range.
+We therefore raise the possibility that the coincidence of the observed radio periodicities of ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 with their spectroscopically confirmed orbital periods does not necessarily imply that they are 1:1 polars.
 
-Similarly, systems in which the spin-orbit (or beat-orbit) ratios are \emph{close to} small-integer ratios, or, equivalently, systems in which precession of the WD is significant, will exhibit an extra beating effect in which an orbitally-induced intermittency is aliased to a much lower frequency.
+In a similar vein, systems in which the spin-orbit (or beat-orbit) ratios are \emph{close to} small-integer ratios, or, equivalently, systems in which precession of the WD is significant, will exhibit an extra beating effect in which an orbitally-induced intermittency is aliased to a much lower frequency.
 The month-long time scale of the intermittency of \src{}, and possibly even GLEAM-X\,J1627$-$5235, may be of this kind; much longer-term monitoring is needed to confirm or refute this.
@@
 It can be shown that pulses scatter-broadened by a thin screen will appear to the observer as the original pulse convolved with a one-sided exponential kernel with an associated timescale $\tau$ [CITATION].
-For intrinsically Gaussian pulses of scale $\sigma$, the result of this convolution is well described by the \textit{exponentially modified Gaussian} (EMG), as given in Eq. \eqref{eqn:emg}.
+For intrinsically Gaussian pulses of scale $\sigma$, the result of this convolution is well described by the \textit{exponentially modified Gaussian} (EMG), as given in \Eqn~\ref{eqn:emg}.
 

### 2025-05-19 paper/main.tex
Added words to final missing sections: data availability, abstract.

@@
 \begin{abstract}
-\dots
+We report the discovery of several new pulses from the source \srcfull{} (\src{}), confirming it as a long period transient (LPT) with a period of ${\sim}1.16\,$hours.
+The pulses are significantly scattered, consistent with Galactic electron density models.
+Two of the new pulses also had measurable polarisation, but unlike the originally detected pulse, the polarisation angle does not behave as expected from the rotating vector model.
+We interpret historical non-detections of \src{} as an intrinsic intermittency that occurs on month-long timescales, and discuss possible causes.
+We conjecture that, like other LPTs with periods $\gtrsim 1\,$hour, \src{} is a white-dwarf binary pulsar, but note that its period is marginally shorter than the minimum known polar orbital period.
 \end{abstract}
@@
 The apparent lack of polarisation in the MeerKAT data set is likely due to low S/N coupled with the source not being not being centred in the beam.
-Much more careful analysis would be needed to obtain reliable limits on the polarised components of those pulses.
+Much more careful imaging analysis would be needed to obtain reliable measurements or limits on the polarised components of those pulses.
 
@@
 
-\dots
+The raw visibilities for the MWA, ASKAP, and MeerKAT data sets are available via the respective telescopes' data portals. 
+The post-imaged dynamic spectra, analyses, and timing analysis data products (ToAs, pulse properties) are publicly available on GitHub\footnote{TODO: Make this available upon publication.}.
 

### 2025-05-19 paper/main.tex
Starting to implement a bunch of suggested changes from co-authors

@@
 \DeclareMathOperator{\erfcx}{erfcx}
+\DeclareMathOperator{\erfc}{erfc}
 \DeclareMathOperator{\erf}{erf}
@@
 \srcfull{} (hereafter, \src{}) is a transient radio source discovered in the Variables and Slow Transients (VAST) survey \citep[][hereafter \citetalias{2024MNRAS.535..909D}]{2024MNRAS.535..909D}.
-A single, highly polarized pulse was observed, lasting approximately 2 minutes, exhibiting a steep spectrum ($\alpha = -3.1$).
+A single, highly polarized pulse was observed, lasting approximately 2 minutes, exhibiting a steep spectrum ($\alpha = -3.1$, for flux density $S_\nu\propto\nu^\alpha$).
 Extensive follow up in new and archival data at multiple wavelengths turned up no other pulses.
-Despite this, the authors concluded that \src{} was most likely a long period transient (LPT), a newly emerging class of radio source with periods ranging from minutes to hours.
+Despite this, the authors concluded that \src{} was most likely a long period transient (LPT), a newly emerging class of radio source with periods ranging from minutes to hours \citep[see e.g.][]{2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C}.
 
-Although optical follow-up has confirmed that at least some LPTs are white dwarfs with main sequence companions \citep{deRuiter2025,2025A&A...695L...8R}, it remains unclear if this model can account for all known LPTs \citep[e.g.][]{2022ApJ...940...72R,Lee2025}.
-Unfortunately, optical follow-up is not possible for LPTs and LPT candidates which are obscured by Galactic foregrounds.
-This is almost certainly the case for \src{}, which is situated very close to the Galactic plane ($b = -0\overset{\circ}{.}12$), and has a dispersion measure (DM) derived distance of ${\sim}4.7\,$kpc \citepalias{2024MNRAS.535..909D}; unsurprisingly, optical follow-up at \src{}'s location did not turn up any source down to ${\sim}23$ AB mag.
+Although optical follow-up has confirmed that at least some LPTs are white dwarfs with main sequence companions \citep{deRuiter2025,2024ApJ...976L..21H,2025A&A...695L...8R}, it remains unclear if this model can account for all known LPTs \citep[e.g.][]{2022ApJ...940...72R,Lee2025}.
+Unfortunately, optical follow-up is challenging for LPTs and LPT candidates obscured by Galactic foregrounds.
+This is almost certainly the case for \src{}, which is situated very close to the Galactic plane ($b = -0\overset{\circ}{.}12$), and has a dispersion measure (DM) derived distance of ${\sim}4.7\,$kpc \citepalias{2024MNRAS.535..909D}; unsurprisingly, archival searches at \src{}'s location did not turn up any source down to ${\sim}23$ AB mag.
 Without more detections in the radio or at other wavelengths, it seemed unlikely that the nature of \src{} could ever be resolved.
@@
 
+The MWA, ASKAP and MeerKAT are all radio interferometers capable of imaging.
+A summary of all the observations included in this work is summarised in \Tab~\ref{tbl:obs}.
+In this section, we describe how each telescope was used to generate dynamic spectra of \src{}.
+
+\begin{table*}
+  \centering
+  \caption{Observations summary}
+  \label{tbl:obs}
+  \begin{tabular}{lllccc}
+    \hline
+    Date range & Telescope & Project & $\nu$ & $\Delta\nu$ & Number of \\ 
+    (MJD) & & & (MHz) & (MHz) & pulses \\
+    \hline 
+    59965 & ASKAP & SB47253 (original discovery) & 887.5 & 288 & 1 \\
+    59966 & MWA & G0060 & 161.92 & 15.36 & 1 \\
+    %60084 & MWA & G0057 & 154.24 & 30.72 & $\le$ 1 \\
+    60040  & ASKAP & SB49153 & 887.5 & 288 & 1 \\
+    60092 - 60093 & MeerKAT & DDT-20230525-DD-01 & 1284 & 856 & 4 \\
+    60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & 16 \\
+    60503 & ASKAP & SB63600 & 887.5 & 288 & 1 \\
+    60572 & MWA & D0042 & 184.96 & 30.72 & 4 \\
+    60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & 17 \\
+    60602 & MeerKAT & DDT-20241015-NH-01 & 812.8 & 495.3 & 1 \\
+    \hline
+  \end{tabular}
+\end{table*}
+
 \subsection{MWA} \label{sec:mwa}
@@
 \src{} was detected blindly with the Murchison Widefield Array \citep[MWA;][]{Tingay2013} in observations taken between June--September 2024 under the ``Galactic Plane Monitor'', project code G0080.
-The prime objective of the campaign was to search for long-period transients by scanning the Galactic plane over $285^\circ < l < 65^\circ$, $|b|<\pm15^\circ$ on a bi-weekly cadence at 185--215\,MHz (see Methods of \citet{2023Natur.619..487H}); a full description will be released by Hurley-Walker et al., in prep.
-We also observed over June--September 2022 but made no detections in these data.
+The prime objective of the campaign was to search for long-period transients by scanning the Galactic plane over $285^\circ < l < 65^\circ$, $|b|<\pm15^\circ$ on a bi-weekly cadence at 185--215\,MHz \citep[see Methods of][]{2023Natur.619..487H}; a full description will be released by Hurley-Walker et al., in prep.
+We also observed over June--September 2022 but made no detections in these data, as reported in \citetalias{2024MNRAS.535..909D}.
+Subsequent to its redetection, we commenced a Director's Discretionary Time (DDT) campaign under project code D0042, to obtain further observations, adjusting the frequency from 200.32\,MHz to 184.96\,MHz for some of the observations to attempt to improve measurements of its DM.
 
-We re-imaged the 2024 data at the location of \src{} using \textsc{WSClean}, masking \src{} itself, forming a deep model of the sky.
+We imaged both the 2024 GPM data and the follow-up DDT data at the location of \src{} using \textsc{WSClean}, masking \src{} itself, forming a deep model of the sky for each observation.
 After subtracting this from the visibilities, we phase-rotated to \src{}, and averaged the baseline data to produce a dynamic spectrum.
@@
 An additional MWA observation made as part of the MWA Interplanetary Scintillation (IPS) Survey, project code G0060, has also been included in this present study. 
-A full description of how MWA IPS observations are scheduled and processed can be found in Section~2 of \citet{Morgan2022}; here, we provide a brief overview.
+A full description of how MWA IPS observations are scheduled and processed can be found in Section~2 of \citet{Morgan2022}.
+Details of the imaging of IPS observations since the first data release can be found in Waszewski et al. (submitted).
 The two adjacent 200-second observations included in this work are a sub-section of a full 10-minute near-Sun observation (30$^{\circ}$ elongation).
-These observations are taken over two equal bands of frequency, centered on approximately 80\,MHz and 160\,MHz. For this study, only the upper band has been processed. 
-IPS observations require a short time integration of 0.5\,s, but can allow for a larger frequency resolution of 40\,kHz, which is then averaged to an even higher 160\,kHz during imaging.
-% SM: TODO: describe various scrunching I did to produce light curve in pulsestack
+These observations are taken over two equal bands of frequency, centred on approximately 80\,MHz and 160\,MHz. For this study, only the upper band has been processed. 
 The observation was self-calibrated against a sky model based on the GLEAM survey \citep{Hurley-Walker2017} using \textsc{mwa\_hyperdrive}\footnote{\url{https://github.com/MWATelescope/mwa_hyperdrive}}, and then imaged using \textsc{WSClean}.
-% NHW: then phase-rotated and averaged to produce a dynamic spectrum?
+\src{} is clearly visible as a point source in the image, and the lightcurve presented in this work is the result of averaging over the 15.36-MHz subband, using 10-second time bins.
 
 \subsection{ASKAP} \label{sec:askap}
-
-% NHW to update this in light of new historical discovery of a dim pulse in SB49153.
 
@@
 The dynamic spectrum of one of the brightest pulses is shown in \Fig~\ref{fig:scattering_DM}.
-
-A summary of all the observations used in this paper is given in \Tab~\ref{tbl:obs}.
-
-\begin{table*}
-  \centering
-  \caption{Observations summary}
-  \label{tbl:obs}
-  \begin{tabular}{lllccc}
-    \hline
-    Date range & Telescope & Project & $\nu$ & $\Delta\nu$ & Number of \\ 
-    (MJD) & & & (MHz) & (MHz) & pulses \\
-    \hline 
-    59965 & ASKAP & SB47253 (original discovery) & 887.5 & 288 & 1 \\
-    59966 & MWA & G0060 & 161.92 & 15.36 & 1 \\
-    %60084 & MWA & G0057 & 154.24 & 30.72 & $\le$ 1 \\
-    60040  & ASKAP & SB49153 & 887.5 & 288 & 1 \\
-    60092 - 60093 & MeerKAT & DDT-20230525-DD-01 & 1284 & 856 & 4 \\
-    60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & 16 \\
-    60503 & ASKAP & SB63600 & 887.5 & 288 & 1 \\
-    60572 & MWA & D0042 & 184.96 & 30.72 & 4 \\
-    60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & 17 \\
-    60602 & MeerKAT & DDT-20241015-NH-01 & 812.8 & 495.3 & 1 \\
-    \hline
-  \end{tabular}
-\end{table*}
 
@@
 The low-frequency asymmetry is consistent with a scattering time scale of a few tens of seconds at MWA frequencies, which scales to a few tens of milliseconds at 1\,GHz.
-This is in broad agreement with the model predictions of NE2001 ($\tau_{\rm sc,1GHz} = 0.066\,$s) and YMW16 ($\tau_{\rm sc,1 GHz} = 0.075\,$s) at the source's location assuming the DM value of 710\,pc\,cm$^{-3}$ reported in \citepalias{2024MNRAS.535..909D}.
+This is in broad agreement with the model predictions of NE2001 ($\tau_{\rm sc,1GHz} = 66\,$ms) and YMW16 ($\tau_{\rm sc,1 GHz} = 75\,$ms) at the source's location assuming the DM value of 710\,pc\,cm$^{-3}$ reported in \citepalias{2024MNRAS.535..909D}.
 
@@
 \end{equation}
-where $A$, $\mu$, and $\sigma$ are the height, location, and scale of an unscattered Gaussian pulse, and the scattering time scale was fixed at
+where $\erfcx(X) = \exp(X^2) \erfc(X)$ is the scaled complimentary error function; $A$, $\mu$, and $\sigma$ are the height, location, and scale of an unscattered Gaussian pulse; and the scattering time scale was fixed at
 \begin{equation}
@@
 
-Because the large scattering time scale at low frequencies significantly distorts the pulse shapes, common methods for defining ToAs can potentially result in systematic errors of up to tens of seconds, as discussed in detail in Appendix \ref{app:scattering_dm}.
+Since the large scattering time scale at low frequencies significantly distorts the pulse shapes, common methods for defining ToAs can potentially result in systematic errors of up to tens of seconds, as discussed in detail in Appendix \ref{app:scattering_dm}.
 These systematic errors set up a degeneracy between DM and scattering time scales that is not easily disambiguated.
@@
 The spectra have not been dedispersed, but the cyan dashed lines indicate where the two components seen in the MeerKAT (2024) observation would appear due to dispersion.
-The white curve in the top panel is the dedispersed profile of the MeerKAT (2024) observation, and the white curves in the bottom panel are the same profile subjected to scattering with $\tau_{\rm sc} = \tau_{\rm sc,1\,GHz} (\nu/{\rm 1\,GHz})^{-4}$ at frequencies 175, 195, and 210 MHz, where $\tau_{\rm sc,1\,GHz} = 0.07\,$s.}
+The white curve in the top panel is the dedispersed profile of the MeerKAT (2024) observation, and the white curves in the bottom panel are the same profile subjected to scattering with $\tau_{\rm sc} = \tau_{\rm sc,1\,GHz} (\nu/{\rm 1\,GHz})^{-4}$ at frequencies 175, 195, and 210 MHz, where $\tau_{\rm sc,1\,GHz} = 70$\,ms.}
                   \label{fig:stacked_spectra}
@@
 We therefore identified the times of arrival (ToAs) with the $\mu$ parameter in the fits given in \Eqn~\ref{eqn:emg}, which represents the location of the assumed Gaussian pulse before scattering.
-Because the scattering time scale could not be reliably measured for all individual pulses, we obtained ToAs by assuming a fixed scattering time of $\tau_{\rm sc,1 GHz} = 0.07\,$s.
+Because the scattering time scale could not be reliably measured for all individual pulses, we obtained ToAs by assuming a fixed scattering time of $\tau_{\rm sc,1 GHz} = 70$\,ms.
 
@@
   \includegraphics[width=0.98\linewidth]{pulse_details.pdf}
-  \caption{Timing residuals (top panel) and other pulse properties derived from the fits of \Eqn~\ref{eqn:emg} to the individual light curves (lower two panels). \dots}
+  \caption{Timing residuals (top panel) and other pulse properties derived from the fits of \Eqn~\ref{eqn:emg} to the individual light curves (lower two panels).
+Notable features of interest include the relative high fluence of the early 2023 detections (leftmost two points), and the relative stability of the pulse fluences (and pulse morphology) of the MWA detections in the time range $60480 \le {\rm MJD} \le 60580$.}
   \label{fig:pulse_details}
@@
 
-For planning observations of \src{} at low ($\lesssim 300 MHz$), care should be taken to incorporate scattering into the predicted ToAs.
+For planning observations of \src{} at low ($\lesssim 300$\,MHz), care should be taken to incorporate scattering into the predicted ToAs.
 The $N$th pulse since PEPOCH is predicted to arrive at the Solar System barycentre at
@@
 No significant polarised emission was detected in the MWA pulses, as well as the 2023 MeerKAT pulses.
-The apparent lack of polarisation in the MeerKAT data set is likely due to low S/N coupled with the source not being not being centred in the beam.
+The apparent lack of polarisation in the 2023 MeerKAT data set is likely due to low S/N coupled with the source not being not being centred in the beam.
 Much more careful imaging analysis would be needed to obtain reliable measurements or limits on the polarised components of those pulses.
@@
 Assuming \src{} remained at a similar brightness (see \Fig~\ref{fig:pulse_details}), it should have been detected in two ASKAP observations (2023-04-06 and 2023-10-18) and a few dozen times throughout the MWA's 2022 GPM run (2022-06-02 to 2022-09-08).
+More careful cleaning and imaging of the 2023-04-06 ASKAP observation revealed a low-S/N pulse, at the time predicted by the ephemeris, which is presented in \Figs~\ref{fig:pulsestack} and \ref{fig:pulse_details}.
 There are also three observations in the earliest part of the 2024 GPM run (one on 2024-06-02 and two on 2024-06-10) in which no pulse was observed.
@@
 The entire set of observations presented in this work, spanning from 2023 to 2024, may represent two or three different activity windows.
-This is reminiscent of the behaviour of GLEAM-X J162759.5$-$523504.3, which was ``on'' in January 2020, ``off'' in Feburary, and ``on'' again in March \citep{2022Natur.601..526H}.
-The periodic (or quasi-periodic) reappearance of \src{} suggests the possibility that other known intermittent LPTs (like GLEAM-X J162759.5$-$523504.3 and GCRT J1745$-$3009) may eventually do likewise.
+This is reminiscent of the behaviour of GLEAM-X J162759.5$-$523504.3, which was ``on'' in January 2018, ``off'' in Feburary, and ``on'' again in March \citep{2022Natur.601..526H}.
+The reappearance of \src{} suggests the possibility that other known intermittent LPTs (like GLEAM-X J162759.5$-$523504.3 and GCRT J1745$-$3009) may eventually do likewise.
 
-As noted in \citetalias{2024MNRAS.535..909D}, optical follow-up of \src{} is hampered by its proximity to the Galactic plane ($b = -0.12^\circ$) and the associated extinction.
+As noted in \citetalias{2024MNRAS.535..909D}, optical follow-up of \src{} is hampered by its position within the Galactic plane ($b = -0.12^\circ$) and the associated extinction.
 Inferring this nature of the system (white dwarf vs neutron star, isolated vs binary) from the radio pulses alone is challenging, until either the population of LPTs is better understood as a whole, or some other property of the radio signal (e.g.
@@
     \includegraphics[width=0.98\linewidth]{lpt_comparison.pdf}
-    \caption{Duty cycle vs radio pulse period for various long period radio emitters \citep{deRuiter2025,2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C,2005Natur.434...50H,deRuiter2025,Lee2025}.
+    \caption{Duty cycle vs radio pulse period for various long period radio emitters \citep{deRuiter2025,2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C,2005Natur.434...50H,deRuiter2025,Lee2025,2024arXiv241116606W}.
 The duty cycles are derived from the reported pulse widths for LPTs, which are compared to the range of the fitted, unscattered pulse widths of \src{} at 10\% of the peak.
@@
 
-Interestingly, systems with spin-orbital (or beat-orbital) resonances of, e.g., 2:1 or 3:1, would be indistinguishable from systems in 1:1 resonances if the only pulses that can be observed occur within a limited orbital phase range.
+Interestingly, systems with spin-orbital (or beat-orbital) resonances of, e.g., 2:1 or 3:1, would be indistinguishable from systems in 1:1 resonances if pulses can be observed within a limited orbital phase range.
 We therefore raise the possibility that the coincidence of the observed radio periodicities of ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 with their spectroscopically confirmed orbital periods does not necessarily imply that they are 1:1 polars.
 
-In a similar vein, systems in which the spin-orbit (or beat-orbit) ratios are \emph{close to} small-integer ratios, or, equivalently, systems in which precession of the WD is significant, will exhibit an extra beating effect in which an orbitally-induced intermittency is aliased to a much lower frequency.
+In a similar vein, systems in which the spin-orbit (or beat-orbit) ratios are \emph{close to} small-integer ratios, or, similarly, systems in which precession of the WD is significant, will exhibit an extra beating effect in which an orbitally-induced intermittency is aliased to a much lower frequency.
 The month-long time scale of the intermittency of \src{}, and possibly even GLEAM-X\,J1627$-$5235, may be of this kind; much longer-term monitoring is needed to confirm or refute this.
@@
 Another possibility is that radio emission is only observed when the MD produces dense enough particle outflows, in the form of winds, to activate the emission mechanism in the vicinity of the WD.
-Such outflows can last for months [CITATION??], and would not be strictly periodic.
+Such outflows can last for months \citep{2021ApJ...915...37W}, and would not be periodic.
 If intermittency is of this kind, then the observed activity windows will be similarly aperiodic, or quasiperiodic.

### 2025-05-19 dynspec/plot_lpt_comparison.py

@@ -237,7 +237,7 @@ for lpt in lpts:
     lpt_label = " " + lpt['name'] if lpt['text_kwargs']['ha'] == 'left' else lpt['name'] + " "
     if 'voffset' in lpt.keys():
         lpt_label = '\n'*lpt['voffset'] + lpt_label
-    plt.annotate(lpt_label, (lpt['period'].to(period_units).value, duty_cycle + 0.5*duty_cycle_err), **lpt['text_kwargs'], alpha=0.5)
+    plt.annotate(lpt_label, (lpt['period'].to(period_units).value, duty_cycle + 0.5*duty_cycle_err), **lpt['text_kwargs'], alpha=0.7)
 
 # Construct custom legend
 custom_lines = []

### 2025-05-20 dynspec/plot_lpt_comparison.py
Updated LPT comparison plot with better value for J1912's duty cycle, thanks to Csanad

@@ -185,17 +185,17 @@ lpts = [
     {
         'name': 'J1912-4410',
         'type': 'AR Sco-like',
-        'min_width': 10 * u.s, # TODO: Get Csanad to give me better numbers from data
-        'max_width': 20 * u.s,
+        'min_width': 16 * u.s, # TODO: Get Csanad to give me better numbers from data
+        'max_width': 16 * u.s,
         'period': 319.34903 * u.s,
         'text_kwargs': {
             'ha': 'left',
             'va': 'center',
         },
         'errorbar_kwargs': {
-            'fmt': 'none',
+            'fmt': 'x',
             'ls': 'none',
-            'capsize': 2,
+            'capsize': 0,
         }
     },
     #{

### 2025-05-20 dynspec/timing.py
Put lack-of-PB-corr warnings in a more sensible place, so that they're only invoked when it's relevant

@@ -90,39 +90,50 @@ def Stokes_ds(dat, pol='I', pb_corr=True):
         raise NotImplementedError(f"Expecting pol to be one of [I, Q, U, V]")
 
     if pb_corr:
-
         if 'PB_CORR' not in dat.keys():
             print("WARNING: no 'PB_CORR' field found in pickle file; no PB correction applied")
             dat['PB_CORR'] = np.ones((len(dat['FREQS']), len(dat['POLS'])))
-        else:
-            for i in range(len(dat['POLS'])):
-                this_pol = dat['POLS'][i]
-
-                if np.all(np.isnan(dat['PB_CORR'][:,i])):
-                    print(f"WARNING: PB corrections for {this_pol} are all nans. No correction applied to this pol.")
-                    dat['PB_CORR'][:,i] = np.ones(dat['FREQS'].shape)
-
     else:
         # This creates a PB correction field (full of ones) in memory, but doesn't save to disk
         dat['PB_CORR'] = np.ones((len(dat['FREQS']), len(dat['POLS'])))
 
+
+    def warn_if_all_nans(dat, pol):
+        pol_idx = dat['POLS'].index(pol)
+
+        if np.all(np.isnan(dat['PB_CORR'][:,pol_idx])):
+            print(f"WARNING: PB corrections for {pol} are all nans. No correction applied to this pol.")
+            dat['PB_CORR'][:,i] = np.ones(dat['FREQS'].shape)
+
     if dat['POLS'] == ['XX', 'XY', 'YX', 'YY']:
         if pol == 'I':
+            warn_if_all_nans(dat, 'XX')
+            warn_if_all_nans(dat, 'YY')
             S = 0.5*np.real(dat['DS'][:,:,0]/dat['PB_CORR'][:,0] + dat['DS'][:,:,3]/dat['PB_CORR'][:,3])
         elif pol == 'Q':
+            warn_if_all_nans(dat, 'XX')
+            warn_if_all_nans(dat, 'YY')
             S = 0.5*np.real(dat['DS'][:,:,0]/dat['PB_CORR'][:,0] - dat['DS'][:,:,3]/dat['PB_CORR'][:,3])
         elif pol == 'U':
+            warn_if_all_nans(dat, 'XY')
+            warn_if_all_nans(dat, 'YX')
[…]

### 2025-05-21 paper/main.tex
Updating paper due to co-author comments.

@@
 We interpret historical non-detections of \src{} as an intrinsic intermittency that occurs on month-long timescales, and discuss possible causes.
-We conjecture that, like other LPTs with periods $\gtrsim 1\,$hour, \src{} is a white-dwarf binary pulsar, but note that its period is marginally shorter than the minimum known polar orbital period.
+We conjecture that, like other LPTs with periods $\gtrsim 1\,$hour, \src{} is a white-dwarf binary pulsar, but note that its period is marginally shorter than the minimum known orbital period for the class of cataclysmic variables known as polars.
 \end{abstract}
@@
 \srcfull{} (hereafter, \src{}) is a transient radio source discovered in the Variables and Slow Transients (VAST) survey \citep[][hereafter \citetalias{2024MNRAS.535..909D}]{2024MNRAS.535..909D}.
-A single, highly polarized pulse was observed, lasting approximately 2 minutes, exhibiting a steep spectrum ($\alpha = -3.1$, for flux density $S_\nu\propto\nu^\alpha$).
+A single, highly polarised pulse was observed, lasting approximately 2 minutes, exhibiting a steep spectrum ($\alpha = -3.1$, for flux density $S_\nu\propto\nu^\alpha$).
 Extensive follow up in new and archival data at multiple wavelengths turned up no other pulses.
@@
 
-Although optical follow-up has confirmed that at least some LPTs are white dwarfs with main sequence companions \citep{deRuiter2025,2024ApJ...976L..21H,2025A&A...695L...8R}, it remains unclear if this model can account for all known LPTs \citep[e.g.][]{2022ApJ...940...72R,Lee2025}.
-Unfortunately, optical follow-up is challenging for LPTs and LPT candidates obscured by Galactic foregrounds.
-This is almost certainly the case for \src{}, which is situated very close to the Galactic plane ($b = -0\overset{\circ}{.}12$), and has a dispersion measure (DM) derived distance of ${\sim}4.7\,$kpc \citepalias{2024MNRAS.535..909D}; unsurprisingly, archival searches at \src{}'s location did not turn up any source down to ${\sim}23$ AB mag.
+Although optical follow-up has confirmed that at least some LPTs are a type of strongly magnetic cataclysmic variable (CV) known as polars \citep{deRuiter2025,2024ApJ...976L..21H,2025A&A...695L...8R}, it remains unclear if this model can account for all known LPTs \citep[e.g.][]{2022ApJ...940...72R,Lee2025}.
+Optical follow-up is challenging for \src{}, which is situated very close to the Galactic plane ($b = -0\overset{\circ}{.}12$), at a distance of ${\sim}4.7\,$kpc \citepalias{2024MNRAS.535..909D}.
+Unsurprisingly, archival searches at \src{}'s location did not turn up any source down to ${\sim}23$ AB mag.
 Without more detections in the radio or at other wavelengths, it seemed unlikely that the nature of \src{} could ever be resolved.
@@
 In \S\ref{sec:observations}, we describe the observations themselves, some of which were taken as part of independent surveys, and some of which were taken as dedicated follow-up of \src{} once it became apparent that it was still active.
-In \S\ref{sec:analysis} we present a timing analysis of the new detections, as well as revised estimates of the DM and the scattering timescale.
-We also include new polarization detections in which the polarisation angle (PA) behavior differs significantly from the originally detected pulse.
-In \S\ref{sec:discussion} we revisit the question of the nature of \src{}, arguing in favor of a white dwarf interpretation.
-The main conclusions are summarized in \S\ref{sec:summary}.
+In \S\ref{sec:analysis} we present a timing analysis of the new detections, as well as revised estimates of the dispersion measure (DM) and the scattering timescale.
+We also include new polarisation detections in which the polarisation angle (PA) behaviour differs significantly from the originally detected pulse.
+In \S\ref{sec:discussion} we revisit the question of the nature of \src{}, arguing in favour of a white dwarf interpretation.
+The main conclusions are summarised in \S\ref{sec:summary}.
 
@@
 
-\src{} was detected blindly with the Murchison Widefield Array \citep[MWA;][]{Tingay2013} in observations taken between June--September 2024 under the ``Galactic Plane Monitor'', project code G0080.
+\src{} was detected blindly with the Murchison Widefield Array \citep[MWA;][]{Tingay2013} in observations taken between June--September 2024 under the `Galactic Plane Monitor', project code G0080.
 The prime objective of the campaign was to search for long-period transients by scanning the Galactic plane over $285^\circ < l < 65^\circ$, $|b|<\pm15^\circ$ on a bi-weekly cadence at 185--215\,MHz \citep[see Methods of][]{2023Natur.619..487H}; a full description will be released by Hurley-Walker et al., in prep.
 We also observed over June--September 2022 but made no detections in these data, as reported in \citetalias{2024MNRAS.535..909D}.
-Subsequent to its redetection, we commenced a Director's Discretionary Time (DDT) campaign under project code D0042, to obtain further observations, adjusting the frequency from 200.32\,MHz to 184.96\,MHz for some of the observations to attempt to improve measurements of its DM.
+Subsequent to its redetection, we commenced a Director's Discretionary Time (DDT) campaign under project code D0042, to obtain further observations, adjusting the frequency from 200.32\,MHz to 184.96\,MHz for some of the observations to attempt to improvehttps://github.com/CIRA-Pulsars-and-Transients-Group/vcsbeam/pull/71 measurements of its DM.
+Time of arrival (ToA) predictions for the DDT observations were made using a preliminary ephemeris derived from the GPM detections, which, by virtue at being at the same or similar frequencies, absorbed the delays due to dispersion and scattering into the `PEPOCH' term.
 
-We imaged both the 2024 GPM data and the follow-up DDT data at the location of \src{} using \textsc{WSClean}, masking \src{} itself, forming a deep model of the sky for each observation.
+We imaged both the 2024 GPM data and the follow-up DDT data at the location of \src{} using \citep[\textsc{WSClean}][]{2014MNRAS.444..606O}, masking \src{} itself, forming a deep model of the sky for each observation.
 After subtracting this from the visibilities, we phase-rotated to \src{}, and averaged the baseline data to produce a dynamic spectrum.
-% SM to write a 'joining sentence' to explain that the timing analysis was a bit more complicated because of the low frequencies and refer the reader to the relevant section -- SM (memo to self): Not that complicated because DM + tau_sc can be ignored if making ToA predictions solely based on pulses at the target frequency.
-
-% SM: commenting the following out because it's a repeat of above...?
-%The GPM also conducted observations of this region in June--September 2022, but \src{} was not detected, either by a blind search, nor by a re-examination of the data following the methods above.
-
-% NWH to add what went into the followup observations: D0042 (both 185 and 200 MHz). SM
 
@@
 
-We also re-imaged the original 2023-05-28 L-band MeerKAT observation described in Paper~1, which was taken under project code DDT-20230525-DD-01 under capture block 1685306788.
-We performed a similar processing of the data, and identified four pulses with TOAs consistent with an ephemeris derived from the other data.
-The dynamic spectrum of one of the brightest pulses is shown in \Fig~\ref{fig:scattering_DM}.
+We also re-imaged the original 2023-05-28 L-band MeerKAT observation described in \citetalias{2024MNRAS.535..909D}, which was taken under project code DDT-20230525-DD-01 under capture block 1685306788.
+We performed a similar processing of the data, and identified four pulses with ToAs consistent with an ephemeris derived from the other data.
+The folded and stacked dynamic spectra are shown in \Fig~\ref{fig:scattering_DM}.
 
@@
 \section{Analysis \& results} \label{sec:analysis}
-
-%[Reference for scattering kernels:] \citep{10.1093/mnras/stw1724}.
 
@@
 
-We therefore identified the times of arrival (ToAs) with the $\mu$ parameter in the fits given in \Eqn~\ref{eqn:emg}, which represents the location of the assumed Gaussian pulse before scattering.
+We therefore identified the ToAs with the $\mu$ parameter in the fits given in \Eqn~\ref{eqn:emg}, which represents the location of the assumed Gaussian pulse before scattering.
 Because the scattering time scale could not be reliably measured for all individual pulses, we obtained ToAs by assuming a fixed scattering time of $\tau_{\rm sc,1 GHz} = 70$\,ms.
@@
 
+The variability of the pulse brightness, coupled with the fact that none of our detections were simultaneous at multiple telescopes, prohibit a direct spectral index measurement.
+We note, however, that the fitted peak flux densities of the ASKAP and MeerKAT pulses are broadly consistent with the MWA flux densities if an approximate spectral index of $-2.0$ is assumed.
+The in-band spectral index measurement of $-3.1$ reported for the 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, if consistent across the span of our observations, implies a turnover or spectral curvature at intermediate frequencies \citep[perhaps comparable with GPM\,1839$-$10][]{2023Natur.619..487H}.
+
 The measured DM of $764 \pm 25\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of $710^{+200}_{-180}\,{\rm pc}\,{\rm cm}^{-3}$ given in \citetalias{2024MNRAS.535..909D}.
@@
 
-\subsection{Polarization} \label{sec:polarization}
+\subsection{Polarisation} \label{sec:polarisation}
 
@@
 The entire set of observations presented in this work, spanning from 2023 to 2024, may represent two or three different activity windows.
-This is reminiscent of the behaviour of GLEAM-X J162759.5$-$523504.3, which was ``on'' in January 2018, ``off'' in Feburary, and ``on'' again in March \citep{2022Natur.601..526H}.
+This is reminiscent of the behaviour of GLEAM-X J162759.5$-$523504.3, which was `on' in January 2018, `off' in Feburary, and `on' again in March \citep{2022Natur.601..526H}.
 The reappearance of \src{} suggests the possibility that other known intermittent LPTs (like GLEAM-X J162759.5$-$523504.3 and GCRT J1745$-$3009) may eventually do likewise.
@@
 However, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for confirmed polars \citep{schwope2025polarcatcatalogpolarslowaccretion}.
-This makes it an interesting testbed for the suggestion advanced by \citet{2025A&A...695L...8R} that ``short LPTs'' ($P \lesssim 78\,$mins) and ``long LPTs'' ($P \gtrsim 78\,$mins) represent different classes of systems (AM CVns and CVs, respectively).
+This makes it an interesting test bed for the suggestion advanced by \citet{2025A&A...695L...8R} that `short LPTs' ($P \lesssim 78\,$mins) and `long LPTs' ($P \gtrsim 78\,$mins) represent different classes of systems (AM Canum Venaticorum stars and CVs, respectively).
 \begin{figure*}{th}
@@
 In this view, the intermittency of these systems have several possible explanations.
-The limited orbital phase range in which J1912$-$4410's radio pulses were observed suggests that the geometric configuration is important in the observability of radio pulsations; ``missing'' pulses may simply occur at unfavourable orbital phases.
+The limited orbital phase range in which J1912$-$4410's radio pulses were observed suggests that the geometric configuration is important in the observability of radio pulsations; `missing' pulses may simply occur at unfavourable orbital phases.
 This is readily testable with long-term monitoring---this kind of intermittency will have the same periodicity as the orbit itself.
@@
 We have shown that \src{} is in fact an LPT, as conjectured in \citetalias{2024MNRAS.535..909D}).
-Its period of ${\sim}1.16\,$hours is slightly shorter than the minimum known orbital period of optically confirmed polars, marking it as an interesting case study in the context of \citet{2025A&A...695L...8R}'s suggestion that `short'-LPTs and `long'-LPTs may correspond to different classes of cataclysmic variables.
+Its period of ${\sim}1.16\,$hours is slightly shorter than the minimum known orbital period of optically confirmed polars, marking it as an interesting case study in the context of \citet{2025A&A...695L...8R}'s suggestion that `short'-LPTs and `long'-LPTs may correspond to different classes of CVs.
 
@@
 
-It can be shown that pulses scatter-broadened by a thin screen will appear to the observer as the original pulse convolved with a one-sided exponential kernel with an associated timescale $\tau$ [CITATION].
+It can be shown that pulses scatter-broadened by a thin screen will appear to the observer as the original pulse convolved with a one-sided exponential kernel with an associated timescale $\tau$ \citep{1972MNRAS.157...55W,1973MNRAS.163..345W}.
 For intrinsically Gaussian pulses of scale $\sigma$, the result of this convolution is well described by the \textit{exponentially modified Gaussian} (EMG), as given in \Eqn~\ref{eqn:emg}.
@@
 In the regime $\tau \ll \sigma$, the effect of scattering is negligible and the scattered pulse resembles the original pulse.
-ToAs can be obtained in the usual way, i.e., using a matched filter ``template'' constructed from the average pulse profile.
+ToAs can be obtained in the usual way, i.e., using a matched filter `template' constructed from the average pulse profile.
 
@@
 In panel (b), the predicted error in DM is shown if the ToA error (compared to a high-frequency ToA measurement) is erroneously attributed to dispersion.
-Panel (c) shows the rate of change of the ToA error with frequency, and panel (d) shows the error in DM measured if this rate of change (the ``slope'' of the pulse across the observed dynamic spectrum) is erroneously attributed to dispersion.
+Panel (c) shows the rate of change of the ToA error with frequency, and panel (d) shows the error in DM measured if this rate of change (the `slope' of the pulse across the observed dynamic spectrum) is erroneously attributed to dispersion.
 In panels (c) and (d), the derived DM errors assume a pulse scale of $\sigma = 25\,$s and $\nu_s = 230\,$MHz, as estimated for \src{}.

### 2025-05-21 dynspec/fit_toas.py

@@ -89,15 +89,11 @@ def fit_toa(dat, fit_scattering=False, output_plot=None, obsid=None):
     popt, pcov = curve_fit(model, t_base.to('s').value, lightcurve, p0=p0, sigma=noise if noise != 0.0 else None, bounds=bounds)
     A, μ, m, c, σ = popt
     A_err, μ_err, m_err, c_err, σ_err = np.sqrt(np.diag(pcov))
+    Aσ_err = pcov[0,4] # Needed for peak flux error calculation
 
     # Pull out the ToA
     toa = t[0] + μ*u.s
     toa_err = (μ_err*u.s).to('d')
-
-    # Estimate peak S/N by getting std of lightcurve with fitted pulse subtracted
-    noise = np.std(lightcurve - model(t_base.to('s').value, *popt)) * u.Jy
-    peak_signal = A * u.Jy
-    peak_snr = (peak_signal / noise).decompose().value
 
     # For plotting, do a bit of frequency scrunching
     fscrunch_factor = 1
@@ -108,9 +104,17 @@ def fit_toa(dat, fit_scattering=False, output_plot=None, obsid=None):
     t_fine_base = np.arange(t_base[0].to('s').value, t_base[-1].to('s').value, dt.to('s').value/100) * u.s
     t_fine = t[0] + t_fine_base
 
-    # Calculate pulse fluence from model
-    fluence = pulse_fluence(*popt) * u.Jy * u.s
-    fluence_err = fluence*np.sqrt(A_err)/A
+    # The A parameter *is* the pulse fluence
+    fluence = A * u.Jy * u.s
+    fluence_err = A_err * u.Jy * u.s
+
+    # Estimate peak S/N by getting std of lightcurve with fitted pulse subtracted
+    noise = np.std(lightcurve - model(t_base.to('s').value, *popt)) * u.Jy
+    peak_signal = A/σ/np.sqrt(2*np.pi) * u.Jy
+    peak_signal_err = peak_signal * np.sqrt((A_err/A)**2 + (σ_err/σ)**2 + 2*Aσ_err/(A*σ))
+    peak_snr = (peak_signal / noise).decompose().value
+    #print(f'{peak_signal = }')
+    #print(f'cf. = {A/σ/np.sqrt(2*np.pi)}')
 
     if output_plot is not None:
 
@@ -132,8 +136,8 @@ def fit_toa(dat, fit_scattering=False, output_plot=None, obsid=None):
                     model(t_fine_base.value, A, μ, m=0, c=0, σ_s=σ),
[…]

### 2025-05-21 dynspec/make_toa_plots.py

@@ -33,10 +33,10 @@ def main():
     pulses, phases = fold(bary_toas_dd, ephem['period'], ephem['PEPOCH'])
 
     # Make plots
-    nrows = 3
+    nrows = 4
     ncols = 3
     width_ratios = [1, 1, 7, 2]
-    fig = plt.figure(figsize=(9,5), constrained_layout=True)
+    fig = plt.figure(figsize=(9,6), constrained_layout=True)
     gs = GridSpec(nrows, ncols+1, figure=fig, width_ratios=width_ratios, wspace=0.03, hspace=0)
     axs = np.empty((nrows, ncols), dtype=object)
     for i in range(nrows):
@@ -47,7 +47,7 @@ def main():
     #                        gridspec_kw={'width_ratios': width_ratios,},# 'wspace': 0.03, 'hspace': 0},
     #                        figsize=(9,5), constrained_layout=True)
     #fig.subplots_adjust(right=0.8)
-    toa_row, fluence_row, width_row = 0, 1, 2
+    toa_row, width_row, peak_flux_row, fluence_row = 0, 1, 2, 3
 
     # Colormap setup
     cmap = plt.cm.rainbow_r
@@ -77,9 +77,30 @@ def main():
                 'ecolor': color,
                 'markerfacecolor': markerfacecolor,
             }
-            axs[fluence_row, col].errorbar(table['ToA'][i], table['fluence'][i], yerr=table['fluence_err'][i], **point_fmt)
-            axs[width_row, col].errorbar(table['ToA'][i], table['width'][i], yerr=table['width_err'][i], **point_fmt)
-            axs[toa_row, col].errorbar(table['ToA'][i], phases[i]*ephem['period'].to('s'), yerr=table['ToA_err'][i].to('s'), **point_fmt)
+            axs[fluence_row, col].errorbar(
+                table['ToA'][i],
+                table['fluence'][i],# / (freq[i]/u.GHz).decompose()**(-3.1),
+                yerr=table['fluence_err'][i],# / (freq[i]/u.GHz).decompose()**(-3.1),
+                **point_fmt
+            )
+            axs[width_row, col].errorbar(
+                table['ToA'][i],
+                table['width'][i],
+                yerr=table['width_err'][i],
+                **point_fmt
+            )
+            axs[peak_flux_row, col].errorbar(
+                table['ToA'][i],
[…]

### 2025-05-21 dynspec/timing.py

@@ -62,9 +62,6 @@ def scattered_pulse_model(t_s, A, μ_s, m, c, σ_s, τ_s):
     baseline = m*t_s + c
     return discrete_emg(t_s, A, μ_s, σ_s, τ_s) + baseline
 
-def pulse_fluence(A, μ_s, m=0, c=0, σ_s=30):
-    return A*σ_s*np.sqrt(2*np.pi)
-
 def fold(times, period, pepoch):
 
     pulses_phases = ((times - pepoch) / period).decompose()

### 2025-05-21 dynspec/make_toa_table.py
Changed fluence column of output ToA table in make_toa_table.py

@@ -11,15 +11,17 @@ def main():
     table = QTable.read(args.toas_file)
 
     print("Telescope & Freq & ToA & Fluence & $\\sigma$ \\\\")
-    print(" & (MHz) & (MJD) & ($\\times 10^3\\,$Jy\\,s) & (s) \\\\")
+    print(" & (MHz) & (MJD) & (Jy\\,s) & (s) \\\\")
     for row in table:
         toa_err = row['ToA_err']
         toa_precision = int(np.floor(-np.log10(toa_err.to('d').value))) + 1
         toa_str = f"{row['ToA']:.{toa_precision+1}f}({int(np.round(row['ToA_err'].to('d').value*10**(toa_precision+1))):02.0f})"
 
         fluence_err = row['fluence_err']
-        fluence_precision = int(np.floor(-np.log10(fluence_err.to('Jy s').value/1e3))) + 1
-        fluence_str = f"{row['fluence'].to('Jy s').value/1e3:.{fluence_precision}f}({int(np.round(fluence_err.to('Jy s').value*10**(fluence_precision-3))):.0f})"
+        fluence_precision = int(np.floor(-np.log10(fluence_err.to('Jy s').value))) + 1
+        if fluence_precision < 0:
+            fluence_precision = 0
+        fluence_str = f"{row['fluence'].to('Jy s').value:.{fluence_precision}f}({int(np.round(fluence_err.to('Jy s').value*10**(fluence_precision))):.0f})"
         
         width = row['width']
         width_err = row['width_err']

### 2025-05-21 paper/main.tex
More paper touch-ups, and updated biblio

@@
 Natasha Hurley-Walker$^{1}$,
+Akash Anumarlapudi$^{2,3}$,
 Dougal Dobie$^{2,3}$,
@@
 We also observed over June--September 2022 but made no detections in these data, as reported in \citetalias{2024MNRAS.535..909D}.
-Subsequent to its redetection, we commenced a Director's Discretionary Time (DDT) campaign under project code D0042, to obtain further observations, adjusting the frequency from 200.32\,MHz to 184.96\,MHz for some of the observations to attempt to improvehttps://github.com/CIRA-Pulsars-and-Transients-Group/vcsbeam/pull/71 measurements of its DM.
+Subsequent to its redetection, we commenced a Director's Discretionary Time (DDT) campaign under project code D0042, to obtain further observations, adjusting the frequency from 200.32\,MHz to 184.96\,MHz for some of the observations to attempt to improve measurements of its DM.
 Time of arrival (ToA) predictions for the DDT observations were made using a preliminary ephemeris derived from the GPM detections, which, by virtue at being at the same or similar frequencies, absorbed the delays due to dispersion and scattering into the `PEPOCH' term.
@@
 
-\begin{figure*}[tp]
+\begin{figure*}
       \centering
@@
 
-\begin{figure}{th}
+\begin{figure}
       \centering
@@
 %    \colhead{Telescope} & \colhead{$\nu$} & \colhead{ToA} & \colhead{Fluence} & \colhead{$\sigma$} \\ 
-%    & \colhead{(MHz)} & \colhead{(MJD)} & \colhead{($10^3$\,Jy\,s)} & \colhead{(s)}
+%    & \colhead{(MHz)} & \colhead{(MJD)} & \colhead{(Jy\,s)} & \colhead{(s)}
 %  } 
 %  \startdata
-%ASKAP & 888 & 59965.0429358(45) & 0.48(2) & 29.1(4) \\
-%MWA & 170 & 59966.061584(40) & 31.7(7) & 40(7) \\
-%ASKAP & 888 & 60040.913447(32) & 0.03(1) & 25(3) \\
-%MeerKAT & 1284 & 60092.899548(10) & 0.003(3) & 13(1) \\
-%MeerKAT & 1284 & 60092.947966(10) & 0.003(3) & 12(1) \\
-%MeerKAT & 1284 & 60092.996466(11) & 0.005(3) & 16(1) \\
-%MeerKAT & 1284 & 60093.044919(12) & 0.005(4) & 16(1) \\
-%MWA & 200 & 60481.637466(65) & 3.0(2) & 24(8) \\
-%MWA & 200 & 60485.658977(33) & 1.18(7) & 16(4) \\
-%MWA & 200 & 60489.632266(20) & 1.65(6) & 14(2) \\
-%MWA & 200 & 60492.588020(24) & 3.12(9) & 14(3) \\
-%MWA & 200 & 60496.609639(18) & 2.87(8) & 17(2) \\
-%MWA & 200 & 60503.587085(14) & 3.40(8) & 17(2) \\
-%ASKAP & 1032 & 60503.634781(17) & 0.09(1) & 16.6(5) \\
-%MWA & 200 & 60506.542809(33) & 1.35(6) & 9(4) \\
-%MWA & 200 & 60510.564531(11) & 3.08(7) & 16(1) \\
-%MWA & 200 & 60519.528812(29) & 3.1(1) & 14(4) \\
-%MWA & 200 & 60522.533028(16) & 3.50(8) & 18(2) \\
-%MWA & 200 & 60527.524033(14) & 2.89(7) & 16(2) \\
-%MWA & 200 & 60530.528339(16) & 2.90(8) & 17(2) \\
-%MWA & 200 & 60537.506042(13) & 3.91(9) & 17(2) \\
-%MWA & 200 & 60541.479448(47) & 1.48(9) & 14(5) \\
-%MWA & 200 & 60544.483761(15) & 3.91(9) & 20(2) \\
-%MWA & 200 & 60551.461625(16) & 3.35(8) & 16(2) \\
-%MWA & 185 & 60572.395455(15) & 2.86(7) & 15(2) \\
-%MWA & 185 & 60572.443943(21) & 3.01(8) & 16(2) \\
-%MWA & 185 & 60572.540824(18) & 2.57(8) & 16(2) \\
-%MWA & 185 & 60572.589281(31) & 4.3(2) & 21(4) \\
-%MWA & 200 & 60592.456765(27) & 1.63(8) & 19(3) \\
-%MWA & 200 & 60592.505159(33) & 1.67(9) & 19(4) \\
-%MWA & 200 & 60593.474369(26) & 1.08(6) & 15(3) \\
-%MWA & 200 & 60593.522901(46) & 1.3(1) & 19(5) \\
-%MWA & 200 & 60594.443484(20) & 1.94(8) & 18(2) \\
-%MWA & 200 & 60594.491990(33) & 0.55(5) & 12(4) \\
-%MWA & 200 & 60595.461118(29) & 1.53(8) & 19(3) \\
-%MWA & 200 & 60595.509617(25) & 0.89(5) & 13(3) \\
-%MWA & 200 & 60596.430282(20) & 1.55(7) & 16(2) \\
-%MWA & 200 & 60596.478721(23) & 1.65(7) & 17(3) \\
-%MWA & 200 & 60597.447846(41) & 0.86(7) & 16(5) \\
-%MWA & 200 & 60597.496319(30) & 1.82(9) & 19(3) \\
-%MWA & 200 & 60599.434635(17) & 1.28(5) & 13(2) \\
-%MWA & 200 & 60599.483121(24) & 1.00(5) & 13(3) \\
-%MWA & 200 & 60600.500655(31) & 1.24(7) & 16(4) \\
-%MWA & 200 & 60602.438964(32) & 1.9(1) & 21(4) \\
-%MWA & 200 & 60602.487394(27) & 1.98(9) & 20(3) \\
-%MeerKAT & 813 & 60602.5835731(40) & 0.061(7) & 14.9(4)
+%ASKAP & 888 & 59965.0429346(42) & 6.7(1) & 29.1(4) \\
+%MWA & 170 & 59966.061584(40) & 358(55) & 40(7) \\
+%ASKAP & 888 & 60040.913447(32) & 0.48(5) & 25(3) \\
+%MeerKAT & 1284 & 60092.8995476(100) & 0.104(7) & 12.8(9) \\
+%MeerKAT & 1284 & 60092.947966(10) & 0.10(1) & 12(1) \\
+%MeerKAT & 1284 & 60092.996466(11) & 0.125(7) & 15.8(9) \\
+%MeerKAT & 1284 & 60093.044919(12) & 0.122(7) & 16(1) \\
+%MWA & 200 & 60481.637466(65) & 50(11) & 24(8) \\
+%MWA & 200 & 60485.658977(33) & 29(3) & 16(4) \\
+%MWA & 200 & 60489.632266(20) & 48(3) & 14(2) \\
+%MWA & 200 & 60492.588020(24) & 87(7) & 14(3) \\
+%MWA & 200 & 60496.609639(18) & 67(4) & 17(2) \\
+%MWA & 200 & 60503.587085(14) & 82(3) & 17(2) \\
+%ASKAP & 888 & 60503.6347610(51) & 3.10(8) & 16.4(5) \\
+%MWA & 200 & 60506.542809(33) & 57(7) & 9(4) \\
+%MWA & 200 & 60510.564531(11) & 79(3) & 16(1) \\
+%MWA & 200 & 60519.528812(29) & 86(10) & 14(4) \\
+%MWA & 200 & 60522.533028(16) & 76(3) & 18(2) \\
+%MWA & 200 & 60527.524033(14) & 73(3) & 16(2) \\
+%MWA & 200 & 60530.528339(16) & 68(4) & 17(2) \\
+%MWA & 200 & 60537.506042(13) & 92(4) & 17(2) \\
+%MWA & 200 & 60541.479448(47) & 41(6) & 14(5) \\
+%MWA & 200 & 60544.483761(15) & 79(3) & 20(2) \\
+%MWA & 200 & 60551.461625(16) & 85(4) & 16(2) \\
+%MWA & 185 & 60572.395455(15) & 74(3) & 15(2) \\
+%MWA & 185 & 60572.443943(21) & 73(4) & 16(2) \\
+%MWA & 185 & 60572.540824(18) & 64(4) & 16(2) \\
+%MWA & 185 & 60572.589281(31) & 82(8) & 21(4) \\
+%MWA & 200 & 60592.456765(27) & 34(3) & 19(3) \\
+%MWA & 200 & 60592.505159(33) & 35(4) & 19(4) \\
+%MWA & 200 & 60593.474369(26) & 29(3) & 15(3) \\
+%MWA & 200 & 60593.522901(46) & 27(4) & 19(5) \\
+%MWA & 200 & 60594.443484(21) & 43(3) & 18(2) \\
+%MWA & 200 & 60594.491990(33) & 19(2) & 12(4) \\
+%MWA & 200 & 60595.461118(29) & 33(3) & 19(3) \\
+%MWA & 200 & 60595.509617(25) & 27(2) & 13(3) \\
+%MWA & 200 & 60596.430283(20) & 39(3) & 16(2) \\
+%MWA & 200 & 60596.478721(23) & 39(3) & 17(3) \\
+%MWA & 200 & 60597.447846(41) & 22(3) & 16(5) \\
+%MWA & 200 & 60597.496319(30) & 38(4) & 19(3) \\
+%MWA & 200 & 60599.434635(17) & 39(2) & 13(2) \\
+%MWA & 200 & 60599.483122(24) & 32(3) & 13(3) \\
+%MWA & 200 & 60600.500655(31) & 30(3) & 16(4) \\
+%MWA & 200 & 60602.438964(32) & 36(4) & 21(4) \\
+%MWA & 200 & 60602.487394(27) & 39(3) & 20(3) \\
+%MeerKAT & 813 & 60602.5835733(40) & 1.64(4) & 14.9(4) \\
   %\enddata
@@
 
-\begin{figure*}{th}
+\begin{figure*}
   \centering
   \includegraphics[width=0.98\linewidth]{pulse_details.pdf}
-  \caption{Timing residuals (top panel) and other pulse properties derived from the fits of \Eqn~\ref{eqn:emg} to the individual light curves (lower two panels).
+  \caption{Timing residuals (top panel) and other pulse properties derived from the fits of \Eqn~\ref{eqn:emg} to the individual light curves (lower three panels).
 Notable features of interest include the relative high fluence of the early 2023 detections (leftmost two points), and the relative stability of the pulse fluences (and pulse morphology) of the MWA detections in the time range $60480 \le {\rm MJD} \le 60580$.}
@@
 
-\begin{figure*}{th}
+\begin{figure*}
     \centering
@@
 
-\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are confirmed polars (\Fig~\ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is a WD-MD polar system.
+\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are confirmed polars (\Fig~\ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is a polar.
 However, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for confirmed polars \citep{schwope2025polarcatcatalogpolarslowaccretion}.
 This makes it an interesting test bed for the suggestion advanced by \citet{2025A&A...695L...8R} that `short LPTs' ($P \lesssim 78\,$mins) and `long LPTs' ($P \gtrsim 78\,$mins) represent different classes of systems (AM Canum Venaticorum stars and CVs, respectively).
-\begin{figure*}{th}
+\begin{figure*}
     \centering
@@
 
-It can be shown that pulses scatter-broadened by a thin screen will appear to the observer as the original pulse convolved with a one-sided exponential kernel with an associated timescale $\tau$ \citep{1972MNRAS.157...55W,1973MNRAS.163..345W}.
+It can be shown that pulses scatter-broadened by a thin screen\footnote{Relaxing the assumption of a single, thin, isotropic screen could affect the shape of the scattered pulse in ways that could plausibly affect timing \citep{2009MNRAS.395.1391R}, but quantification of this is beyond the scope of this appendix.} will appear to the observer as the original pulse convolved with a one-sided exponential kernel with an associated timescale $\tau$ \citep{1972MNRAS.157...55W,1973MNRAS.163..345W}.
 For intrinsically Gaussian pulses of scale $\sigma$, the result of this convolution is well described by the \textit{exponentially modified Gaussian} (EMG), as given in \Eqn~\ref{eqn:emg}.

### 2025-05-21 dynspec/plot_lpt_comparison.py
Made J1755 label bold in lpt comparison plot

@@ -29,6 +29,7 @@ lpts = [
         'text_kwargs': {
             'ha': 'left',
             'va': 'center',
+            'fontweight': 'bold',
         },
         'errorbar_kwargs': {
             'fmt': 'none',
@@ -237,7 +238,9 @@ for lpt in lpts:
     lpt_label = " " + lpt['name'] if lpt['text_kwargs']['ha'] == 'left' else lpt['name'] + " "
     if 'voffset' in lpt.keys():
         lpt_label = '\n'*lpt['voffset'] + lpt_label
-    plt.annotate(lpt_label, (lpt['period'].to(period_units).value, duty_cycle + 0.5*duty_cycle_err), **lpt['text_kwargs'], alpha=0.7)
+    plt.annotate(lpt_label,
+                 (lpt['period'].to(period_units).value, duty_cycle + 0.5*duty_cycle_err),
+                 **lpt['text_kwargs'], alpha=0.7)
 
 # Construct custom legend
 custom_lines = []

### 2025-05-22 dynspec/make_toa_plots.py
Changed pulse details plot

@@ -47,7 +47,7 @@ def main():
     #                        gridspec_kw={'width_ratios': width_ratios,},# 'wspace': 0.03, 'hspace': 0},
     #                        figsize=(9,5), constrained_layout=True)
     #fig.subplots_adjust(right=0.8)
-    toa_row, width_row, peak_flux_row, fluence_row = 0, 1, 2, 3
+    toa_row, width_row, peak_flux_row, scaled_peak_flux_row = 0, 1, 2, 3
 
     # Colormap setup
     cmap = plt.cm.rainbow_r
@@ -77,10 +77,16 @@ def main():
                 'ecolor': color,
                 'markerfacecolor': markerfacecolor,
             }
-            axs[fluence_row, col].errorbar(
+            #axs[fluence_row, col].errorbar(
+            #    table['ToA'][i],
+            #    table['fluence'][i],# / (freq[i]/u.GHz).decompose()**(-3.1),
+            #    yerr=table['fluence_err'][i],# / (freq[i]/u.GHz).decompose()**(-3.1),
+            #    **point_fmt
+            #)
+            axs[scaled_peak_flux_row, col].errorbar(
                 table['ToA'][i],
-                table['fluence'][i],# / (freq[i]/u.GHz).decompose()**(-3.1),
-                yerr=table['fluence_err'][i],# / (freq[i]/u.GHz).decompose()**(-3.1),
+                table['fitted_peak_flux_density'][i] / (freq[i]/u.GHz).decompose()**(-2.0),
+                yerr=table['fitted_peak_flux_density_err'][i] / (freq[i]/u.GHz).decompose()**(-2.0),
                 **point_fmt
             )
             axs[width_row, col].errorbar(
@@ -104,13 +110,15 @@ def main():
         axs[toa_row, col].axhline(0, ls='--', color='k', alpha=0.2)
 
     custom_lines = [Line2D([0], [0], **v) for v in point_types.values()]
-    fig.legend(handles=custom_lines, loc='center right', bbox_to_anchor=(1.0, 0.24))
+    fig.legend(handles=custom_lines, loc='center right', bbox_to_anchor=(1.0, 0.19))
 
-    axs[fluence_row, 0].set_ylabel(f"Fluence ({table['fluence'].unit})")
+    #axs[fluence_row, 0].set_ylabel(f"Fluence ({table['fluence'].unit})")
[…]

### 2025-05-22 dynspec/measure_rm.py
Added correction to ASKAP data (x2), and updated relevant plots

@@ -285,7 +285,7 @@ def main():
         ax_RM.set_ylim([952, 970])
         ax_PA.set_ylim([-90, 270])
         ax_al.set_ylim([-5, 1])
-        ax_lc.set_ylim([-12, 99])
+        ax_lc.set_ylim([-12, 199])
         ax_lc.set_xlabel("Time since ToA (s)")
 
         ax_RM.set_xlim(data[i]['xlim'])

### 2025-05-22 paper/main.tex
Latest synch of paper with Overleaf version.

@@
 Natasha Hurley-Walker$^{1}$,
+Cs\'{a}nad Horv\'{a}th$^{1}$,
 Akash Anumarlapudi$^{2,3}$,
-Dougal Dobie$^{2,3}$,
-Cs\'{a}nad Horv\'{a}th$^{1}$,
 \newauthor
 Angie Waszewski$^{1}$,
+Dougal Dobie$^{2,3}$,
 John Morgan$^{1}$,
+David Kaplan$^{?}$,
 and Ziteng Wang$^{1}$
@@
 
-%\begin{deluxetable*}{cccccc}
-%\tablecaption{Pulse detections and non-detections}
-%\tablehead{
-%\colhead{Obs start} & \colhead{Duration} & \colhead{Telescope} & \colhead{$\nu$} & %\colhead{$\Delta\nu$} & \colhead{Detected?} \\ 
-%\colhead{time (UTC)} & \colhead{(s)} & & \colhead{(MHz)} & \colhead{(MHz)} &
-%} 
-%\startdata
-%2024-09-19 09:25:02 & 592\tablenotemark{a} & MWA & 184.96 & 30.72 & Y \\ % 1410773120 and 1410773416
-%2024-09-19 10:34:06 & 592\tablenotemark{a} & MWA & 184.96 & 30.72 & Y \\ % 1410777264 and 1410777560
-%2024-09-19 12:57:10 & 296 & MWA & 184.96 & 30.72 & Y \\ % 1410785848
-%2024-09-19 14:06:14 & 296 & MWA & 184.96 & 30.72 & Y \\ % 1410789992
-%2024-10-09 10:55:50 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412506568
-%2024-10-09 12:05:34 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412510752
-%2024-10-10 11:21:10 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412594488
-%2024-10-10 12:30:54 & 296 & MWA\tablenotemark{b} & 200.32 & 30.72 & Y \\ % 1412598672
-%2024-10-11 10:36:46 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412678224
-%2024-10-11 11:46:30 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412682408
-%2024-10-12 11:02:06 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412766144
-%2024-10-12 12:11:50 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412770328
-%2024-10-13 10:17:42 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412849880
-%2024-10-13 11:27:26 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412854064
-%2024-10-14 10:43:02 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412937800
-%2024-10-14 11:52:46 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412941984
-%2024-10-16 10:23:58 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413109456
-%2024-10-16 11:33:42 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413113640
-%2024-10-17 11:59:02 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413201560
-%2024-10-19 10:30:14 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413369032
-%2024-10-19 11:39:58 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413373216
-%2024-10-19 13:54:36 & 601 & MeerKAT\tablenotemark{c} & 812.8 & 247.6 & Y \\ % 1413381294
-%\enddata
-%\tablenotetext{a}{Two contiguous 296-second MWA observations were combined}
-%\tablenotetext{b}{Too much RFI to use in downstream analysis}
-%\tablenotetext{c}{Two components in pulse}
-%\end{deluxetable*}
-
 \section{Analysis \& results} \label{sec:analysis}
@@
 %  \startdata
-%ASKAP & 888 & 59965.0429346(42) & 6.7(1) & 29.1(4) \\
+%ASKAP & 888 & 59965.0429346(42) & 13.4(2) & 29.1(4) \\
 %MWA & 170 & 59966.061584(40) & 358(55) & 40(7) \\
-%ASKAP & 888 & 60040.913447(32) & 0.48(5) & 25(3) \\
+%ASKAP & 888 & 60040.913447(32) & 1.0(1) & 25(3) \\
 %MeerKAT & 1284 & 60092.8995476(100) & 0.104(7) & 12.8(9) \\
@@
 %MWA & 200 & 60503.587085(14) & 82(3) & 17(2) \\
-%ASKAP & 888 & 60503.6347610(51) & 3.10(8) & 16.4(5) \\
+%ASKAP & 888 & 60503.6347610(51) & 6.2(2) & 16.4(5) \\
 %MWA & 200 & 60506.542809(33) & 57(7) & 9(4) \\
@@
     Period (s) & $4186.3283 \pm 0.0003$ \\
-    PEPOCH (MJD) & $59965.03790 \pm 0.00003$ \\
-    DM (pc/cm$^{-3}$) & $764 \pm 25$ \\
+    PEPOCH (MJD) & $59965.03791 \pm 0.00003$ \\
+    DM (pc/cm$^{-3}$) & $763 \pm 25$ \\
     $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$ \\
@@
   \includegraphics[width=0.98\linewidth]{pulse_details.pdf}
-  \caption{Timing residuals (top panel) and other pulse properties derived from the fits of \Eqn~\ref{eqn:emg} to the individual light curves (lower three panels).
-Notable features of interest include the relative high fluence of the early 2023 detections (leftmost two points), and the relative stability of the pulse fluences (and pulse morphology) of the MWA detections in the time range $60480 \le {\rm MJD} \le 60580$.}
+  \caption{Timing residuals (top panel) and other pulse properties derived from the fits of \Eqn~\ref{eqn:emg} to the individual light curves (second and third panels).
+The peak flux, $S_{\rm peak}$, equivalent to the $A$ parameter in \eqn~\ref{eqn:emg}, is the peak flux of the modelled unscattered pulse.
+The bottom panel displays $S_{\rm peak,1 GHz} = S_{\rm peak} (\nu/{\rm GHz})^{-\alpha}$, where $\alpha = -2$ has been assumed.
+Notable features of interest include the relative brightness of the early 2023 detections (leftmost two points), and the relative stability of the pulse fluences (and pulse morphology) of the MWA detections in the time range $60480 \le {\rm MJD} \le 60580$.}
   \label{fig:pulse_details}
@@
 The variability of the pulse brightness, coupled with the fact that none of our detections were simultaneous at multiple telescopes, prohibit a direct spectral index measurement.
-We note, however, that the fitted peak flux densities of the ASKAP and MeerKAT pulses are broadly consistent with the MWA flux densities if an approximate spectral index of $-2.0$ is assumed.
-The in-band spectral index measurement of $-3.1$ reported for the 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, if consistent across the span of our observations, implies a turnover or spectral curvature at intermediate frequencies \citep[perhaps comparable with GPM\,1839$-$10][]{2023Natur.619..487H}.
+We note, however, that the fitted peak flux densities of the ASKAP and MeerKAT pulses are broadly consistent with the MWA flux densities at nearby epochs if an approximate spectral index of $\alpha = -2.0$ is assumed.
+The bottom panel of \Fig~\ref{fig:pulse_details} shows the peak flux densities scaled to 1\,GHz under this assumption, revealing a relatively slow change of the pulses' brightness, not unlike GLEAM-X\,J1627$-$5235 \citep{2022Natur.601..526H}.
+The in-band spectral index measurement of $-3.1$ reported for the 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, if consistent across the timespan of our observations, implies a turnover or spectral curvature at intermediate frequencies \citep[perhaps comparable with GPM\,1839$-$10][]{2023Natur.619..487H}.
 
-The measured DM of $764 \pm 25\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of $710^{+200}_{-180}\,{\rm pc}\,{\rm cm}^{-3}$ given in \citetalias{2024MNRAS.535..909D}.
+The measured DM of $763 \pm 25\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of $710^{+200}_{-180}\,{\rm pc}\,{\rm cm}^{-3}$ given in \citetalias{2024MNRAS.535..909D}.
 Because we have not attempted to simultaneously fit for both DM and scattering timescale, there will remain some small systematic error on this reported DM measurement.
@@
 No significant polarised emission was detected in the MWA pulses, as well as the 2023 MeerKAT pulses.
-The apparent lack of polarisation in the 2023 MeerKAT data set is likely due to low S/N coupled with the source not being not being centred in the beam.
+The apparent lack of polarisation in the 2023 MeerKAT data set is likely due to low S/N coupled with the source not being centred in the beam.
 Much more careful imaging analysis would be needed to obtain reliable measurements or limits on the polarised components of those pulses.
@@
 
+S.M. would like to thank J. Pritchard and E. Lenc for technical discussions regarding the ASKAP data sets included in this paper.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2025-05-23 dynspec/ephemeris_fits.py
Updated pulsestack plot

@@ -36,9 +36,6 @@ print(f'  PEPOCH (MJD) = {popt[1]:.6f} ± {errs[1]:.6f}')
 print()
 
 def period_and_pdot_model(toas_mjd, period_d, pepoch_mjd, fdot):
-    print(pepoch_mjd)
-    print(freqs)
-    print(calc_dmdelay(ephemeris['DM'], freqs, np.inf*u.MHz).to('d').value)
     t = toas_mjd - pepoch_mjd - calc_dmdelay(ephemeris['DM'], freqs, np.inf*u.MHz).to('d').value
     _, phases = np.divmod(fdot*t**2 + t/period_d + 0.5, 1)
     return phases - 0.5

### 2025-05-23 dynspec/pulsestack_all.py

@@ -81,10 +81,11 @@ def main():
         lightcurve = np.nanmean(Idd, axis=1)
 
         # Fit a scattered pulse
+        τ = (ephemeris['tau_sc']/ephemeris['period'] * (f_ref/u.GHz)**(-4)).decompose()
         def model(ph, A, μ, m, c, σ):
-            τ = (ephemeris['tau_sc']/ephemeris['period'] * (f_ref/u.GHz)**(-4)).decompose()
             return scattered_pulse_model(ph, A, μ, m, c, σ, τ)
-        p0 = [np.max(lightcurve), 0, 0, 0, 10/ephemeris['period'].to('s').value]
+        peak_idx = np.nanargmax(lightcurve)
+        p0 = [lightcurve[peak_idx], phases[peak_idx], 0, 0, 20/ephemeris['period'].to('s').value]
         #def model(ph, m, c, A, mu, sigma):
         #    return m*ph + c + A*np.exp(-0.5*(ph-mu)**2/sigma**2)
         #p0 = [0, 0, np.max(lightcurve), 0, 10/ephemeris['period'].to('s').value]
@@ -100,11 +101,19 @@ def main():
             phases = phases[mask]
             lightcurve = lightcurve[mask]
 
-        axs[0][col].plot(phases*ephemeris['period'], 0.9*lightcurve/np.nanmax(lightcurve) + ys[col], 'k', lw=0.5, alpha=0.5)
         ph_fine = np.linspace(phases[0], phases[-1], 1000)
+
         y = pulse_model(ph_fine, A, μ, 0, 0, σ)
+        y1 = scattered_pulse_model(ph_fine, A, μ, 0, 0, σ, τ)
+
         ynorm = y / np.nanmax(y)
-        axs[0][col].plot(ph_fine*ephemeris['period'], 0.9*ynorm + ys[col], 'b--')
+        y1norm = y1 / np.nanmax(y1)
+
+        axs[0][col].plot(phases*ephemeris['period'], 0.9*lightcurve/np.max(y1) + ys[col], 'k', lw=0.5, alpha=0.5)
+        #axs[0][col].plot(phases*ephemeris['period'], 0.9*lightcurve/np.max(lightcurve) + ys[col], 'k', lw=0.5, alpha=0.5)
+        axs[0][col].plot(ph_fine*ephemeris['period'], 0.9*ynorm + ys[col], 'b', alpha=0.3)
[…]

### 2025-05-23 dynspec/timing.py

@@ -11,9 +11,9 @@ import sys
 
 def get_J1755_ephemeris():
     return {
-        'PEPOCH': Time(59965.037908, scale='utc', format='mjd'),
-        'period': 4186.32827 * u.s,
-        'DM': 765 * u.pc / u.cm**3,
+        'PEPOCH': Time(59965.037913, scale='utc', format='mjd'),
+        'period': 4186.32825 * u.s,
+        'DM': 763 * u.pc / u.cm**3,
         'tau_sc': 7.0e-2*u.s,
         'coord': SkyCoord("17:55:34.87 -25:27:49.1", unit=(u.hourangle, u.deg), frame='icrs'),
     }

### 2025-05-23 dynspec/pulsestack_all.py
Darked the lines a bit on pulsestack figure

@@ -109,7 +109,7 @@ def main():
         ynorm = y / np.nanmax(y)
         y1norm = y1 / np.nanmax(y1)
 
-        axs[0][col].plot(phases*ephemeris['period'], 0.9*lightcurve/np.max(y1) + ys[col], 'k', lw=0.5, alpha=0.5)
+        axs[0][col].plot(phases*ephemeris['period'], 0.9*lightcurve/np.max(y1) + ys[col], 'k', lw=0.5, alpha=0.7)
         #axs[0][col].plot(phases*ephemeris['period'], 0.9*lightcurve/np.max(lightcurve) + ys[col], 'k', lw=0.5, alpha=0.5)
         axs[0][col].plot(ph_fine*ephemeris['period'], 0.9*ynorm + ys[col], 'b', alpha=0.3)
         axs[0][col].plot(ph_fine*ephemeris['period'], 0.9*y1norm + ys[col], 'r', alpha=0.3)

### 2025-05-23 paper/main.tex
Various updates from co-author suggestions

@@
 Natasha Hurley-Walker$^{1}$,
-Cs\'{a}nad Horv\'{a}th$^{1}$,
-Akash Anumarlapudi$^{2,3}$,
+Csan\'{a}d Horv\'{a}th$^{1}$,
+Akash Anumarlapudi$^{2}$,
 \newauthor
 Angie Waszewski$^{1}$,
-Dougal Dobie$^{2,3}$,
+Dougal Dobie$^{3,4}$,
 John Morgan$^{1}$,
-David Kaplan$^{?}$,
+David L.~Kaplan$^{2}$,
 and Ziteng Wang$^{1}$
@@
 $^{1}$International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia\\
+$^{4}$Department of Physics, University of Wisconsin-Milwaukee, P.O. Box 413, Milwaukee, WI 53201, USA\\
 $^{2}$Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia\\
@@
 \src{} was detected blindly with the Murchison Widefield Array \citep[MWA;][]{Tingay2013} in observations taken between June--September 2024 under the `Galactic Plane Monitor', project code G0080.
-The prime objective of the campaign was to search for long-period transients by scanning the Galactic plane over $285^\circ < l < 65^\circ$, $|b|<\pm15^\circ$ on a bi-weekly cadence at 185--215\,MHz \citep[see Methods of][]{2023Natur.619..487H}; a full description will be released by Hurley-Walker et al., in prep.
+The prime objective of the campaign was to search for long-period transients by scanning the Galactic plane over $285^\circ < l < 65^\circ$, $|b| < 15^\circ$ on a bi-weekly cadence at 185--215\,MHz \citep[see Methods of][]{2023Natur.619..487H}; a full description will be released by Hurley-Walker et al., in prep.
 We also observed over June--September 2022 but made no detections in these data, as reported in \citetalias{2024MNRAS.535..909D}.
@@
 
-We imaged both the 2024 GPM data and the follow-up DDT data at the location of \src{} using \citep[\textsc{WSClean}][]{2014MNRAS.444..606O}, masking \src{} itself, forming a deep model of the sky for each observation.
+We imaged both the 2024 GPM data and the follow-up DDT data at the location of \src{} using \textsc{WSClean} \citep{2014MNRAS.444..606O}, masking \src{} itself, forming a deep model of the sky for each observation.
 After subtracting this from the visibilities, we phase-rotated to \src{}, and averaged the baseline data to produce a dynamic spectrum.
@@
 
-Paper~1 presented an exhaustive search of the ASKAP data available at the time of writing, comprising 60\,h of data, and yielding only a single detection of \src{} (in Scheduling Block ID 47253).
-Subsequent to the writing of Paper~1, a further epoch of the VAST survey was performed (SBID 63600) in which \src{} produced a detectable pulsation.
+\citetalias{2024MNRAS.535..909D} presented an exhaustive search of the ASKAP data available at the time of writing, comprising 60\,h of data, and yielding only a single detection of \src{} (in Scheduling Block ID 47253).
+Subsequent to the writing of \citetalias{2024MNRAS.535..909D}, a further epoch of the VAST survey was performed (SBID 63600) in which \src{} produced a detectable pulsation.
 
@@
 
-MeerKAT observations were undertaken on 2024-10-19, under proposal code 
-DDT-20241015-NH-01 and capture block 1729341386, using the UHF band spanning 544 -- 1088\,MHz.
+MeerKAT observations were undertaken on 2024-10-19, under proposal code DDT-20241015-NH-01 and capture block 1729341386, using the UHF band spanning 544 -- 1088\,MHz.
 As well as correlator observations undertaken at 2-s/132.812-kHz resolution, we also employed the Pulsar Timing User Supplied Equipment \citep[PTUSE;][]{2020PASA...37...28B} in search mode, using 37.45-$\mu$s sampling.
@@
 We formed a deep model of the sources within the primary beam, excepting \src{}, and subtracted this from the visibilities.
-We then averaged the visibilities, excluding all baselines shorter than 150\,m, to produce a dynamic spectrum of the source, shown in \Fig~\ref{fig:scattering_DM}.
+We then averaged the visibilities, excluding all baselines shorter than 150\,m, to produce a dynamic spectrum of the source, shown in \Fig~\ref{fig:stacked_spectra}.
 
@@
 We performed a similar processing of the data, and identified four pulses with ToAs consistent with an ephemeris derived from the other data.
-The folded and stacked dynamic spectra are shown in \Fig~\ref{fig:scattering_DM}.
+The folded and stacked dynamic spectra are shown in \Fig~\ref{fig:stacked_spectra}.
 
@@
 The low-frequency asymmetry is consistent with a scattering time scale of a few tens of seconds at MWA frequencies, which scales to a few tens of milliseconds at 1\,GHz.
-This is in broad agreement with the model predictions of NE2001 ($\tau_{\rm sc,1GHz} = 66\,$ms) and YMW16 ($\tau_{\rm sc,1 GHz} = 75\,$ms) at the source's location assuming the DM value of 710\,pc\,cm$^{-3}$ reported in \citepalias{2024MNRAS.535..909D}.
+This is in broad agreement with the model predictions of NE2001 ($\tau_{\rm sc,1GHz} = 66\,$ms) and YMW16 ($\tau_{\rm sc,1 GHz} = 75\,$ms) at the source's location assuming the DM value of 710\,pc\,cm$^{-3}$ reported in \citetalias{2024MNRAS.535..909D}.
 
@@
   \emg(t) = A \frac{\sigma}{\tau}\sqrt{\frac{\pi}{2}}
-    \exp\left(-\frac12 \left( \frac{t - \mu}{\tau} \right)^2 \right)  \erfcx \left(\frac{1}{\sqrt{2}} \left(\frac{\sigma}{\tau} - \frac{t - \mu}{\tau} \right) \right),
+    \exp\left(-\frac12 \left( \frac{t - \mu}{\sigma} \right)^2 \right)  \erfcx \left(\frac{1}{\sqrt{2}} \left(\frac{\sigma}{\tau} - \frac{t - \mu}{\sigma} \right) \right),
   \label{eqn:emg}
@@
               \caption{Pulsestack of barycentred, dedispersed profiles from the ephemeris.
-The dashed red vertical line marks zero phase.
+The dashed green vertical line marks zero phase.
 Baselines have been fitted and subtracted from each lightcurve.
-The blue dashed lines show (normalised) fitted Gaussians without scattering (see main text for details).}
+The red curves are fits of the normalised pulses to \Eqn~\ref{eqn:emg}, and the blue curves are the inferred Gaussian pulses without scattering, also normalised (see main text for details).}
                   \label{fig:pulsestack}
@@
 
-The apparent lack of linear polarisation in the MWA pulses, however, is expected due to the high RM of ${\sim}961\,{\rm rad}/{\rm m}^2$ \citepalias[as reported in][]{2024MNRAS.535..909D}, causing the pulses to be depolarised within individual channels.
+The apparent lack of linear polarisation in the MWA pulses, however, is expected due to the high rotation measure (RM) of ${\sim}961\,{\rm rad}/{\rm m}^2$ \citepalias[as reported in][]{2024MNRAS.535..909D}, causing the pulses to be depolarised within individual channels.
 We also report that no significantly circularly polarised emission was seen at MWA frequencies.
@@
 
-The high S/N of each time bin allowed us to test whether the rotation measure (RM) was consistent across each pulse.
+The high S/N of each time bin allowed us to test whether the RM was consistent across each pulse.
 We therefore performed a joint fit of the Stokes Q and U spectra of each time bin to
@@
 
-Although there is as yet no clear consensus on whether LPTs represent one class or multiple classes of system \citep[e.g.][]{2024ApJ...961..214R}, the recent confirmation of J1912$-$4410 as a pre-evolved white dwarf pulsar \citep{2023NatAs...7..931P} and ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 as polars \citep{deRuiter2025,2025A&A...695L...8R} raise the intriguing possibility that other LPTs may also be radio-emitting white dwarf pulsars at various stages of evolution \citep{2021NatAs...5..648S}.
+Although there is as yet no clear consensus on whether LPTs represent one class or multiple classes of system \citep[e.g.][]{2024ApJ...961..214R}, the recent confirmation of J1912$-$4410 as a pre-evolved white dwarf pulsar \citep{2023NatAs...7..931P} and ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 as polars \citep{deRuiter2025,2025A&A...695L...8R} raise the intriguing possibility that other LPTs may also be radio-emitting white dwarf pulsars at various stages of evolution (\citealt{2021NatAs...5..648S}, Horv\'{a}th et al.
+in prep).
 

### 2025-05-23 paper/main.tex
Added peak flux to the table of pulse properties, and added table to appendix

@@
 We performed a similar processing of the data, and identified four pulses with ToAs consistent with an ephemeris derived from the other data.
-The folded and stacked dynamic spectra are shown in \Fig~\ref{fig:stacked_spectra}.
+The folded and stacked dynamic spectra are shown in \Fig~\ref{fig:stacked_spectra}\footnote{The signal-to-noise of the MeerKAT detections was insufficient to improve on the localisation derived in \citetalias{2024MNRAS.535..909D}.}.
 
@@
 
-%\begin{deluxetable*}{ccccc}
-%  \tablecaption{Times of arrival and pulse properties\label{tbl:toas}}
-%  \tablehead{
-%    \colhead{Telescope} & \colhead{$\nu$} & \colhead{ToA} & \colhead{Fluence} & \colhead{$\sigma$} \\ 
-%    & \colhead{(MHz)} & \colhead{(MJD)} & \colhead{(Jy\,s)} & \colhead{(s)}
-%  } 
-%  \startdata
-%ASKAP & 888 & 59965.0429346(42) & 13.4(2) & 29.1(4) \\
-%MWA & 170 & 59966.061584(40) & 358(55) & 40(7) \\
-%ASKAP & 888 & 60040.913447(32) & 1.0(1) & 25(3) \\
-%MeerKAT & 1284 & 60092.8995476(100) & 0.104(7) & 12.8(9) \\
-%MeerKAT & 1284 & 60092.947966(10) & 0.10(1) & 12(1) \\
-%MeerKAT & 1284 & 60092.996466(11) & 0.125(7) & 15.8(9) \\
-%MeerKAT & 1284 & 60093.044919(12) & 0.122(7) & 16(1) \\
-%MWA & 200 & 60481.637466(65) & 50(11) & 24(8) \\
-%MWA & 200 & 60485.658977(33) & 29(3) & 16(4) \\
-%MWA & 200 & 60489.632266(20) & 48(3) & 14(2) \\
-%MWA & 200 & 60492.588020(24) & 87(7) & 14(3) \\
-%MWA & 200 & 60496.609639(18) & 67(4) & 17(2) \\
-%MWA & 200 & 60503.587085(14) & 82(3) & 17(2) \\
-%ASKAP & 888 & 60503.6347610(51) & 6.2(2) & 16.4(5) \\
-%MWA & 200 & 60506.542809(33) & 57(7) & 9(4) \\
-%MWA & 200 & 60510.564531(11) & 79(3) & 16(1) \\
-%MWA & 200 & 60519.528812(29) & 86(10) & 14(4) \\
-%MWA & 200 & 60522.533028(16) & 76(3) & 18(2) \\
-%MWA & 200 & 60527.524033(14) & 73(3) & 16(2) \\
-%MWA & 200 & 60530.528339(16) & 68(4) & 17(2) \\
-%MWA & 200 & 60537.506042(13) & 92(4) & 17(2) \\
-%MWA & 200 & 60541.479448(47) & 41(6) & 14(5) \\
-%MWA & 200 & 60544.483761(15) & 79(3) & 20(2) \\
-%MWA & 200 & 60551.461625(16) & 85(4) & 16(2) \\
-%MWA & 185 & 60572.395455(15) & 74(3) & 15(2) \\
-%MWA & 185 & 60572.443943(21) & 73(4) & 16(2) \\
-%MWA & 185 & 60572.540824(18) & 64(4) & 16(2) \\
-%MWA & 185 & 60572.589281(31) & 82(8) & 21(4) \\
-%MWA & 200 & 60592.456765(27) & 34(3) & 19(3) \\
-%MWA & 200 & 60592.505159(33) & 35(4) & 19(4) \\
-%MWA & 200 & 60593.474369(26) & 29(3) & 15(3) \\
-%MWA & 200 & 60593.522901(46) & 27(4) & 19(5) \\
-%MWA & 200 & 60594.443484(21) & 43(3) & 18(2) \\
-%MWA & 200 & 60594.491990(33) & 19(2) & 12(4) \\
-%MWA & 200 & 60595.461118(29) & 33(3) & 19(3) \\
-%MWA & 200 & 60595.509617(25) & 27(2) & 13(3) \\
-%MWA & 200 & 60596.430283(20) & 39(3) & 16(2) \\
-%MWA & 200 & 60596.478721(23) & 39(3) & 17(3) \\
-%MWA & 200 & 60597.447846(41) & 22(3) & 16(5) \\
-%MWA & 200 & 60597.496319(30) & 38(4) & 19(3) \\
-%MWA & 200 & 60599.434635(17) & 39(2) & 13(2) \\
-%MWA & 200 & 60599.483122(24) & 32(3) & 13(3) \\
-%MWA & 200 & 60600.500655(31) & 30(3) & 16(4) \\
-%MWA & 200 & 60602.438964(32) & 36(4) & 21(4) \\
-%MWA & 200 & 60602.487394(27) & 39(3) & 20(3) \\
-%MeerKAT & 813 & 60602.5835733(40) & 1.64(4) & 14.9(4) \\
-  %\enddata
-%\end{deluxetable*}
-
 These ToAs were then barycentred and fit for both period and DM, resulting in the values given in \Tab~\ref{tbl:ephemeris}.
-The residuals are plotted in \ref{fig:pulse_details}, along with the fitted pulse widths and fluences.
+The residuals are presented in \Fig~\ref{fig:pulse_details} and \Tab~\ref{tbl:toas}, along with other fitted properties of the pulses.
 We also tried fitting a timing model that included a spin-down parameter, and found that it was consistent with zero spin-down to within $1\sigma$, and so is not included in the ephemeris.
@@
 The bottom panel displays $S_{\rm peak,1 GHz} = S_{\rm peak} (\nu/{\rm GHz})^{-\alpha}$, where $\alpha = -2$ has been assumed.
-Notable features of interest include the relative brightness of the early 2023 detections (leftmost two points), and the relative stability of the pulse fluences (and pulse morphology) of the MWA detections in the time range $60480 \le {\rm MJD} \le 60580$.}
+Notable features of interest include the relative brightness of the early 2023 detections (leftmost two points), and the relative stability of the pulse fluences (and pulse morphology) of the MWA detections in the time range $60480 \le {\rm MJD} \le 60580$.
+See \Tab~\ref{tbl:toas} for the values shown in this figure.}
   \label{fig:pulse_details}
@@
 
+\section{Pulse properties}
+
+\Tab~\ref{tbl:toas} provides the fitted parameter values of the pulses shown in \Fig~\ref{fig:pulse_details}.
+
+\begin{table*}
+  \centering
+  \caption{Times of arrival and other fitted pulse properties}
+  \label{tbl:toas}
+  \begin{tabular}{cccccc}
+\hline
+Telescope & Freq & ToA & $S_{\rm peak}$ & $\sigma$ & Fluence \\
+ & (MHz) & (MJD) & (Jy) & (s) & (Jy\,s) \\
+\hline
+ASKAP & 888 & 59965.0429346(42) & 0.184(5) & 29.1(4) & 13.4(2) \\
+MWA & 170 & 59966.061584(40) & 4(1) & 40(7) & 358(55) \\
+ASKAP & 888 & 60040.913447(32) & 0.015(3) & 25(3) & 1.0(1) \\
+MeerKAT & 1284 & 60092.8995476(100) & 0.0032(4) & 12.8(9) & 0.104(7) \\
+MeerKAT & 1284 & 60092.947966(10) & 0.0033(6) & 12(1) & 0.10(1) \\
+MeerKAT & 1284 & 60092.996466(11) & 0.0032(3) & 15.8(9) & 0.125(7) \\
+MeerKAT & 1284 & 60093.044919(12) & 0.0030(3) & 16(1) & 0.122(7) \\
+MWA & 200 & 60481.637466(65) & 0.8(4) & 24(8) & 50(11) \\
+MWA & 200 & 60485.658977(33) & 0.7(2) & 16(4) & 29(3) \\
+MWA & 200 & 60489.632266(20) & 1.4(3) & 14(2) & 48(3) \\
+MWA & 200 & 60492.588020(24) & 2.4(6) & 14(3) & 87(7) \\
+MWA & 200 & 60496.609639(18) & 1.5(3) & 17(2) & 67(4) \\
+MWA & 200 & 60503.587085(14) & 2.0(2) & 17(2) & 82(3) \\
+ASKAP & 888 & 60503.6347610(51) & 0.151(7) & 16.4(5) & 6.2(2) \\
+MWA & 200 & 60506.542809(33) & 2(1) & 9(4) & 57(7) \\
+MWA & 200 & 60510.564531(11) & 2.0(2) & 16(1) & 79(3) \\
+MWA & 200 & 60519.528813(29) & 2.4(8) & 14(4) & 86(10) \\
+MWA & 200 & 60522.533028(16) & 1.6(2) & 18(2) & 76(3) \\
+MWA & 200 & 60527.524033(14) & 1.8(2) & 16(2) & 73(3) \\
+MWA & 200 & 60530.528339(16) & 1.6(2) & 17(2) & 68(4) \\
+MWA & 200 & 60537.506042(13) & 2.1(3) & 17(2) & 92(4) \\
+MWA & 200 & 60541.479447(47) & 1.1(5) & 14(5) & 41(6) \\
+MWA & 200 & 60544.483761(15) & 1.6(2) & 20(2) & 79(3) \\
+MWA & 200 & 60551.461625(16) & 2.2(3) & 16(2) & 85(4) \\
+MWA & 185 & 60572.395455(15) & 1.9(3) & 15(2) & 74(3) \\
+MWA & 185 & 60572.443943(21) & 1.8(3) & 16(2) & 73(4) \\
+MWA & 185 & 60572.540824(18) & 1.6(3) & 16(2) & 64(4) \\
+MWA & 185 & 60572.589281(31) & 1.6(4) & 21(4) & 82(8) \\
+MWA & 200 & 60592.456765(27) & 0.7(2) & 19(3) & 34(3) \\
+MWA & 200 & 60592.505159(33) & 0.7(2) & 19(4) & 35(4) \\
+MWA & 200 & 60593.474369(26) & 0.8(2) & 15(3) & 29(3) \\
+MWA & 200 & 60593.522901(46) & 0.6(2) & 19(5) & 27(4) \\
+MWA & 200 & 60594.443484(21) & 0.9(2) & 18(2) & 43(3) \\
+MWA & 200 & 60594.491990(33) & 0.6(3) & 12(4) & 19(2) \\
+MWA & 200 & 60595.461118(29) & 0.7(2) & 19(3) & 33(3) \\
+MWA & 200 & 60595.509617(25) & 0.8(2) & 13(3) & 27(2) \\
+MWA & 200 & 60596.430283(20) & 1.0(2) & 16(2) & 39(3) \\
+MWA & 200 & 60596.478721(23) & 0.9(2) & 17(3) & 39(3) \\
+MWA & 200 & 60597.447846(41) & 0.5(2) & 16(5) & 22(3) \\
+MWA & 200 & 60597.496319(30) & 0.8(2) & 19(3) & 38(4) \\
+MWA & 200 & 60599.434635(17) & 1.2(2) & 13(2) & 39(2) \\
+MWA & 200 & 60599.483122(24) & 1.0(3) & 13(3) & 32(3) \\
+MWA & 200 & 60600.500655(31) & 0.7(2) & 16(4) & 30(3) \\
+MWA & 200 & 60602.438964(32) & 0.7(2) & 21(4) & 36(4) \\
+MWA & 200 & 60602.487394(27) & 0.8(2) & 20(3) & 39(3) \\
+MeerKAT & 813 & 60602.5835733(40) & 0.044(2) & 14.9(4) & 1.64(4) \\
+\hline
+  \end{tabular}
+\end{table*}
+
 % Don't change these lines

### 2025-05-23 dynspec/make_toa_table.py

@@ -10,8 +10,8 @@ def main():
 
     table = QTable.read(args.toas_file)
 
-    print("Telescope & Freq & ToA & Fluence & $\\sigma$ \\\\")
-    print(" & (MHz) & (MJD) & (Jy\\,s) & (s) \\\\")
+    print("Telescope & Freq & ToA & $S_{\\rm peak}$ & $\\sigma$ & Fluence \\\\")
+    print(" & (MHz) & (MJD) & (Jy) & (s) & (Jy\\,s) \\\\")
     for row in table:
         toa_err = row['ToA_err']
         toa_precision = int(np.floor(-np.log10(toa_err.to('d').value))) + 1
@@ -28,7 +28,12 @@ def main():
         width_precision = int(np.floor(-np.log10(width_err.to('s').value))) + 1
         width_str = f"{width.to('s').value:.{width_precision}f}({int(np.round(width_err.to('s').value*10**(width_precision))):.0f})"
 
-        print(f"{row['telescope']} & {row['freq'].to('MHz').value:.0f} & {toa_str} & {fluence_str} & {width_str} \\\\")
+        peak_flux = row['fitted_peak_flux_density']
+        peak_flux_err = row['fitted_peak_flux_density_err']
+        peak_flux_precision = int(np.floor(-np.log10(peak_flux_err.to('Jy').value))) + 1
+        peak_flux_str = f"{peak_flux.to('Jy').value:.{peak_flux_precision}f}({int(np.round(peak_flux_err.to('Jy').value*10**(peak_flux_precision))):.0f})"
+
+        print(f"{row['telescope']} & {row['freq'].to('MHz').value:.0f} & {toa_str} & {peak_flux_str} & {width_str} & {fluence_str} \\\\")
 
 if __name__ == '__main__':
     main()

### 2025-05-26 paper/main.tex
Latest synch of paper with Overleaf version -- including more instances of addressing co-authors' comments

@@
 \begin{abstract}
-We report the discovery of several new pulses from the source \srcfull{} (\src{}), confirming it as a long period transient (LPT) with a period of ${\sim}1.16\,$hours.
+We report the discovery of several new pulses from the source \srcfull{} (\src{}), originally identified from a single 2-min log pulse, confirming it as a long period transient (LPT) with a period of ${\sim}1.16\,$hours.
 The pulses are significantly scattered, consistent with Galactic electron density models.
@@
 
-\srcfull{} (hereafter, \src{}) is a transient radio source discovered in the Variables and Slow Transients (VAST) survey \citep[][hereafter \citetalias{2024MNRAS.535..909D}]{2024MNRAS.535..909D}.
+\srcfull{} (hereafter, \src{}) is a transient radio source discovered \citep[][hereafter \citetalias{2024MNRAS.535..909D}]{2024MNRAS.535..909D} in the Variables and Slow Transients (VAST) survey \citep{2013PASA...30....6M}.
 A single, highly polarised pulse was observed, lasting approximately 2 minutes, exhibiting a steep spectrum ($\alpha = -3.1$, for flux density $S_\nu\propto\nu^\alpha$).
@@
 
-Although optical follow-up has confirmed that at least some LPTs are a type of strongly magnetic cataclysmic variable (CV) known as polars \citep{deRuiter2025,2024ApJ...976L..21H,2025A&A...695L...8R}, it remains unclear if this model can account for all known LPTs \citep[e.g.][]{2022ApJ...940...72R,Lee2025}.
+Although optical observations have provided compelling evidence that at least some LPTs are detached, possibly strongly magnetic, white dwarf (WD) binaries \citep{deRuiter2025,2024ApJ...976L..21H,2025A&A...695L...8R}, it remains unclear if this model can account for all known LPTs \citep[e.g.][]{2022ApJ...940...72R,Lee2025}.
 Optical follow-up is challenging for \src{}, which is situated very close to the Galactic plane ($b = -0\overset{\circ}{.}12$), at a distance of ${\sim}4.7\,$kpc \citepalias{2024MNRAS.535..909D}.
@@
 
-The MWA, ASKAP and MeerKAT are all radio interferometers capable of imaging.
+Pulses from \src{} were detected with the Murchison Widefield Array \citep[MWA;][]{Tingay2013}, the Australian SKA Pathfinder \citep[ASKAP;][]{2021PASA...38....9H} and MeerKAT \citep{2016mks..confE...1J}, are all radio interferometers capable of imaging.
 A summary of all the observations included in this work is summarised in \Tab~\ref{tbl:obs}.
@@
   \label{tbl:obs}
-  \begin{tabular}{lllccc}
+  \begin{tabular}{lllcccc}
     \hline
-    Date range & Telescope & Project & $\nu$ & $\Delta\nu$ & Number of \\ 
-    (MJD) & & & (MHz) & (MHz) & pulses \\
+    Date range & Telescope & Project & $\nu$ & $\Delta\nu$ & Obs. length & Number of \\ 
+    (MJD) & & & (MHz) & (MHz) & (min) & pulses \\
     \hline 
-    59965 & ASKAP & SB47253 (original discovery) & 887.5 & 288 & 1 \\
-    59966 & MWA & G0060 & 161.92 & 15.36 & 1 \\
-    %60084 & MWA & G0057 & 154.24 & 30.72 & $\le$ 1 \\
-    60040  & ASKAP & SB49153 & 887.5 & 288 & 1 \\
-    60092 - 60093 & MeerKAT & DDT-20230525-DD-01 & 1284 & 856 & 4 \\
-    60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & 16 \\
-    60503 & ASKAP & SB63600 & 887.5 & 288 & 1 \\
-    60572 & MWA & D0042 & 184.96 & 30.72 & 4 \\
-    60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & 17 \\
-    60602 & MeerKAT & DDT-20241015-NH-01 & 812.8 & 495.3 & 1 \\
+    59965 & ASKAP & SB47253 (original discovery) & 887.5 & 288 & 12.1 & 1 \\
+    59966 & MWA & G0060 & 161.92 & 15.36 & 6.7 & 1 \\
+    %60084 & MWA & G0057 & 154.24 & 30.72 & N/A & $\le$ 1 \\
+    60040  & ASKAP & SB49153 & 887.5 & 288 & 12.1 & 1 \\
+    60092 - 60093 & MeerKAT & DDT-20230525-DD-01 & 1284 & 856 & 307 & 4 \\
+    60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & (Each obs.) 4.9 & 16 \\
+    60503 & ASKAP & SB63600 & 887.5 & 288 & 12.3 & 1 \\
+    60572 & MWA & D0042 & 184.96 & 30.72 & (Each obs.) 4.9 & 4 \\
+    60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & (Each obs.) 4.9 & 17 \\
+    60602 & MeerKAT & DDT-20241015-NH-01 & 812.8 & 495.3 & 10 & 1 \\
     \hline
@@
 \citetalias{2024MNRAS.535..909D} presented an exhaustive search of the ASKAP data available at the time of writing, comprising 60\,h of data, and yielding only a single detection of \src{} (in Scheduling Block ID 47253).
-Subsequent to the writing of \citetalias{2024MNRAS.535..909D}, a further epoch of the VAST survey was performed (SBID 63600) in which \src{} produced a detectable pulsation.
+Subsequent to the writing of \citetalias{2024MNRAS.535..909D}, a further search for transient signals in ASKAP data was performed (SBID 63600) in which \src{} produced a detectable pulsation.
 
@@
 
-No significant polarised emission was detected in the MWA pulses, as well as the 2023 MeerKAT pulses.
-The apparent lack of polarisation in the 2023 MeerKAT data set is likely due to low S/N coupled with the source not being centred in the beam.
+No significant linear or circular polarised emission was detected in the 2023 MeerKAT pulses.
+This is likely due to low S/N coupled with the source not being centred in the beam.
 Much more careful imaging analysis would be needed to obtain reliable measurements or limits on the polarised components of those pulses.
 
-The apparent lack of linear polarisation in the MWA pulses, however, is expected due to the high rotation measure (RM) of ${\sim}961\,{\rm rad}/{\rm m}^2$ \citepalias[as reported in][]{2024MNRAS.535..909D}, causing the pulses to be depolarised within individual channels.
-We also report that no significantly circularly polarised emission was seen at MWA frequencies.
+Given \src{}'s rotation measure (RM) of ${\sim}961\,{\rm rad}/{\rm m}^2$ \citepalias[as reported in][]{2024MNRAS.535..909D}, linearly polarised emission would undergo several tens of degrees of rotation per 40\,kHz channel of the GPM observations, and therefore be somewhat depolarised.
+To offer the best chance of detecting polarised emission, the MWA DDT observations between MJD 60592 and 60602 (see \Tab~\ref{tbl:obs}) were taken with a frequency resolution of 10\,kHz, which would result in only $12^\circ$ or rotation per channel at 200\,MHz.
+We report no significant linearly polarised emission after de-Faraday rotating\footnote{On account of the possible sign ambiguity of the reported RM, we also tried de-Faraday rotating the MWA observations at $961\,{\rm rad}/{\rm m}^2$.} these observations at $-961\,{\rm rad}/{\rm m}^2$.
+We also report that no significantly circularly polarised emission was seen in any MWA observation.
 
-The three sufficiently bright pulses for which we report significant polarisation are (1) the original 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, (2) the 2024 ASKAP pulse, and (3) the 2024 MeerKAT pulse.
+The three sufficiently bright pulses for which we report significant polarisation are (1) the original 2023 ASKAP pulse, whose polarisation has already been discussed at length in \citetalias{2024MNRAS.535..909D}, (2) the 2024 ASKAP pulse, and (3) the 2024 MeerKAT pulse.
 We applied the parallactic angle correction to the MeerKAT data, as this had not already been applied during upstream processing.
@@
 
-\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are confirmed polars (\Fig~\ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is a polar.
-However, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for confirmed polars \citep{schwope2025polarcatcatalogpolarslowaccretion}.
-This makes it an interesting test bed for the suggestion advanced by \citet{2025A&A...695L...8R} that `short LPTs' ($P \lesssim 78\,$mins) and `long LPTs' ($P \gtrsim 78\,$mins) represent different classes of systems (AM Canum Venaticorum stars and CVs, respectively).
+\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are conjectured to be on the evolutionary path towards becoming polars (\Fig~\ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is such a system.
+Notably, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for confirmed polars \citep{schwope2025polarcatcatalogpolarslowaccretion}.
+This makes it an interesting test bed for the possibility that LPTs with different periods represent different stages of WD binary evolution, as they progress towards becoming polars.
 \begin{figure*}
@@
 
-Although there is as yet no clear consensus on whether LPTs represent one class or multiple classes of system \citep[e.g.][]{2024ApJ...961..214R}, the recent confirmation of J1912$-$4410 as a pre-evolved white dwarf pulsar \citep{2023NatAs...7..931P} and ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 as polars \citep{deRuiter2025,2025A&A...695L...8R} raise the intriguing possibility that other LPTs may also be radio-emitting white dwarf pulsars at various stages of evolution (\citealt{2021NatAs...5..648S}, Horv\'{a}th et al.
+Although there is as yet no clear consensus on whether LPTs represent one class or multiple classes of system \citep[e.g.][]{2024ApJ...961..214R}, the recent confirmation of J1912$-$4410 as a pre-evolved white dwarf pulsar \citep{2023NatAs...7..931P} and ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 as likely candidates for polars or polar-like systems \citep{deRuiter2025,2025A&A...695L...8R} raise the intriguing possibility that other LPTs may also be radio-emitting white dwarf pulsars at various stages of evolution (\citealt{2021NatAs...5..648S}, Horv\'{a}th et al.
 in prep).

### 2025-05-29 paper/main.tex
Updated everything on account of two new ATCA detections. Plots updated, ephemeris updated, scripts updated, paper updated.

@@
 Dougal Dobie$^{3,4}$,
-John Morgan$^{1}$,
 David L.~Kaplan$^{2}$,
+John Morgan$^{5}$,
 and Ziteng Wang$^{1}$
@@
 $^{1}$International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia\\
+$^{2}$Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia\\
+$^{3}$ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav), Hawthorn, VIC 3122, Australia\\
 $^{4}$Department of Physics, University of Wisconsin-Milwaukee, P.O. Box 413, Milwaukee, WI 53201, USA\\
-$^{2}$Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia\\
-$^{3}$ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav), Hawthorn, VIC 3122, Australia
+$^{5}$CSIRO Space and Astronomy, P.O. Box 1130, Bentley, WA 6102, Australia\\
 }
@@
 
-Pulses from \src{} were detected with the Murchison Widefield Array \citep[MWA;][]{Tingay2013}, the Australian SKA Pathfinder \citep[ASKAP;][]{2021PASA...38....9H} and MeerKAT \citep{2016mks..confE...1J}, are all radio interferometers capable of imaging.
-A summary of all the observations included in this work is summarised in \Tab~\ref{tbl:obs}.
+Pulses from \src{} were detected with the Murchison Widefield Array \citep[MWA;][]{Tingay2013}, the Australian SKA Pathfinder \citep[ASKAP;][]{2021PASA...38....9H}, MeerKAT \citep{2016mks..confE...1J}, and the Australia Telescope Compact Array (ATCA, \todo{CITATION??}), all radio interferometers capable of imaging.
+A summary of all the observations containing pulse detections included in this work is summarised in \Tab~\ref{tbl:obs}.
 In this section, we describe how each telescope was used to generate dynamic spectra of \src{}.
@@
     \hline
-    Date range & Telescope & Project & $\nu$ & $\Delta\nu$ & Obs. length & Number of \\ 
-    (MJD) & & & (MHz) & (MHz) & (min) & pulses \\
+    Date range & Telescope & Project & $\nu$ & $\Delta\nu$ & Obs. (num. $\times$) & Number of \\ 
+    (MJD) & & & (MHz) & (MHz) & length (min) & pulses \\
     \hline 
@@
     60092 - 60093 & MeerKAT & DDT-20230525-DD-01 & 1284 & 856 & 307 & 4 \\
-    60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & (Each obs.) 4.9 & 16 \\
+    60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & $16 \times 4.9$ & 16 \\
     60503 & ASKAP & SB63600 & 887.5 & 288 & 12.3 & 1 \\
-    60572 & MWA & D0042 & 184.96 & 30.72 & (Each obs.) 4.9 & 4 \\
-    60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & (Each obs.) 4.9 & 17 \\
+    60572 & MWA & D0042 & 184.96 & 30.72 & $4 \times 4.9$ & 4 \\
+    60587 & ATCA & \todo{?????} & 2100 & 2048 & 93.2 & 2 \\
+    60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & $17 \times 4.9$ & 17 \\
     60602 & MeerKAT & DDT-20241015-NH-01 & 812.8 & 495.3 & 10 & 1 \\
@@
 
-% ** ANGIE **
-% Plz add a short paragraph here with the essential details of the IPS observation included in this paper: G0060, upper half-band only, how the images were made.
-I'll (SM) add a few sentences about how I selected that observation in the first place.
-An additional MWA observation made as part of the MWA Interplanetary Scintillation (IPS) Survey, project code G0060, has also been included in this present study. 
-A full description of how MWA IPS observations are scheduled and processed can be found in Section~2 of \citet{Morgan2022}.
-Details of the imaging of IPS observations since the first data release can be found in Waszewski et al. (submitted).
-The two adjacent 200-second observations included in this work are a sub-section of a full 10-minute near-Sun observation (30$^{\circ}$ elongation).
-These observations are taken over two equal bands of frequency, centred on approximately 80\,MHz and 160\,MHz. For this study, only the upper band has been processed. 
-The observation was self-calibrated against a sky model based on the GLEAM survey \citep{Hurley-Walker2017} using \textsc{mwa\_hyperdrive}\footnote{\url{https://github.com/MWATelescope/mwa_hyperdrive}}, and then imaged using \textsc{WSClean}.
-\src{} is clearly visible as a point source in the image, and the lightcurve presented in this work is the result of averaging over the 15.36-MHz subband, using 10-second time bins.
+An additional MWA observation made as part of the MWA Interplanetary Scintillation (IPS) Survey, project code G0060, taken just one day after the original ASKAP pulse, was found to have \src{} in the field of view.
+The pulse was detected as a point source in the image formed from the third of three adjacent 200-second, near-Sun observations (30$^{\circ}$ elongation).
+In this paper we present both the second and third observations (6.7 minutes total), in order to make the contrast between detection and non-detection more visible in the lightcurve formed by averaging over the 15.36-MHz subband, using 10-second time bins.
+A full description of how MWA IPS observations are scheduled and processed can be found in Section~2 of \citet{Morgan2022}, but the essential details are summarised here.
+The observations are taken over two equal bands of frequency, centred on approximately 80\,MHz and 160\,MHz.
+For this study, only the upper band has been processed. 
+The observations were self-calibrated against a sky model based on the GLEAM survey \citep{Hurley-Walker2017} using \textsc{mwa\_hyperdrive}\footnote{\url{https://github.com/MWATelescope/mwa_hyperdrive}}, and then imaged using \textsc{WSClean}.
+Further details of the imaging of IPS observations since the first data release can be found in Waszewski et al. (submitted).
 
@@
 The folded and stacked dynamic spectra are shown in \Fig~\ref{fig:stacked_spectra}\footnote{The signal-to-noise of the MeerKAT detections was insufficient to improve on the localisation derived in \citetalias{2024MNRAS.535..909D}.}.
+
+\subsection{ATCA}
+
+\todo{Akash to add some paragraphs here with details of processing ATCA data:}
+\begin{itemize}
+    \item Describe both Oct 4 and Oct 12 observations
+    \item Mention that the Oct 12 observations did not yield any detections (even though there were four chances for it to do so!).
+\end{itemize}
 
@@
     \hline
-    Period (s) & $4186.3283 \pm 0.0003$ \\
-    PEPOCH (MJD) & $59965.03791 \pm 0.00003$ \\
-    DM (pc/cm$^{-3}$) & $763 \pm 25$ \\
+    Period (s) & $4186.3285 \pm 0.0002$ \\
+    PEPOCH (MJD) & $59965.03792 \pm 0.00003$ \\
+    DM (pc/cm$^{-3}$) & $733 \pm 22$ \\
     $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$ \\
@@
 
-The measured DM of $763 \pm 25\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of $710^{+200}_{-180}\,{\rm pc}\,{\rm cm}^{-3}$ given in \citetalias{2024MNRAS.535..909D}.
+The measured DM of $733 \pm 22\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of $710^{+200}_{-180}\,{\rm pc}\,{\rm cm}^{-3}$ given in \citetalias{2024MNRAS.535..909D}.
 Because we have not attempted to simultaneously fit for both DM and scattering timescale, there will remain some small systematic error on this reported DM measurement.
@@
 Much more careful imaging analysis would be needed to obtain reliable measurements or limits on the polarised components of those pulses.
+We also find no significant polarised emission from the ATCA pulses. \todo{[Akash: Can you please verify this?]}
 
@@
 However, pulses were detected just ten days later on 2024-06-20 (the first of the MWA 200\,MHz points in \Fig~\ref{fig:pulse_details}), and at each epoch thereafter whenever the MWA was observing in \src{}'s direction when a pulse was due to arrive.
+
+In contrast, the ATCA observation taken on 2025-10-12 did not yield any detections (out of four possible predicted ToAs that occurred during that observation).
+This is despite the fact that pulses were detected with ATCA just eight days prior with a similar noise level, as well as the fact that pulses were detected at the MWA within 24 hours of the ATCA observation (none of the MWA observations were coincident with the ATCA observation).
+However, there is enough pulse-to-pulse variability to allow for the possibility that the pulses during the 2025-10-12 were present, but fell below the detection threshold of ATCA.
 
@@
 % ASKAP -- I have fixed this to use the correct name for the observatory
-The Australian SKA Pathfinder is part of the Australia Telescope National Facility which is managed by CSIRO.
+The Australian SKA Pathfinder is part of the Australia Telescope National Facility which is managed by CSIRO (https://ror.org/05qajvd42).
 Operation of ASKAP is funded by the Australian Government with support from the National Collaborative Research Infrastructure Strategy.
@@
 
-It can be shown that pulses scatter-broadened by a thin screen\footnote{Relaxing the assumption of a single, thin, isotropic screen could affect the shape of the scattered pulse in ways that could plausibly affect timing \citep{2009MNRAS.395.1391R}, but quantification of this is beyond the scope of this appendix.} will appear to the observer as the original pulse convolved with a one-sided exponential kernel with an associated timescale $\tau$ \citep{1972MNRAS.157...55W,1973MNRAS.163..345W}.
+It can be shown that pulses scatter-broadened by a thin screen\footnote{Relaxing the assumption of a single, thin, isotropic screen affects the shape of the scattered pulse in ways that could plausibly affect timing \citep{2009MNRAS.395.1391R}, but quantification of this is beyond the scope of this appendix.} will appear to the observer as the original pulse convolved with a one-sided exponential kernel with an associated timescale $\tau$ \citep{1972MNRAS.157...55W,1973MNRAS.163..345W}.
 For intrinsically Gaussian pulses of scale $\sigma$, the result of this convolution is well described by the \textit{exponentially modified Gaussian} (EMG), as given in \Eqn~\ref{eqn:emg}.
@@
 MWA & 185 & 60572.589281(31) & 1.6(4) & 21(4) & 82(8) \\
+ATCA & 2100 & 60587.270973(26) & 0.003(1) & 12(2) & 0.10(2) \\
+ATCA & 2100 & 60587.319527(28) & 0.003(1) & 10(3) & 0.09(2) \\
 MWA & 200 & 60592.456765(27) & 0.7(2) & 19(3) & 34(3) \\

### 2025-05-29 dynspec/ephemeris_fits.py

@@ -16,7 +16,8 @@ def period_model(toas_mjd, period_d, pepoch_mjd):
 toas_mjd = []
 for row in table:
 
-    location = EarthLocation.of_site(row['telescope'])
+    telescope = row['telescope'] if row['telescope'] != 'ATCA' else 'Siding Spring Observatory'
+    location = EarthLocation.of_site(telescope)
     freq = row['freq']
     toa = Time(row['ToA'], scale='utc', format='mjd', location=location)
     toa_bary_dd = barycentre(toa, ephemeris['coord']) - calc_dmdelay(ephemeris['DM'], freq, np.inf*u.MHz)

### 2025-05-29 dynspec/fit_toas.py

@@ -189,7 +189,7 @@ def main():
             f_ref,
             toa.mjd,
             toa_err,
-            dat['TELESCOPE'],
+            dat['TELESCOPE'] if dat['TELESCOPE'] != "Siding Spring Observatory" else "ATCA",
             fluence,
             fluence_err,
             peak_signal,

### 2025-05-29 dynspec/make_toa_plots.py

@@ -26,7 +26,7 @@ def main():
     # Calculate timing residuals
     ephem = get_J1755_ephemeris()
     freq = table['freq']
-    locations = [EarthLocation.of_site(table['telescope'][i]) for i in range(len(table['ToA']))]
+    locations = [EarthLocation.of_site(table['telescope'][i] if table['telescope'][i] != 'ATCA' else 'Siding Spring Observatory') for i in range(len(table['ToA']))]
     toas = Time([Time(table['ToA'][i], scale='utc', format='mjd', location=locations[i]) for i in range(len(table['ToA']))])
     bary_toas = barycentre(toas, ephem['coord'])
     bary_toas_dd = bary_toas - calc_dmdelay(ephem['DM'], freq, np.inf)
@@ -57,8 +57,9 @@ def main():
         185:  {'label': 'MWA (185 MHz)',      'color': '#009E73', 'marker': '.'},
         200:  {'label': 'MWA (200 MHz)',      'color': '#0072B2', 'marker': '.'},
         813:  {'label': 'MeerKAT (813 MHz)',  'color': '#CC79A7', 'marker': 'x'},
-        888:  {'label': 'ASKAP (888 MHz)',    'color': '#D55E00', 'marker': 'o', 'markerfacecolor': 'none'},
+        888:  {'label': 'ASKAP (888 MHz)',    'color': '#D55E00', 'marker': '+'},
         1284: {'label': 'MeerKAT (1284 MHz)', 'color': '#000000', 'marker': 'x'},
+        2100: {'label': 'ATCA (2100 MHz)',    'color': '#0000FF', 'marker': 'o', 'markerfacecolor': 'none'},
     }
 
     for col in range(ncols):

### 2025-05-29 dynspec/pulsestack_all.py

@@ -115,7 +115,8 @@ def main():
         axs[0][col].plot(ph_fine*ephemeris['period'], 0.9*y1norm + ys[col], 'r', alpha=0.3)
 
         yticks[col].append(ys[col])
-        ylabels[col].append(f"{times[0].iso[:16]}\n{dat['TELESCOPE']}")#\n(Pulse #{int(np.round(np.median(pulses)))})")
+        telescope = dat['TELESCOPE'] if dat['TELESCOPE'] != "Siding Spring Observatory" else "ATCA"
+        ylabels[col].append(f"{times[0].iso[:16]}\n{telescope}")#\n(Pulse #{int(np.round(np.median(pulses)))})")
         ys[col] += 1
 
     for col in range(args.ncols):

### 2025-05-29 dynspec/timing.py

@@ -11,9 +11,9 @@ import sys
 
 def get_J1755_ephemeris():
     return {
-        'PEPOCH': Time(59965.037913, scale='utc', format='mjd'),
-        'period': 4186.32825 * u.s,
-        'DM': 763 * u.pc / u.cm**3,
+        'PEPOCH': Time(59965.037918, scale='utc', format='mjd'),
+        'period': 4186.32849 * u.s,
+        'DM': 733 * u.pc / u.cm**3,
         'tau_sc': 7.0e-2*u.s,
         'coord': SkyCoord("17:55:34.87 -25:27:49.1", unit=(u.hourangle, u.deg), frame='icrs'),
     }

### 2025-06-04 paper/main.tex
Synched paper with Overleaf version

@@
 
-Pulses from \src{} were detected with the Murchison Widefield Array \citep[MWA;][]{Tingay2013}, the Australian SKA Pathfinder \citep[ASKAP;][]{2021PASA...38....9H}, MeerKAT \citep{2016mks..confE...1J}, and the Australia Telescope Compact Array (ATCA, \todo{CITATION??}), all radio interferometers capable of imaging.
+Pulses from \src{} were detected with the Murchison Widefield Array \citep[MWA;][]{Tingay2013}, the Australian SKA Pathfinder \citep[ASKAP;][]{2021PASA...38....9H}, MeerKAT \citep{2016mks..confE...1J}, and the Australia Telescope Compact Array \citep[ATCA;][]{cabb}, all radio interferometers capable of imaging.
 A summary of all the observations containing pulse detections included in this work is summarised in \Tab~\ref{tbl:obs}.
@@
     60572 & MWA & D0042 & 184.96 & 30.72 & $4 \times 4.9$ & 4 \\
-    60587 & ATCA & \todo{?????} & 2100 & 2048 & 93.2 & 2 \\
+    60587 & ATCA & C3363 & 2100 & 2048 & 93.2 & 2 \\
     60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & $17 \times 4.9$ & 17 \\
@@
 
-\todo{Akash to add some paragraphs here with details of processing ATCA data:}
-\begin{itemize}
-    \item Describe both Oct 4 and Oct 12 observations
-    \item Mention that the Oct 12 observations did not yield any detections (even though there were four chances for it to do so!).
-\end{itemize}
+Following its re-detection in the ASKAP data, follow-up observations were conducted at L/S band with the ATCA telescope under the project code C3363 (P.I: Tara Murphy).
+\src\ was observed once on October 4, 2024, for a total of 1.5\,hrs, and again on October 12, 2024, for a total of 2.4\,hrs.
+At the beginning of each observation, 1934$-$638 was used to calibrate the bandpass, and during the observations, 1748$-$253 was used as a phase calibrator.
+Data were flagged, calibrated, and imaged using standard recipes from the Common Astronomy Software Applications package \citep[CASA;][]{casa}.
+The resulting sky model was subtracted from the visibilities (excluding the source of interest).
+These model-subtracted visibilities were phase-centered on the \src{} and averaged over the baselines to produce the dynamic spectra.
+
+We identified two faint pulses (4--5 $\sigma$; see Table~\ref{tbl:toas}) in the observation taken on October 4.
+However, observations taken on October 12 did not yield any pulses (at 3-$\sigma$ level).
+We inspected the data around the expected time of arrival (using Equation~\ref{eqn:timing}) but did not find any pulses.
+The instantaneous noise level around the expected time of arrivals is close to 1\,mJy.
+If pulse-to-pulse flux density variations, similar to ones observed in MWA data (Table~\ref{tbl:toas}), also occur at L/S band, then even a factor 1.5--2 can be sufficient to explain the detection of pulse on October 4 and the absence of pulses on October 12, given that the source is faint at higher frequencies.
 
@@
 \end{equation}
-where $\erfcx(X) = \exp(X^2) \erfc(X)$ is the scaled complimentary error function; $A$, $\mu$, and $\sigma$ are the height, location, and scale of an unscattered Gaussian pulse; and the scattering time scale was fixed at
+where $\erfcx(X) = \exp(X^2) \erfc(X)$ is the scaled complementary error function; $A$, $\mu$, and $\sigma$ are the height, location, and scale of an unscattered Gaussian pulse; and the scattering time scale was fixed at
 \begin{equation}
@@
 Much more careful imaging analysis would be needed to obtain reliable measurements or limits on the polarised components of those pulses.
-We also find no significant polarised emission from the ATCA pulses. \todo{[Akash: Can you please verify this?]}
+We also find no significant polarised emission from the ATCA pulses.
 
@@
 In contrast, the ATCA observation taken on 2025-10-12 did not yield any detections (out of four possible predicted ToAs that occurred during that observation).
-This is despite the fact that pulses were detected with ATCA just eight days prior with a similar noise level, as well as the fact that pulses were detected at the MWA within 24 hours of the ATCA observation (none of the MWA observations were coincident with the ATCA observation).
-However, there is enough pulse-to-pulse variability to allow for the possibility that the pulses during the 2025-10-12 were present, but fell below the detection threshold of ATCA.
+This is despite the fact that pulses were detected with ATCA just eight days prior with a similar instantaneous noise level (${\sim}1\,$mJy), as well as the fact that pulses were detected at the MWA within 24 hours of the ATCA observation (none of the MWA observations were coincident with the ATCA observation).
+However, even a modest amount of pulse-to-pulse variability would allow for the possibility that the pulses during the 2025-10-12 were present, but fell below the detection threshold of ATCA.
 
@@
 The raw visibilities for the MWA, ASKAP, and MeerKAT data sets are available via the respective telescopes' data portals.
+The ATCA data is available on reasonable request to the authors, and will become publicly available from the relevant data portal by November, 2025.
 The post-imaged dynamic spectra, analyses, and timing analysis data products (ToAs, pulse properties) are publicly available on GitHub\footnote{TODO: Make this available upon publication.}.

### 2025-06-05 paper/main.tex
Latest synch of paper with Overleaf

@@
 $^{1}$International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia\\
-$^{2}$Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia\\
-$^{3}$ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav), Hawthorn, VIC 3122, Australia\\
-$^{4}$Department of Physics, University of Wisconsin-Milwaukee, P.O. Box 413, Milwaukee, WI 53201, USA\\
+$^{2}$Department of Physics, University of Wisconsin-Milwaukee, P.O. Box 413, Milwaukee, WI 53201, USA\\
+$^{3}$Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia\\
+$^{4}$ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav), Hawthorn, VIC 3122, Australia\\
 $^{5}$CSIRO Space and Astronomy, P.O. Box 1130, Bentley, WA 6102, Australia\\
@@
 
-For planning observations of \src{} at low ($\lesssim 300$\,MHz), care should be taken to incorporate scattering into the predicted ToAs.
+For planning observations of \src{} at low frequencies ($\lesssim 300$\,MHz), care should be taken to incorporate scattering into the predicted ToAs.
 The $N$th pulse since PEPOCH is predicted to arrive at the Solar System barycentre at
@@
 Given \src{}'s rotation measure (RM) of ${\sim}961\,{\rm rad}/{\rm m}^2$ \citepalias[as reported in][]{2024MNRAS.535..909D}, linearly polarised emission would undergo several tens of degrees of rotation per 40\,kHz channel of the GPM observations, and therefore be somewhat depolarised.
-To offer the best chance of detecting polarised emission, the MWA DDT observations between MJD 60592 and 60602 (see \Tab~\ref{tbl:obs}) were taken with a frequency resolution of 10\,kHz, which would result in only $12^\circ$ or rotation per channel at 200\,MHz.
+To offer the best chance of detecting polarised emission, the MWA DDT observations between MJD 60592 and 60602 (see \Tab~\ref{tbl:obs}) were taken with a frequency resolution of 10\,kHz, which would result in only $12^\circ$ of rotation per channel at 200\,MHz.
 We report no significant linearly polarised emission after de-Faraday rotating\footnote{On account of the possible sign ambiguity of the reported RM, we also tried de-Faraday rotating the MWA observations at $961\,{\rm rad}/{\rm m}^2$.} these observations at $-961\,{\rm rad}/{\rm m}^2$.
@@
 As noted in \citetalias{2024MNRAS.535..909D}, optical follow-up of \src{} is hampered by its position within the Galactic plane ($b = -0.12^\circ$) and the associated extinction.
-Inferring this nature of the system (white dwarf vs neutron star, isolated vs binary) from the radio pulses alone is challenging, until either the population of LPTs is better understood as a whole, or some other property of the radio signal (e.g.
+Inferring the nature of this system (white dwarf vs neutron star, isolated vs binary) from the radio pulses alone is challenging, until either the population of LPTs is better understood as a whole, or some other property of the radio signal (e.g.
 intermittency, polarisation) can be linked to the system properties.
@@
 Although there is as yet no clear consensus on whether LPTs represent one class or multiple classes of system \citep[e.g.][]{2024ApJ...961..214R}, the recent confirmation of J1912$-$4410 as a pre-evolved white dwarf pulsar \citep{2023NatAs...7..931P} and ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 as likely candidates for polars or polar-like systems \citep{deRuiter2025,2025A&A...695L...8R} raise the intriguing possibility that other LPTs may also be radio-emitting white dwarf pulsars at various stages of evolution (\citealt{2021NatAs...5..648S}, Horv\'{a}th et al.
-in prep).
+submitted).
 

### 2025-06-05 paper/main.tex
Final changes by co-authors before submission

@@
 \newauthor
-Angie Waszewski$^{1}$,
+Angie Waszewski$^{1,5}$,
 Dougal Dobie$^{3,4}$,
@@
 John Morgan$^{5}$,
+Kovi Rose$^{3,6}$,
 and Ziteng Wang$^{1}$
@@
 $^{5}$CSIRO Space and Astronomy, P.O. Box 1130, Bentley, WA 6102, Australia\\
+$^{6}$Australian Telescope National Facility CSIRO, P.O. Box 76, Epping, NSW 1710, Australia\\
 }
@@
 \begin{abstract}
-We report the discovery of several new pulses from the source \srcfull{} (\src{}), originally identified from a single 2-min log pulse, confirming it as a long period transient (LPT) with a period of ${\sim}1.16\,$hours.
+We report the discovery of several new pulses from the source \srcfull{} (\src{}), originally identified from a single 2-min long pulse, confirming it as a long period transient (LPT) with a period of ${\sim}1.16\,$hours.
 The pulses are significantly scattered, consistent with Galactic electron density models.
@@
 
-In this paper, we present new radio observations (spanning frequencies from $154\,$MHz to $1.7\,$GHz) in which \src{} was re-detected, confirming that it is indeed an LPT with a period of ${\sim}1.16\,$hours.
+In this paper, we present new radio observations (spanning frequencies from $154\,$MHz to $3.1\,$GHz) in which \src{} was re-detected, confirming that it is indeed an LPT with a period of ${\sim}1.16\,$hours.
 In \S\ref{sec:observations}, we describe the observations themselves, some of which were taken as part of independent surveys, and some of which were taken as dedicated follow-up of \src{} once it became apparent that it was still active.
@@
 Following its re-detection in the ASKAP data, follow-up observations were conducted at L/S band with the ATCA telescope under the project code C3363 (P.I: Tara Murphy).
-\src\ was observed once on October 4, 2024, for a total of 1.5\,hrs, and again on October 12, 2024, for a total of 2.4\,hrs.
+\src\ was observed once on 2024-10-04, for a total of 1.5\,hrs, and again on 2024-10-12, for a total of 2.4\,hrs.
 At the beginning of each observation, 1934$-$638 was used to calibrate the bandpass, and during the observations, 1748$-$253 was used as a phase calibrator.
@@
 
-We identified two faint pulses (4--5 $\sigma$; see Table~\ref{tbl:toas}) in the observation taken on October 4.
-However, observations taken on October 12 did not yield any pulses (at 3-$\sigma$ level).
+We identified two faint pulses (4--5 $\sigma$; see Table~\ref{tbl:toas}) in the observation taken on 2024-10-04.
+However, observations taken on 2024-10-12 did not yield any pulses (at 3-$\sigma$ level).
 We inspected the data around the expected time of arrival (using Equation~\ref{eqn:timing}) but did not find any pulses.
 The instantaneous noise level around the expected time of arrivals is close to 1\,mJy.
-If pulse-to-pulse flux density variations, similar to ones observed in MWA data (Table~\ref{tbl:toas}), also occur at L/S band, then even a factor 1.5--2 can be sufficient to explain the detection of pulse on October 4 and the absence of pulses on October 12, given that the source is faint at higher frequencies.
+If pulse-to-pulse flux density variations, similar to ones observed in MWA data (Table~\ref{tbl:toas}), also occur at L/S band, then even a factor 1.5--2 can be sufficient to explain the detection of pulse on 2024-10-04 and the absence of pulses on 2024-10-12, given that the source is faint at higher frequencies.
 
@@
 All observed pulses consist of a single burst, approximately Gaussian in shape, with the sole exception of the MeerKAT pulse observed on 2024-10-19, for which two bursts were observed separated by ${\sim}125\,$s.
-Generally, the low-frequency (MWA) pulses tend
+Generally, the low-frequency (MWA) pulses tend to
 \begin{itemize}
-    \item to be wider than their higher frequency counterparts,
-    \item to exhibit an asymmetry resembling a scatter-broadened tail, and
-    \item to have minimal pulse-to-pulse morphological variation.
+    \item be wider than their higher frequency counterparts,
+    \item exhibit an asymmetry resembling a scatter-broadened tail, and
+    \item have minimal pulse-to-pulse morphological variation.
 \end{itemize}
@@
     PEPOCH (MJD) & $59965.03792 \pm 0.00003$ \\
-    DM (pc/cm$^{-3}$) & $733 \pm 22$ \\
+    DM (pc cm$^{-3}$) & $733 \pm 22$ \\
     $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$ \\
@@
 The bottom panel of \Fig~\ref{fig:pulse_details} shows the peak flux densities scaled to 1\,GHz under this assumption, revealing a relatively slow change of the pulses' brightness, not unlike GLEAM-X\,J1627$-$5235 \citep{2022Natur.601..526H}.
-The in-band spectral index measurement of $-3.1$ reported for the 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, if consistent across the timespan of our observations, implies a turnover or spectral curvature at intermediate frequencies \citep[perhaps comparable with GPM\,1839$-$10][]{2023Natur.619..487H}.
+The in-band spectral index measurement of $\alpha=-3.1$ reported for the 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, if consistent across the timespan of our observations, implies a turnover or spectral curvature at intermediate frequencies \citep[perhaps comparable with GPM\,1839$-$10][]{2023Natur.619..487H}.
 
@@
 Each pulse was de-Faraday rotated with the weighted average RM given above, to derive the linear polarisation profile and the PA evolution across the pulses.
-For the 2023 ASKAP pulse, we recover the `S'-shaped PA curve discussed at length in \citetalias{2024MNRAS.535..909D} in the context of the RVM.
+For the 2023 ASKAP pulse, we recover the `S'-shaped PA curve discussed at length in \citetalias{2024MNRAS.535..909D} in the context of the rotating vector model (RVM).
 Contrastingly, the PA curve of the 2024 ASKAP pulse is flat (across five 10-second bins), and that of the 2024 MeerKAT pulse is curved, but not in an RVM-like way.
@@
 
-In contrast, the ATCA observation taken on 2025-10-12 did not yield any detections (out of four possible predicted ToAs that occurred during that observation).
+In contrast, the ATCA observation taken on 2024-10-12 did not yield any detections (out of four possible predicted ToAs that occurred during that observation).
 This is despite the fact that pulses were detected with ATCA just eight days prior with a similar instantaneous noise level (${\sim}1\,$mJy), as well as the fact that pulses were detected at the MWA within 24 hours of the ATCA observation (none of the MWA observations were coincident with the ATCA observation).
-However, even a modest amount of pulse-to-pulse variability would allow for the possibility that the pulses during the 2025-10-12 were present, but fell below the detection threshold of ATCA.
+However, even a modest amount of pulse-to-pulse variability would allow for the possibility that the pulses during the 2024-10-12 were present, but fell below the detection threshold of ATCA.
 
@@
 
-Another possibility is that radio emission is only observed when the MD produces dense enough particle outflows, in the form of winds, to activate the emission mechanism in the vicinity of the WD.
+Another possibility is that radio emission is only observed when the companion produces dense enough particle outflows, in the form of winds, to activate the emission mechanism in the vicinity of the WD.
 Such outflows can last for months \citep{2021ApJ...915...37W}, and would not be periodic.
+We also note that the intermittency and varying polarisation properties of \src{} (and other LPTs) may be explained by changes in the local plasma environment (Rose et al., in prep).
 If intermittency is of this kind, then the observed activity windows will be similarly aperiodic, or quasiperiodic.
@@
 The three higher-frequency pulses for which polarimetry was observable exhibited unique single-pulse polarisation behaviours.
-Only the original ASKAP detection exhibited a PA curve that was amenable to being modelled with the rotating vector model; the others show either flat, or slightly concave up PA curves (\Fig~\ref{fig:RM}).
+Only the original ASKAP detection exhibited a PA curve that was amenable to being modelled with the RVM; the others show either flat, or slightly concave up PA curves (\Fig~\ref{fig:RM}).
 
@@
 
+K.R. thanks the LSST-DA Data Science Fellowship Program, which is funded by LSST-DA, the Brinson Foundation, and the Moore Foundation; Their participation in the program has benefited this work.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2025-06-06 paper/main.tex
More tweaks to papers and figures

@@
 We interpret historical non-detections of \src{} as an intrinsic intermittency that occurs on month-long timescales, and discuss possible causes.
-We conjecture that, like other LPTs with periods $\gtrsim 1\,$hour, \src{} is a white-dwarf binary pulsar, but note that its period is marginally shorter than the minimum known orbital period for the class of cataclysmic variables known as polars.
+We conjecture that, like some other LPTs with periods $\gtrsim 1\,$hour, \src{} is a white-dwarf binary pulsar, but note that its period is marginally shorter than the minimum known orbital period for the class of cataclysmic variables known as polars.
 \end{abstract}
@@
 
-Following its re-detection in the ASKAP data, follow-up observations were conducted at L/S band with the ATCA telescope under the project code C3363 (P.I: Tara Murphy).
+Following its re-detection in the ASKAP data, follow-up observations were conducted at L/S bands with the ATCA telescope under the project code C3363 (P.I: Tara Murphy).
 \src\ was observed once on 2024-10-04, for a total of 1.5\,hrs, and again on 2024-10-12, for a total of 2.4\,hrs.
@@
 We inspected the data around the expected time of arrival (using Equation~\ref{eqn:timing}) but did not find any pulses.
-The instantaneous noise level around the expected time of arrivals is close to 1\,mJy.
-If pulse-to-pulse flux density variations, similar to ones observed in MWA data (Table~\ref{tbl:toas}), also occur at L/S band, then even a factor 1.5--2 can be sufficient to explain the detection of pulse on 2024-10-04 and the absence of pulses on 2024-10-12, given that the source is faint at higher frequencies.
+The instantaneous noise level, per 10\,s integration time bin, around the expected time of arrivals is close to 1\,mJy.
+If pulse-to-pulse flux density variations, similar to ones observed in MWA data (Table~\ref{tbl:toas}), also occur at L/S band, then even a factor 1.5--2 variation can be sufficient to explain the detection of pulses on 2024-10-04 and the absence of pulses on 2024-10-12, given that the source is faint at higher frequencies.
 

### 2025-06-06 dynspec/plot_lpt_comparison.py

@@ -8,14 +8,20 @@ point_types = {
     'Polars': {
         'color': 'r',
         'ecolor': 'r',
+        'fmt': 's',
+        'fillstyle': 'none',
     },
     'Unknown': {
         'color': 'k',
         'ecolor': 'k',
+        'fmt': 'x',
+        'fillstyle': 'none',
     },
     'AR Sco-like': {
         'color': 'b',
         'ecolor': 'b',
+        'fmt': 'o',
+        'fillstyle': 'full',
     },
 }
 
@@ -32,7 +38,6 @@ lpts = [
             'fontweight': 'bold',
         },
         'errorbar_kwargs': {
-            'fmt': 'none',
             'ls': 'none',
             'capsize': 2,
         },
@@ -48,7 +53,6 @@ lpts = [
             'va': 'center',
         },
         'errorbar_kwargs': {
-            'fmt': 'none',
             'ls': 'none',
             'capsize': 2,
         }
@@ -64,7 +68,6 @@ lpts = [
             'va': 'center',
         },
         'errorbar_kwargs': {
-            'fmt': 'none',
             'ls': 'none',
             'capsize': 2,
         },
@@ -81,7 +84,6 @@ lpts = [
             'va': 'center',
         },
         'errorbar_kwargs': {
-            'fmt': 'none',
             'ls': 'none',
             'capsize': 2,
         }
@@ -97,7 +99,6 @@ lpts = [
             'va': 'center',
         },
         'errorbar_kwargs': {
-            'fmt': 'none',
             'ls': 'none',
             'capsize': 2,
         }
@@ -113,7 +114,6 @@ lpts = [
             'va': 'center',
         },
         'errorbar_kwargs': {
-            'fmt': 'x',
             'ls': 'none',
             'capsize': 0,
         }
@@ -129,7 +129,6 @@ lpts = [
             'va': 'center',
         },
         'errorbar_kwargs': {
-            'fmt': 'none',
             'ls': 'none',
             'capsize': 2,
         }
@@ -145,7 +144,6 @@ lpts = [
             'va': 'center',
         },
         'errorbar_kwargs': {
-            'fmt': 'none',
             'ls': 'none',
             'capsize': 2,
         },
@@ -162,7 +160,6 @@ lpts = [
             'va': 'center',
         },
         'errorbar_kwargs': {
-            'fmt': 'none',
             'ls': 'none',
             'capsize': 2,
         }
[…]

### 2025-07-09 optical/plot_PanSTARRS.py
Optical image with MeerKAT position overlay finalised

@@ -86,7 +86,7 @@ interval = PercentileInterval(pct)
 
 stretch = AsinhStretch(a=0.8)
 
-framesize = 0.1*u.arcmin
+framesize = 0.3*u.arcmin
 
 w_red = wcs.WCS(red[1].header)
 w_green = wcs.WCS(green[1].header)
@@ -131,26 +131,13 @@ lat.set_axislabel("Declination (J2000)")
 #lat.set_major_formatter('dd:mm')
 
 # Transient source
-# ASKAP
-width = size * err_askap_a / framesize # in "fraction of the frame"
-height = size * err_askap_b / framesize # in "fraction of the frame"
-
-ell = Ellipse((coord_askap_orig.ra.value, coord_askap_orig.dec.value), 
-              width=width, height=height, angle=0,
-              edgecolor='green',
-              facecolor='none',
-              transform=ax.get_transform("world")
-              )
-#ax.add_patch(ell)
-
 # MeerKAT
 width = size * err_mkt_a / framesize # in "fraction of the frame"
 height = size * err_mkt_b / framesize # in "fraction of the frame"
 
 ell = Ellipse((coord_mkt.ra.value, coord_mkt.dec.value), 
-              #width=width, height=height, angle=0,
-              width=err_mkt_a.value, height=err_mkt_b.value, angle=0,
-              edgecolor='green',
+              width=2*err_mkt_a.value, height=2*err_mkt_b.value, angle=180-155.03435,
+              edgecolor='#0f0',
               facecolor='none',
               transform=ax.get_transform("world")
               )
@@ -196,6 +183,6 @@ ax.add_patch(ell)
 #ax.set_xlim(0,xmax)
 #ax.set_ylim(0,ymax)
 
-fig.savefig("J1755_optical.png", dpi=1000, bbox_inches="tight")
+fig.savefig("J1755_optical.pdf", dpi=1000, bbox_inches="tight")
 #fig.savefig("M81_SDSS.eps", dpi=1000)
 #fig.savefig("M81_SDSS.pdf")

### 2025-07-09 nir/plot_UKIDSS.py
Added NIR localisation image as well

@@ -1,0 +1,190 @@
+#!/usr/bin/env python
+
+__author__ = "Natasha Hurley-Walker"
+__date__ = "05/04/2025"
+
+import os
+import sys
+import shutil
+
+import matplotlib
+matplotlib.use('Agg') # So does not use display -- only good if just making plots
+from matplotlib import pyplot as plt
+from matplotlib.patches import Ellipse
+
+from matplotlib import rc
+rc('text', usetex=True)
+rc('font',**{'family':'serif','serif':['serif']})
+
+from astropy.io import fits
+from astropy import wcs
+from astropy import units as u
+from astropy.coordinates import SkyCoord, Angle
+from astropy.visualization.wcsaxes import SphericalCircle
+from astropy.nddata import Cutout2D
+
+import numpy as np
+
+# Didn't work
+#from astropy.visualization import make_lupton_rgb
+#rgb_default = make_lupton_rgb(red, green, blue, filename="temp.jpeg")
+
+from astropy.visualization import PercentileInterval
+from astropy.visualization import AsinhStretch
+
+def normalize(arr, vmin, vmax):
+    nor = (arr - vmin) / (vmax - vmin)
+    nor[np.where(nor<0.0)] = 0.0
+    nor[np.where(nor>1.0)] = 1.0
+    return nor
+
+#coords_old = SkyCoord("17:55:34.87 -25:27:49.1", frame="fk5", unit=(u.hourangle, u.deg))
+# Offset is about 3.5" North
+# Maybe 3" East
+#coords = coords_old.spherical_offsets_by(3*u.arcsec, 3.5*u.arcsec)
+# Highest S/N measurement -- but worst PSF
+#coords_m1= SkyCoord("07:15:07.37 -11:41:53.72", frame="fk5", unit=(u.hourangle, u.deg))
+# Lower S/N measurements -- with better PSF
+#coords_m2= SkyCoord("07:15:07.38 -11:41:53.59", frame="fk5", unit=(u.hourangle, u.deg))
+#coords_m3= SkyCoord("07:15:07.35 -11:41:53.81", frame="fk5", unit=(u.hourangle, u.deg))
+# Average of those two
+#coord_askap_orig= SkyCoord("07:15:07.365 -11:41:53.745", frame="fk5", unit=(u.hourangle, u.deg))
+# Unweighted average from three measurements
[…]

### 2025-07-10 paper/main.tex
Completed draft revision after getting first referee report back

@@
 
-\newcommand{\todo}[1]{{\color{red}#1}}
+% Using this for post-review corrections
+\newcommand{\revision}[2]{{\color{red}#2}}
+
 \newcommand{\src}{J1755$-$2527}
@@
 % Keep the title short and informative.
-\title[Confirmation of \src{} as LPT]{Confirmation of \srcfull{} as a long period radio transient}
+%\title[Confirmation of \src{} as LPT]{Confirmation of \srcfull{} as a long period radio transient}
+\title[1.16-hr pulses from \src{}]{\revision{Confirmation of \srcfull{} as a long period radio transient}{A new long period radio transient: Discovery of pulses repeating every 1.16 hours from \srcfull{}}}
 
@@
 We interpret historical non-detections of \src{} as an intrinsic intermittency that occurs on month-long timescales, and discuss possible causes.
-We conjecture that, like some other LPTs with periods $\gtrsim 1\,$hour, \src{} is a white-dwarf binary pulsar, but note that its period is marginally shorter than the minimum known orbital period for the class of cataclysmic variables known as polars.
+We conjecture that, like some other LPTs with periods $\gtrsim 1\,$hour, \src{} \revision{is a white-dwarf binary pulsar, but note that its period is marginally shorter than the minimum known orbital period for the class of cataclysmic variables known as polars}{may host a white dwarf in a binary orbit, but note that its period is marginally shorter than the canonical orbital period minimum of cataclysmic variables}.
+\revision{}{Our work
+highlights the importance of additional observations in establishing the nature of unusual radio-
+emitting objects.}
 \end{abstract}
@@
 Despite this, the authors concluded that \src{} was most likely a long period transient (LPT), a newly emerging class of radio source with periods ranging from minutes to hours \citep[see e.g.][]{2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C}.
+\revision{}{Without additional evidence, however, \src{}
+has heretofore not been classified as an LPT in current catalogs.}
 
-Although optical observations have provided compelling evidence that at least some LPTs are detached, possibly strongly magnetic, white dwarf (WD) binaries \citep{deRuiter2025,2024ApJ...976L..21H,2025A&A...695L...8R}, it remains unclear if this model can account for all known LPTs \citep[e.g.][]{2022ApJ...940...72R,Lee2025}.
+Although optical observations have provided compelling evidence that at least some LPTs are detached, possibly strongly magnetic, \revision{white dwarf (WD) binaries}{white dwarf / M-dwarf (WD + MD) binary systems} \citep{deRuiter2025,2024ApJ...976L..21H,2025A&A...695L...8R}, it remains unclear if this model can account for all known LPTs \citep[e.g.][]{2022ApJ...940...72R,Lee2025}.
 Optical follow-up is challenging for \src{}, which is situated very close to the Galactic plane ($b = -0\overset{\circ}{.}12$), at a distance of ${\sim}4.7\,$kpc \citepalias{2024MNRAS.535..909D}.
@@
 Pulses from \src{} were detected with the Murchison Widefield Array \citep[MWA;][]{Tingay2013}, the Australian SKA Pathfinder \citep[ASKAP;][]{2021PASA...38....9H}, MeerKAT \citep{2016mks..confE...1J}, and the Australia Telescope Compact Array \citep[ATCA;][]{cabb}, all radio interferometers capable of imaging.
-A summary of all the observations containing pulse detections included in this work is summarised in \Tab~\ref{tbl:obs}.
+A summary of all the observations containing pulse detections included in this work is \revision{summarised}{presented} in \Tab~\ref{tbl:obs}.
 In this section, we describe how each telescope was used to generate dynamic spectra of \src{}.
@@
 
-\src{} was detected blindly with the Murchison Widefield Array \citep[MWA;][]{Tingay2013} in observations taken between June--September 2024 under the `Galactic Plane Monitor', project code G0080.
+\src{} was detected \revision{blindly}{} with the Murchison Widefield Array \citep[MWA;][]{Tingay2013} in observations taken between June--September 2024 under the `Galactic Plane Monitor', project code G0080.
 The prime objective of the campaign was to search for long-period transients by scanning the Galactic plane over $285^\circ < l < 65^\circ$, $|b| < 15^\circ$ on a bi-weekly cadence at 185--215\,MHz \citep[see Methods of][]{2023Natur.619..487H}; a full description will be released by Hurley-Walker et al., in prep.
 We also observed over June--September 2022 but made no detections in these data, as reported in \citetalias{2024MNRAS.535..909D}.
+\revision{}{The root-mean-squared (RMS) noise level in these observations on the processed four-second timescale is $\sim$80\,mJy\,beam$^{-1}$ in this region.
+A time-based convolution filter employed to extract pulse-like signals, as described by Horv\'ath et al., submitted, yielded the first detection in this data set of a pulse whose peak flux density was 665\,mJy.}
 Subsequent to its redetection, we commenced a Director's Discretionary Time (DDT) campaign under project code D0042, to obtain further observations, adjusting the frequency from 200.32\,MHz to 184.96\,MHz for some of the observations to attempt to improve measurements of its DM.
@@
 With the re-detection of the source in the MWA data, and the calculation of an ephemeris (\Sect~\ref{sec:analysis}), we re-reduced the data in which we would predict that \src{} would appear.
-We made one further detection, in SBID~49153, at a relatively low significance ($\sim5\sigma$) compared to the blind detections.
+We made one further detection, in SBID~49153, at a relatively low significance ($\sim5\sigma$)\revision{ compared to the blind detections}.
 We followed a similar procedure as the above to generate dynamic spectra for each of the observations, using a minimum baseline length of 500\,m to suppress uncleaned Galactic diffuse emission.
@@
 We then averaged the visibilities, excluding all baselines shorter than 150\,m, to produce a dynamic spectrum of the source, shown in \Fig~\ref{fig:stacked_spectra}.
+\revision{}{We used the source-finding software \texttt{Aegean} \citep{2018PASA...35...11H} to obtain an updated position of 17:55:34.87(2) $-$25:27:49.9(4).
+As in \citetalias{2024MNRAS.535..909D}, we find no coincident sources in either optical or near infrared at the same location (see Appendix~\ref{app:localization}).}
 
@@
 The residuals are presented in \Fig~\ref{fig:pulse_details} and \Tab~\ref{tbl:toas}, along with other fitted properties of the pulses.
-We also tried fitting a timing model that included a spin-down parameter, and found that it was consistent with zero spin-down to within $1\sigma$, and so is not included in the ephemeris.
+\revision{We also tried fitting a timing model that included a spin-down parameter, and found that it was consistent with zero spin-down to within $1\sigma$, and so is not included in the ephemeris.}{We also tried fitting a timing model that included a spin-down/up parameter (fixing the DM to $733\,{\rm pc}\,{\rm cm}^{-3}$), and found that it was consistent with zero.
+However, owing to recent discovery that CHIME/ILT\,J1634+44 is spinning up \citep[$\dot{P} = (-9.03 \pm 0.11) \times 10^{-12}\,{\rm s}\,{\rm s}^{-1}$;][]{2025arXiv250705139D,2025arXiv250705078B}, we report the fitted period derivative value of $(-10 \pm 92) \times 10^{-12}\,{\rm s}\,{\rm s}^{-1}$ instead of only providing an upper limit for the spin-down.}
 
@@
     $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$ \\
+    \revision{}{Spindown rate (${\rm s}\,{\rm s}^{-1}$)} & \revision{}{$(-10 \pm 92) \times 10^{-12}$} \\
     \hline
@@
 
-\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are conjectured to be on the evolutionary path towards becoming polars (\Fig~\ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is such a system.
-Notably, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for confirmed polars \citep{schwope2025polarcatcatalogpolarslowaccretion}.
-This makes it an interesting test bed for the possibility that LPTs with different periods represent different stages of WD binary evolution, as they progress towards becoming polars.
+\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, \revision{which are conjectured to be on the evolutionary path towards becoming polars}{both WD + MD binary systems} (\Fig~\ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is such a system.
+Notably, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for \revision{confirmed}{} polars \citep{2009MNRAS.397.2170G,schwope2025polarcatcatalogpolarslowaccretion}.
+This makes it an interesting test bed for the possibility that LPTs with different periods represent different stages of \revision{WD binary evolution, as they progress towards becoming polars}{WD + MD binary evolution}.
 \begin{figure*}
@@
 
-Although there is as yet no clear consensus on whether LPTs represent one class or multiple classes of system \citep[e.g.][]{2024ApJ...961..214R}, the recent confirmation of J1912$-$4410 as a pre-evolved white dwarf pulsar \citep{2023NatAs...7..931P} and ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 as likely candidates for polars or polar-like systems \citep{deRuiter2025,2025A&A...695L...8R} raise the intriguing possibility that other LPTs may also be radio-emitting white dwarf pulsars at various stages of evolution (\citealt{2021NatAs...5..648S}, Horv\'{a}th et al.
+\revision{Although there}{There} is as yet no clear consensus on whether LPTs represent one class or multiple classes of system \citep[e.g.][]{2024ApJ...961..214R}\revision{}{.
+However}, the recent confirmation of \revision{J1912$-$4410 as a pre-evolved white dwarf pulsar \citep{2023NatAs...7..931P}}{AR\,Scorpii \citep{2016Natur.537..374M}, J1912$-$4410 \citep{2023NatAs...7..931P}, and SDSS\,J230641.47+244055.8 \citep{2025arXiv250620455C} as white dwarf pulsars} and ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 as \revision{likely candidates for polars or polar-like systems}{WD + MD systems} \citep{deRuiter2025,2025A&A...695L...8R}\revision{}{, and CHIME/ILT J1634+44 as a binary hosting a white dwarf \citep[possibly two,][]{2025arXiv250705139D,2025arXiv250705078B}} raise the intriguing possibility that other LPTs may also be radio-emitting white dwarf pulsars at various stages of evolution (\citealt{2021NatAs...5..648S}, Horv\'{a}th et al.
 submitted).
@@
 
-Interestingly, systems with spin-orbital (or beat-orbital) resonances of, e.g., 2:1 or 3:1, would be indistinguishable from systems in 1:1 resonances if pulses can be observed within a limited orbital phase range.
-We therefore raise the possibility that the coincidence of the observed radio periodicities of ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 with their spectroscopically confirmed orbital periods does not necessarily imply that they are 1:1 polars.
+Interestingly, systems with spin-orbital (or beat-orbital) resonances of, e.g., 2:1 or 3:1, would be indistinguishable from systems in 1:1 resonances if pulses can \revision{}{only} be observed within a limited orbital phase range.
+We therefore raise the possibility that the coincidence of the observed radio periodicities of ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 with their spectroscopically confirmed orbital periods does not necessarily imply that they are 1:1 \revision{polars}{systems}.
 
@@
 Another possibility is that radio emission is only observed when the companion produces dense enough particle outflows, in the form of winds, to activate the emission mechanism in the vicinity of the WD.
+\revision{}{This may be the case, for example, for GLEAM-X\,J0704$-$37, whose spectroscopically detected H$\alpha$ emission is associated with the M-dwarf, and which may come from its stellar wind \citep{2025A&A...695L...8R}.}
 Such outflows can last for months \citep{2021ApJ...915...37W}, and would not be periodic.
@@
 
-The raw visibilities for the MWA, ASKAP, and MeerKAT data sets are available via the respective telescopes' data portals.
-The ATCA data is available on reasonable request to the authors, and will become publicly available from the relevant data portal by November, 2025.
+The raw visibilities for the MWA\footnote{\url{https://asvo.mwatelescope.org/}}, ASKAP\footnote{\url{https://research.csiro.au/casda/}}, and MeerKAT\footnote{\url{https://archive.sarao.ac.za/}} data sets are available via the respective telescopes' data portals.
+The ATCA\footnote{\url{https://atoa.atnf.csiro.au/}} data is available on reasonable request to the authors, and will become publicly available from the relevant data portal by November, 2025.
 The post-imaged dynamic spectra, analyses, and timing analysis data products (ToAs, pulse properties) are publicly available on GitHub\footnote{TODO: Make this available upon publication.}.
@@
 \appendix
+
+\section{\revision{}{MeerKAT localization}}
+\label{app:localization}
+
+\Fig~\ref{fig:localization} shows the position derived from the MeerKAT detection on MJD 60602.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.48\linewidth]{J1755_optical.pdf}
+    \includegraphics[width=0.48\linewidth]{J1755_nir.pdf}
+    \caption{The $1\sigma$ positional uncertainty of \src{} derived from the MeerKAT observation taken on MJD 60602 is shown as the green ellipses overlaid on the optical (z, i, r) Panoramic Survey Telescope and Rapid Response System (PanSTARRS) image (left panel), and the infrared (K, H, J) United Kingdom Infrared Telescope Deep Sky Survey (UKIDSS) image (right panel).}
+    \label{fig:localization}
+\end{figure*}
 

### 2025-07-10 dynspec/plot_lpt_comparison.py

@@ -5,7 +5,7 @@ from matplotlib.legend_handler import HandlerTuple
 import astropy.units as u
 
 point_types = {
-    'WD+MD LPTs': {
+    'Binaries hosting WDs': {
         'color': 'r',
         'ecolor': 'r',
         'fmt': 's',
@@ -120,10 +120,25 @@ lpts = [
     },
     {
         'name': 'GLEAM-X J0704-37',
-        'type': 'WD+MD LPTs',
+        'type': 'Binaries hosting WDs',
         'min_width': 30 * u.s,
         'max_width': 80 * u.s,
         'period': 10496.6 * u.s,
+        'text_kwargs': {
+            'ha': 'left',
+            'va': 'center',
+        },
+        'errorbar_kwargs': {
+            'ls': 'none',
+            'capsize': 2,
+        }
+    },
+    {
+        'name': 'CHIME/ILT J1634+44',
+        'type': 'Binaries hosting WDs',
+        'min_width': 0.07 * u.s,
+        'max_width': 0.8 * u.s,
+        'period': 841.245895 * u.s,
         'text_kwargs': {
             'ha': 'left',
             'va': 'center',
@@ -166,7 +181,7 @@ lpts = [
     },
     {
         'name': 'ILT J1101+5521',
-        'type': 'WD+MD LPTs',
+        'type': 'Binaries hosting WDs',
         'min_width': 30 * u.s,
         'max_width': 90 * u.s,
         'period': 7531.17 * u.s,
@@ -244,7 +259,7 @@ for point_type, kwargs in point_types.items():
         color=kwargs['color'],
         marker=kwargs['fmt'],
         fillstyle=kwargs['fillstyle'],
-        #linestyle=('--' if point_type == 'WD+MD LPTs' else '-'),
+        #linestyle=('--' if point_type == 'Binaries hosting WDs' else '-'),
         label=point_type,
     ))
 plt.legend(handles=custom_lines, loc='lower right')

### 2025-07-10 nir/plot_UKIDSS.py

@@ -86,7 +86,7 @@ interval = PercentileInterval(pct)
 
 stretch = AsinhStretch(a=0.1)
 
-framesize = 0.3*u.arcmin
+framesize = 1.3*u.arcmin
 
 w_red = wcs.WCS(red[1].header)
 w_green = wcs.WCS(green[1].header)
@@ -185,6 +185,6 @@ ax.invert_yaxis()
 #ax.set_xlim(0,xmax)
 #ax.set_ylim(0,ymax)
 
-fig.savefig("J1755_nir.pdf", dpi=1000, bbox_inches="tight")
+fig.savefig("J1755_nir.png", dpi=1000, bbox_inches="tight")
 #fig.savefig("M81_SDSS.eps", dpi=1000)
 #fig.savefig("M81_SDSS.pdf")

### 2025-07-10 paper/main.tex
More tweaks to the paper courtesy of Natasha

@@
 
-\src{} was detected \revision{blindly}{} with the Murchison Widefield Array \citep[MWA;][]{Tingay2013} in observations taken between June--September 2024 under the `Galactic Plane Monitor', project code G0080.
+\revision{\src{} was detected blindly with the Murchison Widefield Array \citep[MWA;][]{Tingay2013} in observations taken between June--September 2024 under the `Galactic Plane Monitor', project code G0080.
 The prime objective of the campaign was to search for long-period transients by scanning the Galactic plane over $285^\circ < l < 65^\circ$, $|b| < 15^\circ$ on a bi-weekly cadence at 185--215\,MHz \citep[see Methods of][]{2023Natur.619..487H}; a full description will be released by Hurley-Walker et al., in prep.
-We also observed over June--September 2022 but made no detections in these data, as reported in \citetalias{2024MNRAS.535..909D}.
-\revision{}{The root-mean-squared (RMS) noise level in these observations on the processed four-second timescale is $\sim$80\,mJy\,beam$^{-1}$ in this region.
-A time-based convolution filter employed to extract pulse-like signals, as described by Horv\'ath et al., submitted, yielded the first detection in this data set of a pulse whose peak flux density was 665\,mJy.}
+We also observed over June--September 2022 but made no detections in these data, as reported in \citetalias{2024MNRAS.535..909D}.}{The MWA, in its Phase~\textsc{ii} ``extended'' configuration \citep[][]{2018PASA...35...33W}, was used to scan the Galactic plane for transient radio sources under the `Galactic Plane Monitor', project code G0080.
+These observations were conducted over June--September\,2022, and June\,2024--March\,2025.
+Relevant to this work, the region $285^\circ < l < 65^\circ$, $|b| < 15^\circ$ was scanned on a bi-weekly cadence at 185--215\,MHz in both June--September\,2022 and 2024 \citep[see Methods of][a full description will be released by Hurley-Walker et al., in prep]{2023Natur.619..487H}.
+In this region, the root-mean-squared (RMS) noise level on the processed four-second timescale is $\sim$80\,mJy\,beam$^{-1}$.
+Amongst several detection methods (described in full by Horv\'ath et al., submitted, a convolution filter is employed to extract pulse-like signals.
+In June--September 2022, no pulses from \src{} were detected, but in June 2024, the source was blindly detected as a ${\sim}70$-s-wide pulse whose peak flux density was 665\,mJy.}
+
 Subsequent to its redetection, we commenced a Director's Discretionary Time (DDT) campaign under project code D0042, to obtain further observations, adjusting the frequency from 200.32\,MHz to 184.96\,MHz for some of the observations to attempt to improve measurements of its DM.
@@
 We inspected the data around the expected time of arrival (using Equation~\ref{eqn:timing}) but did not find any pulses.
-The instantaneous noise level, per 10\,s integration time bin, around the expected time of arrivals is close to 1\,mJy.
+The instantaneous noise level, per 10\,s integration time bin, around the expected time of arrivals is close to 1\,mJy\,beam$^{-1}$.
 If pulse-to-pulse flux density variations, similar to ones observed in MWA data (Table~\ref{tbl:toas}), also occur at L/S band, then even a factor 1.5--2 variation can be sufficient to explain the detection of pulses on 2024-10-04 and the absence of pulses on 2024-10-12, given that the source is faint at higher frequencies.
@@
 For the MeerKAT pulse with two components, we fit only the brighter component.
+\revision{}{We checked the higher time resolution PTUSE data for finer substructure, but did not find anything smaller than the components that can be seen in \Fig~\ref{fig:pulsestack}.}
 
@@
 \revision{We also tried fitting a timing model that included a spin-down parameter, and found that it was consistent with zero spin-down to within $1\sigma$, and so is not included in the ephemeris.}{We also tried fitting a timing model that included a spin-down/up parameter (fixing the DM to $733\,{\rm pc}\,{\rm cm}^{-3}$), and found that it was consistent with zero.
-However, owing to recent discovery that CHIME/ILT\,J1634+44 is spinning up \citep[$\dot{P} = (-9.03 \pm 0.11) \times 10^{-12}\,{\rm s}\,{\rm s}^{-1}$;][]{2025arXiv250705139D,2025arXiv250705078B}, we report the fitted period derivative value of $(-10 \pm 92) \times 10^{-12}\,{\rm s}\,{\rm s}^{-1}$ instead of only providing an upper limit for the spin-down.}
+However, owing to the recent discovery that the LPT CHIME/ILT\,J1634+44 is spinning up \citep[$\dot{P} = (-9.03 \pm 0.11) \times 10^{-12}\,{\rm s}\,{\rm s}^{-1}$;][]{2025arXiv250705139D,2025arXiv250705078B}, we report the fitted period derivative value of $(-10 \pm 92) \times 10^{-12}\,{\rm s}\,{\rm s}^{-1}$ instead of only providing an upper limit for the spin-down.}
 
@@
 The bottom panel of \Fig~\ref{fig:pulse_details} shows the peak flux densities scaled to 1\,GHz under this assumption, revealing a relatively slow change of the pulses' brightness, not unlike GLEAM-X\,J1627$-$5235 \citep{2022Natur.601..526H}.
-The in-band spectral index measurement of $\alpha=-3.1$ reported for the 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, if consistent across the timespan of our observations, implies a turnover or spectral curvature at intermediate frequencies \citep[perhaps comparable with GPM\,1839$-$10][]{2023Natur.619..487H}.
+The in-band spectral index measurement of $\alpha=-3.1$ reported for the 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, if consistent across the timespan of our observations, implies a turnover or spectral curvature at intermediate frequencies \citep[perhaps comparable with GPM\,1839$-$10;][]{2023Natur.619..487H}.
 
@@
 The same explanation may be applied to other LPTs with activity cycles that last on the order of months.
-An alternative explanation is that the radio emission is drived by particle wind outflows from the main sequence companion.
+An alternative explanation is that the radio emission is drived by particle wind outflows from \revision{the}{a} main sequence companion.
 Long-term monitoring of LPTs will reveal whether the intermittency is periodic, and thus help discriminate between these two scenarios.
@@
 \section*{Acknowledgements}
+
+This research is supported by an Australian Government Research Training Program (RTP) Scholarship.
 
@@
 The system design and integration was led by Swinburne University of Technology and Auckland University of Technology in collaboration with SARAO and supported by the ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav) under grant CE170100004.
+
+% ADACS
+The database of MWA candidates, and the webapp designed to facilitate manually inspecting them, were developed by Astronomy Data and Computing Services (ADACS) as part of its software support scheme.
 
@@
     \includegraphics[width=0.48\linewidth]{J1755_nir.pdf}
-    \caption{The $1\sigma$ positional uncertainty of \src{} derived from the MeerKAT observation taken on MJD 60602 is shown as the green ellipses overlaid on the optical (z, i, r) Panoramic Survey Telescope and Rapid Response System (PanSTARRS) image (left panel), and the infrared (K, H, J) United Kingdom Infrared Telescope Deep Sky Survey (UKIDSS) image (right panel).}
+    \caption{The $1\sigma$ positional uncertainty of \src{} derived from the MeerKAT observation taken on MJD 60602 is shown as the green ellipses overlaid on the optical (z, i, r) Panoramic Survey Telescope and Rapid Response System \citep[PanSTARRS;][]{2010SPIE.7733E..0EK,2016arXiv161205560C} image (left panel), and the infrared (K, H, J) United Kingdom Infrared Telescope Deep Sky Survey \citep[UKIDSS;][]{2007MNRAS.379.1599L} image (right panel).}
     \label{fig:localization}

### 2025-07-14 nir/plot_UKIDSS.py
Added labels to optical/NIR images, and changed RGB balance on NIR image

@@ -81,12 +81,13 @@ green = fits.open(fits_green)
 blue = fits.open(fits_blue)
 
 # Percentile interval for image normalisation
-pct = 99.999
-interval = PercentileInterval(pct)
+red_interval = PercentileInterval(99.5)
+green_interval = PercentileInterval(99.7)
+blue_interval = PercentileInterval(99.999)
 
 stretch = AsinhStretch(a=0.1)
 
-framesize = 1.3*u.arcmin
+framesize = 0.3*u.arcmin
 
 w_red = wcs.WCS(red[1].header)
 w_green = wcs.WCS(green[1].header)
@@ -96,11 +97,11 @@ red_data = Cutout2D(red[1].data, coord_mkt, framesize, wcs = w_red)
 green_data = Cutout2D(green[1].data, coord_mkt, framesize, wcs = w_green)
 blue_data = Cutout2D(blue[1].data, coord_mkt, framesize, wcs = w_blue)
 
-i = interval.get_limits(red_data.data)
+i = red_interval.get_limits(red_data.data)
 r = stretch(normalize(red_data.data, *i))
-i = interval.get_limits(green_data.data)
+i = green_interval.get_limits(green_data.data)
 g = stretch(normalize(green_data.data, *i))
-i = interval.get_limits(blue_data.data)
+i = blue_interval.get_limits(blue_data.data)
 b = stretch(normalize(blue_data.data, *i))
 
 rgb = np.dstack([r,g,b])
@@ -185,6 +186,8 @@ ax.invert_yaxis()
 #ax.set_xlim(0,xmax)
 #ax.set_ylim(0,ymax)
 
-fig.savefig("J1755_nir.png", dpi=1000, bbox_inches="tight")
+ax.text(5, 7.2, 'UKIDSS (J, H, K)', bbox={'facecolor': 'white', 'pad': 10, 'alpha': 0.7})
+
+fig.savefig("J1755_nir.pdf", dpi=1000, bbox_inches="tight")
 #fig.savefig("M81_SDSS.eps", dpi=1000)
 #fig.savefig("M81_SDSS.pdf")

### 2025-07-14 optical/plot_PanSTARRS.py

@@ -183,6 +183,8 @@ ax.add_patch(ell)
 #ax.set_xlim(0,xmax)
 #ax.set_ylim(0,ymax)
 
+ax.text(4, 65.3, 'PanSTARRS (r, i, z)', bbox={'facecolor': 'white', 'pad': 10, 'alpha': 0.7})
+
 fig.savefig("J1755_optical.pdf", dpi=1000, bbox_inches="tight")
 #fig.savefig("M81_SDSS.eps", dpi=1000)
 #fig.savefig("M81_SDSS.pdf")

### 2025-07-14 paper/main.tex
Final changes before resubmitting

@@
 %\title[Confirmation of \src{} as LPT]{Confirmation of \srcfull{} as a long period radio transient}
-\title[1.16-hr pulses from \src{}]{\revision{Confirmation of \srcfull{} as a long period radio transient}{A new long period radio transient: Discovery of pulses repeating every 1.16 hours from \srcfull{}}}
+\title[1.16-hr-repeating pulses from \src{}]{\revision{Confirmation of \srcfull{} as a long period radio transient}{A new long period radio transient: Discovery of pulses repeating every 1.16 hours from \srcfull{}}}
 
@@
 \revision{}{Our work
-highlights the importance of additional observations in establishing the nature of unusual radio-
-emitting objects.}
+highlights the importance of additional observations in establishing the nature of unusual radio-emitting objects.}
 \end{abstract}
@@
 
-\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, \revision{which are conjectured to be on the evolutionary path towards becoming polars}{both WD + MD binary systems} (\Fig~\ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is such a system.
+\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, \revision{which are conjectured to be on the evolutionary path towards becoming polars}{both WD + MD binary systems} (\Fig~\ref{fig:lpt_comparison}), suggesting the possibility that \src{} is also such a system.
 Notably, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for \revision{confirmed}{} polars \citep{2009MNRAS.397.2170G,schwope2025polarcatcatalogpolarslowaccretion}.
@@
     \includegraphics[width=0.48\linewidth]{J1755_nir.pdf}
-    \caption{The $1\sigma$ positional uncertainty of \src{} derived from the MeerKAT observation taken on MJD 60602 is shown as the green ellipses overlaid on the optical (z, i, r) Panoramic Survey Telescope and Rapid Response System \citep[PanSTARRS;][]{2010SPIE.7733E..0EK,2016arXiv161205560C} image (left panel), and the infrared (K, H, J) United Kingdom Infrared Telescope Deep Sky Survey \citep[UKIDSS;][]{2007MNRAS.379.1599L} image (right panel).}
+    \caption{The $1\sigma$ positional uncertainty of \src{} derived from the MeerKAT observation taken on MJD 60602 is shown as the green ellipses overlaid on the optical (r, i, z) Panoramic Survey Telescope and Rapid Response System \citep[PanSTARRS;][]{2010SPIE.7733E..0EK,2016arXiv161205560C} image (left panel), and the infrared (J, H, K) United Kingdom Infrared Telescope Deep Sky Survey \citep[UKIDSS;][]{2007MNRAS.379.1599L} image (right panel).}
     \label{fig:localization}

### 2025-07-15 paper/main.tex
Deleted now-redundant footnote

@@
 We performed a similar processing of the data, and identified four pulses with ToAs consistent with an ephemeris derived from the other data.
-The folded and stacked dynamic spectra are shown in \Fig~\ref{fig:stacked_spectra}\footnote{The signal-to-noise of the MeerKAT detections was insufficient to improve on the localisation derived in \citetalias{2024MNRAS.535..909D}.}.
+The folded and stacked dynamic spectra are shown in \Fig~\ref{fig:stacked_spectra}.
+%\footnote{The signal-to-noise of the MeerKAT detections was insufficient to improve on the localisation derived in \citetalias{2024MNRAS.535..909D}.}
 

### 2025-07-19 paper/main.tex
Removed revision formatting, and also a couple of tiny tweaks here and there.

@@
 
-% Using this for post-review corrections
-\newcommand{\revision}[2]{{\color{red}#2}}
-
 \newcommand{\src}{J1755$-$2527}
@@
 %\title[Confirmation of \src{} as LPT]{Confirmation of \srcfull{} as a long period radio transient}
-\title[1.16-hr-repeating pulses from \src{}]{\revision{Confirmation of \srcfull{} as a long period radio transient}{A new long period radio transient: Discovery of pulses repeating every 1.16 hours from \srcfull{}}}
+\title[1.16-hr-repeating pulses from \src{}]{A new long period radio transient: Discovery of pulses repeating every 1.16 hours from \srcfull{}}
 
@@
 We interpret historical non-detections of \src{} as an intrinsic intermittency that occurs on month-long timescales, and discuss possible causes.
-We conjecture that, like some other LPTs with periods $\gtrsim 1\,$hour, \src{} \revision{is a white-dwarf binary pulsar, but note that its period is marginally shorter than the minimum known orbital period for the class of cataclysmic variables known as polars}{may host a white dwarf in a binary orbit, but note that its period is marginally shorter than the canonical orbital period minimum of cataclysmic variables}.
-\revision{}{Our work
-highlights the importance of additional observations in establishing the nature of unusual radio-emitting objects.}
+We conjecture that, like some other LPTs with periods $\gtrsim 1\,$hour, \src{} may host a white dwarf in a binary orbit, but note that its period is marginally shorter than the canonical orbital period minimum of cataclysmic variables.
+Our work highlights the importance of additional observations in establishing the nature of unusual radio-emitting objects.
 \end{abstract}
@@
 
-\srcfull{} (hereafter, \src{}) is a transient radio source discovered \citep[][hereafter \citetalias{2024MNRAS.535..909D}]{2024MNRAS.535..909D} in the Variables and Slow Transients (VAST) survey \citep{2013PASA...30....6M}.
+\srcfull{} (hereafter, \src{}) is a transient radio source \citep[][hereafter \citetalias{2024MNRAS.535..909D}]{2024MNRAS.535..909D} discovered in the Variables and Slow Transients (VAST) survey \citep{2013PASA...30....6M}.
 A single, highly polarised pulse was observed, lasting approximately 2 minutes, exhibiting a steep spectrum ($\alpha = -3.1$, for flux density $S_\nu\propto\nu^\alpha$).
@@
 Despite this, the authors concluded that \src{} was most likely a long period transient (LPT), a newly emerging class of radio source with periods ranging from minutes to hours \citep[see e.g.][]{2022Natur.601..526H,2023Natur.619..487H,2024NatAs...8.1159C}.
-\revision{}{Without additional evidence, however, \src{}
-has heretofore not been classified as an LPT in current catalogs.}
+Without additional evidence, however, \src{} has heretofore not been classified as an LPT in current catalogs.
 
-Although optical observations have provided compelling evidence that at least some LPTs are detached, possibly strongly magnetic, \revision{white dwarf (WD) binaries}{white dwarf / M-dwarf (WD + MD) binary systems} \citep{deRuiter2025,2024ApJ...976L..21H,2025A&A...695L...8R}, it remains unclear if this model can account for all known LPTs \citep[e.g.][]{2022ApJ...940...72R,Lee2025}.
+Although optical observations have provided compelling evidence that at least some LPTs are detached, possibly strongly magnetic, white dwarf / M-dwarf (WD + MD) binary systems \citep{deRuiter2025,2024ApJ...976L..21H,2025A&A...695L...8R}, it remains unclear if this model can account for all known LPTs \citep[e.g.][]{2022ApJ...940...72R,Lee2025}.
 Optical follow-up is challenging for \src{}, which is situated very close to the Galactic plane ($b = -0\overset{\circ}{.}12$), at a distance of ${\sim}4.7\,$kpc \citepalias{2024MNRAS.535..909D}.
@@
 Pulses from \src{} were detected with the Murchison Widefield Array \citep[MWA;][]{Tingay2013}, the Australian SKA Pathfinder \citep[ASKAP;][]{2021PASA...38....9H}, MeerKAT \citep{2016mks..confE...1J}, and the Australia Telescope Compact Array \citep[ATCA;][]{cabb}, all radio interferometers capable of imaging.
-A summary of all the observations containing pulse detections included in this work is \revision{summarised}{presented} in \Tab~\ref{tbl:obs}.
+A summary of all the observations containing pulse detections included in this work is presented in \Tab~\ref{tbl:obs}.
 In this section, we describe how each telescope was used to generate dynamic spectra of \src{}.
@@
 
-\revision{\src{} was detected blindly with the Murchison Widefield Array \citep[MWA;][]{Tingay2013} in observations taken between June--September 2024 under the `Galactic Plane Monitor', project code G0080.
-The prime objective of the campaign was to search for long-period transients by scanning the Galactic plane over $285^\circ < l < 65^\circ$, $|b| < 15^\circ$ on a bi-weekly cadence at 185--215\,MHz \citep[see Methods of][]{2023Natur.619..487H}; a full description will be released by Hurley-Walker et al., in prep.
-We also observed over June--September 2022 but made no detections in these data, as reported in \citetalias{2024MNRAS.535..909D}.}{The MWA, in its Phase~\textsc{ii} ``extended'' configuration \citep[][]{2018PASA...35...33W}, was used to scan the Galactic plane for transient radio sources under the `Galactic Plane Monitor', project code G0080.
+The MWA, in its Phase~\textsc{ii} ``extended'' configuration \citep[][]{2018PASA...35...33W}, was used to scan the Galactic plane for transient radio sources under the `Galactic Plane Monitor', project code G0080.
 These observations were conducted over June--September\,2022, and June\,2024--March\,2025.
@@
 Amongst several detection methods (described in full by Horv\'ath et al., submitted, a convolution filter is employed to extract pulse-like signals.
-In June--September 2022, no pulses from \src{} were detected, but in June 2024, the source was blindly detected as a ${\sim}70$-s-wide pulse whose peak flux density was 665\,mJy.}
+In June--September 2022, no pulses from \src{} were detected, but in June 2024, the source was blindly detected as a ${\sim}70$-s-wide pulse whose peak flux density was 665\,mJy.
 
@@
 With the re-detection of the source in the MWA data, and the calculation of an ephemeris (\Sect~\ref{sec:analysis}), we re-reduced the data in which we would predict that \src{} would appear.
-We made one further detection, in SBID~49153, at a relatively low significance ($\sim5\sigma$)\revision{ compared to the blind detections}.
+We made one further detection, in SBID~49153, at a relatively low significance ($\sim5\sigma$).
 We followed a similar procedure as the above to generate dynamic spectra for each of the observations, using a minimum baseline length of 500\,m to suppress uncleaned Galactic diffuse emission.
@@
 We then averaged the visibilities, excluding all baselines shorter than 150\,m, to produce a dynamic spectrum of the source, shown in \Fig~\ref{fig:stacked_spectra}.
-\revision{}{We used the source-finding software \texttt{Aegean} \citep{2018PASA...35...11H} to obtain an updated position of 17:55:34.87(2) $-$25:27:49.9(4).
-As in \citetalias{2024MNRAS.535..909D}, we find no coincident sources in either optical or near infrared at the same location (see Appendix~\ref{app:localization}).}
+We used the source-finding software \texttt{Aegean} \citep{2018PASA...35...11H} to obtain an updated position of 17:55:34.87(2) $-$25:27:49.9(4).
+As in \citetalias{2024MNRAS.535..909D}, we find no coincident sources in either optical or near infrared at the same location (see Appendix~\ref{app:localization}).
 
@@
 The folded and stacked dynamic spectra are shown in \Fig~\ref{fig:stacked_spectra}.
-%\footnote{The signal-to-noise of the MeerKAT detections was insufficient to improve on the localisation derived in \citetalias{2024MNRAS.535..909D}.}
 
@@
 For the MeerKAT pulse with two components, we fit only the brighter component.
-\revision{}{We checked the higher time resolution PTUSE data for finer substructure, but did not find anything smaller than the components that can be seen in \Fig~\ref{fig:pulsestack}.}
+We checked the higher time resolution PTUSE data for finer substructure, but did not find anything smaller than the components that can be seen in \Fig~\ref{fig:pulsestack}.
 
@@
 The residuals are presented in \Fig~\ref{fig:pulse_details} and \Tab~\ref{tbl:toas}, along with other fitted properties of the pulses.
-\revision{We also tried fitting a timing model that included a spin-down parameter, and found that it was consistent with zero spin-down to within $1\sigma$, and so is not included in the ephemeris.}{We also tried fitting a timing model that included a spin-down/up parameter (fixing the DM to $733\,{\rm pc}\,{\rm cm}^{-3}$), and found that it was consistent with zero.
-However, owing to the recent discovery that the LPT CHIME/ILT\,J1634+44 is spinning up \citep[$\dot{P} = (-9.03 \pm 0.11) \times 10^{-12}\,{\rm s}\,{\rm s}^{-1}$;][]{2025arXiv250705139D,2025arXiv250705078B}, we report the fitted period derivative value of $(-10 \pm 92) \times 10^{-12}\,{\rm s}\,{\rm s}^{-1}$ instead of only providing an upper limit for the spin-down.}
+We also tried fitting a timing model that included a spin-down/up parameter (fixing the DM to $733\,{\rm pc}\,{\rm cm}^{-3}$), and found that it was consistent with zero.
+However, owing to the recent discovery that the LPT CHIME/ILT\,J1634+44 is spinning up \citep[$\dot{P} = (-9.03 \pm 0.11) \times 10^{-12}\,{\rm s}\,{\rm s}^{-1}$;][]{2025arXiv250705139D,2025arXiv250705078B}, we report the fitted period derivative value of $(-10 \pm 92) \times 10^{-12}\,{\rm s}\,{\rm s}^{-1}$ instead of only providing an upper limit for the spin-down.
 
@@
     $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$ \\
-    \revision{}{Spindown rate (${\rm s}\,{\rm s}^{-1}$)} & \revision{}{$(-10 \pm 92) \times 10^{-12}$} \\
+    Spindown rate (${\rm s}\,{\rm s}^{-1}$) & $(-10 \pm 92) \times 10^{-12}$ \\
     \hline
@@
 
-\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, \revision{which are conjectured to be on the evolutionary path towards becoming polars}{both WD + MD binary systems} (\Fig~\ref{fig:lpt_comparison}), suggesting the possibility that \src{} is also such a system.
-Notably, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for \revision{confirmed}{} polars \citep{2009MNRAS.397.2170G,schwope2025polarcatcatalogpolarslowaccretion}.
-This makes it an interesting test bed for the possibility that LPTs with different periods represent different stages of \revision{WD binary evolution, as they progress towards becoming polars}{WD + MD binary evolution}.
+\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, both thought to be WD + MD binary systems (\Fig~\ref{fig:lpt_comparison}), suggesting the possibility that \src{} is also such a system.
+Notably, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for polars \citep{2009MNRAS.397.2170G,schwope2025polarcatcatalogpolarslowaccretion}.
+This makes it an interesting test bed for the possibility that LPTs with different periods represent different stages of WD + MD binary evolution.
 \begin{figure*}
@@
 
-\revision{Although there}{There} is as yet no clear consensus on whether LPTs represent one class or multiple classes of system \citep[e.g.][]{2024ApJ...961..214R}\revision{}{.
-However}, the recent confirmation of \revision{J1912$-$4410 as a pre-evolved white dwarf pulsar \citep{2023NatAs...7..931P}}{AR\,Scorpii \citep{2016Natur.537..374M}, J1912$-$4410 \citep{2023NatAs...7..931P}, and SDSS\,J230641.47+244055.8 \citep{2025arXiv250620455C} as white dwarf pulsars} and ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 as \revision{likely candidates for polars or polar-like systems}{WD + MD systems} \citep{deRuiter2025,2025A&A...695L...8R}\revision{}{, and CHIME/ILT J1634+44 as a binary hosting a white dwarf \citep[possibly two,][]{2025arXiv250705139D,2025arXiv250705078B}} raise the intriguing possibility that other LPTs may also be radio-emitting white dwarf pulsars at various stages of evolution (\citealt{2021NatAs...5..648S}, Horv\'{a}th et al.
+There is as yet no clear consensus on whether LPTs represent one class or multiple classes of system \citep[e.g.][]{2024ApJ...961..214R}.
+However, the recent confirmation of AR\,Scorpii \citep{2016Natur.537..374M}, J1912$-$4410 \citep{2023NatAs...7..931P}, and SDSS\,J230641.47+244055.8 \citep{2025arXiv250620455C} as white dwarf pulsars and ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 as WD + MD systems \citep{deRuiter2025,2025A&A...695L...8R}, and CHIME/ILT J1634+44 as a binary hosting a white dwarf \citep[possibly two,][]{2025arXiv250705139D,2025arXiv250705078B} raise the intriguing possibility that other LPTs may also be radio-emitting white dwarf pulsars at various stages of evolution (\citealt{2021NatAs...5..648S}, Horv\'{a}th et al.
 submitted).
@@
 
-Interestingly, systems with spin-orbital (or beat-orbital) resonances of, e.g., 2:1 or 3:1, would be indistinguishable from systems in 1:1 resonances if pulses can \revision{}{only} be observed within a limited orbital phase range.
-We therefore raise the possibility that the coincidence of the observed radio periodicities of ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 with their spectroscopically confirmed orbital periods does not necessarily imply that they are 1:1 \revision{polars}{systems}.
+Interestingly, systems with spin-orbital (or beat-orbital) resonances of, e.g., 2:1 or 3:1, would be indistinguishable from systems in 1:1 resonances if pulses can only be observed within a limited orbital phase range.
+We therefore raise the possibility that the coincidence of the observed radio periodicities of ILT\,J1101+5521 and GLEAM-X\,J0704$-$37 with their spectroscopically confirmed orbital periods does not necessarily imply that they are 1:1 systems.
 
@@
 Another possibility is that radio emission is only observed when the companion produces dense enough particle outflows, in the form of winds, to activate the emission mechanism in the vicinity of the WD.
-\revision{}{This may be the case, for example, for GLEAM-X\,J0704$-$37, whose spectroscopically detected H$\alpha$ emission is associated with the M-dwarf, and which may come from its stellar wind \citep{2025A&A...695L...8R}.}
+This may be the case, for example, for GLEAM-X\,J0704$-$37, whose spectroscopically detected H$\alpha$ emission is associated with the M-dwarf, and which may come from its stellar wind \citep{2025A&A...695L...8R}.
 Such outflows can last for months \citep{2021ApJ...915...37W}, and would not be periodic.
@@
 The same explanation may be applied to other LPTs with activity cycles that last on the order of months.
-An alternative explanation is that the radio emission is drived by particle wind outflows from \revision{the}{a} main sequence companion.
+An alternative explanation is that the radio emission is drived by particle wind outflows from a main sequence companion.
 Long-term monitoring of LPTs will reveal whether the intermittency is periodic, and thus help discriminate between these two scenarios.
@@
 The ATCA\footnote{\url{https://atoa.atnf.csiro.au/}} data is available on reasonable request to the authors, and will become publicly available from the relevant data portal by November, 2025.
-The post-imaged dynamic spectra, analyses, and timing analysis data products (ToAs, pulse properties) are publicly available on GitHub\footnote{TODO: Make this available upon publication.}.
+The post-imaged dynamic spectra, analyses, and timing analysis data products (ToAs, pulse properties) are publicly available on GitHub\footnote{\url{https://github.com/robotopia/j1755-2527}}.
 
@@
 
-\section{\revision{}{MeerKAT localization}}
+\section{MeerKAT localization}
 \label{app:localization}

### 2025-07-19 dm/scattering_calc.py
Removed obsolete DM folder and discussion

@@ -1,38 +1,0 @@
-import numpy as np
-import pygedm
-import matplotlib.pyplot as plt
-import astropy.units as u
-from astropy.coordinates import SkyCoord
-
-src = SkyCoord("17:55:34.9", "-25:27:49.1", unit=(u.hourangle, u.deg), frame='icrs')
-gl = src.galactic.l
-gb = src.galactic.b
-
-DMunit = u.pc / u.cm**3
-
-D = 4148.8 * u.s
-nu1 = 185 * u.MHz
-DM_at_887MHz = 600 * DMunit
-
-apparent_DM_at_185MHz = 1221 * DMunit
-apparent_slope_at_185MHz = -2*D*apparent_DM_at_185MHz/DMunit *(nu1/u.MHz)**(-3) / u.MHz
-
-DM_slope_at_887MHz = -2*D*DM_at_887MHz/DMunit * (887*u.MHz/u.MHz)**(-3) / u.MHz
-extrapolated_DM_slope = -2*D*DM_at_887MHz/DMunit * (nu1/u.MHz)**(-3) / u.MHz
-inferred_scattering_slope = apparent_slope_at_185MHz - extrapolated_DM_slope
-
-_, tau_sc_1GHz_ne2001 = pygedm.dm_to_dist(gl.deg, gb.deg, DM_at_887MHz, method='ne2001')
-_, tau_sc_1GHz_ymw16 = pygedm.dm_to_dist(gl.deg, gb.deg, DM_at_887MHz, method='ymw16')
-
-beta = -4.0
-scattering_slope_ne2001_at_887MHz = beta * tau_sc_1GHz_ne2001 * (887*u.MHz/u.GHz)**(beta - 1) / u.GHz
-scattering_slope_ne2001 = beta * tau_sc_1GHz_ne2001 * (nu1/u.GHz)**(beta - 1) / u.GHz
-scattering_slope_ymw16 = beta * tau_sc_1GHz_ymw16 * (nu1/u.GHz)**(beta - 1) / u.GHz
-
-print(f"{DM_slope_at_887MHz.to('s MHz-1') = }")
-print(f"{apparent_slope_at_185MHz.to('s MHz-1') = }")
-print(f"{extrapolated_DM_slope.to('s MHz-1') = }")
-print(f"{inferred_scattering_slope.to('s MHz-1') = }")
-print(f"{scattering_slope_ne2001_at_887MHz.to('s MHz-1') = }")
[…]

### 2025-07-22 paper/main.tex
Swapped out one of the figures from PNG to PDF
Added a citation

@@
 On the other hand, in the regime $\tau \gg \sigma$, the leading edge of the EMG rises sharply (resembling the error function, $\erf$) and the trailing edge resembles the exponential kernel itself.
-For this reason, pulse ToAs are typically mapped to the rising edge of highly scattered pulses, which closely approximates the centre of the original unscattered pulse.
+For this reason, pulse ToAs are typically mapped to the rising edge of highly scattered pulses, which closely approximates the centre of the original unscattered pulse \citep[][and references therein]{2025arXiv250614519J}.
 
@@
     \centering
-    \includegraphics[width=0.98\linewidth]{scattering_DM.png}
+    \includegraphics[width=0.98\linewidth]{scattering_DM.pdf}
     \caption{Analysis of DM measurement errors if scattering is not properly taken into account.
